### 2016-03-05 paper/introduction.tex
yasu

\section{Introduction}
Parallel computation has changed the field of Computing.  In the 90s,
most processors had single cores. In 2016, most processors have
multiple cores, often 4 or even 8. Cluster computing further expands
the potential of parallel computation, where one can easily launch a
processing job using hundreds or even thousands of computers in a
cloud. Computer Vision is not an exception in exploiting the powerful
parallel computation. However, in many Computer Vision problems,
state-of-the-art algorithms are still inherently sequential. Take a
Fusion-Move algorithm (FM)~\cite{viktor,second_order_stereo,else} for
example. FM was first introduced by Lempitsky et al. in solving an
optical flow problem. FM allows one to customize domain-specific
proposal generation schemes to boost convergence. FM has been a very
successful optimization framework in solving many challenging problems
in Computer Vision such as optical flow~\cite{viktor},
stereo~\cite{second_order_stereo}, or image segmentation~\cite{some}.
In general, Computer Vision researchers and engineers consider FM to
be a very slow algorithm due to its sequential nature, that is, often
required to fuse hundreds or sometimes thousands of proposals one by
one. This paper will propose a {\it Parallel Fusion Move} (PFM) method
that can instantly speed-up any optimization problem based on FM via
parallel fusion of proposals and solutions.

Our idea is extremely simple. Instead of keeping and refining one
solution via fusion, we keep and refine solutions in multiple threads
(or computational nodes) independently, while sharing their best
solutions for mutual benefits. Note that one can seek to parallelize
the core optimization libraries such as Graph-cuts~\cite{},
TRW~\cite{kolmogorov}, or QPBO~\cite{} to achieve similar
speed-up. However, these core optimization libraries are often very
complicated and used as a complete black box. Some libraries are
provided only in a binary form, especially commercial
packages. Furthermore, this library modification cannot benefit from
higher level parallelism through distributed computer nodes.
\yasu{Mention that existing fm only does binary solution fusion. We
  does multi-solution fusion. This overlaps withour cvpr16, but is
  probably ok by citing the paepr.} This paper will propose a novel
Parallel Fusion Move method, which fuses solution proposals in
parallel. Our framework can exploit parallelism from the levels of
threading to the levels of computer nodes. The idea is very simple and
can immediately benefit every Computer Vision researcher or engineer,
who currently uses fusion move algorithm to solve challenging
problems. \yasu{So far, we only say parallel. Hopefully, more
  interesting things will come up through experiments and we have more
  to say. For example, it would be cool if uniform model is better
  than pure master-slave. Then we can write that ours is not just
  parallel. But keeping multiple solutions somehow benefit (GA/GP
  algorithm's ideas).}

### 2016-03-05 stereo/code/scestereo/optimization.h
Hang

@@ -77,7 +77,9 @@ namespace sce_stereo {
         void genProposal(std::vector<Depth> &proposals) const;
 
         void fusionMove(Depth &p1, const Depth &p2) const;
-
+        inline double lapE(const double x0, const double x1, const double x2) const{
+            return std::min(std::abs(x0 + x2 - 2 * x1), trun);
+        }
         const Depth &noisyDisp;;
         const double trun;
 

### 2016-03-05 stereo/code/scestereo/optimization_fusionmove.cpp

@@ -51,8 +51,10 @@ namespace sce_stereo {
 
         std::default_random_engine generator;
         std::uniform_int_distribution<int> distribution(0, nLabel-1);
-        for(auto i=0; i<width*height; ++i)
-            result.setDepthAtInd(i, (double)distribution(generator));
+        for(auto i=0; i<width*height; ++i) {
+            //result.setDepthAtInd(i, (double) distribution(generator));
+            result.setDepthAtInd(i, noisyDisp[i]);
+        }
 
         list<double> diffE;
         double lastEnergy = evaluateEnergy(result);
@@ -64,12 +66,14 @@ namespace sce_stereo {
         while (true) {
             if(iter == max_iter)
                 break;
+            cout << "======================" << endl;
             cout << "Iteration " << iter << " using proposal " << iter % (proposals.size()) << endl;
             const Depth& proposal = proposals[iter % (proposals.size())];
             cout << "Fusing..." << endl;
+            cout << "Initial energy: " << evaluateEnergy(result) << endl;
             fusionMove(result, proposal);
             double e = evaluateEnergy(result);
-            cout << "Done, energy: " << e << endl;
+            cout << "Done, final energy: " << e << endl;
             double energyDiff = lastEnergy - e;
 
             if(diffE.size() >= average_over)
@@ -79,7 +83,7 @@ namespace sce_stereo {
             lastEnergy = e;
 
            sprintf(buffer, "%s/temp/fusionmove_iter%05d.jpg", file_io.getDirectory().c_str(), iter);
-           result.saveImage(buffer, 255.0 / (double)nLabel);
+           result.saveImage(buffer, 255.0 / (double)nLabel * 4);
 
             if(average_diffe < termination) {
                 cout << "Converge!" << endl;
@@ -90,15 +94,13 @@ namespace sce_stereo {
         }
         timming = ((float)getTickCount() - timming) / (float)getTickFrequency();
         printf("All done. Initial energy: %.3f, final energy: %.3f, time usage: %.2fs\n", initialEnergy, lastEnergy, timming);
-
-
     }
 
[…]

### 2016-03-05 stereo/code/scestereo/proposal.cpp

@@ -24,7 +24,7 @@ namespace sce_stereo{
         const int h = noisyDisp.getHeight();
         const int nPixels = w * h;
         const double epsilon = (double)1e-05;
-        const double dis_thres = 0.3;
+        const double dis_thres = 0.2;
 
         const double max_depth = 255.0;
 
@@ -52,11 +52,8 @@ namespace sce_stereo{
         }
 
         planarDisp = noisyDisp;
-	    Depth planarDepth;
-	    planarDepth.initialize(w, h, 0.0);
         for(auto i=0; i<planarDisp.getRawData().size(); ++i) {
 	        planarDisp.getRawData()[i] = noisyDisp.getRawData()[i];
-	        planarDepth.getRawData()[i] = dispToDepth(noisyDisp.getRawData()[i]);
             //printf("disp: %.5f, depth:%.5f\n", noisyDisp.getRawData()[i], planarDepth.getRawData()[i]);
         }
 
@@ -125,28 +122,15 @@ namespace sce_stereo{
                 int y = idx / w;
                 double newdepth = (-1 * offset - n[0]*x - n[1] * y) / n[2];
                 double d = std::max(std::min(newdepth, max_depth), 0.0);
-	            if(verbose) {
-		            double oridepth = dispToDepth(noisyDisp.getDepthAtInd(idx));
-		            printf("inter: (%d,%d,%.5f), ori disp: %.5f, new disp: %.5f\n", x, y, oridepth, oridepth, newdepth);
-	            }
                 planarDisp.setDepthAtInd(idx, std::max(std::min(depthToDisp(d), (double)dispResolution-1), 0.0));
-	            planarDepth.setDepthAtInd(idx, d);
             }
         }
 
-	    Depth tempd;
-	    tempd.initialize(w, h, 0.0);
-	    for(auto i=0; i<nPixels; ++i)
-		    tempd.getRawData()[i] = dispToDepth(noisyDisp.getRawData()[i]);
 	    char buffer[1024] = {};
 	    sprintf(buffer, "%s/temp/tdisp_%s_%03d_1.jpg", file_io.getDirectory().c_str(), method.c_str(), id);
-	    noisyDisp.saveImage(std::string(buffer), 255.0 / (double)dispResolution);
+	    noisyDisp.saveImage(std::string(buffer), 255.0 / (double)dispResolution * 4);
[…]

### 2016-03-05 stereo/code/scestereo/scestereo.cpp

@@ -4,7 +4,7 @@
 
 #include "scestereo.h"
 #include "local_matcher.h"
-#include "proposal.h"
+#include "optimization.h"
 
 using namespace std;
 using namespace cv;
@@ -106,8 +106,13 @@ namespace sce_stereo{
         initMRF();
 
         sprintf(buffer, "%s/temp/unaryDisp%05d.jpg", file_io.getDirectory().c_str(), anchor);
-        unaryDisp.saveImage(string(buffer), 255.0 / (dispResolution) * 4);
+        unaryDisp.saveImage(string(buffer), 256.0 / (dispResolution) * 4);
 
-        //ProposalSegPlnMeanshift proposalSegPlnMeanshift(file_io, images, unaryDisp, 0, );
+        SecondOrderOptimizeFusionMove fusionmove(file_io, (int)images.size(), images[anchor-offset], MRF_data, (float)MRFRatio, dispResolution, unaryDisp);
+        Depth result_fusionmove;
+        fusionmove.optimize(result_fusionmove, 20);
+
+        sprintf(buffer, "%s/temp/result_fusionmove%05d.jpg", file_io.getDirectory().c_str(), anchor);
+        result_fusionmove.saveImage(string(buffer), 256.0 / (dispResolution) * 4);
     }
 }//namespace sce_stereo

### 2016-03-05 paper/introduction.tex
yasu

@@
 Parallel computation has changed the field of Computing.  In the 90s,
-most processors had single cores. In 2016, most processors have
-multiple cores, often 4 or even 8. Cluster computing further expands
-the potential of parallel computation, where one can easily launch a
+most processors had single cores. In 2016, most processors have multiple
+cores, often 4 or even 8. Cluster computing further expands the
+potential of parallel computation, where one can easily launch a
 processing job using hundreds or even thousands of computers in a
@@
 optical flow problem. FM allows one to customize domain-specific
-proposal generation schemes to boost convergence. FM has been a very
-successful optimization framework in solving many challenging problems
-in Computer Vision such as optical flow~\cite{viktor},
-stereo~\cite{second_order_stereo}, or image segmentation~\cite{some}.
-In general, Computer Vision researchers and engineers consider FM to
-be a very slow algorithm due to its sequential nature, that is, often
-required to fuse hundreds or sometimes thousands of proposals one by
-one. This paper will propose a {\it Parallel Fusion Move} (PFM) method
-that can instantly speed-up any optimization problem based on FM via
-parallel fusion of proposals and solutions.
+proposal generation schemes to achieve efficient convergence. FM has
+been a very successful optimization framework in solving many
+challenging problems in Computer Vision such as optical
+flow~\cite{viktor}, stereo~\cite{second_order_stereo}, or image
+segmentation~\cite{some}. The main limitation of FM is its running time,
+where Computer Vision researchers and engineers generally consider FM to
+be a slow algorithm, as hundreds or sometimes thousands of proposals
+need to be fused sequentially. This paper will propose a {\it Parallel
+Fusion Move} (PFM) method that introduces the concept of parallel fusion
+into the computational framework.
 
-Our idea is extremely simple. Instead of keeping and refining one
-solution via fusion, we keep and refine solutions in multiple threads
-(or computational nodes) independently, while sharing their best
-solutions for mutual benefits. Note that one can seek to parallelize
-the core optimization libraries such as Graph-cuts~\cite{},
-TRW~\cite{kolmogorov}, or QPBO~\cite{} to achieve similar
-speed-up. However, these core optimization libraries are often very
-complicated and used as a complete black box. Some libraries are
-provided only in a binary form, especially commercial
+FM suffers from a few fundamental limitations due to its sequential
+nature. First, standard FM offers only two options in each fusion,
+either the current solution or a single proposal. Recently, an extension
+of FM was proposed for layered depthmap estimation~\cite{chen_2016},
+where a solution subspace, instead of a single solution, is proposed
+from each proposal generation scheme. However, a solution is
+sequentially updated by a single generation scheme one by one. In our
+framework, multiple threads (or computing nodes) simultaneously keep and
+improve solutions. Furthermore, in each fusion step in each thread, our
+approach can take any number of proposals from any number of proposal
+generation schemes, and even concurrent solutions in the other threads
+to fuse them into a new solution.
+%
+Note that one can seek to parallelize the core optimization libraries
+such as Graph-cuts~\cite{}, TRW~\cite{kolmogorov}, or QPBO~\cite{} to
+achieve similar speed-up. However, these core optimization libraries are
+often very complicated and used as a complete black box. Some libraries
+are provided only in a binary form, especially commercial
 packages. Furthermore, this library modification cannot benefit from
 higher level parallelism through distributed computer nodes.
-\yasu{Mention that existing fm only does binary solution fusion. We
-  does multi-solution fusion. This overlaps withour cvpr16, but is
-  probably ok by citing the paepr.} This paper will propose a novel
-Parallel Fusion Move method, which fuses solution proposals in
-parallel. Our framework can exploit parallelism from the levels of
-threading to the levels of computer nodes. The idea is very simple and
-can immediately benefit every Computer Vision researcher or engineer,
-who currently uses fusion move algorithm to solve challenging
-problems. \yasu{So far, we only say parallel. Hopefully, more
-  interesting things will come up through experiments and we have more
-  to say. For example, it would be cool if uniform model is better
-  than pure master-slave. Then we can write that ours is not just
-  parallel. But keeping multiple solutions somehow benefit (GA/GP
-  algorithm's ideas).}
+\yasu{Mention that existing fm only does binary solution fusion. We does
+multi-solution fusion. This overlaps withour cvpr16, but is probably ok
+by citing the paepr.}
+%
+The idea in this paper is extremely simple and easily reproducible. This
+paper can instantly benefit every Computer Vision researcher or
+engineer, who currently uses fusion move algorithm to solve challenging
+problems. We will share our implementation of the algorithm. The rest of
+the paper is organized as follows. Section~\ref{section:related_work}....
+%This paper will propose a novel Parallel Fusion
+%Move method, which fuses solution proposals in parallel. Our framework
+%can exploit parallelism from the levels of threading to the levels of
+%computer nodes.
+%
+ \yasu{Hopefully, more interesting things will come up through
+experiments and we have more to say. For example, it would be cool if
+uniform model is better than pure master-slave. Then we can write that
+ours is not just parallel. But keeping multiple solutions somehow
+benefit (GA/GP algorithm's ideas).}

### 2016-03-05 ToyExample/SegmentationFusionSolver.cpp
toy_example

@@ -1,0 +1,110 @@
+#include "SegmentationFusionSolver.h"
+
+#include <opencv2/highgui/highgui.hpp>
+
+#include <opengm/opengm.hxx>
+#include <opengm/graphicalmodel/graphicalmodel.hxx>
+#include <opengm/operations/minimizer.hxx>
+#include <opengm/operations/adder.hxx>
+#include <opengm/inference/trws/trws_trws.hxx>
+
+#include "../base/cv_utils/cv_utils.h"
+
+using namespace std;
+using namespace cv;
+using namespace cv_utils;
+
+
+vector<int> SegmentationFusionSolver::solve(const LabelSpace &label_space, double &energy) const
+{
+  const int NUM_PIXELS = IMAGE_WIDTH_ * IMAGE_HEIGHT_;
+  const double SMOOTHNESS_TERM_WEIGHT = 0.2;
+  
+  typedef opengm::GraphicalModel<float, opengm::Adder> Model;  
+  vector<size_t> pixel_num_labels(NUM_PIXELS);
+
+  vector<vector<int> > label_space_vec = label_space.getLabelSpace();
+  
+  for (int pixel = 0; pixel < NUM_PIXELS; pixel++)
+    pixel_num_labels[pixel] = label_space_vec[pixel].size();
+  Model gm(opengm::DiscreteSpace<>(pixel_num_labels.begin(), pixel_num_labels.end()));
+  
+  typedef opengm::ExplicitFunction<float> ExplicitFunction;
+  typedef Model::FunctionIdentifier FunctionIdentifier;
+
+  map<int, Vec3b> color_table;
+  color_table[0] = Vec3b(255, 255, 255);
+  color_table[1] = Vec3b(0, 0, 0);
+  color_table[2] = Vec3b(0, 0, 255);
+  color_table[3] = Vec3b(0, 255, 0);
+  color_table[4] = Vec3b(255, 0, 0);
+  
+  for (int pixel = 0; pixel < NUM_PIXELS; pixel++) {
+    Vec3b color = image_.at<Vec3b>(pixel / IMAGE_WIDTH_, pixel % IMAGE_WIDTH_);
+    const size_t shape[] = {label_space_vec[pixel].size()};
+    ExplicitFunction f(shape, shape + 1);
+    for (int proposal_index = 0; proposal_index < label_space_vec[pixel].size(); proposal_index++) {
+      int label = label_space_vec[pixel][proposal_index];
+      double color_diff = 0;
[…]

### 2016-03-05 ToyExample/SegmentationFusionSolver.h

@@ -1,0 +1,21 @@
+#ifndef SEGMENTATION_FUSION_SOLVER_H__
+#define SEGMENTATION_FUSION_SOLVER_H__
+
+#include <vector>
+#include <opencv2/core/core.hpp>
+
+#include "../base/FusionSolver.h"
+
+class SegmentationFusionSolver : FusionSolver
+{
+ public:
+ SegmentationFusionSolver(const cv::Mat &image) : image_(image.clone()), IMAGE_WIDTH_(image.cols), IMAGE_HEIGHT_(image.rows) {};
+  std::vector<int> solve(const LabelSpace &label_space, double &energy) const;
+  
+ private:
+  cv::Mat image_;
+  const int IMAGE_WIDTH_;
+  const int IMAGE_HEIGHT_;
+};
+  
+#endif

### 2016-03-05 ToyExample/SegmentationProposalGenerator.cpp

@@ -1,0 +1,26 @@
+#include "SegmentationProposalGenerator.h"
+
+#include <iostream>
+
+using namespace std;
+
+LabelSpace SegmentationProposalGenerator::getProposal() const
+{
+  // const int NUM_LABELS = 5;
+  // vector<int> node_labels(NUM_LABELS);
+  // for (int c = 0; c < NUM_LABELS; c++)
+  //   node_labels[c] = c;
+  
+  // return LabelSpace(vector<vector<int> >(IMAGE_WIDTH_ * IMAGE_HEIGHT_, node_labels));
+
+  static int index = 0;
+  LabelSpace proposal_label_space(vector<int>(IMAGE_WIDTH_ * IMAGE_HEIGHT_, index));
+  proposal_label_space += LabelSpace(current_solution_);
+  index = (index + 1) % 5;
+  return proposal_label_space;
+}
+
+vector<int> SegmentationProposalGenerator::getInitialSolution() const
+{
+  return vector<int>(IMAGE_WIDTH_ * IMAGE_HEIGHT_, 0);
+}

### 2016-03-05 ToyExample/main.cpp

@@ -1,0 +1,26 @@
+#include <opencv2/core/core.hpp>
+#include <opencv2/highgui/highgui.hpp>
+#include <iostream>
+#include <map>
+
+#include "SegmentationProposalGenerator.h"
+#include "SegmentationFusionSolver.h"
+
+using namespace std;
+using namespace cv;
+
+int main()
+{
+  Mat image = imread("Inputs/toy_example.png");
+  SegmentationProposalGenerator proposal_generator(image);
+  SegmentationFusionSolver fusion_solver(image);
+
+  vector<int> current_solution = vector<int>(image.cols * image.rows, 0);
+  for (int iteration = 0; iteration < 5; iteration++) {
+    proposal_generator.setCurrentSolution(current_solution);
+    LabelSpace label_space = proposal_generator.getProposal();
+    double dummy;
+    current_solution = fusion_solver.solve(label_space, dummy);
+  }
+  return 0;
+}

### 2016-03-05 paper/abstract.tex

\begin{abstract}
\yasu{must be at least 70 and at most 150 words.}
\keywords{A; B; C.}
\end{abstract}

### 2016-03-06 stereo/code/scestereo/local_matcher.cpp
Hang

@@ -69,8 +69,8 @@ namespace sce_stereo {
             if (mCost.size() == 2)
                 return std::min(phid(mCost[0]), phid(mCost[1]));
             //sum of best half
-            sort(mCost.begin(), mCost.end());
-            const size_t kth = mCost.size() / 2;
+            //sort(mCost.begin(), mCost.end());
+            const size_t kth = mCost.size();
             double res = 0.0;
 
             for (auto i = 0; i < kth; ++i) {

### 2016-03-06 stereo/code/scestereo/optimization_firstorder.cpp

@@ -19,33 +19,33 @@ namespace sce_stereo{
     }
 
     void FirstOrderOptimize::optimize(Depth &result, const int max_iter) const {
-//        EnergyFunction *energy_function = new EnergyFunction(new DataCost(const_cast<EnergyType *>(MRF_data.data())),
-//                                                             new SmoothnessCost(1, 4, weight_smooth,
-//                                                                                const_cast<EnergyType *>(hCue.data()),
-//                                                                                const_cast<EnergyType *>(vCue.data())));
-//        shared_ptr<MRF> mrf(new Expansion(width, height, nLabel, energy_function));
-//        mrf->initialize();
-//
-//        //randomly initialize
-//        std::default_random_engine generator;
-//        std::uniform_int_distribution<int> distribution(0, nLabel - 1);
-//        for (auto i = 0; i < width * height; ++i)
-//            mrf->setLabel(i, distribution(generator));
-//
-//        float initDataEnergy = (float) mrf->dataEnergy() / MRFRatio;
-//        float initSmoothEnergy = (float) mrf->smoothnessEnergy() / MRFRatio;
-//        float t;
-//        mrf->optimize(max_iter, t);
-//        float finalDataEnergy = (float) mrf->dataEnergy() / MRFRatio;
-//        float finalSmoothEnergy = (float) mrf->smoothnessEnergy() / MRFRatio;
-//
-//        printf("Graph cut finished.\nInitial energy: (%.3f, %.3f, %.3f)\nFinal energy: (%.3f,%.3f,%.3f)\nTime usage: %.2fs\n",
-//               initDataEnergy, initSmoothEnergy, initDataEnergy + initSmoothEnergy,
-//               finalDataEnergy, finalSmoothEnergy, finalDataEnergy + finalSmoothEnergy, t);
-//
-//        result.initialize(width, height, -1);
-//        for(auto i=0; i<width * height; ++i)
-//            result.setDepthAtInd(i, mrf->getLabel(i));
+        EnergyFunction *energy_function = new EnergyFunction(new DataCost(const_cast<EnergyType *>(MRF_data.data())),
+                                                             new SmoothnessCost(1, 4, weight_smooth,
+                                                                                const_cast<EnergyType *>(hCue.data()),
+                                                                                const_cast<EnergyType *>(vCue.data())));
[…]

### 2016-03-06 stereo/code/scestereo/optimization_fusionmove.cpp

@@ -34,8 +34,8 @@ namespace sce_stereo {
         for (auto i = 0; i < image.cols * image.rows; ++i)
             refSeg[i] = labels[i];
 
-        laml = 9.0 * (double)kFrames / 255.0;
-        lamh = 108.0 * (double)kFrames / 255.5;
+        laml = 9.0 * (double)kFrames / 256;
+        lamh = 108.0 * (double)kFrames / 256;
     }
 
 
@@ -52,8 +52,8 @@ namespace sce_stereo {
         std::default_random_engine generator;
         std::uniform_int_distribution<int> distribution(0, nLabel-1);
         for(auto i=0; i<width*height; ++i) {
-            //result.setDepthAtInd(i, (double) distribution(generator));
-            result.setDepthAtInd(i, noisyDisp[i]);
+            result.setDepthAtInd(i, (double) distribution(generator));
+            //result.setDepthAtInd(i, noisyDisp[i]);
         }
 
         list<double> diffE;
@@ -63,27 +63,60 @@ namespace sce_stereo {
 
         const double termination = 0.1;
         float timming = (float)getTickCount();
+        const int smoothInterval = 5;
         while (true) {
             if(iter == max_iter)
                 break;
             cout << "======================" << endl;
-            cout << "Iteration " << iter << " using proposal " << iter % (proposals.size()) << endl;
-            const Depth& proposal = proposals[iter % (proposals.size())];
-            cout << "Fusing..." << endl;
+            Depth newProposal;
+
+            if(iter > 0 && iter % smoothInterval == 0) {
+                Depth orip1;
+                newProposal.initialize(width, height, -1);
+                orip1.initialize(width, height, -1);
+                for (auto i = 0; i < width * height; ++i) {
+                    orip1.setDepthAtInd(i, result[i]);
+                    newProposal.setDepthAtInd(i, result[i]);
+                }
+                int direction = iter / smoothInterval;
+                if (direction % 2 == 0) {
+                    //horizontally
+                    for (auto y = 0; y < height; ++y) {
+                        for (auto x = 0; x < width - 1; ++x)
+                            newProposal.setDepthAtInt(x, y, (orip1(x + 1, y) + orip1(x, y)) / 2);
[…]

### 2016-03-06 stereo/code/scestereo/proposal.cpp

@@ -24,7 +24,7 @@ namespace sce_stereo{
         const int h = noisyDisp.getHeight();
         const int nPixels = w * h;
         const double epsilon = (double)1e-05;
-        const double dis_thres = 0.2;
+        const double dis_thres = 0.5;
 
         const double max_depth = 255.0;
 

### 2016-03-06 stereo/code/scestereo/scestereo.cpp

@@ -108,9 +108,15 @@ namespace sce_stereo{
         sprintf(buffer, "%s/temp/unaryDisp%05d.jpg", file_io.getDirectory().c_str(), anchor);
         unaryDisp.saveImage(string(buffer), 256.0 / (dispResolution) * 4);
 
+        FirstOrderOptimize firstOrderOptimize(file_io, (int)images.size(), images[anchor-offset], MRF_data, (float)MRFRatio, dispResolution, (EnergyType)(0.01 * MRFRatio));
+        Depth result_firstorder;
+        firstOrderOptimize.optimize(result_firstorder, 10);
+        sprintf(buffer, "%s/temp/result_firstorder%05d.jpg", file_io.getDirectory().c_str(), anchor);
+        result_firstorder.saveImage(string(buffer), 256.0 / (dispResolution) * 4);
+
         SecondOrderOptimizeFusionMove fusionmove(file_io, (int)images.size(), images[anchor-offset], MRF_data, (float)MRFRatio, dispResolution, unaryDisp);
         Depth result_fusionmove;
-        fusionmove.optimize(result_fusionmove, 20);
+        fusionmove.optimize(result_fusionmove, 500);
 
         sprintf(buffer, "%s/temp/result_fusionmove%05d.jpg", file_io.getDirectory().c_str(), anchor);
         result_fusionmove.saveImage(string(buffer), 256.0 / (dispResolution) * 4);

### 2016-03-06 stereo/code/scestereo/scestereo.h

@@ -25,7 +25,6 @@ namespace sce_stereo {
     private:
         typedef int EnergyType;
         void initMRF();
-
         void computeMatchingCost();
 
         const FileIO& file_io;

### 2016-03-06 stereo/code/stereo_base/depth.h

@@ -44,7 +44,7 @@ namespace sce_stereo{
             CHECK_LT(x, getWidth());
             CHECK_LT(y, getHeight());
             int idx = y * getWidth() + x;
-            return this->operator[](idx);
+            return data[idx];
         }
 
         inline void setDepthAtInd(const int ind, const double v){

### 2016-03-06 paper/introduction.tex
yasu

@@
 been a very successful optimization framework in solving many
-challenging problems in Computer Vision such as optical
-flow~\cite{viktor}, stereo~\cite{second_order_stereo}, or image
-segmentation~\cite{some}. The main limitation of FM is its running time,
-where Computer Vision researchers and engineers generally consider FM to
-be a slow algorithm, as hundreds or sometimes thousands of proposals
-need to be fused sequentially. This paper will propose a {\it Parallel
-Fusion Move} (PFM) method that introduces the concept of parallel fusion
-into the computational framework.
+challenging problems in Computer Vision such as optical flow, stereo,
+image denoising, image inpainting, or image
+segmentation~\cite{fusion_moves_for_markov_random_field_optimization}. The
+main limitation of FM is its running time, where Computer Vision
+researchers and engineers generally consider FM to be a slow algorithm
+that can solve challenging problems by fusing hundreds or sometimes
+thousands of proposals sequentially.
+%
+The running time becomes particularly an issue for large
+
+image denoising for high resolution images (24mb), high resolution
+map-tile image stitching (satellite), voxel CRF~\cite{pollefeys}
+
+\yasu{Are there any concrete examples where MRF is used to solve a very
+large problem where parallel fusion is really helpful. Like denoising
+high resolution 24M pixel images. Stitching a high resolution map tiles
+(satellite image tiles) via image stitching.}
+
+%
+This paper will propose a {\it Parallel Fusion Move} (PFM) method that
+introduces the concept of parallel fusion into the computational
+framework.
 

### 2016-03-06 paper/introduction.tex
yasu

@@
 cloud. Computer Vision is not an exception in exploiting the powerful
-parallel computation. However, in many Computer Vision problems,
+parallel computation.
+
+As image sensor technologies improve, Computer Vision need to deal with
+large-scale inference problems more than ever.
+
+However, in many Computer Vision problems,
 state-of-the-art algorithms are still inherently sequential. Take a
@@
 optical flow problem. FM allows one to customize domain-specific
-proposal generation schemes to achieve efficient convergence. FM has
-been a very successful optimization framework in solving many
-challenging problems in Computer Vision such as optical flow, stereo,
-image denoising, image inpainting, or image
+proposal generation schemes, a main advantage over general solvers such
+as message passing algorithms. FM has been a very successful
+optimization framework in solving many challenging problems in Computer
+Vision such as optical flow, stereo, image denoising, image inpainting,
+or image
 segmentation~\cite{fusion_moves_for_markov_random_field_optimization}. The
@@
 researchers and engineers generally consider FM to be a slow algorithm
-that can solve challenging problems by fusing hundreds or sometimes
-thousands of proposals sequentially.
+that can solve challenging problems, as hundreds or sometimes thousands
+of proposals need to be fused sequentially.
 %
-The running time becomes particularly an issue for large
+The running time becomes particularly an issue for large data, for
+instnance, image denoising of professional-grade high resolution (50
+Mpixels) images, image stitching for the
 
-image denoising for high resolution images (24mb), high resolution
-map-tile image stitching (satellite), voxel CRF~\cite{pollefeys}
+generating a high resolution map-tiles (e.g., satellite) by stitching
+hundreds of photographs
 
+generation of high resolution
+map-tiles (e.g., satellite), or volumetric joint reconstruction and
+segmentation potentiallly a trillion ($=1024^3$) voxels~\cite{Joint 3D
+Scene Reconstruction and Class Segmentation}.
 \yasu{Are there any concrete examples where MRF is used to solve a very

### 2016-03-06 paper/introduction.tex
yasu

@@
 cloud. Computer Vision is not an exception in exploiting the powerful
-parallel computation.
+parallel computation, where we are in greater demand to solve very large
+problems.
 
-As image sensor technologies improve, Computer Vision need to deal with
-large-scale inference problems more than ever.
+parallel computation has been and will be an important
+
+\yasu{mention GPU?}
 

### 2016-03-06 paper/introduction.tex
yasu

--- 2016-03-06 paper/introduction.tex
@@
 processing job using hundreds or even thousands of computers in a
-cloud. Computer Vision is not an exception in exploiting the powerful
-parallel computation. However, in many Computer Vision problems,
-state-of-the-art algorithms are still inherently sequential. Take a
-Fusion-Move algorithm (FM)~\cite{viktor,second_order_stereo,else} for
-example. FM was first introduced by Lempitsky et al. in solving an
-optical flow problem. FM allows one to customize domain-specific
-proposal generation schemes to achieve efficient convergence. FM has
-been a very successful optimization framework in solving many
-challenging problems in Computer Vision such as optical flow, stereo,
-image denoising, image inpainting, or image
-segmentation~\cite{fusion_moves_for_markov_random_field_optimization}. The
-main limitation of FM is its running time, where Computer Vision
-researchers and engineers generally consider FM to be a slow algorithm
-that can solve challenging problems by fusing hundreds or sometimes
-thousands of proposals sequentially.
+cloud.
 %
-The running time becomes particularly an issue for large
+Parallel computation offers huge potential for Computer Vision, as
+image sensing technologies have gone through revolutions and we are in
+ever growing demands in solving very large problems. One may need to
+apply image denoising to 50 Megapixel images from latest digital
+SLRs~\cite{canon?}, stitch thousands of images to generate gigapixel
+panoramas~\cite{gigapan}, or solve volumetric reconstruction and
+segmentation problems over a billion ($=1024^3$)
+voxels~\cite{Joint_3D_Scene_Reconstruction_and_class_Segmentation}.
 
-image denoising for high resolution images (24mb), high resolution
-map-tile image stitching (satellite), voxel CRF~\cite{pollefeys}
+Unfortunately, in many Computer Vision problems, state-of-the-art
+algorithms are still inherently sequential. Take a Fusion-Move algorithm
+(FM)~\cite{viktor,second_order_stereo,else} for Markov Random Field
+inference, for example, which has been one of the most effective
+techniques in solving the above three
+problems~\cite{fusion_moves_for_markov_random_field_optimization}.
+%
+FM was first introduced by Lempitsky et al. in solving an optical flow
+problem, where solution proposals are fused sequentially one by one to
+improve the solution. FM allows domain-specific customization of
+proposal generation schemes, a main advantage over general solvers such
+as message passing algorithms~\cite{TRW,loopy_belief_propagation}. FM
+has been successful applied to many challenging problems in optical
+flow, stereo, image denoising, image inpainting, or image
+segmentation~\cite{fusion_moves_for_markov_random_field_optimization}.
 
-\yasu{Are there any concrete examples where MRF is used to solve a very
-large problem where parallel fusion is really helpful. Like denoising
-high resolution 24M pixel images. Stitching a high resolution map tiles
-(satellite image tiles) via image stitching.}
+Breaking the sequential nature of FM would then bring fundamental
+contributions to many major fields in Computer Vision. FM suffers from a
+few vital limitations due to its sequential processing. First, standard
+FM allows only two options per variable in each fusion, either the
+current solution or a
+proposal~\cite{fusion_moves_for_markov_random_field_optimization}.
+Recently, an extension of FM was proposed for layered depthmap
+estimation~\cite{chen_2016}, where a solution subspace, instead of a
+single solution, is proposed and fused with the current
+solution. However, existing approaches use only one proposal generation
+scheme in each fusion.
 
+Our approach, dubbed {\it Parallel Fusion Move Method} (PFM), makes a
+few key distinctions from existing approaches: 1) Multiple threads (or
+computing nodes) simultaneously keep and improve solutions; and 2) Each
+fusion in each thread can take arbitrary number of proposals from
+arbitrary combination of proposal generation schemes, even concurrent
+solutions in the other threads, to be fused with the current solution.
 %
-This paper will propose a {\it Parallel Fusion Move} (PFM) method that
-introduces the concept of parallel fusion into the computational
-framework.
-
-FM suffers from a few fundamental limitations due to its sequential
-nature. First, standard FM offers only two options in each fusion,
-either the current solution or a single proposal. Recently, an extension
-of FM was proposed for layered depthmap estimation~\cite{chen_2016},
-where a solution subspace, instead of a single solution, is proposed
-from each proposal generation scheme. However, a solution is
-sequentially updated by a single generation scheme one by one. In our
-framework, multiple threads (or computing nodes) simultaneously keep and
-improve solutions. Furthermore, in each fusion step in each thread, our
-approach can take any number of proposals from any number of proposal
-generation schemes, and even concurrent solutions in the other threads
-to fuse them into a new solution.
+Note that one may rather seek to parallelize the core optimization
+libraries such as Graph-cuts~\cite{}, TRW~\cite{kolmogorov}, or
+QPBO~\cite{}.~\footnote{GPU speeds-up message-passing algorithms via
+parallel computation. However, these algorithms need to store all the
+messages and states and cannot handle problems with a large label space~\cite{layered_depthmap}.} However, the core optimization libraries are often
+very complex and require significant engineering by experts for
+modification.
 %
-Note that one can seek to parallelize the core optimization libraries
-such as Graph-cuts~\cite{}, TRW~\cite{kolmogorov}, or QPBO~\cite{} to
-achieve similar speed-up. However, these core optimization libraries are
-often very complicated and used as a complete black box. Some libraries
-are provided only in a binary form, especially commercial
-packages. Furthermore, this library modification cannot benefit from
-higher level parallelism through distributed computer nodes.
-\yasu{Mention that existing fm only does binary solution fusion. We does
-multi-solution fusion. This overlaps withour cvpr16, but is probably ok
-by citing the paepr.}
+While state-of-the-art optimization libraries are often freely available for
+non-commercial purposes, most companies have to develop and maintain
+in-house implementation of these optimization algorithms.
 %
-The idea in this paper is extremely simple and easily reproducible. This
-paper can instantly benefit every Computer Vision researcher or
-engineer, who currently uses fusion move algorithm to solve challenging
-problems. We will share our implementation of the algorithm. The rest of
-the paper is organized as follows. Section~\ref{section:related_work}....
+% \yasu{Mention that existing fm only does binary solution fusion. We does
+% multi-solution fusion. This overlaps withour cvpr16, but is probably ok
+% by citing the paepr.}
+%
+Our approach is extremely simple in concept, and will instantly benefit
+every Computer Vision researcher or engineer, who currently uses fusion
+move algorithm to solve challenging problems. We will share our
+implementation of the algorithm. The rest of the paper is organized as
+follows. Section~\ref{section:related_work}....
 %This paper will propose a novel Parallel Fusion
@@
 %computer nodes.
+
+%The main limitation of FM is its running time, where Computer Vision
+%researchers and engineers generally consider FM to be a slow algorithm
+%that can solve challenging problems, as hundreds or sometimes thousands
+%of proposals need to be fused sequentially.
+%
+
+%\yasu{Are there any concrete examples where MRF is used to solve a very
+%large problem where parallel fusion is really helpful. Like denoising
+%high resolution 24M pixel images. Stitching a high resolution map tiles
+%(satellite image tiles) via image stitching.}
+
+%
+%This paper will propose a {\it Parallel Fusion Move} (PFM) method that
+%introduces the concept of parallel fusion into the computational
+%framework.
+
 %
@@
 benefit (GA/GP algorithm's ideas).}
+
+%\yasu{mention GPU somewhere? strange to talk about parallel without
+%mentioning GPU and its relation to our approach}

### 2016-03-07 ToyExample/main.cpp
Hang

@@ -15,75 +15,75 @@ using namespace cv;
 
 int main()
 {
-  Mat image = imread("Inputs/toy_example.png");
-   
-  //parallel fusion move
-  //typedef LabelType int;
-  
-  if (true) {
-    PipelineParams pipeline_params(4, 5);
-    vector<double> fusion_thread_master_likelihood_vec(pipeline_params.NUM_THREADS, 0);
-    fusion_thread_master_likelihood_vec[pipeline_params.NUM_THREADS - 1] = 1;
-    vector<unique_ptr<FusionThread<int> > > fusion_threads;
-    vector<shared_ptr<ProposalGenerator<int> > > proposal_generators;
-    for (int fusion_thread_index = 0; fusion_thread_index < pipeline_params.NUM_THREADS; fusion_thread_index++)
-      proposal_generators.push_back(dynamic_pointer_cast<ProposalGenerator<int> >(shared_ptr<SegmentationProposalGenerator>(new SegmentationProposalGenerator(image))));
-    vector<shared_ptr<FusionSolver<int> > > fusion_solvers;
-    for (int fusion_thread_index = 0; fusion_thread_index < pipeline_params.NUM_THREADS; fusion_thread_index++)
-      fusion_solvers.push_back(dynamic_pointer_cast<FusionSolver<int> >(shared_ptr<SegmentationFusionSolver>(new SegmentationFusionSolver(image))));
-    for (int fusion_thread_index = 0; fusion_thread_index < pipeline_params.NUM_THREADS; fusion_thread_index++)			  
-      fusion_threads.push_back(move(unique_ptr<FusionThread<int> >(new FusionThread<int>(proposal_generators[fusion_thread_index], fusion_solvers[fusion_thread_index], fusion_thread_master_likelihood_vec[fusion_thread_index]))));
-    
-    vector<int> fused_solution = parallelFuse(fusion_threads, pipeline_params, vector<int>(image.cols * image.rows, 0));
+    Mat image = imread("Inputs/toy_example.png");
 
-    {
-      map<int, Vec3b> color_table;
-      color_table[0] = Vec3b(255, 255, 255);
-      color_table[1] = Vec3b(0, 0, 0);
-      color_table[2] = Vec3b(0, 0, 255);
-      color_table[3] = Vec3b(0, 255, 0);
-      color_table[4] = Vec3b(255, 0, 0);
+    //parallel fusion move
+    //typedef LabelType int;
 
[…]

### 2016-03-07 ToyExample/SegmentationProposalGenerator.h
minor changes

@@ -10,7 +10,7 @@ class SegmentationProposalGenerator : public ProposalGenerator<int>
 {
  public:
  SegmentationProposalGenerator(const cv::Mat &image) : image_(image.clone()), IMAGE_WIDTH_(image.cols), IMAGE_HEIGHT_(image.rows) {};
-  LabelSpace<int> getProposal() const;
+  LabelSpace<int> getProposal();
   std::vector<int> getInitialSolution() const;
   void writeSolution(const std::vector<int> &solution, const int iteration, const int thread_index) const;
   

### 2016-03-07 ToyExample/main.cpp

@@ -21,7 +21,7 @@ int main()
   //typedef LabelType int;
   
   if (true) {
-    PipelineParams pipeline_params(4, 5);
+    PipelineParams pipeline_params(4, 5, 2);
     vector<double> fusion_thread_master_likelihood_vec(pipeline_params.NUM_THREADS, 0);
     fusion_thread_master_likelihood_vec[pipeline_params.NUM_THREADS - 1] = 1;
     vector<unique_ptr<FusionThread<int> > > fusion_threads;

### 2016-03-07 base/LabelSpace.h

@@ -60,17 +60,22 @@ template<class LabelType> void LabelSpace<LabelType>::setSingleLabels(const std:
 
 template<class LabelType> LabelSpace<LabelType> &LabelSpace<LabelType>::operator += (const LabelSpace<LabelType> &rhs)
 {
-  std::vector<std::vector<LabelType> > rhs_label_space = rhs.getLabelSpace();
   //CHECK(label_space_.size() == rhs_label_space.size()) << "The number of nodes is inconsistent.";
-  for (int node_index = 0; node_index < num_nodes_; node_index++) {
-    std::vector<LabelType> node_labels = label_space_[node_index];
-    std::vector<LabelType> rhs_node_labels = rhs_label_space[node_index];
-    //sort(node_labels.begin(), node_labels.end());    Maybe we assume?
-    //sort(rhs_node_labels.begin(), rhs_node_labels.end());
-    std::vector<LabelType> union_node_labels(node_labels.size() + rhs_node_labels.size());
-    typename std::vector<LabelType>::const_iterator union_node_labels_it = set_union(node_labels.begin(), node_labels.end(), rhs_node_labels.begin(), rhs_node_labels.end(), union_node_labels.begin());
-    union_node_labels.resize(union_node_labels_it - union_node_labels.begin());
-    label_space_[node_index] = union_node_labels;
+  std::vector<std::vector<LabelType> > rhs_label_space = rhs.getLabelSpace();
+  if (num_nodes_ == 0) {
+    num_nodes_ = rhs_label_space.size();
+    label_space_ = rhs_label_space;
+  } else {
+    for (int node_index = 0; node_index < num_nodes_; node_index++) {
+      std::vector<LabelType> node_labels = label_space_[node_index];
+      std::vector<LabelType> rhs_node_labels = rhs_label_space[node_index];
+      //sort(node_labels.begin(), node_labels.end());    Maybe we assume?
+      //sort(rhs_node_labels.begin(), rhs_node_labels.end());
+      std::vector<LabelType> union_node_labels(node_labels.size() + rhs_node_labels.size());
+      typename std::vector<LabelType>::const_iterator union_node_labels_it = set_union(node_labels.begin(), node_labels.end(), rhs_node_labels.begin(), rhs_node_labels.end(), union_node_labels.begin());
+      union_node_labels.resize(union_node_labels_it - union_node_labels.begin());
+      label_space_[node_index] = union_node_labels;
+    }
   }
   return *this;
 }

### 2016-03-07 base/ProposalGenerator.h

@@ -9,9 +9,10 @@ template<class LabelType> class ProposalGenerator
 {
  public:
   virtual void setCurrentSolution(const std::vector<LabelType> &current_solution) { current_solution_ = current_solution; };
-  virtual LabelSpace<LabelType> getProposal() const = 0;
+  virtual LabelSpace<LabelType> getProposal() = 0;
   virtual std::vector<LabelType> getInitialSolution() const = 0;
   virtual void writeSolution(const std::vector<LabelType> &solution, const int thread_index, const int iteration) const {}; //write temporary solution for visualization purpose
+  virtual void setGroundTruthSolution(const std::vector<LabelType> &solution) {}; //set ground truth solution for debugging purpose
   
  protected:
   std::vector<LabelType> current_solution_;

### 2016-03-07 base/cv_utils/cv_utils.h

@@ -134,8 +134,16 @@ namespace cv_utils
   {
     std::random_device rd;
     std::mt19937 gen(rd());
-    std::uniform_real_distribution<> dis(0, 1);
-    return dis(gen);
+    std::uniform_real_distribution<> distribution(0, 1);
+    return distribution(gen);
+  }
+
+  inline double drawFromNormalDistribution(const double mean = 0, const double stddev = 1)
+  {
+    std::random_device rd;
+    std::mt19937 gen(rd());
+    std::normal_distribution<double> distribution(mean, stddev);
+    return distribution(gen);
   }
 
   inline int drawFromArray(const std::vector<double> &likelihood_values)

### 2016-03-07 paper/introduction.tex

@@
 \section{Introduction}
-Parallel computation has changed the field of Computing.  In the 90s,
+Parallel computation has changed the field of computing.  In the 90s,
 most processors had single cores. In 2016, most processors have multiple
@@
 potential of parallel computation, where one can easily launch a
-processing job using hundreds or even thousands of computers in a
-cloud.
+processing job using hundreds or even thousands of computational nodes
+in a cloud.
 %
@@
 
-Unfortunately, in many Computer Vision problems, state-of-the-art
-algorithms are still inherently sequential. Take a Fusion-Move algorithm
-(FM)~\cite{viktor,second_order_stereo,else} for Markov Random Field
-inference, for example, which has been one of the most effective
+Unfortunately, state-of-the-art algorithms are still inherently
+sequential in many Computer Vision problems. Take a Fusion-Move
+algorithm (FM)~\cite{viktor,second_order_stereo,else} for Markov Random
+Field inference, for example, which has been one of the most effective
 techniques in solving the above three
@@
 FM was first introduced by Lempitsky et al. in solving an optical flow
-problem, where solution proposals are fused sequentially one by one to
-improve the solution. FM allows domain-specific customization of
-proposal generation schemes, a main advantage over general solvers such
-as message passing algorithms~\cite{TRW,loopy_belief_propagation}. FM
-has been successful applied to many challenging problems in optical
-flow, stereo, image denoising, image inpainting, or image
+problem~\cite{first_fusion_viktor}, where proposals are fused
+sequentially one by one to improve the solution. FM allows
+domain-specific customization of proposal generation schemes, a main
+advantage over general solvers such as message passing
+algorithms~\cite{TRW,loopy_belief_propagation}.  Successful applications
+of FM range from optical flow, stereo, image denoising, image
+inpainting, to image
 segmentation~\cite{fusion_moves_for_markov_random_field_optimization}.
 
-Breaking the sequential nature of FM would then bring fundamental
-contributions to many major fields in Computer Vision. FM suffers from a
-few vital limitations due to its sequential processing. First, standard
-FM allows only two options per variable in each fusion, either the
-current solution or a
-proposal~\cite{fusion_moves_for_markov_random_field_optimization}.
-Recently, an extension of FM was proposed for layered depthmap
-estimation~\cite{chen_2016}, where a solution subspace, instead of a
-single solution, is proposed and fused with the current
-solution. However, existing approaches use only one proposal generation
-scheme in each fusion.
-
-Our approach, dubbed {\it Parallel Fusion Move Method} (PFM), makes a
+Unleashing the power of parallel computation in FM
+% Breaking the sequential nature of FM
+would then bring fundamental contributions to Computer
+Vision. Currently, FM suffers from a few vital limitations due to its
+sequential processing. First, standard FM allows only two options per
+variable in each fusion, either the current solution or a
+proposal~\cite{fusion_moves_for_markov_random_field_optimization}. Second,
+only a single proposal generation scheme is used in each fusion
+step.~\footnote{Recently, an extension of FM was proposed for layered
+depthmap estimation~\cite{chen_2016}, where a solution subspace, instead
+of a single solution, is proposed and fused with the current
+solution. However, this approach is also limited to the use of one proposal
+generation scheme in each fusion.}
+%
+Our approach, dubbed {\it Parallel Fusion Moves method} (PFM), makes a
 few key distinctions from existing approaches: 1) Multiple threads (or

### 2016-03-07 paper/related_work.tex
yasu

\section{Related work}

Hiroshi had a paper for doing this for binary variables but not for multilabel variables.

http://www.f.waseda.jp/hfs/CVPR2014.pdf

 This is a good idea.  Rather than having one perfect solution threads, we maintain multiple solution hypothesis which are then combined with each other.  At a high level, this strategy is similar to methods like genetic algorithms (GA) or particle swarm optimization (PSO) where multiple solutions are maintained and improved over time.

However, unlike GA or PSO where the fusion step is essentially just arbitrarily copying part of the solution, we try to find the optimal copy.

While PSO and GA have limited theoretical justification, they have been used to produce great empirical results. For instance, in our recent work on hand tracking, we used the particle swarm optimization method. See “Model Fitting” section on page 5 of the following paper:

http://research.microsoft.com/en-us/um/people/pkohli/papers/skrts_chi2015.pdf

Also see the video here: https://www.youtube.com/watch?v=R-SfOJyZlRQ&list=PLE7aZMY3Wubx6yRgP8U6GRwJCOi2Zyh2S&index=9

### 2016-03-07 paper/stereo.tex
yasu

\section{Implementation details}
\subsection{Stereoo}

### 2016-03-08 base/ParallelFusionPipeline.h
hang

@@ -62,9 +62,10 @@ namespace ParallelFusion {
         ProposalAddition addMethod;
     };
 
-    template<typename T, class SOLVER>
+    template<typename T>
     class ParallelFusionPipeline {
-        ParallelFusionPipeline(const ParallelFusionOption &option_) : option(option_), terminate(false) { }
+        //solver should be read only
+        ParallelFusionPipeline(const std::shared_ptr<const FusionSolver<T> >& solver_, const ParallelFusionOption &option_) : solver(solver_), option(option_), terminate(false) { }
 
         typedef std::shared_ptr<ProposalGenerator<T> > GeneratorPtr;
         typedef std::vector<GeneratorPtr> GeneratorSet;
@@ -102,6 +103,7 @@ namespace ParallelFusion {
 
         //The following two parameters controls the parallel fusion.
         //each fusion
+        const std::shared_ptr<const FusionSolver<T> > solver;
         ParallelFusionOption option;
 
         int kSelfThread;
@@ -114,8 +116,8 @@ namespace ParallelFusion {
 
     ///////////////////////////////////////////////////////////////////////
 
-    template<typename T, class SOLVER>
-    double ParallelFusionPipeline<T, SOLVER>::runParallelFusion(const std::vector<std::vector<T> > &initials,
+    template<typename T>
+    double ParallelFusionPipeline<T>::runParallelFusion(const std::vector<std::vector<T> > &initials,
                                                                 const GeneratorSet& generators){
         CHECK_EQ(option.num_threads, initials.size());
         CHECK_EQ(option.num_threads, generators.size());
@@ -135,25 +137,23 @@ namespace ParallelFusion {
         }
     }
 
-    template<typename T, class SOLVER>
-    void ParallelFusionPipeline<T, SOLVER>::getLabeling(std::vector<T> &solution) {
+    template<typename T>
+    void ParallelFusionPipeline<T>::getLabeling(std::vector<T> &solution) {
 
     }
 
-    template<typename T, class SOLVER>
-    void ParallelFusionPipeline<T, SOLVER>::workerThread(const int id,
+    template<typename T>
+    void ParallelFusionPipeline<T>::workerThread(const int id,
                                                          const std::vector<T> &initial,
                                                          const GeneratorPtr& generator){
         try {
-            SOLVER solver;
-
             std::default_random_engine seed;
             std::uniform_int_distribution<int> distribution(0, option.num_threads);
 
             bool converge = false;
 
             SolutionType<T> current_solution;
[…]

### 2016-03-08 stereo/code/scestereo/local_matcher.h

@@ -1,25 +1,0 @@
-//
-// Created by yanhang on 3/4/16.
-//
-
-#ifndef PARALLELFUSION_LOCAL_MATCHER_H
-#define PARALLELFUSION_LOCAL_MATCHER_H
-
-#include <opencv2/opencv.hpp>
-#include <vector>
-#include <algorithm>
-#include <Eigen/Eigen>
-#include "../stereo_base/utility.h"
-#include "../stereo_base/depth.h"
-#include "../stereo_base/file_io.h"
-
-namespace sce_stereo {
-    namespace local_matcher {
-        void samplePatch(const cv::Mat &img, const Eigen::Vector2d &loc, const int pR, std::vector<double> &pix);
-
-        void getSSDArray(const std::vector<std::vector<double> > &patches, const int refId,
-                         std::vector<double> &mCost);
-        double sumMatchingCostHalf(const std::vector<std::vector<double> > &patches, const int refId);
-    }
-}
-#endif //PARALLELFUSION_LOCAL_MATCHER_H

### 2016-03-08 stereo/code/scestereo/optimization.h

@@ -21,19 +21,19 @@ namespace sce_stereo {
     public:
         typedef int EnergyType;
 
-        StereoOptimization(const FileIO &file_io_, const int kFrames_, const cv::Mat &image_,
+        StereoOptimization(const stereo_base::FileIO &file_io_, const int kFrames_, const cv::Mat &image_,
                            const std::vector<EnergyType> &MRF_data_, const float MRFRatio_, const int nLabel_, const int refId_) :
                 file_io(file_io_), kFrames(kFrames_), image(image_), MRF_data(MRF_data_), MRFRatio(MRFRatio_),
                 nLabel(nLabel_), refId(refId_), width(image_.cols), height(image_.rows) { }
 
-        virtual void optimize(Depth &result, const int max_iter) const = 0;
+        virtual void optimize(stereo_base::Depth &result, const int max_iter) const = 0;
 
-        virtual double evaluateEnergy(const Depth &) const = 0;
+        virtual double evaluateEnergy(const stereo_base::Depth &) const = 0;
 
         //vis = 255 means visible; vis = 0 means occluded
-        void computeVisibility(const Depth& d, Depth& vis) const{
+        void computeVisibility(const stereo_base::Depth& d, stereo_base::Depth& vis) const{
             vis.initialize(width, height, -1.0);
-            std::vector<Depth> zBuffer((size_t)kFrames);
+            std::vector<stereo_base::Depth> zBuffer((size_t)kFrames);
             for(auto& zb: zBuffer)
                 zb.initialize(width, height, -1.0);
             for(auto v=0; v<kFrames; ++v) {
@@ -69,7 +69,7 @@ namespace sce_stereo {
         }
 
     protected:
-        const FileIO &file_io;
+        const stereo_base::FileIO &file_io;
         const int kFrames;
         const cv::Mat &image;
         const std::vector<EnergyType> &MRF_data;
@@ -83,13 +83,13 @@ namespace sce_stereo {
 
     class FirstOrderOptimize : public StereoOptimization {
     public:
-        FirstOrderOptimize(const FileIO &file_io_, const int kFrames_, const cv::Mat &image_,
+        FirstOrderOptimize(const stereo_base::FileIO &file_io_, const int kFrames_, const cv::Mat &image_,
                            const std::vector<EnergyType> &MRF_data_, const float MRFRatio_, const int nLabel_, const int refId_,
                            const EnergyType &weight_smooth_);
 
-        virtual void optimize(Depth &result, const int max_iter) const;
[…]

### 2016-03-08 stereo/code/scestereo/optimization_fusionmove.cpp

@@ -13,6 +13,7 @@
 
 using namespace std;
 using namespace cv;
+using namespace stereo_base;
 namespace sce_stereo {
 
     SecondOrderOptimizeFusionMove::SecondOrderOptimizeFusionMove(const FileIO &file_io_, const int kFrames_,

### 2016-03-08 stereo/code/scestereo/proposal.cpp

@@ -7,6 +7,8 @@
 #include "../external/segment_ms/msImageProcessor.h"
 #include "../external/segment_gb/segment-image.h"
 
+using namespace stereo_base;
+
 namespace sce_stereo{
     ProposalSegPln::ProposalSegPln(const FileIO& file_io_, const cv::Mat &image_, const Depth &noisyDisp_, const int dispResolution_,
                                    const std::string& method_, const int num_proposal_):file_io(file_io_), noisyDisp(noisyDisp_), image(image_),

### 2016-03-08 stereo/code/scestereo/proposal.h

@@ -17,7 +17,7 @@ namespace sce_stereo {
     //interface for proposal creator
     class Proposal {
     public:
-        virtual void genProposal(std::vector<Depth>& proposals) = 0;
+        virtual void genProposal(std::vector<stereo_base::Depth>& proposals) = 0;
     };
 
     class ProposalSegPln: public Proposal{
@@ -26,19 +26,19 @@ namespace sce_stereo {
         //  images_: reference image
         //  noisyDisp_: disparity map from only unary term
         //  num_proposal: number of proposal to generate. NOTE: currently fixed to 7
-        ProposalSegPln(const FileIO& file_io_, const cv::Mat& image_, const Depth& noisyDisp_, const int dispResolution_,
+        ProposalSegPln(const stereo_base::FileIO& file_io_, const cv::Mat& image_, const stereo_base::Depth& noisyDisp_, const int dispResolution_,
                        const std::string& method_, const int num_proposal_ = 7);
-        virtual void genProposal(std::vector<Depth>& proposals);
+        virtual void genProposal(std::vector<stereo_base::Depth>& proposals);
     protected:
-        void fitDisparityToPlane(const std::vector<std::vector<int> >& seg, Depth& planarDisp, int id);
+        void fitDisparityToPlane(const std::vector<std::vector<int> >& seg, stereo_base::Depth& planarDisp, int id);
 
         //input:
         //  pid: id of parameter setting
         //  seg: stores the segmentation result. seg[i] stores pixel indices of region i
         virtual void segment(const int pid, std::vector<std::vector<int> >& seg)  = 0;
 
-        const FileIO& file_io;
-        const Depth& noisyDisp;
+        const stereo_base::FileIO& file_io;
+        const stereo_base::Depth& noisyDisp;
         const cv::Mat& image;
         const int num_proposal;
         std::vector<double> params;
@@ -54,14 +54,14 @@ namespace sce_stereo {
 
     class ProposalSegPlnMeanshift: public ProposalSegPln{
     public:
-	    ProposalSegPlnMeanshift(const FileIO& file_io_, const cv::Mat& image_, const Depth& noisyDisp_, const int dispResolution_, const int num_proposal_ = 10);
+	    ProposalSegPlnMeanshift(const stereo_base::FileIO& file_io_, const cv::Mat& image_, const stereo_base::Depth& noisyDisp_, const int dispResolution_, const int num_proposal_ = 10);
[…]

### 2016-03-08 stereo/code/simplestereo/simplestereo.h

@@ -7,19 +7,52 @@
 
 #include <glog/logging.h>
 #include <iostream>
+#include <opencv2/opencv.hpp>
+#include <Eigen/Eigen>
 
+#include "../stereo_base/file_io.h"
+#include "../stereo_base/depth.h"
 #include "../../../base/LabelSpace.h"
 #include "../../../base/FusionSolver.h"
 #include "../../../base/ParallelFusionPipeline.h"
 #include "../../../base/ProposalGenerator.h"
 
 namespace simple_stereo {
+    class SimpleStereo{
+    public:
+        SimpleStereo(const stereo_base::FileIO& file_io_, const int anchor_, const int dispResolution_);
+        void initMRF();
+        void computeMatchingCost();
+        void assignSmoothWeight();
+
+        void runStereo();
+
+        inline int getWidth() const {return width;}
+        inline int getHeight() const {return height;}
+
+    private:
+        typedef int EnergyType;
+
+        const stereo_base::FileIO& file_io;
+        const int anchor;
+        const int dispResolution;
+        const double MRFRatio;
+        std::vector<cv::Mat> images;
+        std::vector<int> MRF_data;
+        std::vector<int> hCue;
+        std::vector<int> vCue;
+
+        stereo_base::Depth unaryDisp;
+        int width;
+        int height;
+
+    };
+
     class SimpleStereoSolver : public ParallelFusion::FusionSolver<int> {
     public:
+        SimpleStereoSolver(){}
         virtual double solve(const ParallelFusion::LabelSpace<int> &proposals, std::vector<int> &solution) const;
         virtual double evaluateEnergy(const std::vector<int>& solution) const;
-    private:
-
     };
 
     class SimpleStereoGenerator: public ParallelFusion::ProposalGenerator<int>{

### 2016-03-08 stereo/code/stereo_base/depth.h

@@ -7,7 +7,7 @@
 #include <opencv2/opencv.hpp>
 #include <glog/logging.h>
 
-namespace sce_stereo{
+namespace stereo_base{
     class Depth{
     public:
         Depth(): depthwidth(0), depthheight(0), average_depth(0),median_depth(0), depth_var(0),max_depth(-1),min_depth(10000000), statics_computed(false){}

### 2016-03-08 stereo/code/stereo_base/plane3D.cpp

@@ -13,7 +13,7 @@
 using namespace std;
 using namespace Eigen;
 
-namespace sce_stereo {
+namespace stereo_base {
 
 	double Plane3D::epsilon = 1e-4;
 

### 2016-03-08 paper/algorithm.tex

\section{Swarm Fusion Method}

Swarm Fusion is a natural multi-core extension of Fusion Move
Method. Take a multi-threading environment to explain our idea, which is
also applicable to other parallel computation environments such as cloud
computing. Every thread $T_i$ keeps track of a solution $S_i$, and
repeats updating $S_i$ by fusion ($i = 1, 2, \cdots N$). Two parameters
$\alpha_i$ and $\beta_i$ control the behavior of fusion steps in each
thread $T_i$. $\alpha_i$ specifies how many solution proposals are to be
generated from proposal generation schemes. Similarly, $\beta_i$
specifies how many solutions in the other threads are to be
fused. Suppose $N=4$, $\alpha_1 = 2$, and $\beta_1 = 3$. In this
configuration, the first thread $T_1$ fuses its current solution $S_1$,
two new proposal solutions (e.g., by randomly picking two proposal
generation schemes), and the current solutions $(S_2, S_3, S_4)$ in the
other three threads. This is a multi-way fusion with a non-submodular
energy in general, and message passing algorithm such as
TRW~\cite{kolmogorov} can be used. Sequential QPBO application is
another.

Our model is flexible. For example, a parallel fusion move algorithm by
Lempitsky et al.~\cite{viktor} is a special case of ours, where $\alpha_$

, and it is easy to see that 
Existing parallel fusion techniques are special

Our model is flexible and

### 2016-03-08 paper/introduction.tex

@@
 in a cloud.
-%
-Parallel computation offers huge potential for Computer Vision, as
-image sensing technologies have gone through revolutions and we are in
+
+Parallel computation offers tremendous potential for Computer Vision. As
+image sensing technologies have gone through revolutions, we are in
 ever growing demands in solving very large problems. One may need to
@@
 segmentation problems over a billion ($=1024^3$)
-voxels~\cite{Joint_3D_Scene_Reconstruction_and_class_Segmentation}.
-
-Unfortunately, state-of-the-art algorithms are still inherently
-sequential in many Computer Vision problems. Take a Fusion-Move
-algorithm (FM)~\cite{viktor,second_order_stereo,else} for Markov Random
-Field inference, for example, which has been one of the most effective
-techniques in solving the above three
+voxels~\cite{Joint3DSceneReconstructionandclassSegmentation}.
+%
+However, state-of-the-art algorithms are still inherently sequential in
+many Computer Vision problems. Take a Fusion-Move algorithm
+(FM)~\cite{viktor,second_order_stereo,else} for Markov Random Field
+inference, for example. FM has been one of the most effective techniques
+in solving the above
 problems~\cite{fusion_moves_for_markov_random_field_optimization}.
 %
-FM was first introduced by Lempitsky et al. in solving an optical flow
-problem~\cite{first_fusion_viktor}, where proposals are fused
-sequentially one by one to improve the solution. FM allows
-domain-specific customization of proposal generation schemes, a main
-advantage over general solvers such as message passing
-algorithms~\cite{TRW,loopy_belief_propagation}.  Successful applications
-of FM range from optical flow, stereo, image denoising, image
-inpainting, to image
+It sequentially improves solution by fusing the current solution with a
+solution proposal. FM allows domain-specific customization of proposal
+generation schemes, a main advantage over general solvers such as
+message passing algorithms~\cite{TRW,loopy_belief_propagation}.  Its
+successful applications range from optical flow, stereo, image
+denoising, image inpainting, to image
 segmentation~\cite{fusion_moves_for_markov_random_field_optimization}.
@@
 Vision. Currently, FM suffers from a few vital limitations due to its
-sequential processing. First, standard FM allows only two options per
+sequential nature. First, standard FM allows only two options per
 variable in each fusion, either the current solution or a
@@
 %
-Our approach, dubbed {\it Parallel Fusion Moves method} (PFM), makes a
+Our approach, dubbed {\it Swarm Fusion} method (SF), makes a
 few key distinctions from existing approaches: 1) Multiple threads (or
@@
 %
-Note that one may rather seek to parallelize the core optimization
-libraries such as Graph-cuts~\cite{}, TRW~\cite{kolmogorov}, or
-QPBO~\cite{}.~\footnote{GPU speeds-up message-passing algorithms via
-parallel computation. However, these algorithms need to store all the
-messages and states and cannot handle problems with a large label space~\cite{layered_depthmap}.} However, the core optimization libraries are often
-very complex and require significant engineering by experts for
-modification.
-%
-While state-of-the-art optimization libraries are often freely available for
-non-commercial purposes, most companies have to develop and maintain
-in-house implementation of these optimization algorithms.
+
+Our approach is extremely simple in concept, and will instantly benefit
+every Computer Vision researcher or engineer, who currently uses fusion
+move algorithm to solve challenging problems. We will share our
+implementation of the algorithm. The rest of the paper is organized as
+follows. Section~\ref{section:related_work}....
+
 %
@@
 %
-Our approach is extremely simple in concept, and will instantly benefit
-every Computer Vision researcher or engineer, who currently uses fusion
-move algorithm to solve challenging problems. We will share our
-implementation of the algorithm. The rest of the paper is organized as
-follows. Section~\ref{section:related_work}....
 %This paper will propose a novel Parallel Fusion

### 2016-03-08 paper/related_work.tex

@@
 \section{Related work}
+
+FM was first introduced by Lempitsky et al. in solving an optical flow
+problem~\cite{first_fusion_viktor}, where proposals
 
@@
 
-While PSO and GA have limited theoretical justification, they have been used to produce great empirical results.
-For instance, in our recent work on hand tracking, we used the particle swarm optimization method.
-See “Model Fitting” section on page 5 of the following paper:
+While PSO and GA have limited theoretical justification, they have been
+used to produce great empirical results. For instance, in our recent
+work on hand tracking, we used the particle swarm optimization
+method. See Model Fitting section on page 5 of the following paper:
 
-http://research.microsoft.com/en-us/um/people/pkohli/papers/skrts_chi2015.pdf
+\url{http://research.microsoft.com/en-us/um/people/pkohli/papers/skrts_chi2015.pdf}
 
-Also see the video here: https://www.youtube.com/watch?v=R-SfOJyZlRQ&list=PLE7aZMY3Wubx6yRgP8U6GRwJCOi2Zyh2S&index=9
+Also see the video here: \url{https://www.youtube.com/watch?v=R-SfOJyZlRQ&list=PLE7aZMY3Wubx6yRgP8U6GRwJCOi2Zyh2S&index=9}
+
+Note that one may rather seek to parallelize the core optimization
+libraries such as Graph-cuts~\cite{}, TRW~\cite{kolmogorov}, or
+QPBO~\cite{}.~\footnote{GPU speeds-up message-passing algorithms via
+parallel computation. However, these algorithms need to store all the
+messages and states and cannot handle problems with a large label space~\cite{layered_depthmap}.} However, the core optimization libraries are often
+very complex and require significant engineering by experts for
+modification.
+%
+While state-of-the-art optimization libraries are often freely available for
+non-commercial purposes, most companies have to develop and maintain
+in-house implementation of these optimization algorithms.

### 2016-03-08 paper/algorithm.tex
yasu

@@
 \section{Swarm Fusion Method}
+\yasu{need to polish, reads very bad.}  Swarm Fusion is a natural
+multi-core extension of Fusion Move Method. Take a multi-threading
+environment to explain our idea, which is also applicable to other
+parallel computation environments such as cloud computing. Assume we
+have $N$ threads $\{T_i | i=1, 2, \cdots, N\}$. There are two places to
+collect solutions or solution proposals for fusion. First, the {\it
+proposal generation pool} can generate new solution proposals on
+request. Second, the {\it solution pool} stores the fused solutions from
+all the threads. At default, each thread keeps a single current solution
+in the pool, but the scheme can be more general.  Two parameters
+$\alpha_i$ and $\beta_i$ control the behavior of each fusion step in
+$T_i$. The thread collects $\alpha_i$ solution proposals and $\beta_i$
+solutions from the pool
 
-Swarm Fusion is a natural multi-core extension of Fusion Move
-Method. Take a multi-threading environment to explain our idea, which is
-also applicable to other parallel computation environments such as cloud
-computing. Every thread $T_i$ keeps track of a solution $S_i$, and
-repeats updating $S_i$ by fusion ($i = 1, 2, \cdots N$). Two parameters
-$\alpha_i$ and $\beta_i$ control the behavior of fusion steps in each
-thread $T_i$. $\alpha_i$ specifies how many solution proposals are to be
-generated from proposal generation schemes. Similarly, $\beta_i$
-specifies how many solutions in the other threads are to be
-fused. Suppose $N=4$, $\alpha_1 = 2$, and $\beta_1 = 3$. In this
+$\alpha_i$ specifies how many solution proposals are generated
+from proposal generation schemes for a fusion step. Similarly, $\beta_i$
+specifies how many current solutions in the other threads are to be
+fused. Furthermore, one can control how to pick proposal generation
+schemes and how to choose other threads for using the current solutions
+(e.g., random or certain algorithm).
+
+Our framework is general, and many existing parallel fusion algorithms
+are just special cases of our framework.
+%
+For example, the parallel fusion algorithm by Lempitsky et
+al.~\cite{viktor} always performs binary fusion between the current
+solution and another label, which can be achieved by setting $\alpha_i =
+1$ and $\beta_i = 0$ for all the threads. The algorithm by
+Veksler~\cite{olga} or Dejong et al.~\cite{dejong} are a little complex,
+as they need to store as many intermediate solutions as labels, which is
+more than the number of threads. Our framework keeps one solution in
+each thread, but
+
+lets each thread keep a
+single solution, but
+
+Also note that these existing algorithms seek to parallelize
+alpha-expansion with constant solution proposals, and are not true
+fusion move algorithms.
+
+hierarchically fuses all the
+labels. Depending on the input {\it tree structure}, every thread might
+fuse different numbers of existing solutions
+
+We now illustrate the power of Swarm Fusion framework for three problems
+in Computer Vision.
+
+Suppose $N=4$, $\alpha_1 = 2$, and $\beta_1 = 3$. In this
 configuration, the first thread $T_1$ fuses its current solution $S_1$,
@@
 Our model is flexible. For example, a parallel fusion move algorithm by
-Lempitsky et al.~\cite{viktor} is a special case of ours, where $\alpha_$
+Lempitsky et al.~\cite{viktor} is a special case of ours, where $\alpha_i$
 

### 2016-03-08 paper/introduction.tex
yasu

@@
 
-Our approach is extremely simple in concept, and will instantly benefit
-every Computer Vision researcher or engineer, who currently uses fusion
-move algorithm to solve challenging problems. We will share our
-implementation of the algorithm. The rest of the paper is organized as
-follows. Section~\ref{section:related_work}....
+We have validated our ideas on three problems in Computer Vision,
+stereo, optical flow, and layered depthmap estimation. \yasu{add more
+once we see results.}  Our approach is extremely simple in concept, and
+will instantly benefit every Computer Vision researcher or engineer, who
+currently uses fusion move algorithm to solve challenging problems. We
+will share our implementation of the algorithm. The rest of the paper is
+organized as follows. Section~\ref{section:related_work}....
 

### 2016-03-08 paper/algorithm.tex
yasu

--- 2016-03-08 paper/algorithm.tex
@@
 \section{Swarm Fusion Method}
+\yasu{need to polish, reads very bad.}  Swarm Fusion is a natural
+parallel extension of Fusion Move Method. Take a multi-threading
+environment to explain our idea, which is also applicable to other
+parallel computation environments such as cloud computing. Assume we
+have $N$ threads $\{T_i | i=1, 2, \cdots, N\}$. There are two places to
+collect solutions or solution proposals for fusion. First, the {\it
+proposal pool} can generate new solution proposals on request.
+%
+Second, the {\it solution pool} stores the solutions that have been
+fused by the threads. At default, each thread keeps only a current
+solution in the pool, but the scheme can be more general. Two
+parameters $\alpha_i$ and $\beta_i$ control the behavior of each fusion
+step in $T_i$. The thread collects $\alpha_i$ solution proposals
+from the proposal pool and $\beta_i$ solutions from the solution pool
+for fusion in each step.
+%
+Furthermore, one can also control how to choose proposal generation
+schemes and/or solutions from the pools.
 
-Swarm Fusion is a natural multi-core extension of Fusion Move
-Method. Take a multi-threading environment to explain our idea, which is
-also applicable to other parallel computation environments such as cloud
-computing. Every thread $T_i$ keeps track of a solution $S_i$, and
-repeats updating $S_i$ by fusion ($i = 1, 2, \cdots N$). Two parameters
-$\alpha_i$ and $\beta_i$ control the behavior of fusion steps in each
-thread $T_i$. $\alpha_i$ specifies how many solution proposals are to be
-generated from proposal generation schemes. Similarly, $\beta_i$
-specifies how many solutions in the other threads are to be
-fused. Suppose $N=4$, $\alpha_1 = 2$, and $\beta_1 = 3$. In this
+Our framework is general, and it is easy to verify that existing
+parallel fusion algorithms are just our special cases.
+%
+For example, the parallel fusion algorithm by Lempitsky et
+al.~\cite{viktor} always performs binary fusion between the current
+solution and another label, which can be achieved by setting $\alpha_i =
+1$ and $\beta_i = 0$ for all the threads. The algorithm by
+Veksler~\cite{olga} or Dejong et al.~\cite{dejong} hierarchically fuses
+solutions starting from solution proposals. The algorithm can be
+realized by setting $\alpha_i = 1, \beta_i = 0$ initially, then use
+$\alpha_i = 0, \beta_i=1$  for the rest of the algorithm.
+
+standard models.
+
+We now illustrate the power of Swarm Fusion framework for three problems
+in Computer Vision.
+
+Suppose $N=4$, $\alpha_1 = 2$, and $\beta_1 = 3$. In this
 configuration, the first thread $T_1$ fuses its current solution $S_1$,

### 2016-03-08 paper/algorithm.tex
yasu

@@
 
-Our framework is general, and it is easy to verify that existing
-parallel fusion algorithms are just our special cases.
+\mysubsubsection{Base architecture}
+The swarm fusion is highly flexible, and we first introduce our base
+architecture that exploits general strenghts offered by the
+framework. Later, we explain how to further optimize the configuration
+to boost performance for specific problems. In the base architecture,
+all the threads fuse some number of proposals from the proposal pool and
+some number of solutions from the solution pool in each step. In other
+words, all the threads constantly exchange solutions while injecting new
+proposals. This architecture is illustrated in Figure~\ref{fig:base}.
+
+\begin{figure}[tb]
+ \includegraphics[width=\columnwidth]{figure/base_illustration.png}
+ \caption{Base Swarm Fusion architecture.}\label{fig:base}
+\end{figure}
+
+\mysubsubsection{Relationships to existing methods} Our framework is
+general, and it is easy to verify that existing parallel fusion
+algorithms are just our special cases.
 %
@@
 
-standard models.
-
+\noindent
 We now illustrate the power of Swarm Fusion framework for three problems
@@
 
-Suppose $N=4$, $\alpha_1 = 2$, and $\beta_1 = 3$. In this
-configuration, the first thread $T_1$ fuses its current solution $S_1$,
-two new proposal solutions (e.g., by randomly picking two proposal
-generation schemes), and the current solutions $(S_2, S_3, S_4)$ in the
-other three threads. This is a multi-way fusion with a non-submodular
-energy in general, and message passing algorithm such as
-TRW~\cite{kolmogorov} can be used. Sequential QPBO application is
-another.
+% Suppose $N=4$, $\alpha_1 = 2$, and $\beta_1 = 3$. In this
+% configuration, the first thread $T_1$ fuses its current solution $S_1$,
+% two new proposal solutions (e.g., by randomly picking two proposal
+% generation schemes), and the current solutions $(S_2, S_3, S_4)$ in the
+% other three threads. This is a multi-way fusion with a non-submodular
+% energy in general, and message passing algorithm such as
+% TRW~\cite{kolmogorov} can be used. Sequential QPBO application is
+% another.
 
-Our model is flexible. For example, a parallel fusion move algorithm by
-Lempitsky et al.~\cite{viktor} is a special case of ours, where $\alpha_i$
+% Our model is flexible. For example, a parallel fusion move algorithm by
+% Lempitsky et al.~\cite{viktor} is a special case of ours, where $\alpha_i$
 
-, and it is easy to see that 
-Existing parallel fusion techniques are special
+% , and it is easy to see that 
+% Existing parallel fusion techniques are special
 
-Our model is flexible and
+% Our model is flexible and

### 2016-03-08 paper/introduction.tex
yasu

@@
 will instantly benefit every Computer Vision researcher or engineer, who
-currently uses fusion move algorithm to solve challenging problems. We
-will share our implementation of the algorithm. The rest of the paper is
-organized as follows. Section~\ref{section:related_work}....
+currently uses fusion move algorithm on multi-core environments to solve
+challenging problems. We will share our implementation of the
+algorithm. The rest of the paper is organized as
+follows. Section~\ref{section:related_work}....
 

### 2016-03-08 paper/layered_depthmap.tex
yasu

\subsection{Swarm Fusion Layered Depthmap Estimation}

### 2016-03-08 paper/related_work.tex
yasu

@@
 
-FM was first introduced by Lempitsky et al. in solving an optical flow
-problem~\cite{first_fusion_viktor}, where proposals
+Markov Random Field (MRF) inference has been a very active field in
+Computer Vision with extensive literature. We refer the readers to
+survey articles for a comprehensive
+review~\cite{middlebury_mrf,comparative_study_of_modern_inference}, and
+here focus our description on closely related topics.
 
-Hiroshi had a paper for doing this for binary variables but not for multilabel variables.
+\mysubsubsection{Fusion Move Methods}
 
-http://www.f.waseda.jp/hfs/CVPR2014.pdf
+\noindent FM was first introduced by Lempitsky et al. in solving an
+optical flow problem~\cite{first_fusion_viktor}. FM has been effectively
+used to solve challenging problems in Computer Vision such as a stereo
+problem with second order smoothness priors~\cite{woodford}, a stereo
+problem with parameteric surface fitting and segmentation (i.e., Surface
+Stereo)~\cite{surface_stereo}, or multicut
+partiioning~\cite{fusionmovesforcorrelationclustering}.
+%
+FM has two main advantages over the other general inference
+techniques~\cite{trw,loopy_belief_propagation}. \yasu{Pushmeet, is this
+correct? Am not confident to say this?} First, FM allows us to exploit
+domain-specific knowledge in customizing proposal generation
+schemes. Second, FM can handle problems with very large label spaces,
+because the core optimization just solves a binary decision problem. In
+contrast, methods like message passing algorithms need to maintain
+messages and beliefs for the entire label space all the time.
 
- This is a good idea.
-Rather than having one perfect solution threads, we maintain multiple solution hypothesis which are then combined with each other.
-At a high level, this strategy is similar to methods like genetic algorithms (GA) or particle swarm optimization (PSO) where multiple solutions are maintained and improved over time.
+\mysubsubsection{Parallel Fusion Methods}
 
-However, unlike GA or PSO where the fusion step is essentially just arbitrarily copying part of the solution, we try to find the optimal copy.
+\noindent There exist a few but not many parallel fusion
+algorithms~\cite{viktor,olga,delong}. Lempitsky et al. introduces
+parallel computation to an alpha-expansion technique, where multiple
+threads simultaneously fuses mutually exclusive sets of labels. Delong
+et al.~\cite{delong} and Veksler~\cite{olga} proposed an hierarchical
+fusion algorithm, where labels can be simultaneously fused in a
+particular order defined by a tree.
 
-While PSO and GA have limited theoretical justification, they have been
-used to produce great empirical results. For instance, in our recent
-work on hand tracking, we used the particle swarm optimization
-method. See Model Fitting section on page 5 of the following paper:
+\mysubsubsection{Parallel MAP inference}
 
-\url{http://research.microsoft.com/en-us/um/people/pkohli/papers/skrts_chi2015.pdf}
-
-Also see the video here: \url{https://www.youtube.com/watch?v=R-SfOJyZlRQ&list=PLE7aZMY3Wubx6yRgP8U6GRwJCOi2Zyh2S&index=9}
+Although conceptually straightforward, we are not aware of parallel
+fusion move algorithms that fuses solution proposals (as opposed to
+labels) in parallel.
 
@@
 libraries such as Graph-cuts~\cite{}, TRW~\cite{kolmogorov}, or
+
+graph-cuts
+\cite{strandmark2010parallel}
+
 QPBO~\cite{}.~\footnote{GPU speeds-up message-passing algorithms via
@@
 in-house implementation of these optimization algorithms.
+
+\mysubsubsection{Genetic algorithms and Particle Swarm Optimization}
+
+\noindent
+Genetic algorithms (GA)~\cite{ga} and Particle Swarm
+Optimization (PSO)~\cite{pso} maintain multiple solutions and improve
+them over time.
+%
+While GA and PSO have limited theoretical justification, they have been
+used to produce great empirical results, for example, hand tracking via
+PSO~\cite{pushmeet_hand_tracking}.  At high level, our strategy is
+similar to theirs. However, unlike GA or PSO where the fusion step is
+essentially just arbitrarily copying part of the solution, we 
+directly optimize the objective function to find the optimal copy.

### 2016-03-08 paper/related_work.tex
yasu

@@
 here focus our description on closely related topics.
+
+\mysubsubsection{Parallel Alpha-Expansion}
+
+\noindent Lempitsky et al. introduces parallel computation to an
+alpha-expansion technique, where multiple threads simultaneously fuses
+mutually exclusive sets of labels. Delong et al.~\cite{delong} and
+Veksler~\cite{olga} proposed an hierarchical fusion algorithm, where
+labels are simultaneously fused from the bottom to the top in a tree of
+labels. Strictly speaking, these parallelize alpha-expansion and are not
+in the family of Fusion Move methods, because they never generate
+solution proposals. Our approach parallelize fusion move methods.
+
+\mysubsubsection{Parallel MAP inference}
+
+\noindent
+The core MAP inference algorithms themselves can be parallelized.
+Strandmark et al. parallelized graph-cuts~\cite{strandmark2010parallel}.
+%
+Message passing algorithms are friendly to GPU implementation and can
+exploit the power of parallel computation.
+%
+However, the core optimization libraries are often very complex and
+require significant engineering by experts for modification.
+%
+While state-of-the-art optimization libraries are often freely available
+for non-commercial purposes, most companies have to develop and maintain
+in-house implementation of these algorithms. The modification of the
+core optimization libraries is a significant engineering investment for
+many companies. In contrast, our idea is extremely simple and instantly
+reproducible by standard engineers.
+
+% \footnote{GPU speeds-up message-passing algorithms via parallel
+% computation. However, these algorithms need to store all the messages
+% and states and cannot handle problems with a large label
+% space~\cite{layered_depthmap}.}
 
@@
 messages and beliefs for the entire label space all the time. 
-
-\mysubsubsection{Parallel Fusion Methods}
-
-\noindent There exist a few but not many parallel fusion
-algorithms~\cite{viktor,olga,delong}. Lempitsky et al. introduces
-parallel computation to an alpha-expansion technique, where multiple
-threads simultaneously fuses mutually exclusive sets of labels. Delong
-et al.~\cite{delong} and Veksler~\cite{olga} proposed an hierarchical
-fusion algorithm, where labels can be simultaneously fused in a
-particular order defined by a tree.
-
-\mysubsubsection{Parallel MAP inference}
-
-Although conceptually straightforward, we are not aware of parallel
-fusion move algorithms that fuses solution proposals (as opposed to
-labels) in parallel.
-
-Note that one may rather seek to parallelize the core optimization
-libraries such as Graph-cuts~\cite{}, TRW~\cite{kolmogorov}, or
-
-graph-cuts
-\cite{strandmark2010parallel}
-
-QPBO~\cite{}.~\footnote{GPU speeds-up message-passing algorithms via
-parallel computation. However, these algorithms need to store all the
-messages and states and cannot handle problems with a large label space~\cite{layered_depthmap}.} However, the core optimization libraries are often
-very complex and require significant engineering by experts for
-modification.
 %
-While state-of-the-art optimization libraries are often freely available for
-non-commercial purposes, most companies have to develop and maintain
-in-house implementation of these optimization algorithms.
+Although conceptually straightforward, we are not aware of {\it parallel
+fusion move} algorithms that fuses solution proposals, as opposed to
+labels, in parallel. This paper seeks to fully unleash the power of
+parallel computation in FM via a more general framework.
 
@@
 PSO~\cite{pushmeet_hand_tracking}. At high level, our strategy is
-similar to theirs. However, unlike GA or PSO where the fusion step is
-essentially just arbitrarily copying part of the solution, we 
-directly optimize the objective function to find the optimal copy.
+similar in spirit. However, GA or PSO rather arbitrarily copies part of
+the solution or makes random movements in each step. Our approach
+directly optimizes the objective function to improve solutions.

### 2016-03-08 base/FusionSolver.h
Hang

@@ -14,6 +14,9 @@ namespace ParallelFusion {
         //take initial value, run optimization and store solution in 'solution', return error
         virtual double solve(const LabelSpace<LabelType> &proposals, std::vector<LabelType> &solution) const = 0;
 
+        //initialize solver with an initial solution, will be called automatically
+        virtual void initSolver(const std::vector<LabelType>& initial){}
+
         //given a solution, evaluate energy
         virtual double evaluateEnergy(const std::vector<LabelType>& solution) const = 0;
     };

### 2016-03-08 base/LabelSpace.h

@@ -24,6 +24,8 @@ namespace ParallelFusion {
         void clear();
 
         inline int getNumNode()const{return num_nodes_; }
+        inline bool empty() const{ return label_space_.empty();}
+
         inline const std::vector<LabelType>& getLabelOfNode(const int nid) const{
             CHECK_GE(nid, 0);
             CHECK_LT(nid, label_space_.size());

### 2016-03-08 base/ParallelFusionPipeline.h

@@ -53,6 +53,7 @@ namespace ParallelFusion {
 
     struct ParallelFusionOption {
         ParallelFusionOption() : probProposalFromOther(0.2), convergeThreshold(0.01), max_iteration(10), num_threads(6), fuseSize(2), addMethod(APPEND) { }
+        //Addition method: how add two proposals. APPEND: simply append; UNION: take union, remove duplicate labels
         enum ProposalAddition{APPEND, UNION};
         double probProposalFromOther;
         double convergeThreshold;
@@ -65,27 +66,30 @@ namespace ParallelFusion {
     template<typename T>
     class ParallelFusionPipeline {
         //solver should be read only
-        ParallelFusionPipeline(const std::shared_ptr<const FusionSolver<T> >& solver_, const ParallelFusionOption &option_) : solver(solver_), option(option_), terminate(false) { }
+        ParallelFusionPipeline(const ParallelFusionOption &option_) : option(option_), terminate(false) { }
 
         typedef std::shared_ptr<ProposalGenerator<T> > GeneratorPtr;
         typedef std::vector<GeneratorPtr> GeneratorSet;
+        typedef std::shared_ptr<FusionSolver<T> > SolverPtr;
+        typedef std::vector<SolverPtr> SolverSet;
 
         //run parallel fusion. The logic in this routine represents the master thread
         //input: num_threads: number of threads to use
         //       max_iter: maximum iterations of fusion in each thread
         //       initials: initial solution for each thread. The size must be num_threads
+        //       gnerators: shared pointers of ProposalGenerator, one for each thread
+        //       solvers: shared pointers of FusionSolver, one for each thread
         //return: final energy
-        //each thread has its own generator. Note, the size of generators must be the
-        //same with option.num_thread. If all threads use exactly the same generator, duplicate
-        //it multiple times
         double runParallelFusion(const std::vector<std::vector<T> > &initials,
-                                 const GeneratorSet& generator);
+                                 const GeneratorSet& generators,
+                                 const SolverSet& solvers);
 
         void getLabeling(std::vector<T>& solution);
 
         //slave threads
         void workerThread(const int id, const std::vector<T> &initial,
-                          const GeneratorPtr &generator);
+                          const GeneratorPtr &generator,
+                          const SolverPtr& solver);
 
         inline const ParallelFusionOption &getOption() const { return option; }
 
@@ -103,7 +107,6 @@ namespace ParallelFusion {
 
[…]

### 2016-03-08 base/ProposalGenerator.h

@@ -18,7 +18,7 @@ namespace ParallelFusion {
         //NOTE: the method only return one proposal one time!!!!!
         //If you need multiple proposals, call this method multiple times. The concrete subclass should know which
         //proposal to generate (e.g. by a internal counter). Again, be careful of synchronization
-        virtual void getProposals(std::vector<T> & proposal, const std::vector<T>& current_solution) = 0;
+        virtual void getProposals(LabelSpace<T> & proposal, const std::vector<T>& current_solution, const int N) = 0;
 
         virtual void writeSolution(const std::vector<T> &solution, const int thread_index,
                                    const int iteration) const { }; //write temporary solution for visualization purpose

### 2016-03-08 stereo/code/simplestereo/SimpleStereo_cli.cpp

@@ -10,7 +10,7 @@ using namespace stereo_base;
 using namespace simple_stereo;
 DEFINE_int32(resolution, 256, "resolution");
 DEFINE_int32(testFrame, 0, "reference frame");
-
+DEFINE_double(weight_smooth, 0.01, "smoothness weight");
 int main(int argc, char** argv){
     if(argc < 2){
         cerr << "Usage: ./SimpleStereo <path-to-data>" << endl;
@@ -21,7 +21,7 @@ int main(int argc, char** argv){
     google::ParseCommandLineFlags(&argc, &argv, true);
 
     FileIO file_io(argv[1]);
-    SimpleStereo stereo(file_io, FLAGS_testFrame, FLAGS_resolution);
+    SimpleStereo stereo(file_io, FLAGS_testFrame, FLAGS_resolution, FLAGS_weight_smooth);
     stereo.runStereo();
     return 0;
 }

### 2016-03-08 stereo/code/simplestereo/simplestereo.cpp

@@ -2,6 +2,7 @@
 // Created by yanhang on 3/7/16.
 //
 
+#include <stereo/code/external/MRF2.2/mrf.h>
 #include "simplestereo.h"
 #include "../stereo_base/local_matcher.h"
 
@@ -13,12 +14,28 @@ using namespace Eigen;
 namespace simple_stereo {
     void SimpleStereoGenerator::getProposal(std::vector<int> &proposal,
                                             const std::vector<int> &current_solution) {
-
+        proposal.resize(current_solution.size());
+        for(auto& v: proposal)
+            v = nextLabel;
+        nextLabel = (nextLabel + 1) % nLabel;
     }
 
+    void SimpleStereoSolver::initSolver(const std::vector<int>& initial) {
+        CHECK_EQ(initial.size(), model.width * model.height);
+        EnergyFunction *energy_function = new EnergyFunction(new DataCost(const_cast<int *>(model.MRF_data.data())),
+                                                             new SmoothnessCost(1, 4, model.weight_smooth,
+                                                                                const_cast<int *>(model.hCue.data()),
+                                                                                const_cast<int *>(model.vCue.data())));
+    }
 
     double SimpleStereoSolver::solve(const ParallelFusion::LabelSpace<int> &proposals,
                                      std::vector<int> &solution) const {
+        CHECK(!proposals.empty());
+        vector<int> curData;
+
+        for(auto i=0; i<labelToExpand; ++i){
+            if(labelToExpand[i])
+        }
         return 0;
     }
 
@@ -26,14 +43,16 @@ namespace simple_stereo {
         return 0;
     }
 
-    SimpleStereo::SimpleStereo(const FileIO &file_io_, const int anchor_, const int dispResolution_):
-            file_io(file_io_), anchor(anchor_), dispResolution(dispResolution_), MRFRatio(100.0) {
+    SimpleStereo::SimpleStereo(const FileIO &file_io_, const int anchor_, const int dispResolution_, const double weight_smooth_):
+            file_io(file_io_), anchor(anchor_){
         CHECK_GE(file_io.getTotalNum(), 2) << "Too few images at " << file_io.getDirectory();
         images.resize((size_t)file_io.getTotalNum());
         for(auto i=0; i<images.size(); ++i)
             images[i] = imread(file_io.getImage(i));
         width = images[0].cols;
         height = images[0].rows;
+
+        model.init(width, height, dispResolution_, weight_smooth_);
     }
 
[…]

### 2016-03-08 stereo/code/simplestereo/simplestereo.h

@@ -12,15 +12,40 @@
 
 #include "../stereo_base/file_io.h"
 #include "../stereo_base/depth.h"
+#include "../external/MRF2.2/GCoptimization.h"
 #include "../../../base/LabelSpace.h"
 #include "../../../base/FusionSolver.h"
 #include "../../../base/ParallelFusionPipeline.h"
 #include "../../../base/ProposalGenerator.h"
 
 namespace simple_stereo {
+
+    template<typename T>
+    struct MRFModel{
+        MRFModel(): width(0), height(0), MRFRatio(100.0){}
+        int width;
+        int height;
+        int nLabel;
+        std::vector<T> MRF_data;
+        std::vector<T> hCue;
+        std::vector<T> vCue;
+        T weight_smooth;
+        const double MRFRatio;
+
+        void init(const int w, const int h, const int n, const double wei){
+            MRF_data.resize((size_t)w * h * n);
+            hCue.resize((size_t)w * h);
+            vCue.resize((size_t)w * h);
+            width = w;
+            height = h;
+            nLabel = n;
+            weight_smooth = (T)(wei * MRFRatio);
+        }
+    };
+
     class SimpleStereo{
     public:
-        SimpleStereo(const stereo_base::FileIO& file_io_, const int anchor_, const int dispResolution_);
+        SimpleStereo(const stereo_base::FileIO& file_io_, const int anchor_, const int dispResolution_, const double weight_smooth_);
         void initMRF();
         void computeMatchingCost();
         void assignSmoothWeight();
@@ -35,12 +60,9 @@ namespace simple_stereo {
 
         const stereo_base::FileIO& file_io;
         const int anchor;
-        const int dispResolution;
-        const double MRFRatio;
         std::vector<cv::Mat> images;
-        std::vector<int> MRF_data;
-        std::vector<int> hCue;
-        std::vector<int> vCue;
+
+        MRFModel<int> model;
 
         stereo_base::Depth unaryDisp;
         int width;
@@ -50,9 +72,12 @@ namespace simple_stereo {
 
     class SimpleStereoSolver : public ParallelFusion::FusionSolver<int> {
     public:
-        SimpleStereoSolver(){}
+        SimpleStereoSolver(const MRFModel<int>& model_): model(model_){}
+        virtual void initSolver(const std::vector<int>& initial);
         virtual double solve(const ParallelFusion::LabelSpace<int> &proposals, std::vector<int> &solution) const;
[…]

### 2016-03-08 base/ParallelFusionPipeline.h
Hang

@@ -175,14 +175,13 @@ namespace ParallelFusion {
                 }
                 LabelSpace<T> proposals;
                 //generate proposal by own generator
-                for(auto pid=0; pid < kSelfThread; ++pid) {
-                    std::vector<T> curproposal;
-                    generator->getProposals(curproposal, current_solution.second);
-                    if(option.addMethod == ParallelFusionOption::APPEND)
-                        proposals.appendSolution(curproposal);
-                    else
-                        proposals.unionSolution(curproposal);
-                }
+                LabelSpace<T> proposals_self;
+                generator->getProposals(proposals_self, current_solution.second, kSelfThread);
+                if(option.addMethod == ParallelFusionOption::APPEND)
+                    proposals.appendSpace(proposals_self);
+                else
+                    proposals.unionSpace(proposals_self);
+
                 //Take best solutions from other threads. Initially there is no 'best solution', marked by
                 //the energy less than 0. If such condition occurs, replace this with another self generated
                 //proposal.
@@ -196,12 +195,12 @@ namespace ParallelFusion {
                         else
                             proposals.unionSolution(s.second);
                     }else{
-                        std::vector<T> curproposal;
-                        generator->getProposals(curproposal, current_solution.second);
+                        LabelSpace<T> tempProposal;
+                        generator->getProposals(tempProposal, current_solution.second, 1);
                         if(option.addMethod == ParallelFusionOption::APPEND)
-                            proposals.appendSolution(curproposal);
+                            proposals.appendSpace(tempProposal);
                         else
-                            proposals.unionSolution(curproposal);
+                            proposals.unionSpace(tempProposal);
                     }
                 }
 

### 2016-03-08 stereo/code/simplestereo/simplestereo.cpp

@@ -33,9 +33,6 @@ namespace simple_stereo {
         CHECK(!proposals.empty());
         vector<int> curData;
 
-        for(auto i=0; i<labelToExpand; ++i){
-            if(labelToExpand[i])
-        }
         return 0;
     }
 

### 2016-03-09 paper/related_work.tex
yasu

@@
 Stereo)~\cite{surface_stereo}, or multicut
-partiioning~\cite{fusionmovesforcorrelationclustering}.
+partitioning~\cite{fusionmovesforcorrelationclustering}.
 %
@@
 labels, in parallel. This paper seeks to fully unleash the power of
-parallel computation in FM via a more general framework.
+parallel computation in FM via more general framework.
 

### 2016-03-09 paper/algorithm.tex
yasu

@@
 \section{Swarm Fusion Method}
-\yasu{need to polish, reads very bad.}  Swarm Fusion is a natural
-parallel extension of Fusion Move Method. Take a multi-threading
-environment to explain our idea, which is also applicable to other
-parallel computation environments such as cloud computing. Assume we
-have $N$ threads $\{T_i | i=1, 2, \cdots, N\}$. There are two places to
-collect solutions or solution proposals for fusion. First, the {\it
-proposal pool} can generate new solution proposals on request.
+\yasu{need to polish, reads very bad.}  {\it Swarm Fusion} (SF) is a
+natural parallel extension of Fusion Move method (FM). Take a
+multi-threading environment to explain our idea, but the technique is also
+applicable to other parallel programming model such as {\it MapReduce}
+in cloud computing.
 %
-Second, the {\it solution pool} stores the solutions that have been
-fused by the threads. At default, each thread keeps only a current
-solution in the pool, but the scheme can be more general. Two
-parameters $\alpha_i$ and $\beta_i$ control the behavior of each fusion
-step in $T_i$. The thread collects $\alpha_i$ solution proposals
-from the proposal pool and $\beta_i$ solutions from the solution pool
-for fusion in each step.
+Assume we have $N$ threads $\{T_i | i=1, 2, \cdots, N\}$.  Alpha
+expansion picks one label in each iteration to perform fusion, while FM
+invokes one proposal generation scheme and generate a solution proposal
+for fusion. We have 1) a {\it proposal pool}, from which we pick
+arbitrary number of proposal generation schemes and generate proposals,
+and 2) a {\it solution pool}, from which we pick arbitrary number of
+intermediate solutions generated by all the threads.
+%
+% Traditional FM has a set of proposal generation schemes to be
+% invoked
+%
+% There are two places to
+% collect solutions or solution proposals for fusion. First, the {\it
+% proposal pool} can generate new solution proposals on request.
+% %
+% Second, the {\it solution pool} stores the solutions that have been
+% fused by the threads.
+In our base configuration, the solution pool only remembers one (the
+best) solution generated by each thread, but the scheme can be more
+general.
+
+Two parameters $\alpha_i$ and $\beta_i$
+control the behavior of each fusion step in $T_i$. The thread collects
+$\alpha_i$ solution proposals from the proposal pool and $\beta_i$
+solutions from the solution pool for fusion in each step.
 %
@@
 schemes and/or solutions from the pools.
+
+Five architectures.
+
+Sequential.
+Naive parallel sequential (viktor).
+H-fusion (veksler, delong)
+Ours (sharing solutions)
+Ours (multiple proposals)
+Ours (multiple proposals and sharing solutions)
 
@@
 \begin{figure}[tb]
- \includegraphics[width=\columnwidth]{figure/base_illustration.png}
+ \includegraphics[width=\columnwidth]{figure/model.pdf}
  \caption{Base Swarm Fusion architecture.}\label{fig:base}
 \end{figure}
+
+% \begin{figure}[tb]
+%  \includegraphics[width=\columnwidth]{figure/model2.pdf}
+%  \caption{Base Swarm Fusion architecture.}\label{fig:base}
+% \end{figure}
 

### 2016-03-09 paper/algorithm.tex
yasu

@@
 \section{Swarm Fusion Method}
-\yasu{need to polish, reads very bad.}  {\it Swarm Fusion} (SF) is a
-natural parallel extension of Fusion Move method (FM). Take a
-multi-threading environment to explain our idea, but the technique is also
-applicable to other parallel programming model such as {\it MapReduce}
-in cloud computing.
+{\it Swarm Fusion} (SF) is a natural extension of Fusion Move method
+(FM). Take a multi-threading environment to explain our idea, but the
+technique is also applicable to other parallel programming model such as
+{\it MapReduce} in cloud computing.
 %
 Assume we have $N$ threads $\{T_i | i=1, 2, \cdots, N\}$.  Alpha
-expansion picks one label in each iteration to perform fusion, while FM
+expansion picks one label in each iteration to perform fusion. FM
 invokes one proposal generation scheme and generate a solution proposal
-for fusion. We have 1) a {\it proposal pool}, from which we pick
+for fusion. We have 1) a {\it proposal pool}, from which we can pick
 arbitrary number of proposal generation schemes and generate proposals,
-and 2) a {\it solution pool}, from which we pick arbitrary number of
-intermediate solutions generated by all the threads.
+and 2) a {\it solution pool}, from which we can pick arbitrary number of
+intermediate solutions generated by all the other threads.
 %
@@
 
-Two parameters $\alpha_i$ and $\beta_i$
-control the behavior of each fusion step in $T_i$. The thread collects
-$\alpha_i$ solution proposals from the proposal pool and $\beta_i$
-solutions from the solution pool for fusion in each step.
+SF has two main parameters $\alpha_i$ and $\beta_i$ (for each thread
+$T_i$), determining the processing flow of the algorithm: In each fusion
+step, the thread collects $\alpha_i$ solution proposals from the
+proposal pool and $\beta_i$ solutions from the solution pool.
+The bottom right configuration in Figure~\ref{fig:model}
+
+\begin{figure}[tb]
+ \includegraphics[width=\columnwidth]{figure/model.pdf}
+ \caption{Base Swarm Fusion architecture.}\label{fig:model}
+\end{figure}
+
 %
@@
 words, all the threads constantly exchange solutions while injecting new
-proposals. This architecture is illustrated in Figure~\ref{fig:base}.
-
-\begin{figure}[tb]
- \includegraphics[width=\columnwidth]{figure/model.pdf}
- \caption{Base Swarm Fusion architecture.}\label{fig:base}
-\end{figure}
+proposals. This architecture is illustrated in Figure~\ref{fig:model}.
 

### 2016-03-09 paper/algorithm.tex
yasu

@@
-\section{Swarm Fusion Method}
-{\it Swarm Fusion} (SF) is a natural extension of Fusion Move method
-(FM). Take a multi-threading environment to explain our idea, but the
-technique is also applicable to other parallel programming model such as
-{\it MapReduce} in cloud computing.
+\section{Multi-way particle swarm fusion}
+Multi-way Particle Swarm Fusion is a natural extension of Fusion Move
+method (FM). We call our method Swarm Fusion (SF) in short. Take a
+multi-threading environment to explain our idea, while the technique is
+also applicable to other parallel programming model such as {\it
+MapReduce} in cloud computing.
 %
-Assume we have $N$ threads $\{T_i | i=1, 2, \cdots, N\}$.  Alpha
+
+Assume that we have $N$ threads $\{T_i | i=1, 2, \cdots, N\}$.  Alpha
 expansion picks one label in each iteration to perform fusion. FM
 invokes one proposal generation scheme and generate a solution proposal
-for fusion. We have 1) a {\it proposal pool}, from which we can pick
+for fusion. Swarm Fusion has 1) a {\it proposal pool}, from which we can pick
 arbitrary number of proposal generation schemes and generate proposals,
@@
 
-SF has two main parameters $\alpha_i$ and $\beta_i$ (for each thread
+Swarm Fusion has two main parameters $\alpha_i$ and $\beta_i$ (for each thread
 $T_i$), determining the processing flow of the algorithm: In each fusion
@@
 proposal pool and $\beta_i$ solutions from the solution pool.
-The bottom right configuration in Figure~\ref{fig:model}
-
+%
+One can further customize how to pick certain proposal generation
+schemes (as in ~\cite{delong}) or solutions. Swarm Fusion framework is
+very flexible and yields various architecture as shown in
+Figure~\ref{fig:model}.
+%
+The bottom right configuration is the most general one, in which we
+always fuse some solution proposals and some concurrent solutions. This
+is a multi-way fusion (not binary) with a non-submodular energy, and we
+use TRW~\cite{kolmogorov} for the fusion. Of course, if one knows that a
+certain fusion step is a binary fusion with submodular energy, one can
+use graph-cuts instead~\cite{alpha_expansion_paper}. If a certain fusion
+step is a binary fusion with non-submodular energy, one can use
+QPBO~\cite{second_order_smoothness_stereo}.
+%
+Note that the threads are all synchronized in the figure for a
+illustration purpose. In practice, all the threads run asynchronously
+with a (read-write) lock on the data in the solution pool. The
+asynchronous processing could be difficult for cloud parallel computing.
+%
 \begin{figure}[tb]
- \includegraphics[width=\columnwidth]{figure/model.pdf}
- \caption{Base Swarm Fusion architecture.}\label{fig:model}
+ \includegraphics[width=\columnwidth]{figure/model.pdf} \caption{Swarm
+ Fusion architecture and its relationships to existing methods.
+}\label{fig:model}
 \end{figure}
+%
+%
 
 %
-Furthermore, one can also control how to choose proposal generation
-schemes and/or solutions from the pools.
+
+\mysubsubsubsection{Relationships to existing methods}
+
+\noindent
+abc
 

### 2016-03-09 paper/algorithm.tex
yasu

@@
 
-Assume that we have $N$ threads $\{T_i | i=1, 2, \cdots, N\}$.  Alpha
+Assuming we have $N$ threads $\{T_i | i=1, 2, \cdots, N\}$, each thread
+$T_i$ maintains and updates a solution $S_i$ in parallel. Alpha
 expansion picks one label in each iteration to perform fusion. FM
-invokes one proposal generation scheme and generate a solution proposal
-for fusion. Swarm Fusion has 1) a {\it proposal pool}, from which we can pick
-arbitrary number of proposal generation schemes and generate proposals,
-and 2) a {\it solution pool}, from which we can pick arbitrary number of
-intermediate solutions generated by all the other threads.
+invokes one proposal generation scheme and generates a solution proposal
+for fusion. Swarm Fusion has 1) a {\it proposal pool}, from which we
+pick arbitrary number of proposal generation schemes and generate
+proposals, and 2) a {\it solution pool}, from which we pick arbitrary
+number of intermediate solutions generated by all the other threads.
 %
@@
 In our base configuration, the solution pool only remembers one (the
-best) solution generated by each thread, but the scheme can be more
-general.
+best) solution generated by each thread.
 
-Swarm Fusion has two main parameters $\alpha_i$ and $\beta_i$ (for each thread
-$T_i$), determining the processing flow of the algorithm: In each fusion
-step, the thread collects $\alpha_i$ solution proposals from the
-proposal pool and $\beta_i$ solutions from the solution pool.
+Swarm Fusion has two main parameters $\alpha_i$ and $\beta_i$ (for each
+thread $T_i$), determining the processing flow of the algorithm: In each
+fusion step, the thread collects $\alpha_i$ solution proposals from the
+proposal pool and $\beta_i$ solutions from the solution pool, following
+a user-defined strategy or at random to be simple.
 %
-One can further customize how to pick certain proposal generation
-schemes (as in ~\cite{delong}) or solutions. Swarm Fusion framework is
-very flexible and yields various architecture as shown in
-Figure~\ref{fig:model}.
+% One can further customize how to pick certain proposal generation
+% schemes (as in ~\cite{delong}) or solutions.
+Swarm Fusion framework is very flexible and yields various data
+processing architectures as shown in Figure~\ref{fig:model}.
+%
+\begin{figure}[tb]
+ \includegraphics[width=\columnwidth]{figure/model.pdf} \caption{Swarm
+ Fusion architecture and its relationships to existing methods. mention
+ that hierarchical fusion works in a different way, but we can still
+ consider that to be our special case, by letting each thread not using
+ its own solution in the next fusion.}\label{fig:model}
+\end{figure}
 %
 The bottom right configuration is the most general one, in which we
-always fuse some solution proposals and some concurrent solutions. This
-is a multi-way fusion (not binary) with a non-submodular energy, and we
-use TRW~\cite{kolmogorov} for the fusion. Of course, if one knows that a
-certain fusion step is a binary fusion with submodular energy, one can
-use graph-cuts instead~\cite{alpha_expansion_paper}. If a certain fusion
-step is a binary fusion with non-submodular energy, one can use
-QPBO~\cite{second_order_smoothness_stereo}.
+always fuse some solution proposals and some concurrent solutions
+(i.e., $\alpha\ne 0, \beta \ne 0$).
+%
+Each fusion is multi-way (not binary) with a non-submodular energy, and
+we use TRW~\cite{kolmogorov} for the fusion, while any other compatible
+inference techniques can be used~\cite{opengm}. Of course, if one knows
+that a certain fusion step is a binary fusion with submodular energy,
+one can use graph-cuts instead~\cite{alpha_expansion_paper}. If a
+certain fusion step is a binary fusion with non-submodular energy, one
+can use QPBO~\cite{second_order_smoothness_stereo}.
 %
@@
 illustration purpose. In practice, all the threads run asynchronously
-with a (read-write) lock on the data in the solution pool. The
-asynchronous processing could be difficult for cloud parallel computing.
-%
-\begin{figure}[tb]
- \includegraphics[width=\columnwidth]{figure/model.pdf} \caption{Swarm
- Fusion architecture and its relationships to existing methods.
-}\label{fig:model}
-\end{figure}
+with a (read-write) lock on the data in the two pools (See Algorithm~\ref{algorithm:sf}).
+%The asynchronous processing could be difficult for cloud parallel
+%computing.
 %
 %
-
 %
+\begin{algorithm}
+ \caption{Swarm Fusion method}
+ \label{algorithm:sf}
+ \begin{algorithmic}
+  %\Procedure{Swarm Fusion method} {}
+  \Procedure{} {$\alpha, \beta$}
+  \State $\mathcal{S}_{pool} \leftarrow \emptyset$ //
+  Solution pool
+  \State Initialize $\mathcal{P}_{pool}$ // Proposal pool
+  \ForEach{thread $T_i$}
+  \State Initialize its solution $S_i$
+  \EndFor
+  \State
+  \ForEach{thread $T_i$ in parallel till convergence}
+  \State Pick $\alpha$ solution proposals $\mathcal{P}\subset \mathcal{P_{\mbox{pool}}}$
+  \State Pick $\beta$ solutions $\mathcal{S} \subset \mathcal{S_{\mbox{pool}}}$
+  \State $S_i \leftarrow \mbox{Fuse}(S_i, \mathcal{P}, \mathcal{S})$
+  \State Replaces the solution in $\mathcal{S}_{pool}$ with $S_i$
+  \State [ Generates proposals and update $\mathcal{P}_{pool}$ ]
+  \EndFor
+  \EndProcedure
+ \end{algorithmic}
+\end{algorithm}
 
@@
 
-\noindent
-abc
+\noindent It is easy to verify that alpha-expansion
+(AE)~\cite{alpha_expansion}, fusion move (FM)~\cite{viktor}, parallel
+alpha-expansion (PAE)~\cite{delong}, and hierarchical fusion
+(HF)~\cite{delong_hierarchical,olga} are all special cases of the Swarm
+Fusion method.~\footnote{The hierarchical fusion has a slightly
+different data processing model, without strong ties between threads
+data, but this can be considered as a special case of SF by not using
+$S_i$ in each fusion step of $T_i$.} For example, AE can be realized by
+setting $\alpha=1, \beta=0$ and restricting the proposal generation to
+constant labels with a single thread. Same goes for FM, this time,
+without the restriction on the proposal generation scheme. PAE is
+realized by setting $\alpha=1,\beta=1$ with multiple threads, again with
+a restriction on the proposal generation scheme. The last sequential
+fusion (at the top of the diagram in the figure) can be modeled by
+changing to $\alpha=0, \beta=1$ with a single thread.
 
-Five architectures.
-
-Sequential.
-Naive parallel sequential (viktor).
-H-fusion (veksler, delong)
-Ours (sharing solutions)
-Ours (multiple proposals)
-Ours (multiple proposals and sharing solutions)
-
-\mysubsubsection{Base architecture}
-The swarm fusion is highly flexible, and we first introduce our base
-architecture that exploits general strenghts offered by the
-framework. Later, we explain how to further optimize the configuration
-to boost performance for specific problems. In the base architecture,
-all the threads fuse some number of proposals from the proposal pool and
-some number of solutions from the solution pool in each step. In other
-words, all the threads constantly exchange solutions while injecting new
-proposals. This architecture is illustrated in Figure~\ref{fig:model}.
+% The swarm fusion is highly flexible, and we first introduce our base
+% architecture that exploits general strenghts offered by the
+% framework. Later, we explain how to further optimize the configuration
+% to boost performance for specific problems. In the base architecture,
+% all the threads fuse some number of proposals from the proposal pool and
+% some number of solutions from the solution pool in each step. In other
+% words, all the threads constantly exchange solutions while injecting new
+% proposals. This architecture is illustrated in Figure~\ref{fig:model}.
 
@@
 
-\mysubsubsection{Relationships to existing methods} Our framework is
-general, and it is easy to verify that existing parallel fusion
-algorithms are just our special cases.
+% \mysubsubsection{Relationships to existing methods} Our framework is
+% general, and it is easy to verify that existing parallel fusion
+% algorithms are just our special cases.
 %
-For example, the parallel fusion algorithm by Lempitsky et
-al.~\cite{viktor} always performs binary fusion between the current
-solution and another label, which can be achieved by setting $\alpha_i =
-1$ and $\beta_i = 0$ for all the threads. The algorithm by
-Veksler~\cite{olga} or Dejong et al.~\cite{dejong} hierarchically fuses
-solutions starting from solution proposals. The algorithm can be
-realized by setting $\alpha_i = 1, \beta_i = 0$ initially, then use
-$\alpha_i = 0, \beta_i=1$  for the rest of the algorithm.
+% For example, the parallel fusion algorithm by Lempitsky et
+% al.~\cite{viktor} always performs binary fusion between the current
+% solution and another label, which can be achieved by setting $\alpha_i =
+% 1$ and $\beta_i = 0$ for all the threads. The algorithm by
+% Veksler~\cite{olga} or Dejong et al.~\cite{dejong} hierarchically fuses
+% solutions starting from solution proposals. The algorithm can be
+% realized by setting $\alpha_i = 1, \beta_i = 0$ initially, then use
+% $\alpha_i = 0, \beta_i=1$  for the rest of the algorithm.
 
-\noindent
-We now illustrate the power of Swarm Fusion framework for three problems
-in Computer Vision.
+% \noindent
+% We now illustrate the power of Swarm Fusion framework for three problems
+% in Computer Vision.
 

### 2016-03-09 paper/stereo.tex
yasu

@@
-\section{Implementation details}
-\subsection{Stereoo}
+\section{Swarm Fusion implementations}
+We now explain detailed implementation of the Swarm Fusion method for
+three problems in Computer Vision.
+
+\subsection{Swarm Fusion stereo}
+We start with a simple Swarm Fusion implementation for a standard stereo
+problem with unary and pairwise (submodular) terms.

### 2016-03-09 paper/results.tex

\section{Experimental results} \label{section:results}

### 2016-03-09 paper/stereo.tex
yasu

@@
 \subsection{Swarm Fusion stereo}
-We start with a simple Swarm Fusion implementation for a standard stereo
-problem with unary and pairwise (submodular) terms.
+We start with a relatively ``easy'' problem, a depthmap stereo problem
+with unary and submodular pairwise terms. Parallel
+alpha-expansion~\cite{delong} or hierarchical fusion~\cite{delong,olga}
+with Graph-cuts (when submodular) or QPBO (when non-submodular) have
+been the most effective techniques.
+%
+To make the comparison simple, we restrict our proposal generation to be
+constant-label proposals, and limit to binary fusion so that Swarm
+Fusion will also use either Graph-cuts or QPBO for the core
+optimization. The main difference is that SF exchanges solutions among
+threads throughout the process.
+%
+We use Middlebury stereo datasets for the experiments. Unary terms are
+computed a standard Normalized Cross Correlation inside a $7\times 7$
+window.

### 2016-03-09 paper/stereo.tex

@@
 threads throughout the process.
+
+bottom middle example...
+
 %
 We use Middlebury stereo datasets for the experiments. Unary terms are
-computed a standard Normalized Cross Correlation inside a $7\times 7$
-window.
+computed as the average Normalized Cross Correlation score between the
+reference image and all the others inside a $7\times 7$ pixels
+window. Pairwise terms are simple Pottz model. We multiply \yasu{X
+value?} to the unary term to define the total energy.

### 2016-03-09 base/ParallelFusionPipeline.h
Hang

@@ -122,8 +122,8 @@ namespace ParallelFusion {
         //slave threads
         void workerThread(const int id,
                           const LABELSPACE& initial,
-                          const GeneratorPtr &generator,
-                          const SolverPtr& solver,
+                          GeneratorPtr generator,
+                          SolverPtr solver,
                           const ThreadOption &thread_option);
 
         inline const ParallelFusionOption &getOption() const { return option; }
@@ -181,7 +181,7 @@ namespace ParallelFusion {
         std::vector<thread_guard> slaves(option.num_threads);
         for(auto tid=0; tid<slaves.size(); ++tid){
             printf("Lauching threads %d...\n", tid);
-            std::thread t(&ParallelFusionPipeline::workerThread, this, tid, std::ref(initials[tid]), std::ref(generators[tid]), std::ref(solvers[tid]), std::ref(thread_options[tid]));
+            std::thread t(&ParallelFusionPipeline::workerThread, this, tid, std::ref(initials[tid]), generators[tid], solvers[tid], thread_options[tid]);
             slaves[tid].bind(t);
         }
     }
@@ -189,18 +189,7 @@ namespace ParallelFusion {
     template<class LABELSPACE>
     double ParallelFusionPipeline<LABELSPACE>::getBestLabeling(SolutionType<LABELSPACE> &solution) const {
         double minE = std::numeric_limits<double>::max();
-//        for(auto i=0; i<bestSolutions.size(); ++i){
-//            SolutionType<LABELSPACE> cursolution;
-//            //bestSolutions[i]->get(cursolution);
-//            if(cursolution.first < minE){
-//                solution.second.clear();
-//                solution.second.appendSpace(cursolution.second);
-//                solution.first = cursolution.first;
-//                minE = cursolution.first;
-//            }
-
         for(auto i=0; i<bestSolutions.size(); ++i){
-            SolutionType<LABELSPACE> curSolution;
             if(bestSolutions[i].getSolution().first < minE){
                 solution.second.clear();
                 solution.second.appendSpace(bestSolutions[i].getSolution().second);
@@ -214,8 +203,8 @@ namespace ParallelFusion {
     template<class LABELSPACE>
     void ParallelFusionPipeline<LABELSPACE>::workerThread(const int id,
                                                           const LABELSPACE& initial,
-                                                          const GeneratorPtr& generator,
-                                                          const SolverPtr& solver,
+                                                          GeneratorPtr generator,
+                                                          SolverPtr solver,
                                                           const ThreadOption &thread_option){
         try {
[…]

### 2016-03-09 paper/algorithm.tex

@@
  \includegraphics[width=\columnwidth]{figure/model.pdf} \caption{Swarm
- Fusion architecture and its relationships to existing methods. mention
- that hierarchical fusion works in a different way, but we can still
- consider that to be our special case, by letting each thread not using
- its own solution in the next fusion.}\label{fig:model}
+ Fusion architecture and its relationships to existing methods. The
+ bottom right diagram shows the general Swarm fusion architecture, where
+ each thread takes arbitrary number of solution proposals and concurrent
+ solutions from other threads for fusion. The left two examples at the
+ bottom row are Swarm fusion architecture with some restrictions, for
+ which we provide comparative evaluations in
+ Section~\ref{section:results}. Swarm fusion is a very flexible model,
+ and it is easy to verify that existing methods such as
+ alpha-expansion~\cite{alpha_expansion}, Fusion move~\cite{FM}, parallel
+ alpha-expansion~\cite{delong}, or hierarchical
+ fusion~\cite{delong_hierarchical_fusion,olga}, are all its special
+ cases.}\label{fig:model}
 \end{figure}

### 2016-03-09 paper/optical_flow.tex
yasu

\subsection{Swarm Fusion optical flow}

We use Swarm fusion to solve an optical flow problem, where a baseline
is a FM-based algorithm by Lempitsky et al.~\cite{viktor_optical_flow}.
Although their paper did not consider parallel implementation, it is
straightfoward to apply the concept of parallel alpha-expansion and
construct a ``parallel fusion move'' method, where multiple threads
repeat fusing two solutions via QPBO. This time, we will compare it with
our full swarm fusion model (bottom right example in
Fig.~\ref{fig:model}).

### 2016-03-09 paper/stereo.tex
yasu

--- 2016-03-09 paper/stereo.tex
@@
 \subsection{Swarm Fusion stereo}
-We start with a simple Swarm Fusion implementation for a standard stereo
-problem with unary and pairwise (submodular) terms.
+We start with a relatively ``easy'' problem, a depthmap stereo problem
+with unary and submodular pairwise terms.
+%
+We use Middlebury stereo datasets for the experiments. Unary terms are
+computed as the average Normalized Cross Correlation score between the
+reference image and the others inside a $7\times 7$ pixels
+window. Pairwise terms are simple Pottz model. Unary terms are rescaled
+by a factor of \yasu{X value?} to define the total energy.
+
+\mysubsubsubsection{Baseline methods}
+
+\noindent
+Parallel alpha-expansion~\cite{delong} or hierarchical
+fusion~\cite{delong,olga} with Graph-cuts (when submodular) or QPBO
+(when non-submodular) have been the most effective parallel techniques.
+%
+
+\mysubsubsubsection{Swarm fusion implementation}
+
+\noindent
+To make the comparison simple, we restrict our proposal generation to be
+constant-label proposals, and limit to binary fusion so that Swarm
+Fusion will also use either Graph-cuts or QPBO for the core
+optimization. Limiting to binary fusion deprived SF of multi-way fusion
+and SF architecture becomes the middle example in the bottom row of
+Fig.~\ref{fig:model}.
+%
+The advantage of SF is that threads exchange solutions throughout the
+process.

### 2016-03-09 paper/layered_depthmap.tex
yasu

@@
-\subsection{Swarm Fusion Layered Depthmap Estimation}
+\subsection{Swarm Fusion layered depthmap estimation}
+Lastly, we will evaluate Swarm fusion on a very challenging layered
+depthmap estimation problem~\cite{layered_depthmap}, which has been
+recently proposed (see the anonymized pdf in the supplementary
+material). The problem seeks to infer layered depthmap representation
+from an RGBD image, where the challenge is the massive solution space,
+which is exponential in the number of layers.~\footnote{Authors have
+proposed a novel fusion scheme, where a solution subspace instead of a
+single solution is generated by a proposal generation scheme in each
+iteration. Since a solution subspace is eqivalent to multiple solution
+proposals, their algorithm can be easily integrated into our swarm
+fusion framework.  However, competing fusion methods (e.g., fusion move
+or hierarchical fusion) cannot handle a solution subspace proposal,
+making it impossible to conduct comparative evaluations. Therefore, we
+choose to use a simple solution proposal instead of a subspace in our experiments.}
+
+\mysubsubsection{Baseline methods}
+The number of labels is extremely large (an order of 10,000 \yasu{what
+were the number of labels in our cvpr16?}), which eliminates the
+possibility of using hierarchical fusion. Therefore, we will evaluate
+fusion move and parallel fusion move algorithm as in the case of optical
+flow problem, where one solution proposal repeats being fused via QPBO.
+
+\mysubsubsection{Swarm fusion implementation}
+All the three swarm fusion methods are tested.

### 2016-03-09 paper/optical_flow.tex
yasu

@@
 
-We use Swarm fusion to solve an optical flow problem, where a baseline
-is a FM-based algorithm by Lempitsky et al.~\cite{viktor_optical_flow}.
-Although their paper did not consider parallel implementation, it is
-straightfoward to apply the concept of parallel alpha-expansion and
-construct a ``parallel fusion move'' method, where multiple threads
-repeat fusing two solutions via QPBO. This time, we will compare it with
-our full swarm fusion model (bottom right example in
+The second problem is an optical flow problem, where Lempitsky
+introduced the fusion move algorithm~\cite{viktor}. We have used the
+energy definitions and proposals generation schemes as described in the
+paper. We again use test datasets from
+Middlebury~\cite{middlebury_optical_flow}.
+
+\mysubsubsection{Baseline methods} The first baseline is the FM
+algorithm exactly as given in the paper.  Although their paper did not
+consider parallel implementation, it is straightfoward to apply the
+concept of parallel alpha-expansion. Therefore, the second baseline is
+the ``parallel fusion move'' method (replacing constant label solutions
+with proposals inside ``parallel alpha-expansion'' in
 Fig.~\ref{fig:model}).
+
+\mysubsubsection{Swarm fusion implementation}
+%The three swarm fusion models (at the bottom of Fig.~\ref{fig:model})
+%are used to evaluate the effectiveness of our method.
+The full swarm fusion model (at the bottom right in
+Fig.~\ref{fig:model}) will be used to evaluate the effectiveness of our
+method. We will also try the other two Swarm fusion variants in
+Fig.~\ref{fig:model} with restrictions.

### 2016-03-09 paper/stereo.tex
yasu

@@
-\section{Swarm Fusion implementations}
+\section{Swarm Fusion implementations} \yasu{this section is very rough
+at the moment. requires polishing. but algorithms might change as we run
+experiments.}
 We now explain detailed implementation of the Swarm Fusion method for
@@
 
-\mysubsubsubsection{Baseline methods}
+\mysubsubsection{Baseline methods}
 
@@
 
-\mysubsubsubsection{Swarm fusion implementation}
+\mysubsubsection{Swarm fusion implementation}
 

### 2016-03-09 paper/stereo.tex
yasu

@@
 We now explain detailed implementation of the Swarm Fusion method for
-three problems in Computer Vision.
+three problems in Computer Vision (See Fig.~\ref{fig:problem}).
+5
+\begin{figure}[tb]
+ \includegraphics[width=\columnwidth]{figure/problem.pdf}
+ \caption{We compare our Swarm Fusion methods against various baselines
+ on the three problems in Computer Vision.}\label{fig:problem}
+\end{figure}
 

### 2016-03-09 base/FusionSolver.h
Hang

@@ -21,7 +21,7 @@ namespace ParallelFusion {
         virtual void initSolver(const LABELSPACE & initial){}
 
         //given a solution, evaluate energy
-	virtual double evaluateEnergy(const LABELSPACE & solution) const = 0;
+        virtual double evaluateEnergy(const LABELSPACE & solution) const = 0;
     };
 }//namespace ParallelFusion
 #endif

### 2016-03-09 base/ParallelFusionPipeline.h

@@ -250,9 +250,10 @@ namespace ParallelFusion {
                 //proposal.
                 for(auto pid=0; pid < thread_option.kOtherThread; ++pid) {
                     //TODO: better thread selecting
-                    int tid = distribution(seed);
-                    while (tid == id)
-                        tid = distribution(seed);
+//                    int tid = distribution(seed);
+//                    while (tid == id)
+//                        tid = distribution(seed);
+                    int tid = (id + pid) % option.num_threads;
                     SolutionType<LABELSPACE> s;
                     //bestSolutions[tid]->get(s);
                     bestSolutions[tid].get(s);

### 2016-03-09 stereo/code/simplestereo/SimpleStereo_cli.cpp

@@ -11,6 +11,8 @@ using namespace simple_stereo;
 DEFINE_int32(resolution, 256, "resolution");
 DEFINE_int32(testFrame, 0, "reference frame");
 DEFINE_double(weight_smooth, 0.01, "smoothness weight");
+DEFINE_int32(downsample, 2, "downsample");
+
 int main(int argc, char** argv){
     if(argc < 2){
         cerr << "Usage: ./SimpleStereo <path-to-data>" << endl;
@@ -21,7 +23,7 @@ int main(int argc, char** argv){
     google::ParseCommandLineFlags(&argc, &argv, true);
 
     FileIO file_io(argv[1]);
-    SimpleStereo stereo(file_io, FLAGS_testFrame, FLAGS_resolution, FLAGS_weight_smooth);
+    SimpleStereo stereo(file_io, FLAGS_testFrame, FLAGS_resolution, FLAGS_downsample, FLAGS_weight_smooth);
     stereo.runStereo();
     return 0;
 }

### 2016-03-09 stereo/code/simplestereo/optimization_parallel.cpp

@@ -17,9 +17,9 @@ namespace simple_stereo {
         result.initialize(width, height, -1);
         //configure as sequential fusion
         ParallelFusionOption pipelineOption;
-        pipelineOption.num_threads = 7;
+        pipelineOption.num_threads = 1;
         pipelineOption.max_iteration = 1;
-        const int kLabelPerThread = model.nLabel / pipelineOption.num_threads;
+        const int kLabelPerThread = model->nLabel / pipelineOption.num_threads;
 
         Pipeline::GeneratorSet generators((size_t)pipelineOption.num_threads);
         Pipeline::SolverSet solvers((size_t)pipelineOption.num_threads);
@@ -27,9 +27,9 @@ namespace simple_stereo {
         vector<ThreadOption> threadOptions((size_t)pipelineOption.num_threads);
         for(auto& to: threadOptions){
             to.kOtherThread = 0;
-            to.kSelfThread = 40;
+            to.kSelfThread = 256;
         }
-        const int kPix = model.width * model.height;
+        const int kPix = model->width * model->height;
 
         for(auto i=0; i<pipelineOption.num_threads; ++i){
             const int startid = i * kLabelPerThread;
@@ -37,8 +37,8 @@ namespace simple_stereo {
 
             initials[i].init(kPix, vector<int>(1, startid));
             printf("Thread %d, start: %d, end: %d\n", i, startid, endid);
-            generators[i] = shared_ptr<ProposalGenerator<Space> >(new SimpleStereoGenerator(model.width * model.height, startid, endid));
-            solvers[i] = shared_ptr<FusionSolver<Space> >(new SimpleStereoSolver(&model));
+            generators[i] = shared_ptr<ProposalGenerator<Space> >(new SimpleStereoGenerator(model->width * model->height, startid, endid));
+            solvers[i] = shared_ptr<FusionSolver<Space> >(new SimpleStereoSolver(model));
             printf("Initial energy on thread %d: %.5f\n", i, solvers[i]->evaluateEnergy(initials[i]));
         }
 
@@ -53,7 +53,7 @@ namespace simple_stereo {
         parallelFusionPipeline.getBestLabeling(solution);
         printf("Done! Final energy: %.5f, running time: %.3f\n", solution.first, t);
 
-        for(auto i=0; i<model.width * model.height; ++i){
+        for(auto i=0; i<model->width * model->height; ++i){
             result.setDepthAtInd(i, solution.second(i,0));
[…]

### 2016-03-09 paper/algorithm.tex
yasu

--- 2016-03-09 paper/algorithm.tex
@@
 Multi-way Particle Swarm Fusion is a natural extension of Fusion Move
-method (FM). We call our method Swarm Fusion (SF) in short. Take a
-multi-threading environment to explain our idea, while the technique is
-also applicable to other parallel programming model such as {\it
+method (FM). We call our method Swarm Fusion (SF) in short. Let us take
+a multi-threading environment to explain our idea, while the technique
+is also applicable to other parallel programming model such as {\it
 MapReduce} in cloud computing.
@@
 proposals, and 2) a {\it solution pool}, from which we pick arbitrary
-number of intermediate solutions generated by all the other threads.
+number of intermediate solutions generated by the other threads.
 %
@@
 % fused by the threads.
-In our base configuration, the solution pool only remembers one (the
-best) solution generated by each thread.
+In our base configuration, the solution pool only remembers the solution
+from each thread.
 
@@
 fusion step, the thread collects $\alpha_i$ solution proposals from the
-proposal pool and $\beta_i$ solutions from the solution pool, following
-a user-defined strategy or at random to be simple.
+proposal pool and $\beta_i$ solutions from the solution pool, based on a
+user-defined strategy or at random to be simple.
 %
@@
  \includegraphics[width=\columnwidth]{figure/model.pdf} \caption{Swarm
- Fusion architecture and its relationships to existing methods. mention
- that hierarchical fusion works in a different way, but we can still
- consider that to be our special case, by letting each thread not using
- its own solution in the next fusion.}\label{fig:model}
+ Fusion architecture and its relationships to existing methods. The
+ bottom right example shows the general Swarm fusion architecture, where
+ each thread takes arbitrary number of solution proposals and concurrent
+ solutions from other threads for fusion. The framework is flexible and
+ can realize other data processing architectures depending on the parameters.
+ %
+ % The left two examples at the
+ % bottom row are other Swarm fusion architectures with some restrictions,
+ % for which we provide comparative evaluations in
+ % Section~\ref{section:results}.
+ %
+ The left two examples at the bottom are other Swarm fusion
+ architectures with some restrictions, to be used for evaluations later.
+ %
+ It is also easy to verify that existing methods such as
+ alpha-expansion~\cite{alpha_expansion}, Fusion move~\cite{FM}, parallel
+ alpha-expansion~\cite{delong}, or hierarchical
+ fusion~\cite{delong_hierarchical_fusion,olga}, are all special
+ cases of the Swarm fusion.}\label{fig:model}
 \end{figure}
 %
-The bottom right configuration is the most general one, in which we
-always fuse some solution proposals and some concurrent solutions
-(i.e., $\alpha\ne 0, \beta \ne 0$).
+The bottom right architecture is the most general one, in which we
+always fuse some solution proposals and some concurrent solutions (i.e.,
+$\alpha\ne 0, \beta \ne 0$).
 %
@@
 we use TRW~\cite{kolmogorov} for the fusion, while any other compatible
-inference techniques can be used~\cite{opengm}. Of course, if one knows
-that a certain fusion step is a binary fusion with submodular energy,
-one can use graph-cuts instead~\cite{alpha_expansion_paper}. If a
+inference techniques can be used~\cite{opengm}. For instance, if one
+knows that a certain fusion step is a binary fusion with submodular
+energy, one can use graph-cuts~\cite{alpha_expansion_paper}. If a
 certain fusion step is a binary fusion with non-submodular energy, one
@@
 
-\mysubsubsubsection{Relationships to existing methods}
+\mysubsubsection{Relationships to existing methods}
 
@@
 (HF)~\cite{delong_hierarchical,olga} are all special cases of the Swarm
-Fusion method.~\footnote{The hierarchical fusion has a slightly
-different data processing model, without strong ties between threads
-data, but this can be considered as a special case of SF by not using
-$S_i$ in each fusion step of $T_i$.} For example, AE can be realized by
-setting $\alpha=1, \beta=0$ and restricting the proposal generation to
-constant labels with a single thread. Same goes for FM, this time,
-without the restriction on the proposal generation scheme. PAE is
-realized by setting $\alpha=1,\beta=1$ with multiple threads, again with
-a restriction on the proposal generation scheme. The last sequential
-fusion (at the top of the diagram in the figure) can be modeled by
-changing to $\alpha=0, \beta=1$ with a single thread.
+Fusion method. AE can be realized by setting $(\alpha=1, \beta=0)$ and
+restricting the proposal generation to constant labels with a single
+thread. Same goes for FM, this time, without the restriction on the
+proposal generation scheme. PAE is realized by setting
+$(\alpha=1,\beta=1)$ with multiple threads, again with a restriction on
+the proposal generation scheme (the last sequential fusion in PAE is
+realized by $(\alpha=0, \beta=1)$ with a single thread).
+%
+% The last sequential fusion (at the top of the example in the figure) can
+% be modeled by changing to $\alpha=0, \beta=1$ with a single thread.
+HF has a slightly different data processing model, without strong ties
+between threads and data, but can be realized by setting ($\alpha=2,
+\beta=0$) at the bottom level and ($\alpha=0, \beta=2$) at the remaining
+levels, while allowing $S_i$ not to be used in the fusion steps of
+$T_i$.
 

### 2016-03-10 stereo/code/simplestereo/optimization_parallel.cpp
Hang

@@ -86,6 +86,9 @@ namespace simple_stereo {
                                                                                 const_cast<int*>(model->vCue)));
         mrf = new Expansion(model->width, model->height, model->nLabel, energy_function);
         mrf->initialize();
+
+//        qpbo = new kolmogorov::qpbo::QPBO<int>(kPix, 2 * kPix);
+//        qpbo->AddNode(kPix);
     }
 
     void SimpleStereoSolver::solve(const CompactLabelSpace &proposals,
@@ -114,9 +117,8 @@ namespace simple_stereo {
         for (auto i = 0; i < kFullProposal; ++i) {
             //run QPBO
             //printf("Running QPBO...\n");
-            kolmogorov::qpbo::QPBO<int> qpbo(kPix, 2 * kPix);
+            kolmogorov::qpbo::QPBO<int> qpbo(kPix, kPix*2);
             qpbo.AddNode(kPix);
-
             for (auto j = 0; j < kPix; ++j) {
                 qpbo.AddUnaryTerm(j, model->operator()(j, solution.second(j, 0)),
                                   model->operator()(j, proposals(j, i)));

### 2016-03-10 stereo/code/simplestereo/simplestereo.cpp

@@ -77,8 +77,8 @@ namespace simple_stereo {
                         //project onto other views and compute matching cost
                         vector<vector<double>> patches(images.size());
                         for (auto v = 0; v < images.size(); ++v) {
-                            double distance = (double) (v - anchor) * (double)d / downsample;
-                            Vector2d imgpt(x - distance, y);
+                            double distance = (double) (v - anchor) * (double)d / downsample / 5;
+                            Vector2d imgpt(x + distance, y);
                             local_matcher::samplePatch(images[v], imgpt, 3, patches[v]);
                         }
                         double mCost = local_matcher::sumMatchingCost(patches, anchor);

### 2016-03-10 paper/stereo.tex

--- 2016-03-09 paper/stereo.tex
@@
-\section{Swarm Fusion implementations} \yasu{this section is very rough
-at the moment. requires polishing. but algorithms might change as we run
-experiments.}
-We now explain detailed implementation of the Swarm Fusion method for
-three problems in Computer Vision.
+\section{Swarm Fusion implementations}
+We compare our Swarm fusion methods against competing approaches over three
+problems in Computer Vision. The SF architecture has high degrees of
+freedom and the challenge is to properly quantity the contribution of
+various algorithmic aspects. For this purpose, we carefully design the
+SF architecture for each problem independently, sometimes limiting the
+capabilities on purpose, to enable effective and fair comparative evaluation.
+We now explain the details of the three problems.
+
+% We pick three representative problems in Computer Vision to evaluate the
+% effectiveness of the Fusion swarm methods against existing methods. We
+% control the SF architectures for each problem independently to make
+% compa
+%
+%\yasu{this section is very rough at the moment. requires polishing. but
+%algorithms might change as we run experiments.}  We now explain detailed
+%implementation of the Swarm Fusion method for three problems in Computer
+%Vision (See Fig.~\ref{fig:problem}).  5
+\begin{figure}[tb]
+ \includegraphics[width=\columnwidth]{figure/problem.pdf} \caption{We
+ compare our Swarm Fusion methods against various baselines on a
+ depthmap stereo~\cite{middle_bury_stereo}, an optical
+ flow~\cite{middlebury_optical_flow}, or a layered depthmap
+ estimation~\cite{layered_depthmap} problem.  }\label{fig:problem}
+\end{figure}
 
 \subsection{Swarm Fusion stereo}
-We start with a relatively ``easy'' problem, a depthmap stereo problem
-with unary and submodular pairwise terms.
+We start with a simple depthmap stereo problem with standard unary and
+submodular pairwise terms. Unary terms are computed as the average
+Normalized Cross Correlation score between the reference image and the
+others inside a $7\times 7$ pixels window. Pairwise terms are simple
+Pottz model. The total energy is defined by the sum of the two, while
+the pairwise term is scaled by a factor of \yasu{X value}.
 %
-We use Middlebury stereo datasets for the experiments. Unary terms are
-computed as the average Normalized Cross Correlation score between the
-reference image and the others inside a $7\times 7$ pixels
-window. Pairwise terms are simple Pottz model. Unary terms are rescaled
-by a factor of \yasu{X value?} to define the total energy.
+We use Middlebury stereo datasets for the experiments.
 

### 2016-03-10 base/ParallelFusionPipeline.h
minor changes

@@ -23,7 +23,7 @@
 namespace ParallelFusion {
 
     //synchronized solution type
-    template<class LABELSPACE>
+  template<class LABELSPACE>
     class SynSolution {
     public:
         SynSolution(): solution(SolutionType<LABELSPACE>(-1, LABELSPACE())){}
@@ -263,7 +263,7 @@ namespace ParallelFusion {
                         bestSolutions[tid].get(s);
                         proposals.appendSpace(s.second);
 
-                        write_flag[tid].store(true);
+                        //write_flag[tid].store(true);
                     }
                 } else if (option.selectionMethod == ParallelFusionOption::RANDOM) {
                     for(auto pid=0; pid < thread_option.kOtherThread; ++pid) {
@@ -304,7 +304,7 @@ namespace ParallelFusion {
                 //set the current best solution. It will be visible from other threads
                 bestSolutions[id].set(curSolution);
 
-                if(!thread_option.is_monitor && option.synchronize)
+                if(!thread_option.is_monitor)
                     write_flag[id].store(false);
 
                 //double diffE =  lastEnergy - curSolution.first;

### 2016-03-10 paper/layered_depthmap.tex
yasu

@@
 
-\mysubsubsection{Baseline methods}
+\mysubsubsection{Competing methods}
 The number of labels is extremely large (an order of 10,000 \yasu{what
@@
 
-\mysubsubsection{Swarm fusion implementation}
+\mysubsubsection{Swarm fusion architecture}
 All the three swarm fusion methods are tested.

### 2016-03-10 paper/stereo.tex
yasu

@@
 \section{Swarm Fusion implementations}
-We compare our Swarm fusion methods against competing approaches over three
-problems in Computer Vision. The SF architecture has high degrees of
-freedom and the challenge is to properly quantity the contribution of
+We compare our Swarm fusion methods against competing approaches over
+three problems in Computer Vision. The SF architecture has high degrees
+of freedom and the challenge is to properly quantity the contribution of
 various algorithmic aspects. For this purpose, we carefully design the
 SF architecture for each problem independently, sometimes limiting the
-capabilities on purpose, to enable effective and fair comparative evaluation.
-We now explain the details of the three problems.
+capabilities on purpose, to enable effective and fair comparative
+evaluation.  We now explain the details of the three problems.
 
@@
  \includegraphics[width=\columnwidth]{figure/problem.pdf} \caption{We
- compare our Swarm Fusion methods against various baselines on a
+ compare our Swarm Fusion methods against competing approaches on a
  depthmap stereo~\cite{middle_bury_stereo}, an optical
  flow~\cite{middlebury_optical_flow}, or a layered depthmap
- estimation~\cite{layered_depthmap} problem.  }\label{fig:problem}
+ estimation~\cite{layered_depthmap} problem. In the layered depthmap
+ problem, the input is an RGBD image, and the output is multiple layeres
+ of depthmaps. Each layer is a piecewise smooth parametric surface
+ model.}\label{fig:problem}
 \end{figure}
@@
 We start with a simple depthmap stereo problem with standard unary and
-submodular pairwise terms. Unary terms are computed as the average
-Normalized Cross Correlation score between the reference image and the
-others inside a $7\times 7$ pixels window. Pairwise terms are simple
-Pottz model. The total energy is defined by the sum of the two, while
-the pairwise term is scaled by a factor of \yasu{X value}.
+pairwise terms. We employ submodular pairwise terms to make this stereo
+represent relatively ``easy'' MRF inference problems.
+%
+Unary terms are computed as the average Normalized Cross Correlation
+score between the reference image and the others inside a $7\times 7$
+pixels window. Pairwise terms are simple Pottz model. The total energy
+is defined by the sum of the two, while scaling the pairwise term by a
+factor of \yasu{X value}.
 %
@@
 
-\mysubsubsection{Baseline methods}
+\mysubsubsection{Competing methods}
 
-\noindent
-Parallel alpha-expansion~\cite{delong} or hierarchical
-fusion~\cite{delong,olga} with Graph-cuts (when submodular) or QPBO
-(when non-submodular) have been the most effective parallel techniques.
-%
+\noindent The sophistication of photometric consistency
+function~\cite{mvs_furukawa_survey} makes unary terms dominant in most
+stereo problems.  Our experiments have also supported this, where the
+fusion method (i.e., the use of proposal generation) rather makes it slow
+due to the overhead.  Therefore, we pick parallel
+alpha-expansion~\cite{delong} and hierarchical fusion~\cite{delong,olga}
+with graph-cuts optimization as the competing methods.
 
-\mysubsubsection{Swarm fusion implementation}
+\mysubsubsection{Swarm fusion architecture}
 
-\noindent
-To make the comparison simple, we restrict our proposal generation to be
-constant-label proposals, and limit to binary fusion so that Swarm
-Fusion will also use either Graph-cuts or QPBO for the core
-optimization. Limiting to binary fusion deprived SF of multi-way fusion
-and SF architecture becomes the middle example in the bottom row of
-Fig.~\ref{fig:model}.
-%
-The advantage of SF is that threads exchange solutions throughout the
-process.
+\noindent To make the comparison simple, we restrict our proposal
+generation to be constant-label proposals, and limit to binary fusion
+(i.e., without multi-way fusion). Graph-cuts is used in fusing a
+constant-label proposal as the energy is submodular. QPBO is used in
+fusing a different solution from another thread as the energy is
+non-submodular.  Due to the lack of multi-way fusion, the swarm fusion
+architecture for the stereo problem is represented by the middle
+example at the bottom of Fig.~\ref{fig:model}.

### 2016-03-10 paper/abstract.tex
yasu

@@
 \begin{abstract}
-\yasu{must be at least 70 and at most 150 words.}
-\keywords{A; B; C.}
+This paper proposes a novel MAP inference framework for Markov Random
+Field (MRF) problems in parallel computing environments.  The inference
+framework, dubbed Swarm Fusion method, is a natural generalization of
+Fusion Move method for parallel computation. Every thread (in a case of
+multi-threading environment) maintains and updates a solution. At every
+iteration, each thread can generate arbitrary number of solution
+proposals and take arbitrary number of concurrent solutions from the
+other threads to perform multi-way fusion in updating its solution. The
+framework is general, making popular existing inference techniques such
+as alpha-expansion, fusion move, parallel alpha-expansion, or
+hierarchical fusion, its special cases. We have evaluated the approach
+against competing methods on stereo, optical flow, and layered depthmap
+estimation problems. Our experiments have shown that the Swarm Fusion
+method exploits the parallel computing resources and become effective
+especially for challenging problems.
+%\yasu{must be at least 70 and at most 150 words.}
+\keywords{MRF; Fusion Move; Particle Swarm Optimization}
 \end{abstract}

### 2016-03-10 paper/layered_depthmap.tex
yasu

--- 2016-03-08 paper/layered_depthmap.tex
@@
-\subsection{Swarm Fusion Layered Depthmap Estimation}
+\subsection{Swarm Fusion layered depthmap estimation}
+Our last problem is layered depthmap estimation, recently proposed
+in~\cite{layered_depthmap} (see the anonymious paper in the
+supplementary material).  The problem seeks to infer layered depthmap
+representation from an RGBD image, where each layer is a piecewise
+smooth segmented depthmap. This is essentially a multi-layer extension
+of Surface Stereo algorithm~\cite{surface_stereo}.
+%
+Layered depthmap estimation is one of the most difficult kinds for MAP
+inference due to its massive solution space, where the number of labels
+per pixel is exponential in the number of layers. In practice, each
+pixel might take an order of 100,000 \yasu{is this number correc?}
+possible labels. We copy their problem formulation and the proposal
+generation schemes.~\footnote{Authors have proposed a novel fusion scheme,
+where a solution subspace instead of a single solution is generated by a
+proposal generation scheme. Since a solution subspace is equivalent to
+multiple solution proposals, their algorithm can be easily integrated
+into our swarm fusion framework.  However, competing fusion methods
+(e.g., Parallel Fusion Move or Hierarchical Fusion) cannot handle a
+solution subspace proposal, making it impossible to conduct fair
+comparative evaluations. We choose to use a simple solution proposal for
+experiments in this paper.}
+%Lastly, we will evaluate Swarm fusion on a very challenging layered
+%depthmap estimation problem~\cite{layered_depthmap}, which has been
+%recently proposed (see the anonymized pdf in the supplementary
+%material).
+
+\mysubsubsection{Competing methods}
+
+Solution proposals depend heavily on the current solution, eliminating
+the possibility of using hierarchical approach, which needs to enumerate
+all the proposals to start. Therefore, the only viable competing method
+is Parallel Fusion Move, that replaces constant label solutions by
+solution proposals in parallel alpha-expansion framework. We will also
+evaluate the standard Fusion Move method.
+%
+The fusions are binary, for which we use QPBO.
+
+%The number of labels is extremely large (an order of 10,000 \yasu{what
+%were the number of labels in our cvpr16?}), which eliminates the
+%possibility of using hierarchical fusion. Therefore, we will evaluate
+%fusion move and parallel fusion move algorithm as in the case of optical
+%flow problem, where one solution proposal repeats being fused via QPBO.
+
+\mysubsubsection{Swarm fusion architecture}
+The three swarm architectures in Fig.~\ref{fig:model} are evaluated. The
+fusions are multi-way, for which we use TRW-S.

### 2016-03-10 paper/optical_flow.tex
yasu

--- 2016-03-09 paper/optical_flow.tex
@@
 
-We use Swarm fusion to solve an optical flow problem, where a baseline
-is a FM-based algorithm by Lempitsky et al.~\cite{viktor_optical_flow}.
-Although their paper did not consider parallel implementation, it is
-straightfoward to apply the concept of parallel alpha-expansion and
-construct a ``parallel fusion move'' method, where multiple threads
-repeat fusing two solutions via QPBO. This time, we will compare it with
-our full swarm fusion model (bottom right example in
-Fig.~\ref{fig:model}).
+Fusion Move was first introduced by Lempitsky et al.~\cite{viktor} to
+solve optical flow problem.
+%Optical flow was the problem, in which the Fusion Move method was first
+%introduced by Lempitsky et al.~\cite{viktor}.
+We copy their problem setting and fusion proposal schemes for our second
+problem.  We again use test images in the Middlebury optical flow
+benchmark~\cite{middlebury_optical_flow}.
+
+\mysubsubsection{Competing methods} Fusion Move method in their paper is
+the first natural contender. While they did not consider parallel
+implementation, it is straightforward to combine the idea of parallel
+alpha-expansion and Fusion Move. Then, the second competing method is
+``parallel fusion move'', where each thread repeats generating a
+solution proposal and fusing it to the current solution. Final solutions
+from all the results are sequentially fused to obtain the final solution
+as in the parallel alpha-expansion method. In Fig.~\ref{fig:model}, this
+computational framework corresponds to ``parallel alpha-expansion'' with
+the label solutions replaced by solution proposals. The last contender
+is the mix of the hierarchical fusion and the fusion move method, dubbed
+``hierarchical fusion method'', where they start from solution proposals
+as opposed to constant labels.
+%
+The fusions are binary, for which we use QPBO.
+
+\mysubsubsection{Swarm fusion architecture}
+%The three swarm fusion models (at the bottom of Fig.~\ref{fig:model})
+%are used to evaluate the effectiveness of our method.
+The three swarm architectures in Fig.~\ref{fig:model} will be evaluated
+against the competing methods. Note that we use the same set of proposal
+generation schemes. The fusions are multi-way, for which we ues TRW-S.
+
+% The full swarm fusion model (at the bottom right in
+% Fig.~\ref{fig:model}) will be used to evaluate the effectiveness of our
+% method. We will also try the other two Swarm fusion variants in
+% Fig.~\ref{fig:model} with restrictions.

### 2016-03-10 paper/conclusion.tex
yasu

\section{Conclusion and future direction}
We have proposed a novel MAP inference framework, Swarm Fusion, for MRF
problems in parallel computing environments. The framework is general,
and we showed that most popular inference techniques such as
alpha-expansion, Fusion Move, parallel alpha-expansion, or hierarchical
fusion, are its special cases. Our experiments have revealed that the
framework exploits parallel computational resources and achieves faster
convergence, epseically for challenging problems.  Our first future work
is to conduct experiments on cloud computing environments, in
particular, the MapReduce programming model, where the roles of mappers
and reducers exactly correspond to the processes of parallel multi-way
fusion and solution exchanges, respectively.  Another future work is the
automatic configuration of the Swarm Fusion architecture. Due to its
vast degrees of freedom, one needs to currently hand-tune the
architecture for the optical performance. An interesting direction is to
adaptively change its architecture during the computation, for example,
switching to simple parallel alpha-expansion for easy problems, or
increasing the rate of solution exchanges when solutions vary
significantly across threads.
%
Parallel MAP inference has been a relatively under-explored topic in
Computer Vsion. Our idea is very simple and adapting the Swarm Fusion
framework require minimal coding. We believe that this paper has a
potential to immediately benefit tens of thousands of Computer Vision
researchers or engineers in the world, who currently solve MRF problems
with conventional solvers. We will share our source code and the
datasets with the community.

### 2016-03-10 paper/conclusion.tex
yasu

@@
-\section{Conclusion and future direction}
+\section{Conclusion and future directions}
 We have proposed a novel MAP inference framework, Swarm Fusion, for MRF

### 2016-03-10 paper/stereo.tex
yasu

@@
-\section{Swarm Fusion implementations}
+\section{Swarm Fusion implementations \yasu{I don't like this title..}}
 We compare our Swarm fusion methods against competing approaches over
@@
 
-\mysubsubsection{Swarm fusion architecture}
+\mysubsubsection{Swarm fusion architectures}
 

### 2016-03-10 paper/results.tex
yasu

@@
 \section{Experimental results} \label{section:results}
+We have implemented the algorithms in C++ and conducted the experiments
+on Linux PCs with Intel Core i7 processor with 4 cores, enabling 8 threads
+with the hyper threading technology. We have used the Graph-cuts
+optimization code written by Veksler, using the libraries provided by
+Boykov and Kolmogorov~\cite{middle_bury,2,3,4_below}.
+% [2] Fast Approximate Energy Minimization via Graph Cuts.
+%         Y. Boykov, O. Veksler, and R. Zabih.
+%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
+%         (PAMI), vol. 23, no. 11, pages 1222-1239, November 2001.  
+%
+%     [3] What Energy Functions can be Minimized via Graph Cuts?
+%         V. Kolmogorov and R. Zabih. 
+%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
+%         (PAMI), vol. 26, no. 2, pages 147-159, February 2004. 
+%         An earlier version appeared in European Conference on Computer
+%         Vision (ECCV), May 2002.
+%
+%     [4] An Experimental Comparison of Min-Cut/Max-Flow Algorithms for
+%         Energy Minimization in Vision. 
+%         Y. Boykov and Vladimir Kolmogorov.
+%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
+%         (PAMI), vol. 26, no. 9, pages 1124-1137, September 2004. 
+We have used the QPBO and TRW-S implementations by
+Kolmogorov~\cite{msr_link?,trw_link}.
+
+\begin{figure}[tb]
+ \includegraphics[width=\columnwidth]{figure/result_layered_depthmap.pdf}
+ \caption{}\label{fig:result_layered_depthmap}
+\end{figure}

### 2016-03-10 OpticalFlow/main.cpp
solution exchange interval

@@ -27,9 +27,11 @@ DEFINE_bool(evaluation, false, "Write log file or not.");
 //DEFINE_string(dataset_category, "other-data", "The dataset image category.");
 
 DEFINE_int32(num_threads, 2, "The number of threads.");
-DEFINE_int32(num_iterations, 10, "The number of iterations.");
-DEFINE_int32(num_proposals_from_self, 1, "The number of proposals from self.");
-DEFINE_int32(num_proposals_from_others, 1, "The number of proposals from others.");
+DEFINE_int32(num_iterations, 30, "The number of iterations.");
+
+DEFINE_int32(num_proposals_in_total, 1, "The number of proposals in total.");
+DEFINE_int32(num_proposals_from_others, 0, "The number of proposals from others.");
+DEFINE_int32(solution_exchange_interval, 3, "The number of iterations between consecutive solution exchanges.");
 
 using namespace std;
 using namespace cv;
@@ -96,8 +98,10 @@ int main(int argc, char *argv[])
     solvers[i] = shared_ptr<ParallelFusion::FusionSolver<LABELSPACE> >(new OpticalFlowFusionSolver(image_1, image_2));
     initials[i].setSingleLabels(vector<pair<double, double> >(IMAGE_WIDTH * IMAGE_HEIGHT));
     
-    thread_options[i].kSelfThread = FLAGS_num_proposals_from_self;
+    thread_options[i].kTotal = FLAGS_num_proposals_in_total;
     thread_options[i].kOtherThread = FLAGS_num_proposals_from_others;
+    thread_options[i].solution_exchange_interval = FLAGS_solution_exchange_interval;
+    
     // if (i == option.num_threads - 1 && false) {
     //   thread_options[i].kSelfThread = 0;
     //   thread_options[i].kOtherThread = 4;

### 2016-03-10 paper/introduction.tex
yasu

@@
 in a cloud.
+%
+In the recent work on Go (AlphaGo from DeepMind), parallelization plays
+a key role in the Monte-Carlo tree search~\cite{nature_alpha_go}.
 
@@
 %
+%
 However, state-of-the-art algorithms are still inherently sequential in
@@
 It sequentially improves solution by fusing the current solution with a
-solution proposal. FM allows domain-specific customization of proposal
-generation schemes, a main advantage over general solvers such as
-message passing algorithms~\cite{TRW,loopy_belief_propagation}.  Its
-successful applications range from optical flow, stereo, image
-denoising, image inpainting, to image
+solution proposal. Its successful applications range from optical flow,
+stereo, image denoising, image inpainting, to image
 segmentation~\cite{fusion_moves_for_markov_random_field_optimization}.
@@
 %mentioning GPU and its relation to our approach}
+
+%1. In the introduction, we could mention the recent work on Go (DeepMind's AlphaGo Nature paper) in which parallization plays a key role in the monte carlo search.
+
+%2. Yasu, your explanation of the advantages of Fusion Move (described in
+%section 2) is correct. In the sentence on "Second, FM can handle
+%problems with very large label spaces.." we could add "and even
+%real-valued variables".
+
+3. I would suggest removing "Genetic algorithms" from the paragraph heading at the end of section 2 or replacing it with "Evolutionary Algorithm".
+
+4. We should cite two more papers
+(a) Hierarchical Graph cuts (Kumar and Koller, UAI 2009)
+(b) Making the right move (Batra and Kohli, CVPR 2010)

### 2016-03-10 base/HFusionPipeline.h
Hang

@@ -7,8 +7,14 @@
 #include "LabelSpace.h"
 #include "ProposalGenerator.h"
 #include "FusionSolver.h"
-
 namespace ParallelFusion{
+
+    template<typename T>
+    class BinaryTree{
+    private:
+
+    };
+
 
     struct HFusionPipelineOption{
     public:

### 2016-03-10 base/ParallelFusionPipeline.h

@@ -15,20 +15,26 @@
 //#include "cv_utils/cv_utils.h"
 #include "FusionSolver.h"
 #include "thread_guard.h"
-#include <mutex>
 #include "LabelSpace.h"
 #include "ProposalGenerator.h"
+#include <list>
+#include <mutex>
+#include <opencv2/opencv.hpp>
+
 
 
 namespace ParallelFusion {
 
+    //type for energy observation: <time, energy>
+    using Observation = std::pair<double, double>;
+
     //synchronized solution type
-  template<class LABELSPACE>
+    template<class LABELSPACE>
     class SynSolution {
     public:
         SynSolution(): solution(SolutionType<LABELSPACE>(-1, LABELSPACE())){}
         void set(const SolutionType<LABELSPACE> &l) {
-	  std::lock_guard<std::mutex> lock(mt);
+            std::lock_guard<std::mutex> lock(mt);
             solution = l;
         }
 
@@ -79,32 +85,32 @@ namespace ParallelFusion {
 //    };
 
     struct ParallelFusionOption {
-    ParallelFusionOption() : convergeThreshold(0.01), max_iteration(10), num_threads(6), synchronize(false), selectionMethod(RANDOM){ }
-      //Addition method: how add two proposals. APPEND: simply append; UNION: take union, remove duplicate labels
+        ParallelFusionOption() : convergeThreshold(0.01), max_iteration(10), num_threads(6), synchronize(false), selectionMethod(RANDOM){ }
+        //Addition method: how add two proposals. APPEND: simply append; UNION: take union, remove duplicate labels
         double convergeThreshold;
         int max_iteration;
         int num_threads;
-      bool synchronize;
+        bool synchronize;
 
-      
-      enum SolutionSelection{RANDOM, BEST};
+
+        enum SolutionSelection{RANDOM, BEST};
         SolutionSelection selectionMethod;
     };
 
     struct ThreadOption {
-    ThreadOption() : kTotal(1), kOtherThread(0), solution_exchange_interval(1), is_monitor(false) { }
+        ThreadOption() : kTotal(1), kOtherThread(0), solution_exchange_interval(1), is_monitor(false) { }
         int kTotal;
-      int kOtherThread;
-      int solution_exchange_interval;
+        int kOtherThread;
+        int solution_exchange_interval;
         bool is_monitor;
     };
 
     template<class LABELSPACE>
-      class ParallelFusionPipeline {
+    class ParallelFusionPipeline {
     public:
[…]

### 2016-03-10 paper/related_work.tex

@@
 FM has two main advantages over the other general inference
-techniques~\cite{trw,loopy_belief_propagation}. \yasu{Pushmeet, is this
-correct? Am not confident to say this?} First, FM allows us to exploit
-domain-specific knowledge in customizing proposal generation
-schemes. Second, FM can handle problems with very large label spaces,
-because the core optimization just solves a binary decision problem. In
-contrast, methods like message passing algorithms need to maintain
+techniques~\cite{trw,loopy_belief_propagation}. First, FM allows us to
+exploit domain-specific knowledge in customizing proposal generation
+schemes. Second, FM can handle problems with very large label spaces
+(and even real-values variables), because the core optimization just
+solves a binary decision problem.
+
+In contrast, methods like message passing algorithms need to maintain
 messages and beliefs for the entire label space all the time.
@@
 
-\mysubsubsection{Genetic algorithms and Particle Swarm Optimization}
+\mysubsubsection{Evolutionary algorithms and Particle Swarm Optimization}
 

### 2016-03-10 paper/stereo.tex
yasu

@@
 
-\noindent To make the comparison simple, we restrict our proposal
-generation to be constant-label proposals, and limit to binary fusion
-(i.e., without multi-way fusion). Graph-cuts is used in fusing a
-constant-label proposal as the energy is submodular. QPBO is used in
+\noindent The three swarm architectures in Fig.~\ref{fig:model} have
+been evaluated: SFWSS (SF without solution sharing), SFWMF (SF without
+multi-way fusion), and the standard SF.
+%
+For SFWSS, we have chosen $\alpha=2$ ($\beta=0$). For SFWMF, each thread
+iterates the step of ($\alpha=1, \beta=0$) or ($\alpha=0, \beta=1$) so
+that it can take a solution proposal in one step and a neighboring
+solution in the next. For the standard SF, we have used ($\alpha=1, \beta=1$).
+%
+%
+%
+%
+To make the comparison simple, we restrict our proposal
+generation to be constant-label proposals. Graph-cuts is used in fusing
+a constant-label proposal as the energy is submodular. QPBO is used in
 fusing a different solution from another thread as the energy is
-non-submodular.  Due to the lack of multi-way fusion, the swarm fusion
-architecture for the stereo problem is represented by the middle
-example at the bottom of Fig.~\ref{fig:model}.
+non-submodular.
+%
+% Due to the lack of multi-way fusion, the swarm fusion architecture for
+% the stereo problem is represented by the middle example at the bottom of
+% Fig.~\ref{fig:model}.

### 2016-03-10 base/HFusionPipeline.h
Hang

@@ -7,12 +7,40 @@
 #include "LabelSpace.h"
 #include "ProposalGenerator.h"
 #include "FusionSolver.h"
+#include "pipeline_util.h"
+
 namespace ParallelFusion{
 
     template<typename T>
     class BinaryTree{
-    private:
+    public:
+        struct Node{
+            Node(): data(NULL), lchild(NULL), rchild(NULL), parent(NULL), flag(false){}
+            std::shared_ptr<T> data;
+            std::shared_ptr<Node> lchild;
+            std::shared_ptr<Node> rchild;
+            std::shared_ptr<Node> parent;
+            //in HFusion, flag indicates whether this node contains data
+            bool flag;
+        };
 
+        BinaryTree(const BinaryTree& t2){
+            root = t2.getRoot();
+        }
+
+        BinaryTree(const std::shared_ptr<Node> r2){
+            root = r2;
+        }
+
+        void buildFromLeafData(const std::vector<T>& leafData);
+
+        void buildFromLeafNodes(const std::vector<std::shared_ptr<Node> >& leafNodes);
+
+        inline const std::shared_ptr<Node> getRoot()const{
+            return root;
+        }
+    private:
+        std::shared_ptr<Node> root;
     };
 
 
@@ -30,6 +58,30 @@ namespace ParallelFusion{
     private:
         HFusionPipelineOption option;
     };
+
+    /////////////////////////////////////////////////////////////
+    template<typename T>
+    void BinaryTree<T>::buildFromLeafData(const std::vector<T>& leafData){
+        std::vector<std::shared_ptr<Node> > leafNodes(leafData.size(), new Node());
+        for(auto i=0; i<leafData; ++i){
+            leafNodes[i].reset();
+        }
+        buildFromLeafNodes(leafNodes);
+    }
+
+    template<typename T>
+    void BinaryTree<T>::buildFromLeafNodes(const std::vector<std::shared_ptr<Node> >& leafNodes) {
+        std::vector<Node> tree = leafNodes;
+        while(tree.size() >= 2){
+            std::vector<Node> cachedNode;
+            for(auto i=0; i< tree.size(); i += 2){
+                if(i < tree.size() - 1){
+                    Node newNode;
+                    newNode.parent =
+                }
+            }
+        }
+    }
 }//namespace ParallelFusion
 
 #endif //PARALLELFUSION_HFUSIONPIPELINE_H

### 2016-03-10 paper/introduction.tex

@@
 
-We have validated our ideas on three problems in Computer Vision,
-stereo, optical flow, and layered depthmap estimation. \yasu{add more
-once we see results.}  Our approach is extremely simple in concept, and
-will instantly benefit every Computer Vision researcher or engineer, who
-currently uses fusion move algorithm on multi-core environments to solve
-challenging problems. We will share our implementation of the
-algorithm. The rest of the paper is organized as
-follows. Section~\ref{section:related_work}....
+We have evaluated our ideas on three problems in Computer Vision,
+stereo, optical flow, and layered depthmap estimation. Our approach
+outperforms all the other competing methods, especially for challenging
+problems with a large label space.  Our approach is extremely simple in
+concept, and is easily reproducible by standard Computer Vision engineers.
+% will instantly benefit every Computer Vision researcher or
+% engineer, who currently uses fusion move algorithm on multi-core
+% environments to solve challenging problems.
+% We will share our implementation of the algorithm.
 
@@
 %
- \yasu{Hopefully, more interesting things will come up through
-experiments and we have more to say. For example, it would be cool if
-uniform model is better than pure master-slave. Then we can write that
-ours is not just parallel. But keeping multiple solutions somehow
-benefit (GA/GP algorithm's ideas).}
+%  \yasu{Hopefully, more interesting things will come up through
+% experiments and we have more to say. For example, it would be cool if
+% uniform model is better than pure master-slave. Then we can write that
+% ours is not just parallel. But keeping multiple solutions somehow
+% benefit (GA/GP algorithm's ideas).}
 
@@
 
-3. I would suggest removing "Genetic algorithms" from the paragraph heading at the end of section 2 or replacing it with "Evolutionary Algorithm".
+%3. I would suggest removing "Genetic algorithms" from the paragraph heading at the end of section 2 or replacing it with "Evolutionary Algorithm".
 
-4. We should cite two more papers
-(a) Hierarchical Graph cuts (Kumar and Koller, UAI 2009)
-(b) Making the right move (Batra and Kohli, CVPR 2010)
+%4. We should cite two more paper

### 2016-03-10 paper/layered_depthmap.tex
yasu

@@
 all the proposals to start. Therefore, the only viable competing method
-is Parallel Fusion Move, that replaces constant label solutions by
-solution proposals in parallel alpha-expansion framework. We will also
+is Parallel Fusion Move as in the optical flow problem. We will also
 evaluate the standard Fusion Move method.
@@
 
-\mysubsubsection{Swarm fusion architecture}
-The three swarm architectures in Fig.~\ref{fig:model} are evaluated. The
-fusions are multi-way, for which we use TRW-S.
+\mysubsubsection{Swarm fusion architectures}
+The three swarm architectures in Fig.~\ref{fig:model} are evaluated.
+The architecture parameters are exactly the same as in the optical flow problem:
+$\alpha=2$ ($\beta=0$) in SFWSS, the iteration of
+($\alpha=1, \beta=0$) and ($\alpha=0, \beta=1$) in SFWMF, and
+($\alpha=1, \beta=1$) for the standard SF.
+%
+The fusions are multi-way, for which we use TRW-S.

### 2016-03-10 paper/optical_flow.tex
yasu

--- 2016-03-09 paper/optical_flow.tex
@@
 
-We use Swarm fusion to solve an optical flow problem, where a baseline
-is a FM-based algorithm by Lempitsky et al.~\cite{viktor_optical_flow}.
-Although their paper did not consider parallel implementation, it is
-straightfoward to apply the concept of parallel alpha-expansion and
-construct a ``parallel fusion move'' method, where multiple threads
-repeat fusing two solutions via QPBO. This time, we will compare it with
-our full swarm fusion model (bottom right example in
-Fig.~\ref{fig:model}).
+Fusion Move was first introduced by Lempitsky et al.~\cite{viktor} to
+solve the optical flow problem.
+%Optical flow was the problem, in which the Fusion Move method was first
+%introduced by Lempitsky et al.~\cite{viktor}.
+We copy their problem setting and proposal generation schemes for our
+second problem.  We use test images in the Middlebury optical flow
+benchmark~\cite{middlebury_optical_flow}.
+
+\mysubsubsection{Competing methods} Fusion Move method in Lempitsky's
+paper is the first natural contender. While they did not consider
+parallel implementation, it is straightforward to combine the idea of
+Parallel Alpha-Expansion and Fusion Move. Therefore, the second competing
+method is ``Parallel Fusion Move (PFM)'', which is equivalent to
+Parallel Alpha-Expansion with the constant label solutions replaced by
+the solution proposals.
+%each thread repeats generating
+%a solution proposal and fusing it to the current solution. Solutions
+%from all the results are sequentially fused to obtain the final solution
+%as in the Parallel Alpha-Expansion method.
+%
+One problem of PFM is that infinite number of solution proposals can be
+generated in their algorithm, and we do not know when we should stop and
+perform the final sequential fusion. In our experiments, we manually
+picked a time limit to initiate the final fusion.
+%In Fig.~\ref{fig:model}, this computational framework corresponds to
+%``parallel alpha-expansion'' with the label solutions replaced by
+%solution proposals.
+%
+The last contender is the mix of the Hierarchical Fusion and the Fusion
+Move method, dubbed ``Hierarchical Fusion Method'', where they start
+from solution proposals as opposed to constant labels. One problem is
+that we do not know how many solution proposals to generate to start
+with. We have manually picked a good number (X \yasu{how many Hang?})
+for the experiments.
+%
+The fusions are binary in these methods and we have used QPBO.
+
+\mysubsubsection{Swarm fusion architectures}
+%The three swarm fusion models (at the bottom of Fig.~\ref{fig:model})
+%are used to evaluate the effectiveness of our method.
+The three swarm architectures in Fig.~\ref{fig:model} (SFWSS, SFWMF, SF)
+have been evaluated against the competing methods. Note that we have
+used the same set of proposal generation schemes. The fusions are
+multi-way, for which we have used TRW-S.
+% The full swarm fusion model (at the bottom right in
+% Fig.~\ref{fig:model}) will be used to evaluate the effectiveness of our
+% method. We will also try the other two Swarm fusion variants in
+% Fig.~\ref{fig:model} with restrictions.
+We have chosen $\alpha=2$ ($\beta=0$) in SFWSS, the iteration of
+($\alpha=1, \beta=0$) and ($\alpha=0, \beta=1$) in SFWMF, and
+($\alpha=1, \beta=1$) for the standard SF.  The fusions are multi-way,
+for which we use TRW-S.

### 2016-03-10 paper/related_work.tex

@@
 alpha-expansion technique, where multiple threads simultaneously fuses
-mutually exclusive sets of labels. Delong et al.~\cite{delong} and
-Veksler~\cite{olga} proposed an hierarchical fusion algorithm, where
-labels are simultaneously fused from the bottom to the top in a tree of
-labels. Strictly speaking, these parallelize alpha-expansion and are not
-in the family of Fusion Move methods, because they never generate
-solution proposals. Our approach parallelize fusion move methods.
+mutually exclusive sets of labels. Kumar et
+al.~\cite{hierarchical_graph_cuts_kumar_and_koller}, Delong et
+al.~\cite{delong}, and Veksler~\cite{olga} proposed an hierarchical
+approach, where labels can be simultaneously fused from the bottom to
+the top in a tree of labels. 
+% 
+%Strictly speaking, these parallelize alpha-expansion approaches are not
+%in the family of Fusion Move methods, because they never generate
+%solution proposals. Our approach parallelize fusion move methods.
+Instead of taking a hierarchical approach, Batra et
+al.~\cite{Dhruv_pushmeet_making_the_right_move} adaptively computed an
+effective sequence of labels to explore. This technique can be combined
+with parallel alpha-expansion techniques to further obtain speed-up.
 
@@
 core optimization libraries is a significant engineering investment for
-many companies. In contrast, our idea is extremely simple and instantly
-reproducible by standard engineers.
+many companies. In contrast, our idea is extremely simple and easily
+reproducible.
 
@@
 solves a binary decision problem.
-
+%
 In contrast, methods like message passing algorithms need to maintain

### 2016-03-10 paper/introduction.tex
yasu

@@
 %
-In the recent work on Go (AlphaGo from DeepMind), parallelization plays
-a key role in the Monte-Carlo tree search~\cite{nature_alpha_go}.
+In the recent work on the AI program playing the ancient Chinese board
+game of {\it Go} (AlphaGo from DeepMind), parallelization plays a key
+role in the Monte-Carlo tree search~\cite{nature_alpha_go}.
 
@@
 However, state-of-the-art algorithms are still inherently sequential in
-many Computer Vision problems. Take a Fusion-Move algorithm
-(FM)~\cite{viktor,second_order_stereo,else} for Markov Random Field
-inference, for example. FM has been one of the most effective techniques
-in solving the above
-problems~\cite{fusion_moves_for_markov_random_field_optimization}.
+many Computer Vision problems. Take a Fusion Move method
+(FM)~\cite{viktor,second_order_stereo,else}, which has been one of the
+most effective techniques for the Markov Random Field (MRF) inference,
+for example~\cite{fusion_moves}.
 %
@@
 
-Unleashing the power of parallel computation in FM
+Unleashing the power of parallel computation for effective MRF inference
 % Breaking the sequential nature of FM
@@
 
-We have evaluated our ideas on three problems in Computer Vision,
-stereo, optical flow, and layered depthmap estimation. Our approach
-outperforms all the other competing methods, especially for challenging
-problems with a large label space.  Our approach is extremely simple in
-concept, and is easily reproducible by standard Computer Vision engineers.
+We have evaluated the effectiveness of our approach over three problems
+in Computer Vision, stereo, optical flow, and layered
+depthmap estimation.
+%
+%Our approach outperforms all the other competing methods, especially for
+%challenging problems with a large label space.
+Our idea is very simple and the method is easily reproducible with
+minimal coding.
 % will instantly benefit every Computer Vision researcher or

### 2016-03-11 base/HFusionPipeline.h
Hang

@@ -5,82 +5,212 @@
 #ifndef PARALLELFUSION_HFUSIONPIPELINE_H
 #define PARALLELFUSION_HFUSIONPIPELINE_H
 #include "LabelSpace.h"
-#include "ProposalGenerator.h"
 #include "FusionSolver.h"
 #include "pipeline_util.h"
+#include "thread_guard.h"
+#include "binaryTree.h"
 
-namespace ParallelFusion{
+#include <opencv2/opencv.hpp>
+#include <queue>
+#include <future>
+#include <thread>
+#include <condition_variable>
+#include <atomic>
+#include <chrono>
 
-    template<typename T>
-    class BinaryTree{
-    public:
-        struct Node{
-            Node(): data(NULL), lchild(NULL), rchild(NULL), parent(NULL), flag(false){}
-            std::shared_ptr<T> data;
-            std::shared_ptr<Node> lchild;
-            std::shared_ptr<Node> rchild;
-            std::shared_ptr<Node> parent;
-            //in HFusion, flag indicates whether this node contains data
-            bool flag;
-        };
+namespace ParallelFusion {
+    template<class LABELSPACE>
+    using SolutionPtr = std::shared_ptr<LABELSPACE>;
 
-        BinaryTree(const BinaryTree& t2){
-            root = t2.getRoot();
-        }
+    template<class LABELSPACE>
+    using NodeT = Hang_BinaryTree::Node<SolutionPtr<LABELSPACE> >;
 
-        BinaryTree(const std::shared_ptr<Node> r2){
-            root = r2;
-        }
+    template<class LABELSPACE>
+    using NodePtr = std::shared_ptr<NodeT<LABELSPACE> >;
 
-        void buildFromLeafData(const std::vector<T>& leafData);
+    template<class LABELSPACE>
+    struct AsynTask {
+        AsynTask(NodePtr<LABELSPACE> p1, NodePtr<LABELSPACE> p2, NodeT<LABELSPACE> s) : lchild(p1), rchild(p2),
+                                                                                        selfNode(s) { }
 
-        void buildFromLeafNodes(const std::vector<std::shared_ptr<Node> >& leafNodes);
-
-        inline const std::shared_ptr<Node> getRoot()const{
-            return root;
-        }
-    private:
-        std::shared_ptr<Node> root;
+        NodePtr<LABELSPACE> lchild;
+        NodePtr<LABELSPACE> rchild;
+        NodeT<LABELSPACE> selfNode;
[…]

### 2016-03-11 base/basetest.cpp

@@ -3,12 +3,36 @@
 //
 
 #include "FusionSolver.h"
-#include "ParallelFusionPipeline.h"
+#include "HFusionPipeline.h"
+#include <iostream>
 
 using namespace std;
 using namespace ParallelFusion;
 
 int main(int argc, char** argv){
+    google::InitGoogleLogging(argv[0]);
+    FLAGS_logtostderr = true;
 
+    //test for binary tree
+    Hang_BinaryTree::BinaryTree<int> btree;
+    vector<int> leaf{1,2,3,4,5,6,7,8,9,10};
+
+    cout << "Building tree" << endl << flush;
+    btree.buildFromLeafData(leaf);
+    cout << "done. Number of nodes: " << btree.getNumNode() <<  endl << flush;
+
+    Hang_BinaryTree::BinaryTree<int>::FunctorType traversePrint = [](shared_ptr<Hang_BinaryTree::Node<int> > node){
+        printf("(%d,%d) ", node->nodeId, node->data);
+    };
+
+    cout << "Preorder:" << endl;
+    btree.traverseTree(traversePrint, Hang_BinaryTree::PRE_ORDER, btree.getRoot());
+    cout << endl;
+    cout << "Inorder:" << endl;
+    btree.traverseTree(traversePrint, Hang_BinaryTree::IN_ORDER, btree.getRoot());
+    cout << endl;
+    cout << "Posteorder:" << endl;
+    btree.traverseTree(traversePrint, Hang_BinaryTree::POST_ORDER, btree.getRoot());
+    cout << endl;
     return 0;
 }

### 2016-03-11 base/binaryTree.h

@@ -1,0 +1,165 @@
+//
+// Created by Hang Yan on 3/10/16.
+// Washington University in St. Louis
+// yanhang@wustl.edu
+//
+
+#ifndef HANG_BINARY_TREE_H
+#define HANG_BINARY_TREE_H
+
+#include <vector>
+#include <memory>
+#include <functional>
+#include <glog/logging.h>
+#include <atomic>
+
+namespace Hang_BinaryTree {
+    template<typename T>
+    struct Node {
+        Node():lchild(NULL), rchild(NULL), parent(NULL), depth(-1), nodeId(-1), flag1(false), flag2(false) { }
+
+        T data;
+        std::shared_ptr<Node> lchild;
+        std::shared_ptr<Node> rchild;
+        std::shared_ptr<Node> parent;
+        int depth;
+        int nodeId;
+
+        //two auxilary flags
+        std::atomic<bool> flag1;
+        std::atomic<bool> flag2;
+    };
+
+    enum TraverseMethod {
+        PRE_ORDER, IN_ORDER, POST_ORDER
+    };
+
+    template<typename T>
+    class BinaryTree {
+    public:
+        typedef Node<T> NodeT;
+        typedef std::function<void(std::shared_ptr<NodeT>)> FunctorType;
+        BinaryTree(): depth(-1), numNode(0){}
+
+        BinaryTree(const BinaryTree &t2) {
+            BinaryTree();
+            root = t2.getRoot();
+        }
+
+        BinaryTree(const std::shared_ptr<NodeT> r2) {
+            BinaryTree();
+            root = r2;
+        }
+
+        void buildFromLeafData(const std::vector<T> &leafData);
+
+        //method of tree traversal.
+        //input: method: pre-order, in-order or post-order
+        //option: callable object represents what options should be perform on each node.
+        //        This can be a struct or class with operator(), or a lambda function.
+        //        Notice that this operation can not have return value.
+        void traverseTree(std::function<void(std::shared_ptr<NodeT>)> &operation, const TraverseMethod method,
+                          std::shared_ptr<NodeT> startNode);
+
+        inline const std::shared_ptr<NodeT> getRoot() const {
+            return root;
+        }
+
+        const inline int getTreeDepth() const{
+            return depth;
+        }
+
+        const inline int getNumNode() const{
+            return numNode;
+        }
+
+    private:
+        void assignNodeDepth();
+        void assignNodeId();
+
+        std::shared_ptr<NodeT> root;
+        int depth;
+        int numNode;
+    };
+
[…]

### 2016-03-11 stereo/code/simplestereo/optimization.h

@@ -151,6 +151,15 @@ namespace simple_stereo {
         const int num_threads;
     };
 
+    class HierarchyOptimize: public StereoOptimizer {
+    public:
+        HierarchyOptimize(const stereo_base::FileIO &file_io_, const MRFModel<int> *model_, const int num_threads_):
+                StereoOptimizer(file_io_, model_), num_threads(num_threads_){}
+        virtual double optimize(stereo_base::Depth& result, const int max_iter) const;
+    private:
+        const int num_threads;
+    };
+
     class DummyGenerator: public ParallelFusion::ProposalGenerator<CompactLabelSpace>{
     public:
         virtual void getProposals(CompactLabelSpace& proposals, const CompactLabelSpace& current_solution, const int N){}

### 2016-03-11 stereo/code/simplestereo/optimization_hierarchy.cpp

@@ -1,0 +1,37 @@
+//
+// Created by yanhang on 3/10/16.
+//
+
+#include "optimization.h"
+#include "../../../base/HFusionPipeline.h"
+using namespace std;
+using namespace cv;
+using namespace ParallelFusion;
+
+namespace simple_stereo{
+
+    double HierarchyOptimize::optimize(stereo_base::Depth &result, const int max_iter) const {
+        typedef CompactLabelSpace Space;
+        HFusionPipelineOption option;
+        option.num_threads = num_threads;
+        HFusionPipeline<Space> pipeline(option);
+
+        std::vector<std::shared_ptr<FusionSolver<Space> > >solvers((size_t)option.num_threads);
+        for(auto& s: solvers)
+            s = shared_ptr<FusionSolver<Space> >(new SimpleStereoSolver(model));
+
+        std::vector<Space> proposals((size_t)model->nLabel);
+        for(auto i=0; i<proposals.size(); ++i)
+            proposals[i].getSingleLabel().push_back(i);
+
+        Space initial;
+        initial.init(width * height, vector<int>(1,0));
+
+        float t = (float)getTickCount();
+        pipeline.runHFusion(proposals, solvers, initial);
+        t = ((float)getTickCount() - t) / (float)getTickFrequency();
+        printf("Done. Time usage: %.3fs\n", t);
+    }
+
+}//namespace simple_stereo
+

### 2016-03-11 stereo/code/simplestereo/optimization_parallel.cpp

@@ -138,9 +138,6 @@ namespace simple_stereo {
                                                                                 const_cast<int*>(model->vCue)));
         mrf = new Expansion(model->width, model->height, model->nLabel, energy_function);
         mrf->initialize();
-
-//        qpbo = new kolmogorov::qpbo::QPBO<int>(kPix, 2 * kPix);
-//        qpbo->AddNode(kPix);
     }
 
     void SimpleStereoSolver::solve(const CompactLabelSpace &proposals,
@@ -172,8 +169,7 @@ namespace simple_stereo {
             fuseTwoSolution(solution.second, proposals,i,model);
             //printf("Done. Unlabeled:%.3f, label changed:%.3f\n", unlabeled / (float)kPix, changed / (float)kPix);
         }
-
-        //solution.first = evaluateEnergy(solution.second);
+        solution.second.getSingleLabel().clear();
         solution.first = evaluateEnergy(solution.second);
     }
 

### 2016-03-11 stereo/code/simplestereo/simplestereo.cpp

@@ -151,11 +151,18 @@ namespace simple_stereo {
         sprintf(buffer, "%s/temp/unaryDisp.jpg", file_io.getDirectory().c_str());
         unaryDisp.saveImage(buffer, 256.0 / (double)model->nLabel);
 
-        ParallelOptimize optimize_parallel(file_io, model, 1);
-        Depth result_parallel;
-        optimize_parallel.optimize(result_parallel, 1);
-        sprintf(buffer, "%s/temp/result_parallel.jpg", file_io.getDirectory().c_str());
-        result_parallel.saveImage(buffer);
+//        ParallelOptimize optimize_parallel(file_io, model, 1);
+//        Depth result_parallel;
+//        optimize_parallel.optimize(result_parallel, 1);
+//        sprintf(buffer, "%s/temp/result_parallel.jpg", file_io.getDirectory().c_str());
+//        result_parallel.saveImage(buffer);
+
+        HierarchyOptimize optimize_hierarchy(file_io, model, 4);
+        Depth result_hierarchy;
+        optimize_hierarchy.optimize(result_hierarchy, 1);
+        sprintf(buffer, "%s/temp/result_hierarchy.jpg", file_io.getDirectory().c_str());
+        result_hierarchy.saveImage(buffer);
+
 
 //        FirstOrderOptimize optimize_firstOrder(file_io, model);
 //        Depth result_firstOrder;

### 2016-03-11 paper/abstract.tex

--- 2016-03-05 paper/abstract.tex
@@
 \begin{abstract}
-\yasu{must be at least 70 and at most 150 words.}
-\keywords{A; B; C.}
+This paper proposes a novel MAP inference framework for Markov Random
+Field (MRF) problems in parallel computing environments.  The inference
+framework, dubbed Swarm Fusion method, is a natural generalization of
+the Fusion Move method. Every thread (in a case of multi-threading
+environments) maintains and updates a solution. At every iteration, a
+thread can generate arbitrary number of solution proposals and take
+arbitrary number of concurrent solutions from the other threads to
+perform multi-way fusion in updating its solution. The framework is
+general, making popular existing inference techniques such as
+alpha-expansion, fusion move, parallel alpha-expansion, or hierarchical
+fusion, its special cases. We have evaluated the effectiveness of our
+approach against competing methods on three problems of varying
+difficulties, in particular, the stereo, the optical flow, and the
+layered depthmap estimation problems.
+%Our experiments have shown that the Swarm Fusion method outperform
+%competing methods, especially for challenging problems with massive
+%solution space.
+% can effectively exploits the parallel computing resources and become
+%effective especially for challenging problems.
+%\yasu{must be at least 70 and at most 150 words.}
+\keywords{MRF; Fusion Move; Particle Swarm Optimization}
 \end{abstract}

### 2016-03-11 paper/algorithm.tex
yasu

@@
 \section{Multi-way particle swarm fusion}
-Multi-way Particle Swarm Fusion is a natural extension of Fusion Move
-method (FM). We call our method Swarm Fusion (SF) in short. Let us take
-a multi-threading environment to explain our idea, while the technique
-is also applicable to other parallel programming model such as {\it
-MapReduce} in cloud computing.
+Multi-way Particle Swarm Fusion is a natural extension of the Fusion
+Move method (FM). We call our method Swarm Fusion (SF) in short. Let us
+take a multi-threading environment to explain our idea, while the
+technique is also applicable to other parallel programming model such as
+{\it MapReduce} in cloud computing.
 %
@@
   \State Replaces the solution in $\mathcal{S}_{pool}$ with $S_i$
-  \State [ Generates proposals and update $\mathcal{P}_{pool}$ ]
+  \State [ Generates proposals and update $\mathcal{P}_{pool}$, if necessary ]
   \EndFor

### 2016-03-11 paper/related_work.tex

@@
 % 
-%Strictly speaking, these parallelize alpha-expansion approaches are not
-%in the family of Fusion Move methods, because they never generate
-%solution proposals. Our approach parallelize fusion move methods.
 Instead of taking a hierarchical approach, Batra et
@@
 with parallel alpha-expansion techniques to further obtain speed-up.
+%
+Strictly speaking, these approaches are not in the family of FM, because
+they only consider constant label proposals. Our approach is a
+generalization of FM.
 
@@
 %
-However, the core optimization libraries are often very complex and
-require significant engineering by experts for modification.
 %
@@
 for non-commercial purposes, most companies have to develop and maintain
-in-house implementation of these algorithms. The modification of the
-core optimization libraries is a significant engineering investment for
-many companies. In contrast, our idea is extremely simple and easily
-reproducible.
+in-house implementation of these algorithms.  The core optimization
+libraries are often very complex and their modifications require
+significant engineering investments for many companies. In contrast, our
+idea is extremely simple and easily reproducible by standard engineers.
 
@@
 %
-Although conceptually straightforward, we are not aware of {\it parallel
-fusion move} algorithms that fuses solution proposals, as opposed to
+Although conceptually straightforward, we are not aware of {\it Parallel
+Fusion Move} algorithms that fuses solution proposals, as opposed to
 labels, in parallel. This paper seeks to fully unleash the power of
-parallel computation in FM via more general framework.
+parallel computation in FM via a more general framework.
 
@@
 While GA and PSO have limited theoretical justification, they have been
-used to produce great empirical results, for example, hand tracking via
-PSO~\cite{pushmeet_hand_tracking}. At high level, our strategy is
+used to produce great empirical results, for example, hand
+tracking~\cite{pushmeet_hand_tracking}. At high level, our strategy is
 similar in spirit. However, GA or PSO rather arbitrarily copies part of

### 2016-03-11 paper/related_work.tex
yasu

@@
 
-Markov Random Field (MRF) inference has been a very active field in
-Computer Vision with extensive literature. We refer the readers to
-survey articles for a comprehensive
-review~\cite{middlebury_mrf,comparative_study_of_modern_inference}, and
+MRF inference has been a very active field in Computer Vision with the
+extensive literature. We refer the readers to survey articles for
+comprehensive
+reviews~\cite{middlebury_mrf,comparative_study_of_modern_inference}, and
 here focus our description on closely related topics.
@@
 %
-Strictly speaking, these approaches are not in the family of FM, because
-they only consider constant label proposals. Our approach is a
-generalization of FM.
+Strictly speaking, these approaches are not in the family of Fusion Move
+methods (FM), because they only consider constant label proposals. Our
+approach is a generalization of FM.
 
@@
 
-\noindent
-The core MAP inference algorithms themselves can be parallelized.
-Strandmark et al. parallelized graph-cuts~\cite{strandmark2010parallel}.
+\noindent The core MAP inference itself can be parallelized.  Strandmark
+et al. parallelized graph-cuts~\cite{strandmark2010parallel}.
 %
@@
 in-house implementation of these algorithms.  The core optimization
-libraries are often very complex and their modifications require
-significant engineering investments for many companies. In contrast, our
-idea is extremely simple and easily reproducible by standard engineers.
+libraries are very complex and their modifications require significant
+engineering investments. In contrast, our idea is extremely simple and
+easily reproducible by standard engineers.
 
@@
 optical flow problem~\cite{first_fusion_viktor}. FM has been effectively
-used to solve challenging problems in Computer Vision such as a stereo
-problem with second order smoothness priors~\cite{woodford}, a stereo
-problem with parameteric surface fitting and segmentation (i.e., Surface
+used to solve challenging problems in Computer Vision such as stereo
+with second order smoothness priors~\cite{woodford}, stereo
+with parameteric surface fitting and segmentation (i.e., Surface
 Stereo)~\cite{surface_stereo}, or multicut
@@
 schemes. Second, FM can handle problems with very large label spaces
-(and even real-values variables), because the core optimization just
-solves a binary decision problem.
+(and even real-values variables), because the core optimization
+solves a sequence of binary decision problems.
 %
@@
 Although conceptually straightforward, we are not aware of {\it Parallel
-Fusion Move} algorithms that fuses solution proposals, as opposed to
+Fusion move} algorithms that fuse solution proposals, as opposed to
 labels, in parallel. This paper seeks to fully unleash the power of
-parallel computation in FM via a more general framework.
+parallel computation based on FM in the most general setting.
+%for the most general FM via a more general framework.
 
@@
 %
-While GA and PSO have limited theoretical justification, they have been
-used to produce great empirical results, for example, hand
-tracking~\cite{pushmeet_hand_tracking}. At high level, our strategy is
-similar in spirit. However, GA or PSO rather arbitrarily copies part of
-the solution or makes random movements in each step. Our approach
-directly optimizes the objective function to improve solutions.
+GA or PSO has been used to produce great empirical results, for example,
+hand tracking~\cite{pushmeet_hand_tracking}.
+%
+At high level, our strategy is similar in spirit. However, GA or PSO
+rather arbitrarily copies parts of the solutions or makes random movements
+in each step (i.e., limited theoretical justification).
+%
+Our approach directly optimizes the objective function to improve
+solutions.

### 2016-03-11 paper/algorithm.tex
yasu

@@
 $T_i$ maintains and updates a solution $S_i$ in parallel. Alpha
-expansion picks one label in each iteration to perform fusion. FM
-invokes one proposal generation scheme and generates a solution proposal
-for fusion. Swarm Fusion has 1) a {\it proposal pool}, from which we
-pick arbitrary number of proposal generation schemes and generate
-proposals, and 2) a {\it solution pool}, from which we pick arbitrary
-number of intermediate solutions generated by the other threads.
+Expansion picks one label in each iteration to perform fusion. FM
+generates a solution proposal via a proposal generation scheme.
+%invokes one proposal generation scheme and generates a solution proposal
+%for fusion.
+SF has 1) a {\it proposal pool}, from which a thread picks arbitrary
+number of proposal generation schemes and generates proposals, and 2) a
+{\it solution pool}, from which a thread picks arbitrary number of
+intermediate solutions generated by the others.
+% threads.
 %
@@
 % fused by the threads.
-In our base configuration, the solution pool only remembers the solution
-from each thread.
+In our base configuration, the solution pool remembers just the best
+solution from each thread.
 
-Swarm Fusion has two main parameters $\alpha_i$ and $\beta_i$ (for each
-thread $T_i$), determining the processing flow of the algorithm: In each
-fusion step, the thread collects $\alpha_i$ solution proposals from the
-proposal pool and $\beta_i$ solutions from the solution pool, based on a
-user-defined strategy or at random to be simple.
+SF has two main parameters $\alpha_i$ and $\beta_i$ (for each thread
+$T_i$), determining its processing flow: In each fusion step, a thread
+collects $\alpha_i$ solution proposals from the proposal pool and
+$\beta_i$ solutions from the solution pool, based on a user-defined
+strategy or at random to be simple.
 %
@@
 % schemes (as in ~\cite{delong}) or solutions.
+
 Swarm Fusion framework is very flexible and yields various data
@@
  \includegraphics[width=\columnwidth]{figure/model.pdf} \caption{Swarm
- Fusion architecture and its relationships to existing methods. The
- bottom right example shows the general Swarm fusion architecture, where
+ Fusion (SF) architecture and its relationships to existing methods. The
+ bottom right example shows the general SF architecture, where
  each thread takes arbitrary number of solution proposals and concurrent
  solutions from other threads for fusion. The framework is flexible and
- can realize other data processing architectures depending on the parameters.
+ can realize other data processing architectures depending on the
+ parameters (e.g., the left two examples in the bottom row).
  %
@@
  %
- The left two examples at the bottom are other Swarm fusion
- architectures with some restrictions, to be used for evaluations later.
+% The left two examples at the bottom are other Swarm fusion
+% architectures with some restrictions, to be used for evaluations later.
  %
- It is also easy to verify that existing methods such as
- alpha-expansion~\cite{alpha_expansion}, Fusion move~\cite{FM}, parallel
- alpha-expansion~\cite{delong}, or hierarchical
- fusion~\cite{delong_hierarchical_fusion,olga}, are all special
- cases of the Swarm fusion.}\label{fig:model}
+ It is easy to verify that existing popular MRF inference methods such
+ as Alpha Expansion~\cite{alpha_expansion}, Fusion Move~\cite{FM},
+ Parallel Alpha Expansion~\cite{delong}, or Hierarchical
+ Fusion~\cite{delong_hierarchical_fusion,olga}, are all special cases of
+ SF.}\label{fig:model}
 \end{figure}
 %
-The bottom right architecture is the most general one, in which we
+The bottom right architecture is the most general one, in which threads
 always fuse some solution proposals and some concurrent solutions (i.e.,
@@
 %
-Each fusion is multi-way (not binary) with a non-submodular energy, and
-we use TRW~\cite{kolmogorov} for the fusion, while any other compatible
-inference techniques can be used~\cite{opengm}. For instance, if one
-knows that a certain fusion step is a binary fusion with submodular
-energy, one can use graph-cuts~\cite{alpha_expansion_paper}. If a
-certain fusion step is a binary fusion with non-submodular energy, one
-can use QPBO~\cite{second_order_smoothness_stereo}.
+Each fusion is multi-way (not binary) and the energy is not submodular
+in general, for which effective inference techniques such as
+TRW~\cite{kolmogorov,opengm} exist.
+%, and hence we use TRW~\cite{kolmogorov} for the fusion, while any other
+%compatible inference techniques can be used~\cite{opengm}.
+However, if one knows that a certain fusion step is a binary fusion with
+submodular energy, one can use
+graph-cuts~\cite{alpha_expansion_paper}. If a certain fusion step is a
+binary fusion with non-submodular energy, one can use
+QPBO~\cite{second_order_smoothness_stereo}.
 %
-Note that the threads are all synchronized in the figure for a
+Note that the threads appear synchronized in the figure for a
 illustration purpose. In practice, all the threads run asynchronously
-with a (read-write) lock on the data in the two pools (See Algorithm~\ref{algorithm:sf}).
+with a (read-write) lock on the data in the two pools (See
+Algorithm~\ref{algorithm:sf}).
 %The asynchronous processing could be difficult for cloud parallel
@@
 
-\noindent It is easy to verify that alpha-expansion
-(AE)~\cite{alpha_expansion}, fusion move (FM)~\cite{viktor}, parallel
-alpha-expansion (PAE)~\cite{delong}, and hierarchical fusion
+\noindent It is easy to verify that Alpha-Expansion
+(AE)~\cite{alpha_expansion}, Fusion Move (FM)~\cite{viktor}, Parallel
+Alpha Expansion (PAE)~\cite{delong}, and Hierarchical Fusion
 (HF)~\cite{delong_hierarchical,olga} are all special cases of the Swarm
-Fusion method. AE can be realized by setting $(\alpha=1, \beta=0)$ and
+Fusion method (SF). AE can be realized by setting $(\alpha=1, \beta=0)$ and
 restricting the proposal generation to constant labels with a single

### 2016-03-11 paper/stereo.tex
yasu

@@
-\section{Swarm Fusion implementations \yasu{I don't like this title..}}
-We compare our Swarm fusion methods against competing approaches over
-three problems in Computer Vision. The SF architecture has high degrees
-of freedom and the challenge is to properly quantity the contribution of
-various algorithmic aspects. For this purpose, we carefully design the
-SF architecture for each problem independently, sometimes limiting the
-capabilities on purpose, to enable effective and fair comparative
-evaluation.  We now explain the details of the three problems.
+\section{Swarm Fusion instantiation}
+We compare SF against competing approaches over three problems in
+Computer Vision. SF framework has high degrees of freedom and the
+challenge is to properly quantity the contributions of various
+algorithmic aspects. For this purpose, we have used the three SF
+architectures illustrated in Fig.~\ref{fig:model}. For some problems, we
+have further limited the capabilities of SF on purpose, to enable
+effective and fair comparative evaluations. We now explain the details
+of the three problems.
 
@@
  \includegraphics[width=\columnwidth]{figure/problem.pdf} \caption{We
- compare our Swarm Fusion methods against competing approaches on a
+ compare our Swarm Fusion method against competing approaches on a
  depthmap stereo~\cite{middle_bury_stereo}, an optical

### 2016-03-11 paper/stereo.tex
yasu

@@
 fusion method (i.e., the use of proposal generation) rather makes it slow
-due to the overhead.  Therefore, we pick parallel
-alpha-expansion~\cite{delong} and hierarchical fusion~\cite{delong,olga}
+due to the overhead.  Therefore, we have chosen Parallel
+Alpha Expansion~\cite{delong} and Hierarchical Fusion~\cite{delong,olga}
 with graph-cuts optimization as the competing methods.
 
-\mysubsubsection{Swarm fusion architectures}
+\mysubsubsection{Swarm Fusion architectures}
 
 \noindent The three swarm architectures in Fig.~\ref{fig:model} have
-been evaluated: SFWSS (SF without solution sharing), SFWMF (SF without
+been evaluated: SF-SS (SF without solution sharing), SF-MF (SF without
 multi-way fusion), and the standard SF.
 %
-For SFWSS, we have chosen $\alpha=2$ ($\beta=0$). For SFWMF, each thread
+For SF-SS, we have chosen $\alpha=2$ ($\beta=0$). For SF-MF, each thread
 iterates the step of ($\alpha=1, \beta=0$) or ($\alpha=0, \beta=1$) so

### 2016-03-11 paper/layered_depthmap.tex
yasu

--- 2016-03-10 paper/layered_depthmap.tex
@@
 Our last problem is layered depthmap estimation, recently proposed
-in~\cite{layered_depthmap} (see the anonymious paper in the
+in~\cite{layered_depthmap} (see the anonymous paper in the
 supplementary material).  The problem seeks to infer layered depthmap
@@
 %
-Layered depthmap estimation is one of the most difficult kinds for MAP
-inference due to its massive solution space, where the number of labels
-per pixel is exponential in the number of layers. In practice, each
-pixel might take an order of 100,000 \yasu{is this number correc?}
-possible labels. We copy their problem formulation and the proposal
-generation schemes.~\footnote{Authors have proposed a novel fusion scheme,
-where a solution subspace instead of a single solution is generated by a
-proposal generation scheme. Since a solution subspace is equivalent to
-multiple solution proposals, their algorithm can be easily integrated
-into our swarm fusion framework.  However, competing fusion methods
-(e.g., Parallel Fusion Move or Hierarchical Fusion) cannot handle a
-solution subspace proposal, making it impossible to conduct fair
-comparative evaluations. We choose to use a simple solution proposal for
-experiments in this paper.}
+Layered depthmap estimation is one of the most difficult kinds in MRF
+inference due to its massive solution space. The number of labels per
+pixel is exponential in the number of layers, and is an order of 100,000
+\yasu{is this number correc?}. We copy their problem
+formulation and the proposal generation schemes.~\footnote{Authors have
+proposed a novel fusion scheme, where a solution subspace instead of a
+single solution is generated by a proposal generation scheme. Since a
+solution subspace is equivalent to multiple solution proposals, their
+algorithm can be easily integrated into our swarm fusion framework.
+However, competing fusion methods (e.g., Parallel Fusion Move or
+Hierarchical Fusion) cannot handle a solution subspace proposal, making
+it impossible to conduct fair comparative evaluations. We choose to use
+a simple solution proposal for experiments in this paper.}
 %Lastly, we will evaluate Swarm fusion on a very challenging layered
@@
 
-Solution proposals depend heavily on the current solution, eliminating
-the possibility of using hierarchical approach, which needs to enumerate
-all the proposals to start. Therefore, the only viable competing method
-is Parallel Fusion Move, that replaces constant label solutions by
-solution proposals in parallel alpha-expansion framework. We will also
-evaluate the standard Fusion Move method.
+\noindent Solution proposals depend heavily on the current solution,
+eliminating the possibility of using Hierarchical Fusion, which needs to
+enumerate all the proposals to start. Therefore, viable competing
+methods are Fusion Move and Parallel Fusion Move.
+%
+%We will also evaluate the standard Fusion Move method.
 %
@@
 
-\mysubsubsection{Swarm fusion architecture}
-The three swarm architectures in Fig.~\ref{fig:model} are evaluated. The
-fusions are multi-way, for which we use TRW-S.
+\mysubsubsection{Swarm fusion architectures}
+
+\noindent The three swarm architectures with the same configurations as
+in the optical flow problems have been evaluated.
+%in Fig.~\ref{fig:model} are evaluated.
+%The architecture parameters are exactly the same as in the optical flow problem:
+%$\alpha=2$ ($\beta=0$) in SFWSS, the iteration of
+%($\alpha=1, \beta=0$) and ($\alpha=0, \beta=1$) in SFWMF, and
+%($\alpha=1, \beta=1$) for the standard SF.
+%
+%The fusions are multi-way, for which we use TRW-S.

### 2016-03-11 paper/optical_flow.tex
yasu

@@
 %introduced by Lempitsky et al.~\cite{viktor}.
-We copy their problem setting and proposal generation schemes for our
-second problem.  We use test images in the Middlebury optical flow
+We copy their problem setting and proposal generation schemes for
+our second problem.  We use images from the Middlebury optical flow
 benchmark~\cite{middlebury_optical_flow}.
 
-\mysubsubsection{Competing methods} Fusion Move method in Lempitsky's
-paper is the first natural contender. While they did not consider
-parallel implementation, it is straightforward to combine the idea of
-Parallel Alpha-Expansion and Fusion Move. Therefore, the second competing
-method is ``Parallel Fusion Move (PFM)'', which is equivalent to
-Parallel Alpha-Expansion with the constant label solutions replaced by
-the solution proposals.
+\mysubsubsection{Competing methods}
+
+\noindent Fusion Move method in Lempitsky's paper is the first natural
+contender. While they did not consider parallel implementation, it is
+straightforward to combine the idea of Parallel Alpha Expansion and
+Fusion Move. Therefore, the second competing method is ``Parallel Fusion
+Move''(PFM), which is equivalent to Parallel Alpha Expansion with constant
+label solutions replaced by solution proposals.
 %each thread repeats generating
@@
 One problem of PFM is that infinite number of solution proposals can be
-generated in their algorithm, and we do not know when we should stop and
-perform the final sequential fusion. In our experiments, we manually
-picked a time limit to initiate the final fusion.
+generated in their algorithm, and we do not know when to stop and
+perform the final sequential fusion (See Parallel Alpha Expansion
+architecture in Fig.~\ref{fig:model}). In our experiments, we manually
+picked time limits to initiate the final fusion to make the comparisons
+fair.
 %In Fig.~\ref{fig:model}, this computational framework corresponds to
@@
 The last contender is the mix of the Hierarchical Fusion and the Fusion
-Move method, dubbed ``Hierarchical Fusion Method'', where they start
-from solution proposals as opposed to constant labels. One problem is
-that we do not know how many solution proposals to generate to start
-with. We have manually picked a good number (X \yasu{how many Hang?})
-for the experiments.
+Move methods, dubbed ``Hierarchical Fusion Method''(HFM), where they
+start from solution proposals as opposed to constant labels. One problem
+of HFM is that the number of necessary solution proposals is unknown
+before solving the problem, and the tree of labels cannot be defined. In
+our experiments, we have manually picked a good number (X \yasu{how many
+Hang?}) to generate proposals.
 %
@@
 \mysubsubsection{Swarm fusion architectures}
+
+\noindent
 %The three swarm fusion models (at the bottom of Fig.~\ref{fig:model})
 %are used to evaluate the effectiveness of our method.
-The three swarm architectures in Fig.~\ref{fig:model} (SFWSS, SFWMF, SF)
-have been evaluated against the competing methods. Note that we have
-used the same set of proposal generation schemes. The fusions are
-multi-way, for which we have used TRW-S.
+The three swarm architectures in Fig.~\ref{fig:model} (SF-SS, SF-MF, SF)
+have been evaluated against the competing methods. The same
+configurations as in the stereo problem have been used for optical flow,
+that is, $\alpha=2$ ($\beta=0$) for SF-SS, the iteration of
+($\alpha=1, \beta=0$) and ($\alpha=0, \beta=1$) for SF-MF, and
+($\alpha=1, \beta=1$) for SF.
+%
+Note that we have used the same set of proposal generation schemes as
+the competing methods. We have used TRW-S for multi-way fusion and QPBO
+for binary fusion.
+%, while our fusions are multi-way, for which we have used TRW-S.
+%
 % The full swarm fusion model (at the bottom right in
@@
 % Fig.~\ref{fig:model} with restrictions.
-We have chosen $\alpha=2$ ($\beta=0$) in SFWSS, the iteration of
-($\alpha=1, \beta=0$) and ($\alpha=0, \beta=1$) in SFWMF, and
-($\alpha=1, \beta=1$) for the standard SF.  The fusions are multi-way,
-for which we use TRW-S.

### 2016-03-11 LayerDepthMap/LayerDepthRepresenter.cpp
minor changes

@@ -128,7 +128,7 @@ void LayerDepthRepresenter::optimizeLayerRepresentation()
   ParallelFusion::ParallelFusionOption option;
   option.num_threads = PIPELINE_PARAMS_.num_threads;
   option.max_iteration = PIPELINE_PARAMS_.num_iterations;
-  option.selectionMethod = ParallelFusion::ParallelFusionOption::BEST;
+  option.selectionMethod = ParallelFusion::ParallelFusionOption::RANDOM;
   //option.synchronize = true;
   
 

### 2016-03-11 LayerDepthMap/TRWSFusion.cpp

@@ -906,7 +906,7 @@ void TRWSFusion::solve(const LayerLabelSpace &proposal_label_space, const Parall
   
   
   MRFEnergy<TypeGeneral>::Options options;
-  options.m_iterMax = 200;
+  options.m_iterMax = 2000;
   options.m_printIter = 200;
   options.m_printMinIter = 100;
   options.m_eps = 0.1;

### 2016-03-11 base/ParallelFusionPipeline.h

@@ -25,7 +25,7 @@ namespace ParallelFusion {
         //solver should be read only
         ParallelFusionPipeline(const ParallelFusionOption &option_) : option(option_), bestSolutions((size_t)option_.num_threads),
                                                                       terminate(false), write_flag((size_t)option_.num_threads),
-                                                                      threadProfile((size_t)option_.num_threads){ }
+	threadProfile((size_t)option_.num_threads){ }
 
         typedef std::shared_ptr<ProposalGenerator<LABELSPACE> > GeneratorPtr;
         typedef std::vector<GeneratorPtr> GeneratorSet;

### 2016-03-11 paper/abstract.tex

@@
 This paper proposes a novel MAP inference framework for Markov Random
-Field (MRF) problems in parallel computing environments.  The inference
-framework, dubbed Swarm Fusion method, is a natural generalization of
-the Fusion Move method. Every thread (in a case of multi-threading
+Field (MRF) in parallel computing environments.  The inference
+framework, dubbed Swarm Fusion, is a natural generalization of the
+Fusion Move method. Every thread (in a case of multi-threading
 environments) maintains and updates a solution. At every iteration, a

### 2016-03-11 paper/conclusion.tex

--- 2016-03-10 paper/conclusion.tex
@@
-\section{Conclusion and future direction}
-We have proposed a novel MAP inference framework, Swarm Fusion, for MRF
-problems in parallel computing environments. The framework is general,
-and we showed that most popular inference techniques such as
-alpha-expansion, Fusion Move, parallel alpha-expansion, or hierarchical
-fusion, are its special cases. Our experiments have revealed that the
-framework exploits parallel computational resources and achieves faster
-convergence, epseically for challenging problems.  Our first future work
-is to conduct experiments on cloud computing environments, in
-particular, the MapReduce programming model, where the roles of mappers
-and reducers exactly correspond to the processes of parallel multi-way
-fusion and solution exchanges, respectively.  Another future work is the
-automatic configuration of the Swarm Fusion architecture. Due to its
-vast degrees of freedom, one needs to currently hand-tune the
-architecture for the optical performance. An interesting direction is to
-adaptively change its architecture during the computation, for example,
-switching to simple parallel alpha-expansion for easy problems, or
-increasing the rate of solution exchanges when solutions vary
-significantly across threads.
+\section{Conclusion and future directions}
+We have proposed a novel MRF inference framework, Swarm Fusion, in
+parallel computing environments. The framework is general and makes
+popular inference techniques such as Alpha Expansion, Fusion Move,
+Parallel Alpha Expansion, or Hierarchical Fusion, its special cases. Our
+experiments have revealed that the framework exploits parallel
+computational resources and achieves faster convergence, epseically for
+challenging problems.  Our first future work is to conduct experiments
+on cloud computing environments, in particular, the MapReduce
+programming model, where the roles of mappers and reducers exactly
+correspond to the processes of parallel multi-way fusion and solution
+sharing, respectively.  Another future work is the automatic
+configuration of the Swarm Fusion architecture.  Our experiments have
+shown that optimal architectures are different for different problems.
+An interesting direction is to adaptively change its architecture during
+the computation, for example, switching to simple parallel
+alpha-expansion for easy problems, or increasing the rate of solution
+exchanges when solutions vary significantly across threads.
 %
-Parallel MAP inference has been a relatively under-explored topic in
-Computer Vsion. Our idea is very simple and adapting the Swarm Fusion
-framework require minimal coding. We believe that this paper has a
-potential to immediately benefit tens of thousands of Computer Vision
-researchers or engineers in the world, who currently solve MRF problems
-with conventional solvers. We will share our source code and the
-datasets with the community.
+Parallel MRF inference has been a relatively under-explored topic in
+Computer Vsion. Our idea is very simple, where adapting the Swarm Fusion
+framework require minimal coding. We believe that this paper would
+immediately benefit tens of thousands of Computer Vision researchers or
+engineers in the world, who currently solve MRF problems. We will share
+our source code and the datasets with the community.

### 2016-03-11 paper/introduction.tex

@@
 In the recent work on the AI program playing the ancient Chinese board
-game of {\it Go} (AlphaGo from DeepMind), parallelization plays a key
-role in the Monte-Carlo tree search~\cite{nature_alpha_go}.
+game of {\it Go}, parallelization plays a key role in the Monte-Carlo
+tree search~\cite{nature_alpha_go}.
 
@@
 apply image denoising to 50 Megapixel images from latest digital
-SLRs~\cite{canon?}, stitch thousands of images to generate gigapixel
+SLRs (e.g., Canon EOS 5DS), stitch thousands of images to generate gigapixel
 panoramas~\cite{gigapan}, or solve volumetric reconstruction and
@@
 many Computer Vision problems. Take a Fusion Move method
-(FM)~\cite{viktor,second_order_stereo,else}, which has been one of the
-most effective techniques for the Markov Random Field (MRF) inference,
-for example~\cite{fusion_moves}.
+(FM)~\cite{viktor,second_order_stereo,else} for example, which has been
+one of the most effective techniques for Markov Random Field (MRF)
+inference, including the above problems like image denoising, image
+stitching, or volumetric reconstruction.
 %
 It sequentially improves solution by fusing the current solution with a
-solution proposal. Its successful applications range from optical flow,
-stereo, image denoising, image inpainting, to image
-segmentation~\cite{fusion_moves_for_markov_random_field_optimization}.
+solution proposal. Its successful applications go beyond and also cover
+optical flow, stereo, image inpainting, or image segmentation
+problems~\cite{fusion_moves_for_markov_random_field_optimization}.
 
@@
 %challenging problems with a large label space.
-Our idea is very simple and the method is easily reproducible with
-minimal coding.
+Our idea is very simple. We believe that the method is easily
+reproducible with minimal coding, and would have immediate impact on
+numerous Computer Vision researchers or engineers, who currently solve
+MRF problems.
 % will instantly benefit every Computer Vision researcher or

### 2016-03-11 paper/stereo.tex

@@
 %
-We use Middlebury stereo datasets for the experiments.
+We use images from the Middlebury stereo benchmark~\cite{middlebury_stereo}.
 
@@
 %
-For SF-SS, we have chosen $\alpha=2$ ($\beta=0$). For SF-MF, each thread
-iterates the step of ($\alpha=1, \beta=0$) or ($\alpha=0, \beta=1$) so
-that it can take a solution proposal in one step and a neighboring
-solution in the next. For the standard SF, we have used ($\alpha=1, \beta=1$).
+SF-SS implies $\beta=0$, where $\alpha$ is the free parameter and set to
+2. SF-MF implies $\alpha+\beta=1$, where each thread iterates the step
+of ($\alpha=1, \beta=0$) or ($\alpha=0, \beta=1$) so that it can take a
+solution proposal in one step and a neighboring solution in the
+next. For standard SF, we have used ($\alpha=1, \beta=1$).
 %

### 2016-03-11 OpticalFlow/OpticalFlowCalculation.cpp
OpticalFlow

@@ -6,8 +6,8 @@
 #include <opencv2/cudaarithm.hpp>
 #include <opencv2/cudaoptflow.hpp>
 
-#include "lib/OpticalFlow/OpticalFlow.h"
-#include "lib/OpticalFlow/GaussianPyramid.h"
+// #include "lib/OpticalFlow/OpticalFlow.h"
+// #include "lib/OpticalFlow/GaussianPyramid.h"
 
 using namespace std;
 using namespace cv;
@@ -72,45 +72,45 @@ std::vector<std::pair<double, double> > calcFlowsFarneback(const cv::Mat &image_
 
 std::vector<std::pair<double, double> > calcFlowsLayerWise(const cv::Mat &image_1, const cv::Mat &image_2, const double ALPHA, const double RATIO)
 {
-  const int IMAGE_WIDTH = image_1.cols;
-  const int IMAGE_HEIGHT = image_1.rows;
+//   const int IMAGE_WIDTH = image_1.cols;
+//   const int IMAGE_HEIGHT = image_1.rows;
 
-  // Mat image_1_small, image_2_small;
-  // downSample(img1, img1_small, nLevel);
-  // downSample(img2, img2_small, nLevel);
-  DImage d_image_1, d_image_2, d_flow_image;
-  //copy image data to DImage
-  d_image_1.allocate(image_1.cols, image_1.rows, image_1.channels());
-  d_image_2.allocate(image_2.cols, image_2.rows, image_2.channels());
-  for (int pixel = 0; pixel < IMAGE_WIDTH * IMAGE_HEIGHT; pixel++) {
-    Vec3b color_1 = image_1.at<Vec3b>(pixel / IMAGE_WIDTH, pixel % IMAGE_WIDTH);
-    for (int c = 0; c < 3; c++)
-      d_image_1[pixel * 3 + c] = 1.0 * color_1[c] / 255;
-    Vec3b color_2 = image_2.at<Vec3b>(pixel / IMAGE_WIDTH, pixel % IMAGE_WIDTH);
-    for (int c = 0; c < 3; c++)
-      d_image_2[pixel * 3 + c] = 1.0 * color_2[c] / 255;
-  }
+//   // Mat image_1_small, image_2_small;
+//   // downSample(img1, img1_small, nLevel);
+//   // downSample(img2, img2_small, nLevel);
[…]

### 2016-03-11 OpticalFlow/main.cpp

@@ -1,4 +1,4 @@
-//#include <gflags/gflags.h>
+#include <gflags/gflags.h>
 
 #include <iostream>
 #include <fstream>
@@ -16,6 +16,7 @@
 #include "OpticalFlowUtils.h"
 #include "OpticalFlowFusionSolver.h"
 #include "OpticalFlowProposalGenerator.h"
+
 
 // DEFINE_int32(num_fusion_iterations, 1, "The number of iterations in fusion pipeline.");
 // DEFINE_int32(num_threads, 1, "The number of threads.");
@@ -100,8 +101,8 @@ int main(int argc, char *argv[])
     ParallelFusion::HFusionPipeline<LABELSPACE> h_fusion_pipeline(option);
     h_fusion_pipeline.runHFusion(all_proposals, solvers, LABELSPACE(vector<pair<double, double> >(IMAGE_WIDTH * IMAGE_HEIGHT)));
 
-    list<ParallelFusion::Observation> observations = h_fusion_pipeline.getGlobalProfile().getProfile();
-    for (list<ParallelFusion::Observation>::const_iterator observation_it = observations.begin(); observation_it != observations.end(); observation_it++) {
+    vector<ParallelFusion::Observation> observations = h_fusion_pipeline.getGlobalProfile().getProfile();
+    for (vector<ParallelFusion::Observation>::const_iterator observation_it = observations.begin(); observation_it != observations.end(); observation_it++) {
       cout << observation_it->first << '\t' << observation_it->second << endl;
     }
     exit(1);

### 2016-03-11 OpticalFlow/run_comparison_threads.sh

@@ -1,0 +1,4 @@
+./OpticalFlow --num_threads=1 --num_iterations=20 --num_proposals_in_total=2 --num_proposals_from_others=0 -- --solution_exchange_interval=3 --result_index=5
+./OpticalFlow --num_threads=2 --num_iterations=20 --num_proposals_in_total=2 --num_proposals_from_others=1 -- --solution_exchange_interval=3 --result_index=6
+./OpticalFlow --num_threads=4 --num_iterations=20 --num_proposals_in_total=2 --num_proposals_from_others=1 -- --solution_exchange_interval=3 --result_index=7
+./OpticalFlow --num_threads=8 --num_iterations=20 --num_proposals_in_total=2 --num_proposals_from_others=1 -- --solution_exchange_interval=3 --result_index=8

### 2016-03-11 base/ParallelFusionPipeline.h

@@ -222,30 +222,33 @@ namespace ParallelFusion {
                 const int num_proposals_from_others = (iter + 1) % thread_option.solution_exchange_interval == 0 ? thread_option.kOtherThread : 0;
 
                 bool grabbed_solution_from_self = false;
-                if (option.selectionMethod == ParallelFusionOption::RANDOM) {
+		if (num_proposals_from_others > 0) {
+		  if (option.selectionMethod == ParallelFusionOption::RANDOM) {
                     for(auto pid=0; pid < num_proposals_from_others; ++pid) {
-                        int idshift = distribution(seed);
-                        int tid = (id + idshift) % (int)slaveThreadIds.size();
-                        SolutionType<LABELSPACE> s;
-                        bestSolutions[tid].get(s);
-                        proposals.appendSpace(s.second);
+		      int idshift = distribution(seed);
+		      int tid = (id + idshift) % (int)slaveThreadIds.size();
+		      SolutionType<LABELSPACE> s;
+		      bestSolutions[tid].get(s);
+		      proposals.appendSpace(s.second);
                     }
-                } else if (option.selectionMethod == ParallelFusionOption::BEST) { //
+		  } else if (option.selectionMethod == ParallelFusionOption::BEST) { //
                     std::vector<std::pair<double, int> > solution_energy_index_pairs(slaveThreadIds.size());
                     for(auto tid=0; tid < slaveThreadIds.size(); ++tid)
+		      if (tid != id)
                         solution_energy_index_pairs[tid] = std::make_pair(bestSolutions[tid].getEnergy(), tid);
                     sort(solution_energy_index_pairs.begin(), solution_energy_index_pairs.end());
                     for(auto pid=0; pid < num_proposals_from_others; ++pid) {
-                        int tid = solution_energy_index_pairs[pid].second;
-                        if (tid == id) {
-                            grabbed_solution_from_self = true;
-                            continue;
-                        }
-                        SolutionType<LABELSPACE> s;
-                        bestSolutions[tid].get(s);
-                        proposals.appendSpace(s.second);
+		      int tid = solution_energy_index_pairs[pid].second;
+		      if (tid == id) {
+			grabbed_solution_from_self = true;
+			continue;
+		      }
+		      SolutionType<LABELSPACE> s;
+		      bestSolutions[tid].get(s);
+		      proposals.appendSpace(s.second);
                     }
-                }
+		  }
+		}
 
[…]

### 2016-03-11 paper/stereo.tex
Hang

@@
 %
-Unary terms are computed as the average Normalized Cross Correlation
-score between the reference image and the others inside a $7\times 7$
-pixels window. Pairwise terms are simple Pottz model. The total energy
-is defined by the sum of the two, while scaling the pairwise term by a
-factor of \yasu{X value}.
+Unary terms are computed as the average robust photoconsistancy
+score~\cite{woodford} between the reference image and the others inside a $7\times 7$
+pixels window.
+\begin{equation}
+  \text{\hang{equation to fill in}}
+\end{equation}
+Pairwise terms are simple truncated absolute label
+difference with maximum label difference $\sigma_s=4$. The total energy is
+defined by the sum of the two, while scaling the pairwise term by a
+factor of $0.005$. For simplicity we don't enforce visibility constraint.
+
 %
-We use images from the Middlebury stereo benchmark~\cite{middlebury_stereo}.
+We performed our experiments on Book sequence from Middlebury stereo datasets.~\cite{middlebury_stereo}.
 
@@
 fusion method (i.e., the use of proposal generation) rather makes it slow
-due to the overhead.  Therefore, we have chosen Parallel
+due to the overhead.\hang{Don't quite understand this sentence.
+Does the ``dominant'' means running time or energy?
+In my experiments, unary terms are pre-computed and are not counted into the running time}  Therefore, we have chosen Parallel
 Alpha Expansion~\cite{delong} and Hierarchical Fusion~\cite{delong,olga}
 with graph-cuts optimization as the competing methods.
+
+add Alpha Expansion.
+uniform and random splitting for parallel alpha expansion
 
@@
 next. For standard SF, we have used ($\alpha=1, \beta=1$).
+
+after 4 iterations (alpha, beta),
+
 %

### 2016-03-12 paper/optical_flow.tex
comments

@@
 Fusion Move was first introduced by Lempitsky et al.~\cite{viktor} to
-solve the optical flow problem.
+solve the optical flow problem. \chen{Again, I think Lempitsky's work doesn't
+  aim at the optical flow problem.}
 %Optical flow was the problem, in which the Fusion Move method was first
@@
 We copy their problem setting and proposal generation schemes for
-our second problem.  We use images from the Middlebury optical flow
+our second problem.
+  We use images from the Middlebury optical flow
 benchmark~\cite{middlebury_optical_flow}.
+
+\chen{I made a mistake that I didn't use the same proposal generation schemes
+  with their work.
+Instead of HS algorithm, I use Farneback algorithm to generate proposals because it is right there in OpenCV.
+I also add a bunch of other less useful proposals to have more proposal generation schemes for more clear comparisons..
+  I think we could write in short as follows.}
+
+\chen{We share similar proposal generation schemes with Lempitsky et al ~\cite{viktor}, but instead of the HS algorithm, we use more recent Farneback algorithm and changes its pyramid levels from 1 to 5 and use different polyN {3, 5, 7}.
+Besides the clustering idea, ~\cite{viktor} also suggests to use more proposals generation schemes based on the current solution.
+We add three simple proposal generation schemes to better explore the power of our parallel pipeline.
+In \textit{shift proposal}, the flow field in the current solution is shifted in either x direction or y direction for either 1, 2 or 3 pixels.
+In \textit{stagger proposal}, the flow field is shifted by a vector randomly drawed from a Gaussian distribution.
+In \textit{disturb proposal}, each flow value in the field is indenpendantly shifted by a vector randomly drawed from a Gaussian distribution.}
 
@@
 our experiments, we have manually picked a good number (X \yasu{how many
-Hang?}) to generate proposals.
+  Hang?}) \chen{77 proposals in total (We first generate 11 proposals using LK and Farneback algorithms which do not require current solution and generate other proposals based on these initial proposals).} to generate proposals.
 %
@@
 ($\alpha=1, \beta=0$) and ($\alpha=0, \beta=1$) for SF-MF, and
-($\alpha=1, \beta=1$) for SF.
+($\alpha=1, \beta=1$) \chen{($\alpha=2, \beta=0$) and ($\alpha=0, \beta=2$)} for SF.
 %
@@
 the competing methods. We have used TRW-S for multi-way fusion and QPBO
-for binary fusion.
+for binary fusion. \chen{Just for clarification, I always use TRW-S and just set the number of
+  labels to be 2. It is the same with QPBO as mentioned by Pushmeet.}
 %, while our fusions are multi-way, for which we have used TRW-S.
@@
 % Fig.~\ref{fig:model} with restrictions.
+
+2 k-way 1 solution sharing. \chen{?}

### 2016-03-12 paper/results.tex
result_section

@@
 
+The figure illustrates the convergence rate of three competing methods
+(alpha expansion, parallel alpha expansion, hierarchical fusion) against
+our swarm fusion method (only binary fusion without proposal
+generation \chen{We generate proposals on the fly for optical flow and layered depth map.
+So the time actually includes proposal generation stage which can be ignored.
+I think we can just delete this sentence.}).
+
 \begin{figure}[tb]
- \includegraphics[width=\columnwidth]{figure/result_layered_depthmap.pdf}
- \caption{}\label{fig:result_layered_depthmap}
+  \includegraphics[width=\columnwidth]{figure/optical_flow_convergence.pdf}
+  \caption{}\label{fig:optical_flow_convergence}
 \end{figure}
+\begin{figure}[tb]
+ \includegraphics[width=\columnwidth]{figure/layered_depthmap_convergence.pdf}
+ \caption{}\label{fig:layered_depthmap_convergence}
+\end{figure}
+
+\chen{
+  From the convergence plot of layered depth map estimation, we can see that, Fusion Move, Parallel Fusion Move, and FS-MF all stalk at a high energy state.
+The reason is binary fusion of solution proposals (either from others or self) is too limited to further decrease the energy due to the complexity of the problem itself.
+Only when multi-way fusion is used (in FS-SS and FS), it becomes possible for the energy to further decrease.
+This coincides with the observation in \cite{layered_depthmap} that binary fusion of proposal solutions is not as powerful as their subspace fusion which is a special form of multi-way fusion here.
+
+  As shown in \ref{section:results}, the multi-way fusion and solution sharing enabled by our uniform framework play a key role for improving performance in different settings.
+For better understanding our framework, we examine the role played by each factor more closely by varying each factor while keeping others the same.
+There are four parameters in our framework: \textit{the number of threads}, \textit{the number }
+}

### 2016-03-12 stereo/code/simplestereo/simplestereo.cpp
Hang

@@ -151,36 +151,54 @@ namespace simple_stereo {
         sprintf(buffer, "%s/temp/unaryDisp.jpg", file_io.getDirectory().c_str());
         unaryDisp.saveImage(buffer, 256.0 / (double)model->nLabel);
 
-//        cout << "========================================" << endl;
-//        cout << "Runing sequential alpha-expansion" << endl;
-//        ParallelOptimize optimize_sequential(file_io, model, 1);
-//        Depth result_sequential;
-//        optimize_sequential.optimize(result_sequential, 2);
-//        sprintf(buffer, "%s/temp/result_sequential.jpg", file_io.getDirectory().c_str());
-//        result_sequential.saveImage(buffer);
+        cout << "========================================" << endl;
+        cout << "Runing sequential alpha-expansion" << endl;
+        ParallelOptimize optimize_sequential(file_io, model,  1, "Sequential");
+        Depth result_sequential;
+        optimize_sequential.optimize(result_sequential, 2);
+        sprintf(buffer, "%s/temp/result_sequential.jpg", file_io.getDirectory().c_str());
+        result_sequential.saveImage(buffer);
 
         cout << "========================================" << endl;
         cout << "Runing parallel method with solution sharing" << endl;
-        ParallelOptimize optimize_parallel(file_io, model, 4, true);
+        ParallelOptimize optimize_parallel(file_io, model, 4, "Swarn");
         Depth result_parallel;
         optimize_parallel.optimize(result_parallel, 2);
         sprintf(buffer, "%s/temp/result_parallel.jpg", file_io.getDirectory().c_str());
         result_parallel.saveImage(buffer);
 
-//        cout << "========================================" << endl;
-//        cout << "Runing Victor's method" << endl;
-//        VictorOptimize optimize_victor(file_io, model, 4);
-//        Depth result_victor;
-//        optimize_victor.optimize(result_victor, 2);
-//        sprintf(buffer, "%s/temp/result_victor.jpg", file_io.getDirectory().c_str());
-//        result_victor.saveImage(buffer);
-//
-//        HierarchyOptimize optimize_hierarchy(file_io, model, 6);
-//        Depth result_hierarchy;
-//        optimize_hierarchy.optimize(result_hierarchy, 1);
-//        sprintf(buffer, "%s/temp/result_hierarchy.jpg", file_io.getDirectory().c_str());
-//        cout << "Saving " << buffer << endl << flush;
[…]

### 2016-03-12 paper/algorithm.tex

@@
 $T_i$), determining its processing flow: In each fusion step, a thread
-collects $\alpha_i$ solution proposals from the proposal pool and
+collects $\alpha_i$ solution proposals from the proposal pool \chen{A proposal pool sounds confusing.
+We often don't really maintain such a pool as many proposals are generated dynamically based on current solution.
+We just have certain strategies right there and in each iteration, we pick some strategies to generate proposals on the fly.
+This is different with the solution pool which is really there.}
 $\beta_i$ solutions from the solution pool, based on a user-defined
@@
  Fusion~\cite{delong_hierarchical_fusion,olga}, are all special cases of
- SF.}\label{fig:model}
+ SF.} \label{fig:model}
 \end{figure}
@@
 The bottom right architecture is the most general one, in which threads
-always fuse some solution proposals and some concurrent solutions (i.e.,
+always fuse some solution proposals and \chen{or?} some concurrent solutions (i.e.,
 $\alpha\ne 0, \beta \ne 0$).
@@
 in general, for which effective inference techniques such as
-TRW~\cite{kolmogorov,opengm} exist.
+TRW~\cite{kolmogorov,opengm} \chen{TRW-S?} exist.
 %, and hence we use TRW~\cite{kolmogorov} for the fusion, while any other
@@
 proposal generation scheme. PAE is realized by setting
-$(\alpha=1,\beta=1)$ with multiple threads, again with a restriction on
+$(\alpha=1,\beta=1)$ \chen{$(\alpha=1,\beta=0)$} with multiple threads, again with a restriction on
 the proposal generation scheme (the last sequential fusion in PAE is

### 2016-03-12 paper/layered_depthmap.tex

@@
 \subsection{Swarm Fusion layered depthmap estimation}
+
 Our last problem is layered depthmap estimation, recently proposed
@@
 Layered depthmap estimation is one of the most difficult kinds in MRF
-inference due to its massive solution space. The number of labels per
+inference due to its massive solution space \chen{and complex energy function?}. The number of labels per
 pixel is exponential in the number of layers, and is an order of 100,000
-\yasu{is this number correc?}. We copy their problem
+\yasu{is this number correc?} \chen{The number is correct but ``an order of'' sounds strange to me. Maybe say: usually between 100,000 and 10,000,000.}. We copy their problem
 formulation and the proposal generation schemes.~\footnote{Authors have
@@
 single solution is generated by a proposal generation scheme. Since a
-solution subspace is equivalent to multiple solution proposals, their
+solution subspace is equivalent to multiple solution proposals \chen{It is a good explanation for this paper's purpose, but from the perspective of our previous work, I am reluctant to say a subspace equals to multiple solution proposals.
+When we design proposals, we find the subspace directly and there's no concept of solution proposals (we later simplify our subspace proposals to binary labels just for the comparison reason).
+It is essentially the same, but a subspace proposal is conceptually more general than concatenated solution proposals.}, their
 algorithm can be easily integrated into our swarm fusion framework.
@@
 \noindent The three swarm architectures with the same configurations as
-in the optical flow problems have been evaluated.
+in the optical flow problems have been evaluated. \chen{same with optical flow, but slightly
+  different with stereo (1 sharing in 3 iterations instead of 5 iterations).}
 %in Fig.~\ref{fig:model} are evaluated.

### 2016-03-12 paper/results.tex

@@
 This coincides with the observation in \cite{layered_depthmap} that binary fusion of proposal solutions is not as powerful as their subspace fusion which is a special form of multi-way fusion here.
-
-  As shown in \ref{section:results}, the multi-way fusion and solution sharing enabled by our uniform framework play a key role for improving performance in different settings.
-For better understanding our framework, we examine the role played by each factor more closely by varying each factor while keeping others the same.
-There are four parameters in our framework: \textit{the number of threads}, \textit{the number }
 }

### 2016-03-12 paper/stereo.tex
Hang

@@
 of the three problems.
+
+\hang{Better to explain the methology we used, either here or in
+  Result part. For example:}
+
+\hang{To evaluate the effectness of different parallel structures, we
+  plot the energy minimization process against time. We define the
+  energy of the parallel system at a certain time as the minimum
+  energy of all threads at that time.}
 
@@
 stereo problems.  Our experiments have also supported this, where the
-fusion method (i.e., the use of proposal generation) rather makes it slow
-due to the overhead.\hang{Don't quite understand this sentence.
-Does the ``dominant'' means running time or energy?
-In my experiments, unary terms are pre-computed and are not counted into the running time}  Therefore, we have chosen Parallel
-Alpha Expansion~\cite{delong} and Hierarchical Fusion~\cite{delong,olga}
+fusion method (i.e., the use of proposal generation) rather makes it
+slow due to the overhead.\hang{Don't quite understand this
+  sentence. Does the ``dominant'' means running time or energy? In my
+  experiments, unary terms are pre-computed and are not counted into
+  the running time} Therefore, we have chosen Parallel Alpha
+Expansion~\cite{delong} and Hierarchical Fusion~\cite{delong,olga}
 with graph-cuts optimization as the competing methods.
+
+Since the optimization in the above stereo problem is fairly easy, we
+compare our method with both parallel alpha expansion
+\cite{first_fusion_viktor} and hierarchy fusion \cite{olga}.
 

### 2016-03-12 paper/stereo.tex
Hang

@@
 Since the optimization in the above stereo problem is fairly easy, we
-compare our method with both parallel alpha expansion
-\cite{first_fusion_viktor} and hierarchy fusion \cite{olga}.
-
-add Alpha Expansion.
-uniform and random splitting for parallel alpha expansion
+compare our method with standard sequential alpha expansion, parallel
+alpha expansion \cite{first_fusion_viktor} and hierarchy fusion
+\cite{olga}. In all experiment, we use $\alpha$-expansion to fuse
+single label proposals, and QPBO to fuse multi-label proposals.
 

### 2016-03-12 OpticalFlow/OpticalFlowFusionSolver.cpp
minor changes

@@ -39,8 +39,8 @@ namespace flow_fusion {
 
       for (int c = 0; c < 3; c++)
         color_vec.push_back(color_high_freq[c]);
-      for (int c = 0; c < 3; c++)
-        color_vec.push_back(color[c]);
+      //for (int c = 0; c < 3; c++)
+      //color_vec.push_back(color[c]);
       return color_vec;
     }
 
@@ -118,10 +118,10 @@ namespace flow_fusion {
       vector<double> color_1 = getImageColor(true, pixel_1 % IMAGE_WIDTH_, pixel_1 / IMAGE_WIDTH_);
       vector<double> color_2 = getImageColor(false, pixel_2 % IMAGE_WIDTH_, pixel_2 / IMAGE_WIDTH_);
       double color_distance = cv_utils::calcDistance(color_1, color_2);
-      double weight = exp(-pow(color_distance, 0.8));
+      //double weight = exp(-pow(color_distance, 0.8));
       //  double color_difference = calcDistance(convertVec3bToVector(image_1_.at<Vec3b>(pixel_1 / IMAGE_WIDTH_, pixel_1 % IMAGE_WIDTH_)), convertVec3bToVector(image_1_.at<Vec3b>(pixel_2 / IMAGE_WIDTH_, pixel_2 % IMAGE_WIDTH_)));
       //double weight = 1; //0.01 * exp(-pow(color_difference / 30, 2) / 2);
-      //double weight = color_difference < 30 ? 0.024 : 0.008;
+      double weight = color_distance < 30 ? 0.024 : 0.008;
       smoothness_cost *= weight;
       // double flow_distance = sqrt(pow(flow_1.first - flow_2.first, 2) + pow(flow_1.second - flow_2.second, 2));
 

### 2016-03-12 OpticalFlow/OpticalFlowFusionSolver.h

@@ -34,7 +34,7 @@ namespace flow_fusion {
         const int IMAGE_WIDTH_;
         const int IMAGE_HEIGHT_;
 
-        const double SMOOTHNESS_TERM_WEIGHT_ = 5;
+        const double SMOOTHNESS_TERM_WEIGHT_ = 1;
 
         std::vector<std::map<int, double> > pixel_neighbor_weights_;
 

### 2016-03-12 OpticalFlow/main.cpp

@@ -128,7 +128,7 @@ int main(int argc, char *argv[])
     generators[i] = shared_ptr<ParallelFusion::ProposalGenerator<LABELSPACE> >(new OpticalFlowProposalGenerator(image_1, image_2));
     solvers[i] = shared_ptr<ParallelFusion::FusionSolver<LABELSPACE> >(new OpticalFlowFusionSolver(image_1, image_2));
     initials[i].setSingleLabels(vector<pair<double, double> >(IMAGE_WIDTH * IMAGE_HEIGHT));
-    
+
     thread_options[i].kTotal = FLAGS_num_proposals_in_total;
     thread_options[i].kOtherThread = FLAGS_num_proposals_from_others;
     thread_options[i].solution_exchange_interval = FLAGS_solution_exchange_interval;

### 2016-03-12 OpticalFlow/run_comparison_methods.sh

@@ -1,5 +1,10 @@
-./OpticalFlow --num_threads=1 --num_iterations=50 --num_proposals_in_total=1 --num_proposals_from_others=0 --result_index=0
-./OpticalFlow --num_threads=5 --num_iterations=30 --num_proposals_in_total=1 --num_proposals_from_others=0 --solution_exchange_interval=3 --use_monitor_thread=true --result_index=1
-./OpticalFlow --num_threads=5 --num_iterations=30 --num_proposals_in_total=1 --num_proposals_from_others=1 --solution_exchange_interval=3 --use_monitor_thread=true --result_index=2
-./OpticalFlow --num_threads=5 --num_iterations=20 --num_proposals_in_total=2 --num_proposals_from_others=0 --solution_exchange_interval=3 --use_monitor_thread=true --result_index=3
-./OpticalFlow --num_threads=5 --num_iterations=20 --num_proposals_in_total=2 --num_proposals_from_others=2 --solution_exchange_interval=3 --use_monitor_thread=true --result_index=4
+./OpticalFlow --num_threads=1 --num_iterations=200 --num_proposals_in_total=1 --num_proposals_from_others=0 --result_index=0
+./OpticalFlow --num_threads=5 --num_iterations=100 --num_proposals_in_total=1 --num_proposals_from_others=0 --solution_exchange_interval=3 --use_monitor_thread=true --result_index=1
+./OpticalFlow --num_threads=5 --num_iterations=100 --num_proposals_in_total=1 --num_proposals_from_others=1 --solution_exchange_interval=3 --use_monitor_thread=true --result_index=2
+./OpticalFlow --num_threads=5 --num_iterations=50 --num_proposals_in_total=3 --num_proposals_from_others=0 --solution_exchange_interval=3 --use_monitor_thread=true --result_index=3
+./OpticalFlow --num_threads=5 --num_iterations=50 --num_proposals_in_total=3 --num_proposals_from_others=3 --solution_exchange_interval=3 --use_monitor_thread=true --result_index=4
+
+./OpticalFlow --num_threads=1 --num_iterations=20 --num_proposals_in_total=2 --num_proposals_from_others=0 -- --solution_exchange_interval=3 --result_index=5
+./OpticalFlow --num_threads=2 --num_iterations=20 --num_proposals_in_total=2 --num_proposals_from_others=1 -- --solution_exchange_interval=3 --result_index=6
[…]

### 2016-03-12 base/ParallelFusionPipeline.h

@@ -194,7 +194,7 @@ namespace ParallelFusion {
                                                           SolverPtr solver,
                                                           const ThreadOption &thread_option){
       try {
-	srand(id + 1);
+	srand(id);
             printf("Thread %d lauched\n", id);
             std::default_random_engine seed;
             std::uniform_int_distribution<int> distribution(1, (int)slaveThreadIds.size() - 1);

### 2016-03-12 paper/introduction.tex

@@
 \section{Introduction}
+\hang{Should we use $\alpha$-expansion instead of alpha-expansion?}
+
 Parallel computation has changed the field of computing.  In the 90s,
@@
 MRF problems.
+\chen{We will share our implementation of our pipeline with clear interface,
+  so that others can utilizing the parallel pipeline with minimal coding}
 % will instantly benefit every Computer Vision researcher or

### 2016-03-12 paper/results.tex
figure

@@
-\section{Experimental results} \label{section:results}
+\section{Experimental results}
+\label{section:results}
 We have implemented the algorithms in C++ and conducted the experiments
@@
 
+%\hang{figure file missing}
 \begin{figure}[tb]
-  \includegraphics[width=\columnwidth]{figure/optical_flow_convergence.pdf}
+  \includegraphics[width=\columnwidth]{figure/optical_flow_convergence.png}
   \caption{}\label{fig:optical_flow_convergence}
@@
 \begin{figure}[tb]
- \includegraphics[width=\columnwidth]{figure/layered_depthmap_convergence.pdf}
+ \includegraphics[width=\columnwidth]{figure/layered_depthmap_convergence.png}
  \caption{}\label{fig:layered_depthmap_convergence}
@@
 }
+
+\chen{
+  As shown in \ref{section:results}, the multi-way fusion and solution sharing enabled by our uniform framework play a key role for improving performance in different settings.
+For better understanding our framework, we examine the role played by each factor more closely by varying each factor while keeping others the same.
+There are four parameters in our framework: \textit{the number of threads}, \textit{the number alpha}, \textit{the number beta}, \textit{the number of iterations between each solution sharing}.
+}

### 2016-03-12 OpticalFlow/main.cpp
pipeline fusion from all others

@@ -115,7 +115,7 @@ int main(int argc, char *argv[])
   ParallelFusion::ParallelFusionOption option;
   option.num_threads = FLAGS_num_threads;
   option.max_iteration = FLAGS_num_iterations;
-  option.selectionMethod = ParallelFusion::ParallelFusionOption::BEST;
+  option.selectionMethod = ParallelFusion::ParallelFusionOption::ALL;
   //option.synchronize = true;
   
   

### 2016-03-12 base/ParallelFusionPipeline.h

@@ -19,7 +19,7 @@
 
 namespace ParallelFusion {
 
-    template<class LABELSPACE>
+  template<class LABELSPACE>
     class ParallelFusionPipeline {
     public:
         //solver should be read only
@@ -248,8 +248,46 @@ namespace ParallelFusion {
 		      bestSolutions[tid].get(s);
 		      proposals.appendSpace(s.second);
                     }
-		  }
-		}
+		  } else if (option.selectionMethod == ParallelFusionOption::ALL) { //
+		    proposals.appendSpace(current_solution.second);
+		    int num_proposals_to_fuse = 1;
+                    for (auto tid = 0; tid < slaveThreadIds.size(); ++tid) {
+		      if (tid == id)
+			continue;
+		      
+                      SolutionType<LABELSPACE> s;
+                      bestSolutions[tid].get(s);
+                      proposals.appendSpace(s.second);
+		      
+                      num_proposals_to_fuse++;
+                      if (num_proposals_to_fuse == thread_option.kTotal) {
+                        SolutionType<LABELSPACE> curSolution;
+                        solver->solve(proposals, current_solution, curSolution);
+                        current_solution = curSolution;
+                        proposals = curSolution.second;
+                        num_proposals_to_fuse = 1;
+                      }
+                    }
+                    float dt = ((float)cv::getTickCount() - start_time) / (float)cv::getTickFrequency();
+                    threadProfile[slaveThreadIds[id]].push_back(Observation(dt, current_solution.first));
+                    globalProfile.addObservation(dt, current_solution.first);
+
+                    generator->writeSolution(current_solution, slaveThreadIds[id], iter);
+
+                    //if synchronization is needed, thread won't submit solution unless
+                    //last submitted solution is read by the monitor thread.
+                    if(option.synchronize){
+                      while(!write_flag[id].load())
+                        std::this_thread::yield();
+                    }
+		    
+                    bestSolutions[id].set(current_solution);
+                    //if(option.synchronize) //Always set this flag so that a minotor could know whether results are ready, synchronization is guaranteed it the minotor thread set the flag to true.
+                    write_flag[id].store(false);
+		    
+                    return;
+                  }
+                }
 
                 int num_proposals_from_self = thread_option.kTotal - num_proposals_from_others;
                 if (grabbed_solution_from_self)
@@ -354,7 +392,7 @@ namespace ParallelFusion {
 
 
[…]

### 2016-03-12 base/pipeline_util.h

@@ -98,7 +98,7 @@ namespace ParallelFusion{
         bool synchronize;
 
 
-        enum SolutionSelection{RANDOM, BEST};
+      enum SolutionSelection{RANDOM, BEST, ALL};
         SolutionSelection selectionMethod;
     };
 

### 2016-03-12 paper/results.tex

@@
 \end{figure}
+\begin{figure}[tb]
+  \includegraphics[width=\columnwidth]{figure/optical_flow_by_threads.png}
+  \caption{}\label{fig:optical_flow_by_threads}
+\end{figure}
 
+\chen{
+  There are interesting pattern in the convergence plot of optical flow estimation problem.
+As both FS-MF and PAE are doing binary fusion, FS-MF finds lower energy faster than PAE.
+The reason is as follows.
+Some solution proposals are more effective than others, so once a thread grabs an effective solution proposal, it find a much lower energy.
+Since there is no solution sharing in PAE model, other threads cannot share this lower energy state, and keeps working on improving its own state.
+On the other hand, FS-MF allows solution sharing, so once a thread grabs an effective solution proposal and moves to a lower energy state, other threads can share this lower energy state.
+To further demonstrate what is happening here, we plot the energy-time for each thread in PAE and FS-MF in figure \ref{fig:optical_flow_by_threads}.
+As we can see from the figure, in PAE model, one thread finds lower energy state faster than others, while other threads waste resources working at a high energy state.
+But in FS-MF model, all threads exchange information about the lowest energy state and work on improving the lowest energy state together.
+Same comparison holds for FS-SS and FS.
+}
   \chen{

### 2016-03-13 paper/results.tex
results_section

@@
 \begin{figure}[tb]
+  \includegraphics[width=\columnwidth]{figure/layered_depthmap_by_alpha.png}
+  \caption{}\label{fig:layered_depthmap_by_alpha}
+\end{figure}
+\begin{figure}[tb]
   \includegraphics[width=\columnwidth]{figure/optical_flow_by_threads.png}
   \caption{}\label{fig:optical_flow_by_threads}
+\end{figure}
+\begin{figure}[tb]
+  \includegraphics[width=\columnwidth]{figure/optical_flow_by_beta.png}
+  \caption{}\label{fig:optical_flow_by_beta}
 \end{figure}
@@
 To further demonstrate what is happening here, we plot the energy-time for each thread in PAE and FS-MF in figure \ref{fig:optical_flow_by_threads}.
-As we can see from the figure, in PAE model, one thread finds lower energy state faster than others, while other threads waste resources working at a high energy state.
+As we can see from the plots, in PAE model, one thread finds lower energy state faster than others, while other threads keep working at their own energy state.
 But in FS-MF model, all threads exchange information about the lowest energy state and work on improving the lowest energy state together.
+So there are more chance of finding effective proposals faster and thus the energy goes down faster.
+Since the solution for optical flow can be locally improved by each thread, the final merging of PAE can effectively fuse good local results in different threads together and achieve a similar energy state with FS-MF model.
+Because FS-MF model shares information in the middle, a final merging becomes less necessary.
 Same comparison holds for FS-SS and FS.
 }
+
+\chen{
+  To further understand the effect of solution sharing, we did two other experiments.
+In one experiment, we change the number of solutions each thread grabed from others from 0 to 3 (as there are 4 threads in total) while keeping others the same.
+The energy-time plot is shown in figure \ref{fig:optical_flow_by_beta}.
+In another experiment, we change the number of iterations between two consecutive solution sharing iterations as in figure \ref{fig:optical_flow_by_interval}.
+}
+
 \chen{
@@
 This coincides with the observation in \cite{layered_depthmap} that binary fusion of proposal solutions is not as powerful as their subspace fusion which is a special form of multi-way fusion here.
+To further explore the effect of multi-way fusion, we use different $\alpha$ {1, 3, 7, 15} in FS model while keeping other parameters the same and plot the energy-time curve in figure \ref{fig:layered_depth_map_by_alpha}.
 }

### 2016-03-13 paper/results.tex
Hang
results.tex

@@
 (alpha expansion, parallel alpha expansion, hierarchical fusion) against
-our swarm fusion method (only binary fusion without proposal
-generation \chen{We generate proposals on the fly for optical flow and layered depth map.
-So the time actually includes proposal generation stage which can be ignored.
-I think we can just delete this sentence.}).
+our swarm fusion method.
 
@@
 \end{figure}
+\begin{figure}[tb]
+  \includegraphics[width=\columnwidth]{figure/optical_flow_by_interval.png}
+  \caption{}\label{fig:optical_flow_by_interval}
+\end{figure}
 
@@
 In one experiment, we change the number of solutions each thread grabed from others from 0 to 3 (as there are 4 threads in total) while keeping others the same.
-The energy-time plot is shown in figure \ref{fig:optical_flow_by_beta}.
+The energy-time plots are shown in figure \ref{fig:optical_flow_by_beta}.
+As shown in the figure, energy decreases faster with solution sharing.
+While since we need to perform one fusion for sharing each solution, sharing more solution leads to unnecessary overhead in this problem setting.
+While sharing multiple solutions might be benefitial in some problem setting as it means each thread can get more global information early.
 In another experiment, we change the number of iterations between two consecutive solution sharing iterations as in figure \ref{fig:optical_flow_by_interval}.
+From the figure, we can see that although solution sharing generally speed up the optimization process, sharing solution too frequently is not a good practice.
+This is because When we share solution frequently, we have less time for generating and fusing new proposals.
+A good choice of the solution sharing frequency depends on specific problem setting.
 }

### 2016-03-13 paper/result_stereo.tex

\mysubsubsection{Stereo}
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/stereo_global.eps}
  \caption{The energy minimization process of difference parallel systems.}
  \label{fig:stereo_global}
\end{figure}

\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/stereo_threads.png}
  \caption{Per thread energy. The left and right figures show the energy minimization process on each working thread of our method in SF-MF configuration and parallel $\alpha$-expansion method, respectively. The energy is in $\log$ scale}
  \label{fig:stereo_global}
\end{figure}

Figure \ref{fig:stereo_global} shows the

\hang{}

### 2016-03-13 paper/result_stereo.tex
Hang

@@
 \mysubsubsection{Stereo}
+
+We performed our experiments on the half-size Book sequence from Middlebury stereo
+datasets.~\cite{middlebury_stereo}. We use 7 images with the
+resolution of $695\times555$ and optimize for 256 disparity labels. We
+recoreded both single thread energy and system energy (minimum energy
+so far from all threads) against time.
+
 \begin{figure}[tb]
@@
   \includegraphics[width=\columnwidth]{figure/stereo_threads.png}
-  \caption{Per thread energy.
-The left and right figures show the energy minimization process on each working thread of our method in SF-MF configuration and parallel $\alpha$-expansion method, respectively.
-The energy is in $\log$ scale}
-  \label{fig:stereo_global}
+  \caption{Per thread energy. The left and right figures show the
+    energy minimization process on each working thread of our method
+    in SF-MF configuration and parallel $\alpha$-expansion method,
+    respectively. The energy is in $\log$ scale}
+  \label{fig:stereo_threads}
 \end{figure}
 
-Figure \ref{fig:stereo_global} shows the
+Figure \ref{fig:stereo_global} shows the energy minimization process
+against time. In this experiment, both PAE and SF-MF converge faster
+than sequential method. However, since fusing solutions with multiple
+labels by QPBO is slower than a single $\alpha$-expansion, PAE method
+reaches convergence faster than SF-MF. Architectures with multiway
+fusion, e.g. SF and SF-SS perform worse than PAE and SF-MF, because
+the TRWS algorihtm used in multiway fusion is slower than multiple
+$\alpha$-expansion. Finally, the line of hierarchy fusion only makes
+jump when fusing on root node of the tree. This is because any fusion
+step on non-root nodes only have partial label information.
 
-\hang{}
+Figure \ref{fig:stereo_threads} shows the per-thread energy
+minimization process in SF-MF and PAE. The per-thread energy in SF-MF
+architecture decreases more uniformly than that of PAE. In the
+scenario where we need to query the best solution so far before the
+whole optimization converges, SF-MF architecture is a better choice.
+
+For a easy optimization problem as shown in this section, our full
+architecture with solution sharing and multiway fusion actually makes
+convergence slower by adopting sophisticated algorihtm and introducing
+multi-threading overhead. However, we can easily configure the
+architecture to make it better fit the problem, e.g. turn off multiway
+fusion and/or solution sharing.
+
+\hang{The end of stereo experiment......}

### 2016-03-13 paper/stereo.tex
Hang

@@
   plot the energy minimization process against time. We define the
-  energy of the parallel system at a certain time as the minimum
+  energy of a parallel system at a certain time as the minimum
   energy of all threads at that time.}
@@
 %
-We performed our experiments on Book sequence from Middlebury stereo datasets.~\cite{middlebury_stereo}.
 

### 2016-03-13 paper/algorithm.tex
hang

@@
  Fusion~\cite{delong_hierarchical_fusion,olga}, are all special cases of
- SF.} \label{fig:model}
+ SF.}
+ \label{fig:model}
 \end{figure}

### 2016-03-13 paper/result_stereo.tex
hang

@@
 
-We performed our experiments on the half-size Book sequence from Middlebury stereo
+We performed our experiments on the Book sequence from Middlebury stereo
 datasets.~\cite{middlebury_stereo}. We use 7 images with the
@@
 recoreded both single thread energy and system energy (minimum energy
-so far from all threads) against time.
+so far from all threads) against time. Since the order of labels to be
+expanded or fused will have impact on minimization, we randomly
+shuffled 256 labels and provide this order to all methods.
 

### 2016-03-13 paper/results.tex
hang

@@
 \label{section:results}
-We have implemented the algorithms in C++ and conducted the experiments
-on Linux PCs with Intel Core i7 processor with 4 cores, enabling 8 threads
-with the hyper threading technology. We have used the Graph-cuts
-optimization code written by Veksler, using the libraries provided by
-Boykov and Kolmogorov~\cite{middle_bury,2,3,4_below}.
+We have implemented the algorithms with multithreading supporting from
+C++ 11 and conducted the experiments on Linux PCs with Intel Core i7
+4790 processor with 4 cores, enabling 8 threads with the hyper
+threading technology. We have used the Graph-cuts optimization code
+written by Veksler, using the libraries provided by Boykov and
+Kolmogorov~\cite{middle_bury,2,3,4_below}.
 % [2] Fast Approximate Energy Minimization via Graph Cuts.
@@
 Kolmogorov~\cite{msr_link?,trw_link}.
+
+\input{result_stereo}
 

### 2016-03-13 LayerDepthMap/Statistics/Binary/convertValues.m
Statistics

@@ -1,0 +1,19 @@
+function [ time_energy_values ] = convertValues( raw_values )
+%UNTITLED Summary of this function goes here
+%   Detailed explanation goes here
+
+start_time = raw_values(1, 1);
+previous_energy = inf;
+%time_energy_values = [0, previous_energy]
+for i = 2:size(raw_values, 1)
+    if (raw_values(i, 2) <= previous_energy)
+        if (i == 2)
+            time_energy_values = [raw_values(i, 1) - start_time, raw_values(i, 2)];
+        else
+            time_energy_values = [time_energy_values; raw_values(i, 1) - start_time, raw_values(i, 2)];
+        end
+        previous_energy = raw_values(i, 2);
+    end
+end
+
+end

### 2016-03-13 LayerDepthMap/Statistics/Binary/readNumbers.sh

@@ -1,0 +1,3 @@
+#!/bin/bash
+
+cat output | awk '{ print $5 " " $8 }' > output_values

### 2016-03-13 LayerDepthMap/Statistics/readNumbers.sh

@@ -1,0 +1,19 @@
+#!/bin/bash
+
+cat output_sequential | awk '{ print $5 "\t" $8 "\t" $7 }' > output_values_sequential
+cat output_Victor | awk '{ print $5 "\t" $8 "\t" $7}' > output_values_Victor
+cat output_solution_exchange | awk '{ print $5 "\t" $8 "\t" $7 }' > output_values_solution_exchange
+cat output_multiway | awk '{ print $5 "\t" $8 "\t" $7 }' > output_values_multiway
+cat output_full | awk '{ print $5 "\t" $8 "\t" $7 }' > output_values_full
+
+cat output_full_2_2| awk '{ print $5 "\t" $8 "\t" $7}' > output_values_full_2_2
+cat output_full_4_3 | awk '{ print $5 "\t" $8 "\t" $7 }' > output_values_full_4_3
+cat output_full_5_3 | awk '{ print $5 "\t" $8 "\t" $7 }' > output_values_full_5_3
+cat output_full_7_3 | awk '{ print $5 "\t" $8 "\t" $7 }' > output_values_full_7_3
+cat output_full_9_3 | awk '{ print $5 "\t" $8 "\t" $7 }' > output_values_full_9_3
+cat output_full_15_3 | awk '{ print $5 "\t" $8 "\t" $7 }' > output_values_full_15_3
+
+cat output_multiway_5| awk '{ print $5 "\t" $8 "\t" $7}' > output_values_multiway_5
+cat output_multiway_7| awk '{ print $5 "\t" $8 "\t" $7}' > output_values_multiway_7
+cat output_multiway_9| awk '{ print $5 "\t" $8 "\t" $7}' > output_values_multiway_9
+cat output_multiway_11| awk '{ print $5 "\t" $8 "\t" $7}' > output_values_multiway_11

### 2016-03-13 OpticalFlow/Statistics/plotValues.m

@@ -1,0 +1,48 @@
+sequential_raw_values = load('output_values_sequential');
+sequential = convertValues(sequential_raw_values, 0);
+Victor_raw_values = load('output_values_Victor');
+Victor = convertValues(Victor_raw_values, 1);
+solution_exchange_raw_values = load('output_values_solution_exchange_5');
+solution_exchange = convertValues(solution_exchange_raw_values, 0);
+multiway_raw_values = load('output_values_multiway');
+multiway = convertValues(multiway_raw_values, 0);
+full_raw_values = load('output_values_full');
+full = convertValues(full_raw_values, 0);
+hierarchy_raw_values = load('output_values_hierarchy');
+hierarchy = convertValues(hierarchy_raw_values, 0);
+
+dlmwrite('statistics_sequential.txt', sequential, '\t');
+dlmwrite('statistics_Victor.txt', Victor, '\t');
+dlmwrite('statistics_solution_exchange.txt', solution_exchange, '\t');
+dlmwrite('statistics_multiway.txt', multiway, '\t');
+dlmwrite('statistics_full.txt', full, '\t');
+
+
+Victor_by_thread = {4};
+for (thread = 0:3)
+    thread_values = convertValues([Victor_raw_values(1, :); Victor_raw_values(find(Victor_raw_values(:, 3) == thread), :)], 0);
+        Victor_by_thread{thread + 1} = thread_values;
+end
+%dlmwrite('thread_Victor.txt', Victor_by_thread, '\t');
+
+solution_exchange_by_thread = {4}
+for (thread = 0:3)
+    thread_values = convertValues([solution_exchange_raw_values(1, :); solution_exchange_raw_values(find(solution_exchange_raw_values(:, 3) == thread), :)], 0);
+        solution_exchange_by_thread{thread + 1} = thread_values;
+end
+%dlmwrite('thread_solution_exchange.txt', solution_exchange_by_thread, '\t');
+
+
+%plot(sequential(:, 1), sequential(:, 2), '-xm', Victor(:, 1), Victor(:,
+%2), '-.c', solution_exchange(:, 1), solution_exchange(:, 2), '-*b', multiway(:, 1), multiway(:, 2), '-og', full(:, 1), full(:, 2), '-+r');
[…]

### 2016-03-13 paper/stereo.tex

@@
 Computer Vision. SF framework has high degrees of freedom and the
-challenge is to properly quantity the contributions of various
+challenge is to properly quantify the contributions of various
 algorithmic aspects. For this purpose, we have used the three SF
-architectures illustrated in Fig.~\ref{fig:model}. For some problems, we
-have further limited the capabilities of SF on purpose, to enable
+architectures illustrated in Fig.~\ref{fig:model}. For some problems,
+we have further limited the capabilities of SF on purpose, to enable
 effective and fair comparative evaluations. We now explain the details
@@
   plot the energy minimization process against time. We define the
-  energy of a parallel system at a certain time as the minimum
-  energy of all threads at that time.}
+  energy of a parallel system at a certain time as the minimum energy
+  of all threads at that time.}
 
@@
     flow~\cite{middlebury_optical_flow}, or a layered depthmap
- estimation~\cite{layered_depthmap} problem. In the layered depthmap
- problem, the input is an RGBD image, and the output is multiple layeres
- of depthmaps. Each layer is a piecewise smooth parametric surface
- model.}\label{fig:problem}
+    estimation~\cite{layered_depthmap} problem. In the layered
+    depthmap problem, the input is an RGBD image, and the output is
+    multiple layeres of depthmaps. Each layer is a piecewise smooth
+    parametric surface model.}\label{fig:problem}
 \end{figure}
@@
 We start with a simple depthmap stereo problem with standard unary and
-pairwise terms. We employ submodular pairwise terms to make this stereo
-represent relatively ``easy'' MRF inference problems.
+pairwise terms. We employ submodular pairwise terms to make this
+stereo represent relatively ``easy'' MRF inference problems.
 %
 Unary terms are computed as the average robust photoconsistancy
-score~\cite{woodford} between the reference image and the others inside a $7\times 7$
-pixels window.
-\begin{equation}
-  \text{\hang{equation to fill in}}
-\end{equation}
-Pairwise terms are simple truncated absolute label
-difference with maximum label difference $\sigma_s=4$. The total energy is
-defined by the sum of the two, while scaling the pairwise term by a
-factor of $0.005$. For simplicity we don't enforce visibility constraint.
+score~\cite{woodford} between the reference image and the others
+inside a $7\times 7$ pixels window.  Pairwise terms are simple
+truncated absolute label difference with maximum label difference
+$\sigma_s=4$. The total energy is defined by the sum of the two, while
+scaling the pairwise term by a factor of $0.005$. For simplicity we
+don't enforce visibility constraint.
 
@@
   experiments, unary terms are pre-computed and are not counted into
-  the running time} Therefore, we have chosen Parallel Alpha
-Expansion~\cite{delong} and Hierarchical Fusion~\cite{delong,olga}
-with graph-cuts optimization as the competing methods.
-
-Since the optimization in the above stereo problem is fairly easy, we
-compare our method with standard sequential alpha expansion, parallel
-alpha expansion \cite{first_fusion_viktor} and hierarchy fusion
-\cite{olga}. In all experiment, we use $\alpha$-expansion to fuse
-single label proposals, and QPBO to fuse multi-label proposals.
+  the running time} Therefore, we have chosen standard sequential
+$\alpha$-expansion, Parallel Alpha Expansion(PAE)~\cite{delong} and
+Hierarchical Fusion~\cite{delong,olga} with graph-cuts optimization as
+the competing methods.
 
@@
 %
-SF-SS implies $\beta=0$, where $\alpha$ is the free parameter and set to
-2. SF-MF implies $\alpha+\beta=1$, where each thread iterates the step
-of ($\alpha=1, \beta=0$) or ($\alpha=0, \beta=1$) so that it can take a
-solution proposal in one step and a neighboring solution in the
-next. For standard SF, we have used ($\alpha=1, \beta=1$).
-
-after 4 iterations (alpha, beta),
+SF-SS implies $\beta=0$, where $\alpha$ is the free parameter and set
+to 4. In this case one thread will fuse 4 labels by TRW-S per
+iteration and never exchanges solutions with other threads. SF-MF
+implies $\alpha+\beta=1$, where each thread will expand 3 labels
+(repeat $\alpha=1, \beta=0$ for 3 iterations) and then fuse one
+solution from other threads ($\alpha=0, \beta=1$) by QPBO. In the later
+case, a thread randomly chooses one target thread to grab solution
+from. For standard SF, we have used ($\alpha=4, \beta=1$). For the
+SF-SS architecture, we performed a final fuse of solutions from all
+thread by multiway fusion.
 
@@
 %
-To make the comparison simple, we restrict our proposal
-generation to be constant-label proposals. Graph-cuts is used in fusing
-a constant-label proposal as the energy is submodular. QPBO is used in
+To make the comparison simple, we restrict our proposal generation to
+be constant-label proposals. Graph-cuts is used in fusing a
+constant-label proposal as the energy is submodular. QPBO is used in
 fusing a different solution from another thread as the energy is

### 2016-03-13 paper/algorithm.tex
bib

@@
 %for fusion.
-SF has 1) a {\it proposal pool}, from which a thread picks arbitrary
-number of proposal generation schemes and generates proposals, and 2) a
+SF has 1) a {\it proposal generator} for each thread, with which a thread
+picks arbitrary number of proposal generation schemes and generates proposals, and 2) a
 {\it solution pool}, from which a thread picks arbitrary number of
@@
 
-SF has two main parameters $\alpha_i$ and $\beta_i$ (for each thread
+SF has three main parameters $\alpha_i$, $\beta_i$ (for each thread
 $T_i$), determining its processing flow: In each fusion step, a thread
@@
  It is easy to verify that existing popular MRF inference methods such
- as Alpha Expansion~\cite{alpha_expansion}, Fusion Move~\cite{FM},
- Parallel Alpha Expansion~\cite{delong}, or Hierarchical
- Fusion~\cite{delong_hierarchical_fusion,olga}, are all special cases of
+ as Alpha Expansion~\cite{alpha_expansion}, Fusion Move~\cite{fusion_moves_for_markov_random_field_optimization},
+ Parallel Alpha Expansion~\cite{olga_hierarchical_alpha_expansion}, or Hierarchical
+ Fusion~\cite{delong_hierarchical_fusion}, are all special cases of
  SF.}
@@
 in general, for which effective inference techniques such as
-TRW~\cite{kolmogorov,opengm} \chen{TRW-S?} exist.
+TRW-S~\cite{TRW-S,opengm} exist.
 %, and hence we use TRW~\cite{kolmogorov} for the fusion, while any other
@@
 submodular energy, one can use
-graph-cuts~\cite{alpha_expansion_paper}. If a certain fusion step is a
+graph-cuts~\cite{alpha_expansion}. If a certain fusion step is a
 binary fusion with non-submodular energy, one can use
-QPBO~\cite{second_order_smoothness_stereo}.
+QPBO~\cite{second_order_stereo}.
 %
@@
 \noindent It is easy to verify that Alpha-Expansion
-(AE)~\cite{alpha_expansion}, Fusion Move (FM)~\cite{viktor}, Parallel
-Alpha Expansion (PAE)~\cite{delong}, and Hierarchical Fusion
-(HF)~\cite{delong_hierarchical,olga} are all special cases of the Swarm
+(AE)~\cite{alpha_expansion}, Fusion Move (FM)~\cite{fusion_moves_for_markov_random_field_optimization}, Parallel
+Alpha Expansion (PAE)~\cite{fusion_moves_for_markov_random_field_optimization}, and Hierarchical Fusion
+(HF)~\cite{delong_hierarchical_fusion,olga_hierarchical_alpha_expansion} are all special cases of the Swarm
 Fusion method (SF). AE can be realized by setting $(\alpha=1, \beta=0)$ and

### 2016-03-13 paper/introduction.tex
bib

@@
 many Computer Vision problems. Take a Fusion Move method
-(FM)~\cite{viktor,second_order_stereo,else} for example, which has been
+(FM)~\cite{fusion_flow,fusion_moves_for_markov_random_field_optimization,second_order_stereo} for example, which has been
 one of the most effective techniques for Markov Random Field (MRF)
@@
 step.~\footnote{Recently, an extension of FM was proposed for layered
-depthmap estimation~\cite{chen_2016}, where a solution subspace, instead
+depthmap estimation~\cite{layered_depthmap}, where a solution subspace, instead
 of a single solution, is proposed and fused with the current
@@
 numerous Computer Vision researchers or engineers, who currently solve
-MRF problems.
-\chen{We will share our implementation of our pipeline with clear interface,
-  so that others can utilizing the parallel pipeline with minimal coding}
+MRF problems. We will share our implementation of our pipeline which provides
+parallism through simple interfaces.
 % will instantly benefit every Computer Vision researcher or

### 2016-03-13 stereo/code/plotEnergy.m
Hang

@@ -3,9 +3,9 @@ function [plots_global, plots_thread] = plotEnergy(dataset, nt, max_time)
 % dataset: path to root of dataset
 % nt: number of threads
 set(0, 'DefaultAxesFontName', 'Times New Roman');
-set(0, 'DefaultAxesFontSize', 25);
+set(0, 'DefaultAxesFontSize', 28);
 set(0, 'DefaultTextFontname', 'Times New Roman');
-set(0, 'DefaultTextFontSize', 25);
+set(0, 'DefaultTextFontSize', 28);
 
 method_name = {'Sequential', 'Swarn_multiway', 'Swarn', 'Victor_multiway', 'Victor', 'Hierarchy'};
 legend_name_global = {'Sequential alpha-expansion', 'SF', 'SF-MF', 'SF-SS', 'Parallel alpha-expansion', 'Hierarchy'};

### 2016-03-13 paper/related_work.tex
comments
yasu

@@
 al.~\cite{hierarchical_graph_cuts_kumar_and_koller}, Delong et
-al.~\cite{delong}, and Veksler~\cite{olga} proposed an hierarchical
+al.~\cite{delong_hierarchical_fusion}, and Veksler~\cite{olga_hierarchical_alpha_expansion} proposed an hierarchical
 approach, where labels can be simultaneously fused from the bottom to
@@
 \noindent The core MAP inference itself can be parallelized.  Strandmark
-et al. parallelized graph-cuts~\cite{strandmark2010parallel}.
+et al. parallelized graph-cuts~\cite{strandmark_parallel}.
 %
@@
 \noindent FM was first introduced by Lempitsky et al. in solving an
-optical flow problem~\cite{first_fusion_viktor}. FM has been effectively
-used to solve challenging problems in Computer Vision such as stereo
-with second order smoothness priors~\cite{woodford}, stereo
-with parameteric surface fitting and segmentation (i.e., Surface
-Stereo)~\cite{surface_stereo}, or multicut
-partitioning~\cite{fusionmovesforcorrelationclustering}.
+optical flow problem~\cite{fusion_flow}. FM has been effectively used to solve challenging
+problems in Computer Vision such as stereo with second order smoothness
+priors~\cite{second_order_stereo}, stereo with parameteric surface fitting and
+segmentation (i.e., Surface Stereo)~\cite{surface_stereo}, or multicut
+partitioning~\cite{fusion_moves_for_correlation_clustering}.
 %
 FM has two main advantages over the other general inference
-techniques~\cite{trw,loopy_belief_propagation}. First, FM allows us to
+techniques~\cite{TRW-S,loopy_belief_propagation}. First, FM allows us to
 exploit domain-specific knowledge in customizing proposal generation

### 2016-03-13 paper/results.tex

@@
 written by Veksler, using the libraries provided by Boykov and
-Kolmogorov~\cite{middle_bury,2,3,4_below}.
+Kolmogorov~\cite{middlebury_mrf,2,3,4_below}.
 % [2] Fast Approximate Energy Minimization via Graph Cuts.
@@
 We have used the QPBO and TRW-S implementations by
-Kolmogorov~\cite{msr_link?,trw_link}.
+Kolmogorov~\cite{}.
 

### 2016-03-13 paper/stereo.tex

@@
     compare our Swarm Fusion method against competing approaches on a
-    depthmap stereo~\cite{middle_bury_stereo}, an optical
+    depthmap stereo~\cite{middlebury_stereo}, an optical
     flow~\cite{middlebury_optical_flow}, or a layered depthmap
@@
 $\alpha$-expansion, Parallel Alpha Expansion(PAE)~\cite{delong} and
-Hierarchical Fusion~\cite{delong,olga} with graph-cuts optimization as
+Hierarchical Fusion~\cite{delong_hierarchical_fusion,olga_hierarchical_alpha_expansion} with graph-cuts optimization as
 the competing methods.

### 2016-03-13 paper/introduction.tex
Hang

@@
 game of {\it Go}, parallelization plays a key role in the Monte-Carlo
-tree search~\cite{nature_alpha_go}.
+tree search~\cite{silver2016mastering}.
 
@@
 SLRs (e.g., Canon EOS 5DS), stitch thousands of images to generate gigapixel
-panoramas~\cite{gigapan}, or solve volumetric reconstruction and
+panoramas~\cite{kopf2007capturing}, or solve volumetric reconstruction and
 segmentation problems over a billion ($=1024^3$)
-voxels~\cite{Joint3DSceneReconstructionandclassSegmentation}.
+voxels~\cite{hane2013joint}.
 %
 %
-However, state-of-the-art algorithms are still inherently sequential in
-many Computer Vision problems. Take a Fusion Move method
-(FM)~\cite{fusion_flow,fusion_moves_for_markov_random_field_optimization,second_order_stereo} for example, which has been
-one of the most effective techniques for Markov Random Field (MRF)
-inference, including the above problems like image denoising, image
-stitching, or volumetric reconstruction.
+However, state-of-the-art algorithms are still inherently sequential
+in many Computer Vision problems. Take a Fusion Move method
+(FM)~\cite{fusion_flow,fusion_moves_for_markov_random_field_optimization,second_order_stereo}
+for example, which has been one of the most effective techniques for
+Markov Random Field (MRF) inference, including the above problems like
+image denoising, image stitching, or volumetric reconstruction.
 %

### 2016-03-13 paper/results.tex
Hang

@@
 written by Veksler, using the libraries provided by Boykov and
-Kolmogorov~\cite{middlebury_mrf,2,3,4_below}.
+Kolmogorov~\cite{middlebury_mrf,alpha_expansion,
+  what_energy_can_be_min_by_gc, mrf_experimental}.
 % [2] Fast Approximate Energy Minimization via Graph Cuts.

### 2016-03-13 paper/stereo.tex
Hang

@@
 Unary terms are computed as the average robust photoconsistancy
-score~\cite{woodford} between the reference image and the others
+score~\cite{second_order_stereo} between the reference image and the others
 inside a $7\times 7$ pixels window.  Pairwise terms are simple

### 2016-03-13 paper/results.tex
Hang

--- 2016-03-13 paper/results.tex
@@
 written by Veksler, using the libraries provided by Boykov and
-Kolmogorov~\cite{middlebury_mrf,2,3,4_below}.
+Kolmogorov~\cite{middlebury_mrf,alpha_expansion,what_energy_can_be_min_by_gc, mrf_experimental}.
 % [2] Fast Approximate Energy Minimization via Graph Cuts.
@@
 We have used the QPBO and TRW-S implementations by
-Kolmogorov~\cite{}.
+Kolmogorov~\cite{QPBO, TRW-S}.
 

### 2016-03-13 paper/algorithm.tex
figures

@@
 
-SF has three main parameters $\alpha_i$, $\beta_i$ (for each thread
+SF has two main parameters $\alpha_i$, $\beta_i$ (for each thread
 $T_i$), determining its processing flow: In each fusion step, a thread
-collects $\alpha_i$ solution proposals from the proposal pool \chen{A proposal pool sounds confusing.
+generates $\alpha_i$ solution proposals using its proposal generator, and collects
+%\chen{A proposal pool sounds confusing.
 We often don't really maintain such a pool as many proposals are generated dynamically based on current solution.
@@
 This is different with the solution pool which is really there.}
-$\beta_i$ solutions from the solution pool, based on a user-defined
-strategy or at random to be simple.
+$\beta_i$ or $0$ solutions from the solution pool, based on a user-defined
+strategy or at random to be simple. (The value of $\alpha_i$ and $\beta_i$ can vary in each iteration to encourage different behaviors.) The thread then fuse all these solutions
+together to find a solution with lower energy state and update the solution pool accordingly.
 %
@@
 The bottom right architecture is the most general one, in which threads
-always fuse some solution proposals and \chen{or?} some concurrent solutions (i.e.,
+conduct multi-way fusion of either solution proposals, or some concurrent solutions, or both (i.e.,
 $\alpha\ne 0, \beta \ne 0$).
 %
-Each fusion is multi-way (not binary) and the energy is not submodular
+And the energy is not submodular
 in general, for which effective inference techniques such as
@@
 with a (read-write) lock on the data in the two pools (See
-Algorithm~\ref{algorithm:sf}).
+Algorithm~\ref{algorithm:sf}). The asynchronous computing further unleashes the power of parallism.
 %The asynchronous processing could be difficult for cloud parallel
@@
   Solution pool
-  \State Initialize $\mathcal{P}_{pool}$ // Proposal pool
+  %\State Initialize $\mathcal{P}_{pool}$ // Proposal pool
   \ForEach{thread $T_i$}
@@
   \ForEach{thread $T_i$ in parallel till convergence}
-  \State Pick $\alpha$ solution proposals $\mathcal{P}\subset \mathcal{P_{\mbox{pool}}}$
+  \State Generate $\alpha$ solution proposals $\mathcal{P}$ %\subset \mathcal{P_{\mbox{pool}}}$
   \State Pick $\beta$ solutions $\mathcal{S} \subset \mathcal{S_{\mbox{pool}}}$
@@
   \State Replaces the solution in $\mathcal{S}_{pool}$ with $S_i$
-  \State [ Generates proposals and update $\mathcal{P}_{pool}$, if necessary ]
+  %\State [ Generates proposals and update $\mathcal{P}_{pool}$, if necessary ]
   \EndFor
@@
 proposal generation scheme. PAE is realized by setting
-$(\alpha=1,\beta=1)$ \chen{$(\alpha=1,\beta=0)$} with multiple threads, again with a restriction on
+$(\alpha=1,\beta=0)$ with multiple threads, again with a restriction on
 the proposal generation scheme (the last sequential fusion in PAE is

### 2016-03-13 paper/optical_flow.tex
figures

--- 2016-03-11 paper/optical_flow.tex
@@
 
-Fusion Move was first introduced by Lempitsky et al.~\cite{viktor} to
+Fusion Move was first introduced by Lempitsky et al.~\cite{fusion_flow} to
 solve the optical flow problem.
@@
 %introduced by Lempitsky et al.~\cite{viktor}.
-We copy their problem setting and proposal generation schemes for
-our second problem.  We use images from the Middlebury optical flow
+We copy their problem setting and use images from the Middlebury optical flow
 benchmark~\cite{middlebury_optical_flow}.
+We share similar proposal generation schemes with Lempitsky et al ~\cite{fusion_flow}, but instead of the HS algorithm, we use more recent Farneback algorithm and change its pyramid levels from 1 to 5 and use {3, 5, 7} as the parameter polyN.
+Besides the clustering idea, we add three simple proposal generation schemes based on the current solution as suggested in ~\cite{fusion_flow}.
+In \textit{shift proposal}, the flow field in the current solution is shifted in either x direction or y direction for either 1, 2 or 3 pixels.
+In \textit{stagger proposal}, the flow field is shifted by a vector randomly drawed from a Gaussian distribution.
+In \textit{disturb proposal}, each flow value in the field is indenpendantly shifted by a vector randomly drawed from a Gaussian distribution.
+We choose schemes randomly when generating proposals.
 
@@
 start from solution proposals as opposed to constant labels. One problem
-of HFM is that the number of necessary solution proposals is unknown
-before solving the problem, and the tree of labels cannot be defined. In
-our experiments, we have manually picked a good number (X \yasu{how many
-Hang?}) to generate proposals.
-%
-The fusions are binary in these methods and we have used QPBO.
+of HFM is that we need to generate all proposals at the very beginning in order to build the fusion tree.
+This undermines the power of fusion move to dynamically generate solution proposals based on current solution.
+In
+our experiments, we have manually generate 250 proposals at the beginning.
+We first generate 25 proposals using LK and Farneback algorithms which are independant and generate other proposals based on these initial proposals).
+The fusions are binary in these methods.
+% and we have used QPBO.
 
@@
 %are used to evaluate the effectiveness of our method.
-The three swarm architectures in Fig.~\ref{fig:model} (SF-SS, SF-MF, SF)
+The three swarm architectures in Fig.~\ref{fig:model} (SF-MF, SF-SS, SF)
 have been evaluated against the competing methods. The same
 configurations as in the stereo problem have been used for optical flow,
-that is, $\alpha=2$ ($\beta=0$) for SF-SS, the iteration of
+that is, ($\alpha=1$, $\beta=1$, $k=5$) for SF-MF, the iteration of
 ($\alpha=1, \beta=0$) and ($\alpha=0, \beta=1$) for SF-MF, and
-($\alpha=1, \beta=1$) for SF.
+($\alpha=1, \beta=1$) \chen{($\alpha=2, \beta=0$) and ($\alpha=0, \beta=2$)} for SF.
 %

### 2016-03-13 LayerDepthMap/Statistics/plotValues.m

@@ -32,6 +32,10 @@ for (thread = 0:3)
 end
 %dlmwrite('thread_solution_exchange.txt', solution_exchange_by_thread, '\t');
 
+set(0, 'DefaultAxesFontName', 'Times New Roman');
+set(0, 'DefaultAxesFontSize', 30);
+set(0, 'DefaultTextFontName', 'Times New Roman');
+set(0, 'DefaultTextFontSize', 30);
 
 %plot(sequential(:, 1), sequential(:, 2), '-xm', Victor(:, 1), Victor(:,
 %2), '-.c', solution_exchange(:, 1), solution_exchange(:, 2), '-*b', multiway(:, 1), multiway(:, 2), '-og', full(:, 1), full(:, 2), '-+r');\
@@ -42,6 +46,9 @@ xlabel('Time/s');
 ylabel('Energy');
 %ylim([8, 9.8]);
 fig_1.Position = [500, 500, 1280, 720];
+
+print(fig_1, '../../paper/figure/layered_depthmap_convergence', '-dpng');
+
 fig_2 = figure(2);
 %plot(Victor_by_thread{1}(:, 1), log(Victor_by_thread{1}(:, 2)), '-+m', Victor_by_thread{2}(:, 1), log(Victor_by_thread{2}(:, 2)), '-om', Victor_by_thread{3}(:, 1), log(Victor_by_thread{3}(:, 2)), '-*m', Victor_by_thread{4}(:, 1), log(Victor_by_thread{4}(:, 2)), '-xm', solution_exchange_by_thread{1}(:, 1), log(solution_exchange_by_thread{1}(:, 2)), '-+b', solution_exchange_by_thread{2}(:, 1), log(solution_exchange_by_thread{2}(:, 2)), '-+b', solution_exchange_by_thread{3}(:, 1), log(solution_exchange_by_thread{3}(:, 2)), '-*b', solution_exchange_by_thread{4}(:, 1), log(solution_exchange_by_thread{4}(:, 2)), '-xb', 'LineWidth', 2)
 plot(Victor_by_thread{1}(:, 1), log(Victor_by_thread{1}(:, 2)), Victor_by_thread{2}(:, 1), log(Victor_by_thread{2}(:, 2)), Victor_by_thread{3}(:, 1), log(Victor_by_thread{3}(:, 2)), Victor_by_thread{4}(:, 1), log(Victor_by_thread{4}(:, 2)), 'LineWidth', 2);
[…]

### 2016-03-13 LayerDepthMap/Statistics/plotValuesAlpha.m

@@ -30,17 +30,22 @@ multiway_11 = convertValues(multiway_11_raw_values, 0);
 % dlmwrite('statistics_multiway.txt', multiway, '\t');
 % dlmwrite('statistics_full.txt', full, '\t');
 
-
+set(0, 'DefaultAxesFontName', 'Times New Roman');
+set(0, 'DefaultAxesFontSize', 30);
+set(0, 'DefaultTextFontName', 'Times New Roman');
+set(0, 'DefaultTextFontSize', 30);
 
 %plot(sequential(:, 1), sequential(:, 2), '-xm', Victor(:, 1), Victor(:,
 %2), '-.c', solution_exchange(:, 1), solution_exchange(:, 2), '-*b', multiway(:, 1), multiway(:, 2), '-og', full(:, 1), full(:, 2), '-+r');\
-figure(1);
+fig = figure(1);
 %plot(full(:, 1), log(full(:, 2)), 'c', full_5_3(:, 1), log(full_5_3(:, 2)), 'b', full_7_3(:, 1), log(full_7_3(:, 2)), 'g', full_9_3(:, 1), log(full_9_3(:, 2)), 'r');
 plot(Victor(:, 1), log(Victor(:, 2)), multiway(:, 1), log(multiway(:, 2)), multiway_5(:, 1), log(multiway_5(:, 2)), multiway_7(:, 1), log(multiway_7(:, 2)), multiway_9(:, 1), log(multiway_9(:, 2)), multiway_11(:, 1), log(multiway_11(:, 2)), 'LineWidth', 2);
 legend('\alpha=1', '\alpha=3', '\alpha=5', '\alpha=7', '\alpha=9', '\alpha=11');
 xlabel('Time/s');
 ylabel('Energy');
 fig.Position = [500, 500, 1280, 720];
+
+print(fig, '../../paper/figure/layered_depthmap_by_alpha', '-dpng');
 
 
 

### 2016-03-13 OpticalFlow/Statistics/plotValues.m

@@ -11,11 +11,11 @@ full = convertValues(full_raw_values, 0);
 hierarchy_raw_values = load('output_values_hierarchy');
 hierarchy = convertValues(hierarchy_raw_values, 0);
 
-dlmwrite('statistics_sequential.txt', sequential, '\t');
-dlmwrite('statistics_Victor.txt', Victor, '\t');
-dlmwrite('statistics_solution_exchange.txt', solution_exchange, '\t');
-dlmwrite('statistics_multiway.txt', multiway, '\t');
-dlmwrite('statistics_full.txt', full, '\t');
+%dlmwrite('statistics_sequential.txt', sequential, '\t');
+%dlmwrite('statistics_Victor.txt', Victor, '\t');
+%dlmwrite('statistics_solution_exchange.txt', solution_exchange, '\t');
+%dlmwrite('statistics_multiway.txt', multiway, '\t');
+%lmwrite('statistics_full.txt', full, '\t');
 
 
 Victor_by_thread = {4};
@@ -38,17 +38,20 @@ end
 %figureHandle = gcf;
 
 set(0, 'DefaultAxesFontName', 'Times New Roman');
-set(0, 'DefaultAxesFontSize', 25);
+set(0, 'DefaultAxesFontSize', 30);
 set(0, 'DefaultTextFontName', 'Times New Roman');
-set(0, 'DefaultTextFontSize', 25);
+set(0, 'DefaultTextFontSize', 30);
 
 fig_1 = figure(1);
 plot(sequential(:, 1), log(sequential(:, 2)), '--', Victor(:, 1), log(Victor(:, 2)), '--', hierarchy(:, 1), log(hierarchy(:, 2)), '--', solution_exchange(:, 1), log(solution_exchange(:, 2)), multiway(:, 1), log(multiway(:, 2)), full(:, 1), log(full(:, 2)), 'LineWidth', 2);
-l = legend('FM', 'PFM', 'HF', 'SF-MF(ours)', 'SF-SS(ours)', 'SF(ours)');
+l = legend('FM', 'PFM', 'HFM', 'SF-MF(ours)', 'SF-SS(ours)', 'SF(ours)');
 xlabel('Time/s');
 ylabel('Energy');
 %ylim([8, 9.8]);
 fig_1.Position = [500, 500, 1280, 720];
+
[…]

### 2016-03-13 OpticalFlow/Statistics/plotValuesBeta.m

@@ -15,7 +15,10 @@ solution_exchange_3_other = convertValues(solution_exchange_3_other_raw_values, 
 % dlmwrite('statistics_multiway.txt', multiway, '\t');
 % dlmwrite('statistics_full.txt', full, '\t');
 
-
+set(0, 'DefaultAxesFontName', 'Times New Roman');
+set(0, 'DefaultAxesFontSize', 30);
+set(0, 'DefaultTextFontName', 'Times New Roman');
+set(0, 'DefaultTextFontSize', 30);
 
 %plot(sequential(:, 1), sequential(:, 2), '-xm', Victor(:, 1), Victor(:,
 %2), '-.c', solution_exchange(:, 1), solution_exchange(:, 2), '-*b', multiway(:, 1), multiway(:, 2), '-og', full(:, 1), full(:, 2), '-+r');\
@@ -26,4 +29,5 @@ xlabel('Time/s');
 ylabel('Energy');
 fig.Position = [500, 500, 1280, 720];
 
+print(fig, '../../paper/figure/optical_flow_by_beta', '-dpng');
 

### 2016-03-13 OpticalFlow/Statistics/plotValuesInterval.m

@@ -16,7 +16,10 @@ solution_exchange_9 = convertValues(solution_exchange_9_raw_values, 0);
 % dlmwrite('statistics_multiway.txt', multiway, '\t');
 % dlmwrite('statistics_full.txt', full, '\t');
 
-
+set(0, 'DefaultAxesFontName', 'Times New Roman');
+set(0, 'DefaultAxesFontSize', 30);
+set(0, 'DefaultTextFontName', 'Times New Roman');
+set(0, 'DefaultTextFontSize', 30);
 
 %plot(sequential(:, 1), sequential(:, 2), '-xm', Victor(:, 1), Victor(:,
 %2), '-.c', solution_exchange(:, 1), solution_exchange(:, 2), '-*b', multiway(:, 1), multiway(:, 2), '-og', full(:, 1), full(:, 2), '-+r');\
@@ -27,3 +30,4 @@ xlabel('Time/s');
 ylabel('Energy');
 fig.Position = [500, 500, 1280, 720];
 
+print(fig, '../../paper/figure/optical_flow_by_interval', '-dpng');

### 2016-03-14 paper/layered_depthmap.tex
results

--- 2016-03-11 paper/layered_depthmap.tex
@@
 inference due to its massive solution space. The number of labels per
-pixel is exponential in the number of layers, and is an order of 100,000
-\yasu{is this number correc?}. We copy their problem
+pixel is exponential in the number of layers, and is usually between 100,000 and 10,000,000. We copy their problem
 formulation and the proposal generation schemes.~\footnote{Authors have
@@
 single solution is generated by a proposal generation scheme. Since a
-solution subspace is equivalent to multiple solution proposals, their
-algorithm can be easily integrated into our swarm fusion framework.
+solution subspace can be represented by a concatenation of multiple solution proposals,
+% \chen{It is a good explanation for this paper's purpose, but from the perspective of our previous work, I am reluctant to say a subspace equals to multiple solution proposals.
+When we design proposals, we find the subspace directly and there's no concept of solution proposals (we later simplify our subspace proposals to binary labels just for the comparison reason).
+It is essentially the same, but a subspace proposal is conceptually more general than concatenated solution proposals.},
+their algorithm can be easily integrated into our swarm fusion framework.
 However, competing fusion methods (e.g., Parallel Fusion Move or

### 2016-03-14 paper/optical_flow.tex
results

@@
 solve the optical flow problem.
-%Optical flow was the problem, in which the Fusion Move method was first
+% Optical flow was the problem, in which the Fusion Move method was first
 %introduced by Lempitsky et al.~\cite{viktor}.
@@
 This undermines the power of fusion move to dynamically generate solution proposals based on current solution.
-In
-our experiments, we have manually generate 250 proposals at the beginning.
+In our experiments, we have manually generate 250 proposals at the beginning.
 We first generate 25 proposals using LK and Farneback algorithms which are independant and generate other proposals based on these initial proposals).
@@
 configurations as in the stereo problem have been used for optical flow,
-that is, ($\alpha=1$, $\beta=1$, $k=5$) for SF-MF, the iteration of
-($\alpha=1, \beta=0$) and ($\alpha=0, \beta=1$) for SF-MF, and
-($\alpha=1, \beta=1$) \chen{($\alpha=2, \beta=0$) and ($\alpha=0, \beta=2$)} for SF.
+that is, one iteration with ($\alpha=0, \beta=1$) in every 5 iterations and other iterations with ($\alpha=1, \beta=0$) for SF-MF, ($\alpha=3$, $\beta=0$) for SF-MF, and one iteration with ($\alpha=0, \beta=3$) in every 5 iterations and other iterations with ($\alpha=3, \beta=0$) for SF-MF.
+
 %
@@
 the competing methods. We have used TRW-S for multi-way fusion and QPBO
-for binary fusion. \chen{Just for clarification, I always use TRW-S and just set the number of
-  labels to be 2. It is the same with QPBO as mentioned by Pushmeet.}
-%, while our fusions are multi-way, for which we have used TRW-S.
+for binary fusion.
+% , while our fusions are multi-way, for which we have used TRW-S.
 %
@@
 % Fig.~\ref{fig:model} with restrictions.
-
-2 k-way 1 solution sharing. \chen{?}
+%
+% 2 k-way 1 solution sharing. \chen{?}

### 2016-03-14 paper/results.tex
figures
results

@@
   \includegraphics[width=\columnwidth]{figure/optical_flow_convergence.png}
-  \caption{}\label{fig:optical_flow_convergence}
+  \caption{The energy minimization process for optical flow estimation of different methods.
+FS-MF has the best performance because of the solution sharing in early stage.}\label{fig:optical_flow_convergence}
 \end{figure}
@@
  \includegraphics[width=\columnwidth]{figure/layered_depthmap_convergence.png}
- \caption{}\label{fig:layered_depthmap_convergence}
+ \caption{The energy minimization process for layered depthmap estimation of different methods.
+Multi-way fusion is shown to be more effectvie than binary fusion in this problem setting.}\label{fig:layered_depthmap_convergence}
 \end{figure}
@@
   \includegraphics[width=\columnwidth]{figure/layered_depthmap_by_alpha.png}
-  \caption{}\label{fig:layered_depthmap_by_alpha}
+  \caption{The energy minimization process for layered depthmap estimation with different $\alpha$ values.
+Multi-way fusion generally performs better than binary fusion, but the optimization becomes harder for using more ways in each step.}\label{fig:layered_depthmap_by_alpha}
 \end{figure}
 \begin{figure}[tb]
-  \includegraphics[width=\columnwidth]{figure/optical_flow_by_threads.png}
-  \caption{}\label{fig:optical_flow_by_threads}
+  \includegraphics[width=0.5\columnwidth]{figure/optical_flow_SF_MF_threads.png}
+  \includegraphics[width=0.5\columnwidth]{figure/optical_flow_PFM_threads.png}
+  \caption{Per thread energy.
+The left and right figures show the energy minimization process on each working thread of our method in SF-MF configuration and parallel fusion move, respectively.}\label{fig:optical_flow_by_threads}
 \end{figure}
@@
   \includegraphics[width=\columnwidth]{figure/optical_flow_by_beta.png}
-  \caption{}\label{fig:optical_flow_by_beta}
+  \caption{The energy minimization process for optical flow estimation with different $\beta$ values.
+Solution sharing generally makes energy minimization faster, but more solution sharing also means less time for exploring new solution proposals.}\label{fig:optical_flow_by_beta}
 \end{figure}
@@
   \includegraphics[width=\columnwidth]{figure/optical_flow_by_interval.png}
-  \caption{}\label{fig:optical_flow_by_interval}
+  \caption{The energy minimization process for optical flow estimation with different solution sharing frequency.
+Solution sharing generally makes energy minimization faster, but frequent solution sharing also means less time for exploring new solution proposals.}\label{fig:optical_flow_by_beta}\label{fig:optical_flow_by_interval}
 \end{figure}

### 2016-03-14 paper/results.tex
results

@@
 We have used the QPBO and TRW-S implementations by
-Kolmogorov~\cite{QPBO, TRW-S}.
+Kolmogorov~\cite{QPBO, TRW-S_implementation}.
 
@@
 
-\chen{
 There are interesting pattern in the convergence plot of optical flow estimation problem.
@@
 Same comparison holds for FS-SS and FS.
-}
 
-\chen{
 To further understand the effect of solution sharing, we did two other experiments.
@@
 A good choice of the solution sharing frequency depends on specific problem setting.
-}
 
-\chen{
 From the convergence plot of layered depth map estimation, we can see that, Fusion Move, Parallel Fusion Move, and FS-MF all stalk at a high energy state.
@@
 To further explore the effect of multi-way fusion, we use different $\alpha$ {1, 3, 7, 15} in FS model while keeping other parameters the same and plot the energy-time curve in figure \ref{fig:layered_depth_map_by_alpha}.
-}
 
-\chen{
 As shown in \ref{section:results}, the multi-way fusion and solution sharing enabled by our uniform framework play a key role for improving performance in different settings.
 For better understanding our framework, we examine the role played by each factor more closely by varying each factor while keeping others the same.
-There are four parameters in our framework: \textit{the number of threads}, \textit{the number alpha}, \textit{the number beta}, \textit{the number of iterations between each solution sharing}.
-}

### 2016-03-14 paper/optical_flow.tex
optical_flow

@@
 benchmark~\cite{middlebury_optical_flow}.
-We share similar proposal generation schemes with Lempitsky et al ~\cite{fusion_flow}, but instead of the HS algorithm, we use more recent Farneback algorithm and change its pyramid levels from 1 to 5 and use {3, 5, 7} as the parameter polyN.
+We share similar proposal generation schemes with Lempitsky et al~\cite{fusion_flow}, but instead of the HS algorithm, we use more recent Farneback algorithm and change its pyramid levels from 1 to 5 and use either 3, 5 or 7 for parameter polyN.
 Besides the clustering idea, we add three simple proposal generation schemes based on the current solution as suggested in ~\cite{fusion_flow}.

### 2016-03-14 paper/result_layered_depthmap.tex
results

--- 2016-03-14 paper/results.tex
@@
-\section{Experimental results}
-\label{section:results}
-We have implemented the algorithms with multithreading supporting from
-C++ 11 and conducted the experiments on Linux PCs with Intel Core i7
-4790 processor with 4 cores, enabling 8 threads with the hyper
-threading technology. We have used the Graph-cuts optimization code
-written by Veksler, using the libraries provided by Boykov and
-Kolmogorov~\cite{middlebury_mrf,alpha_expansion,what_energy_can_be_min_by_gc, mrf_experimental}.
-% [2] Fast Approximate Energy Minimization via Graph Cuts.
-%         Y. Boykov, O. Veksler, and R. Zabih.
-%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
-%         (PAMI), vol. 23, no. 11, pages 1222-1239, November 2001.  
-%
-%     [3] What Energy Functions can be Minimized via Graph Cuts?
-%         V. Kolmogorov and R. Zabih. 
-%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
-%         (PAMI), vol. 26, no. 2, pages 147-159, February 2004. 
-%         An earlier version appeared in European Conference on Computer
-%         Vision (ECCV), May 2002.
-%
-%     [4] An Experimental Comparison of Min-Cut/Max-Flow Algorithms for
-%         Energy Minimization in Vision. 
-%         Y. Boykov and Vladimir Kolmogorov.
-%         In IEEE Transactions on Pattern Analysis and Machine Intelligence
-%         (PAMI), vol. 26, no. 9, pages 1124-1137, September 2004. 
-We have used the QPBO and TRW-S implementations by
-Kolmogorov~\cite{QPBO, TRW-S_implementation}.
+\mysubsubsection{Layered Depthmap}
 
-\input{result_stereo}
-
-The figure illustrates the convergence rate of three competing methods
-(alpha expansion, parallel alpha expansion, hierarchical fusion) against
-our swarm fusion method.
-
-%\hang{figure file missing}
-\begin{figure}[tb]
-  \includegraphics[width=\columnwidth]{figure/optical_flow_convergence.png}
-  \caption{The energy minimization process for optical flow estimation of different methods.
-FS-MF has the best performance because of the solution sharing in early stage.}\label{fig:optical_flow_convergence}
-\end{figure}
 \begin{figure}[tb]
@@
 \end{figure}
-\begin{figure}[tb]
-  \includegraphics[width=0.5\columnwidth]{figure/optical_flow_SF_MF_threads.png}
-  \includegraphics[width=0.5\columnwidth]{figure/optical_flow_PFM_threads.png}
-  \caption{Per thread energy.
-The left and right figures show the energy minimization process on each working thread of our method in SF-MF configuration and parallel fusion move, respectively.}\label{fig:optical_flow_by_threads}
-\end{figure}
-\begin{figure}[tb]
-  \includegraphics[width=\columnwidth]{figure/optical_flow_by_beta.png}
-  \caption{The energy minimization process for optical flow estimation with different $\beta$ values.
-Solution sharing generally makes energy minimization faster, but more solution sharing also means less time for exploring new solution proposals.}\label{fig:optical_flow_by_beta}
-\end{figure}
-\begin{figure}[tb]
-  \includegraphics[width=\columnwidth]{figure/optical_flow_by_interval.png}
-  \caption{The energy minimization process for optical flow estimation with different solution sharing frequency.
-Solution sharing generally makes energy minimization faster, but frequent solution sharing also means less time for exploring new solution proposals.}\label{fig:optical_flow_by_beta}\label{fig:optical_flow_by_interval}
-\end{figure}
-
-There are interesting pattern in the convergence plot of optical flow estimation problem.
-As both FS-MF and PAE are doing binary fusion, FS-MF finds lower energy faster than PAE.
-The reason is as follows.
-Some solution proposals are more effective than others, so once a thread grabs an effective solution proposal, it find a much lower energy.
-Since there is no solution sharing in PAE model, other threads cannot share this lower energy state, and keeps working on improving its own state.
-On the other hand, FS-MF allows solution sharing, so once a thread grabs an effective solution proposal and moves to a lower energy state, other threads can share this lower energy state.
-To further demonstrate what is happening here, we plot the energy-time for each thread in PAE and FS-MF in figure \ref{fig:optical_flow_by_threads}.
-As we can see from the plots, in PAE model, one thread finds lower energy state faster than others, while other threads keep working at their own energy state.
-But in FS-MF model, all threads exchange information about the lowest energy state and work on improving the lowest energy state together.
-So there are more chance of finding effective proposals faster and thus the energy goes down faster.
-Since the solution for optical flow can be locally improved by each thread, the final merging of PAE can effectively fuse good local results in different threads together and achieve a similar energy state with FS-MF model.
-Because FS-MF model shares information in the middle, a final merging becomes less necessary.
-Same comparison holds for FS-SS and FS.
-
-To further understand the effect of solution sharing, we did two other experiments.
-In one experiment, we change the number of solutions each thread grabed from others from 0 to 3 (as there are 4 threads in total) while keeping others the same.
-The energy-time plots are shown in figure \ref{fig:optical_flow_by_beta}.
-As shown in the figure, energy decreases faster with solution sharing.
-While since we need to perform one fusion for sharing each solution, sharing more solution leads to unnecessary overhead in this problem setting.
-While sharing multiple solutions might be benefitial in some problem setting as it means each thread can get more global information early.
-In another experiment, we change the number of iterations between two consecutive solution sharing iterations as in figure \ref{fig:optical_flow_by_interval}.
-From the figure, we can see that although solution sharing generally speed up the optimization process, sharing solution too frequently is not a good practice.
-This is because When we share solution frequently, we have less time for generating and fusing new proposals.
-A good choice of the solution sharing frequency depends on specific problem setting.
 

### 2016-03-14 paper/result_optical_flow.tex
results

\mysubsubsection{Optical Flow}

% \hang{figure file missing}
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/optical_flow_convergence.png}
  \caption{The energy minimization process for optical flow estimation of different methods. FS-MF has the best performance because of the solution sharing in early stage.}\label{fig:optical_flow_convergence}
\end{figure}
\begin{figure}[tb]
  \includegraphics[width=0.5\columnwidth]{figure/optical_flow_SF_MF_threads.png}
  \includegraphics[width=0.5\columnwidth]{figure/optical_flow_PFM_threads.png}
  \caption{Per thread energy. The left and right figures show the energy minimization process on each working thread of our method in SF-MF configuration and parallel fusion move, respectively.}\label{fig:optical_flow_by_threads}
\end{figure}
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/optical_flow_by_beta.png}
  \caption{The energy minimization process for optical flow estimation with different $\beta$ values. Solution sharing generally makes energy minimization faster, but more solution sharing also means less time for exploring new solution proposals.}\label{fig:optical_flow_by_beta}
\end{figure}
\begin{figure}[tb]
  \includegraphics[width=\columnwidth]{figure/optical_flow_by_interval.png}
  \caption{The energy minimization process for optical flow estimation with different solution sharing frequency. Solution sharing generally makes energy minimization faster, but frequent solution sharing also means less time for exploring new solution proposals.}\label{fig:optical_flow_by_beta}\label{fig:optical_flow_by_interval}
\end{figure}

Figure \ref{fig:optical_flow_convergence} illustrates the convergence rate of three competing methods (alpha expansion, parallel alpha expansion, hierarchical fusion) against
our swarm fusion method. From the figure we can observe that, both conducting binary fusion, FS-MF finds lower energy faster than PFM. This is because some solution proposals are more effective than others, so once a thread grabs an effective solution proposal, it find a lower energy quickly. Since there is no solution sharing in PFM model, other threads cannot share this lower energy state, and keeps working on its own state. On the other hand, FS-MF allows solution sharing, so once a thread grabs an effective solution proposal and moves to a lower energy state, other threads can share this lower energy state. To further demonstrate what is happening here, we plot per thread energy in PFM and FS-MF in figure \ref{fig:optical_flow_by_threads}. As we can see from the plots, in PFM model, one thread finds lower energy state faster than others, while other threads keep working at their own energy state. But in FS-MF model, all threads exchange information about the lowest energy state and work on improving the lowest energy state together. So there are more chance of finding effective proposals faster. Since the solution for optical flow can be locally improved by each thread, the final merging of PFM can effectively fuse good local results in different threads together and achieve a similar energy state with FS-MF model. But since FS-MF model shares information in the middle, a final merging becomes less necessary. Same comparison holds for FS-SS and FS. The multi-way fusion is ineffective in this problem setting since solution proposals are relatively independant and fusing multiple solutions together using TRW-S~\cite{TRW-S} is less efficient than fusing them one by one using~\cite{QPBO}.

They are two factors influencing solution sharing: 1) \textit{the number of solutions to share} and 2) \textit{the solution sharing frequency}. Both factors are controlled by $\beta$. As mentioned in the section \label{optical_flow}, we use $\beta = 1$ once in every five iterations and use $\beta = 0$ for all other iterations. This means we share one solution in every five iterations. To further understand the effect of solution sharing, we did two other experiments for comparison. In one experiment, we use $\beta = {0, 1, 2, 3}$ in every five iterations and $\beta = 0$ for other iterations (when $\beta = 0$, it is same with PFM without final merging). While keeping all other factor same, we plot the energy minimization process in figure \ref{fig:optical_flow_by_beta}. As shown in the figure, energy generally decreases faster with solution sharing. But since we need to perform one fusion for sharing each solution, sharing more solution decreases efficiency in this problem setting. While sharing multiple solutions might be useful in some other problem setting as it means each thread can get more global information early. In another experiment, we change the number of iterations between two consecutive solution sharing iterations (the number of zero $\beta$ between two non-zero $\beta$) and plot the energy minimization process in figure \ref{fig:optical_flow_by_interval}. From this figure, we can see that although solution sharing generally speeds up the optimization process, sharing solution too frequently is not a good practice. This is because when we share solution frequently, we have less time for generating and fusing new proposals. A good choice of the solution sharing frequency depends on specific problem setting.

### 2016-03-14 paper/results.tex
results

--- 2016-03-13 paper/results.tex
@@
 We have used the QPBO and TRW-S implementations by
-Kolmogorov~\cite{QPBO, TRW-S}.
+Kolmogorov~\cite{QPBO, TRW-S_implementation}.
 
 \input{result_stereo}
-
-The figure illustrates the convergence rate of three competing methods
-(alpha expansion, parallel alpha expansion, hierarchical fusion) against
-our swarm fusion method.
-
-%\hang{figure file missing}
-\begin{figure}[tb]
-  \includegraphics[width=\columnwidth]{figure/optical_flow_convergence.png}
-  \caption{}\label{fig:optical_flow_convergence}
-\end{figure}
-\begin{figure}[tb]
- \includegraphics[width=\columnwidth]{figure/layered_depthmap_convergence.png}
- \caption{}\label{fig:layered_depthmap_convergence}
-\end{figure}
-\begin{figure}[tb]
-  \includegraphics[width=\columnwidth]{figure/layered_depthmap_by_alpha.png}
-  \caption{}\label{fig:layered_depthmap_by_alpha}
-\end{figure}
-\begin{figure}[tb]
-  \includegraphics[width=\columnwidth]{figure/optical_flow_by_threads.png}
-  \caption{}\label{fig:optical_flow_by_threads}
-\end{figure}
-\begin{figure}[tb]
-  \includegraphics[width=\columnwidth]{figure/optical_flow_by_beta.png}
-  \caption{}\label{fig:optical_flow_by_beta}
-\end{figure}
-\begin{figure}[tb]
-  \includegraphics[width=\columnwidth]{figure/optical_flow_by_interval.png}
-  \caption{}\label{fig:optical_flow_by_interval}
-\end{figure}
-
-\chen{
-  There are interesting pattern in the convergence plot of optical flow estimation problem.
-As both FS-MF and PAE are doing binary fusion, FS-MF finds lower energy faster than PAE.
-The reason is as follows.
-Some solution proposals are more effective than others, so once a thread grabs an effective solution proposal, it find a much lower energy.
-Since there is no solution sharing in PAE model, other threads cannot share this lower energy state, and keeps working on improving its own state.
-On the other hand, FS-MF allows solution sharing, so once a thread grabs an effective solution proposal and moves to a lower energy state, other threads can share this lower energy state.
-To further demonstrate what is happening here, we plot the energy-time for each thread in PAE and FS-MF in figure \ref{fig:optical_flow_by_threads}.
-As we can see from the plots, in PAE model, one thread finds lower energy state faster than others, while other threads keep working at their own energy state.
-But in FS-MF model, all threads exchange information about the lowest energy state and work on improving the lowest energy state together.
-So there are more chance of finding effective proposals faster and thus the energy goes down faster.
-Since the solution for optical flow can be locally improved by each thread, the final merging of PAE can effectively fuse good local results in different threads together and achieve a similar energy state with FS-MF model.
-Because FS-MF model shares information in the middle, a final merging becomes less necessary.
-Same comparison holds for FS-SS and FS.
-}
-
-\chen{
-  To further understand the effect of solution sharing, we did two other experiments.
-In one experiment, we change the number of solutions each thread grabed from others from 0 to 3 (as there are 4 threads in total) while keeping others the same.
-The energy-time plots are shown in figure \ref{fig:optical_flow_by_beta}.
-As shown in the figure, energy decreases faster with solution sharing.
-While since we need to perform one fusion for sharing each solution, sharing more solution leads to unnecessary overhead in this problem setting.
-While sharing multiple solutions might be benefitial in some problem setting as it means each thread can get more global information early.
-In another experiment, we change the number of iterations between two consecutive solution sharing iterations as in figure \ref{fig:optical_flow_by_interval}.
-From the figure, we can see that although solution sharing generally speed up the optimization process, sharing solution too frequently is not a good practice.
-This is because When we share solution frequently, we have less time for generating and fusing new proposals.
-A good choice of the solution sharing frequency depends on specific problem setting.
-}
-
-\chen{
-  From the convergence plot of layered depth map estimation, we can see that, Fusion Move, Parallel Fusion Move, and FS-MF all stalk at a high energy state.
-The reason is binary fusion of solution proposals (either from others or self) is too limited to further decrease the energy due to the complexity of the problem itself.
-Only when multi-way fusion is used (in FS-SS and FS), it becomes possible for the energy to further decrease.
-This coincides with the observation in \cite{layered_depthmap} that binary fusion of proposal solutions is not as powerful as their subspace fusion which is a special form of multi-way fusion here.
-To further explore the effect of multi-way fusion, we use different $\alpha$ {1, 3, 7, 15} in FS model while keeping other parameters the same and plot the energy-time curve in figure \ref{fig:layered_depth_map_by_alpha}.
-}
-
-\chen{
-  As shown in \ref{section:results}, the multi-way fusion and solution sharing enabled by our uniform framework play a key role for improving performance in different settings.
-For better understanding our framework, we examine the role played by each factor more closely by varying each factor while keeping others the same.
-There are four parameters in our framework: \textit{the number of threads}, \textit{the number alpha}, \textit{the number beta}, \textit{the number of iterations between each solution sharing}.
-}
+\input{result_optical_flow}
+\input{result_layered_depthmap}

### 2016-03-14 paper/result_layered_depthmap.tex
results

@@
 
-From the convergence plot of layered depth map estimation, we can see that, Fusion Move, Parallel Fusion Move, and FS-MF all stalk at a high energy state.
-The reason is binary fusion of solution proposals (either from others or self) is too limited to further decrease the energy due to the complexity of the problem itself.
-Only when multi-way fusion is used (in FS-SS and FS), it becomes possible for the energy to further decrease.
+We plot the energy minimization process in figure \ref{fig:layered_depthmap_convergence}.
+From the plot, we can see that, Fusion Move, Parallel Fusion Move, and FS-MF all stalk at a high energy state.
+The reason is binary fusion of solution proposals (either from others or self) is too limited to contain a lower energy state due to the complexity of the problem itself.
+Only when multi-way fusion which explores much larger solution space is used (in FS-SS and FS), it becomes possible for the energy to further decrease.
 This coincides with the observation in \cite{layered_depthmap} that binary fusion of proposal solutions is not as powerful as their subspace fusion which is a special form of multi-way fusion here.
-To further explore the effect of multi-way fusion, we use different $\alpha$ {1, 3, 7, 15} in FS model while keeping other parameters the same and plot the energy-time curve in figure \ref{fig:layered_depth_map_by_alpha}.
+Note that FS also utilize multi-way fusion for solution sharing so that it performs better than FS-SS which has no solution sharing.
 
-As shown in \ref{section:results}, the multi-way fusion and solution sharing enabled by our uniform framework play a key role for improving performance in different settings.
-For better understanding our framework, we examine the role played by each factor more closely by varying each factor while keeping others the same.
+To further explore the effect of multi-way fusion, we use different $\alpha$ {1, 3, 7, 15} in FS model while keeping other parameters the same and plot the energy minimization process in figure \ref{fig:layered_depthmap_by_alpha}.
+We can see that as the number of ways to fuse becomes larger, each fusion step takes longer time, but the chance of finding a lower energy state increases.
+
+As shown in section \ref{section:results}, the multi-way fusion and solution sharing enabled by our uniform framework play a key role for improving performance in different problem settings.

### 2016-03-14 paper/algorithm.tex
hang
Hang

@@
 %
-And the energy is not submodular
-in general, for which effective inference techniques such as
-TRW-S~\cite{TRW-S,opengm} exist.
+For general non-submodular energy, we use TRW-S~\cite{TRW-S, opengm} for inference.
+%% And the energy is not submodular
+%% in general, for which effective inference techniques such as
+%% TRW-S~\cite{TRW-S,opengm} exist.
+
 %, and hence we use TRW~\cite{kolmogorov} for the fusion, while any other
@@
 %
-Note that the threads appear synchronized in the figure for a
+Note that the threads appear synchronized in the figure only for
 illustration purpose. In practice, all the threads run asynchronously
-with a (read-write) lock on the data in the two pools (See
+with a (read-write) lock on the data in the solution pool (See
 Algorithm~\ref{algorithm:sf}). The asynchronous computing further unleashes the power of parallism.

### 2016-03-14 paper/optical_flow.tex
Hang

@@
 The three swarm architectures in Fig.~\ref{fig:model} (SF-MF, SF-SS, SF)
-have been evaluated against the competing methods. The same
+have been evaluated against the competing methods. The similar
 configurations as in the stereo problem have been used for optical flow,
-that is, one iteration with ($\alpha=0, \beta=1$) in every 5 iterations and other iterations with ($\alpha=1, \beta=0$) for SF-MF, ($\alpha=3$, $\beta=0$) for SF-MF, and one iteration with ($\alpha=0, \beta=3$) in every 5 iterations and other iterations with ($\alpha=3, \beta=0$) for SF-MF.
+that is, one iteration with ($\alpha=0, \beta=1$) in every 5 iterations and other iterations with ($\alpha=1, \beta=0$) for SF-MF, ($\alpha=3$, $\beta=0$) for SF-MF, and one iteration with ($\alpha=0, \beta=3$) in every 5 iterations and other iterations with ($\alpha=3, \beta=0$) for SF-MF.\hang{seems to have some repeating and incomplete sentences here}
 

### 2016-03-14 paper/stereo.tex
Hang

@@
 algorithmic aspects. For this purpose, we have used the three SF
-architectures illustrated in Fig.~\ref{fig:model}. For some problems,
-we have further limited the capabilities of SF on purpose, to enable
-effective and fair comparative evaluations. We now explain the details
-of the three problems.
+architectures illustrated in Fig.~\ref{fig:model}.
+%% For some problems, we have further limited the capabilities of SF
+%% on purpose, to enable effective and fair comparative
+%% evaluations. We now explain the details of the three problems.
 
@@
   experiments, unary terms are pre-computed and are not counted into
-  the running time} Therefore, we have chosen standard sequential
-$\alpha$-expansion, Parallel Alpha Expansion(PAE)~\cite{delong} and
-Hierarchical Fusion~\cite{delong_hierarchical_fusion,olga_hierarchical_alpha_expansion} with graph-cuts optimization as
-the competing methods.
+  the running time} Therefore, we have chosen single thread Alpha
+Expansion(AE), Parallel Alpha
+Expansion(PAE)~\cite{fusion_moves_for_markov_random_field_optimization}
+and Hierarchical
+Fusion~\cite{delong_hierarchical_fusion,olga_hierarchical_alpha_expansion}
+with graph-cuts optimization as the competing methods.
 
@@
 %
-To make the comparison simple, we restrict our proposal generation to
-be constant-label proposals. Graph-cuts is used in fusing a
-constant-label proposal as the energy is submodular. QPBO is used in
-fusing a different solution from another thread as the energy is
+To make the comparison simple, we restrict our proposal generator
+in each thread to only generate constant-label proposals within a
+subset of all labels. Graph-cuts is used in fusing a constant-label
+proposal as the energy is submodular. QPBO is used in fusing a
+different solution from another thread as the energy is typically
 non-submodular.

### 2016-03-14 paper/result_stereo.tex
Hang
results

@@
 
-We performed our experiments on the Book sequence from Middlebury stereo
-datasets.~\cite{middlebury_stereo}. We use 7 images with the
+We performed our experiments on the Book sequence from Middlebury
+stereo datasets.~\cite{middlebury_stereo}. We use 7 images with the
 resolution of $695\times555$ and optimize for 256 disparity labels. We
-recoreded both single thread energy and system energy (minimum energy
-so far from all threads) against time. Since the order of labels to be
-expanded or fused will have impact on minimization, we randomly
-shuffled 256 labels and provide this order to all methods.
+recoreded both single thread energy and system energy against
+time. Since the order of labels to be expanded or fused will have
+impact on minimization, we randomly shuffled 256 labels and provide
+this order to all methods. In PAE, SF-MF, SF-SS and SF algorithms, the
+proposal generator in each thread can only generate constant-label
+proposals within a evenly split subset of all labels.
 
 \begin{figure}[tb]
-  \includegraphics[width=\columnwidth]{figure/stereo_global.eps}
+  \includegraphics[width=\columnwidth]{figure/stereo_global.png}
   \caption{The energy minimization process of difference parallel systems.}
@@
 the TRWS algorihtm used in multiway fusion is slower than multiple
-$\alpha$-expansion. Finally, the line of hierarchy fusion only makes
+$\alpha$-expansions. Finally, the line of hierarchy fusion only makes
 jump when fusing on root node of the tree. This is because any fusion
@@
 
-For a easy optimization problem as shown in this section, our full
-architecture with solution sharing and multiway fusion actually makes
-convergence slower by adopting sophisticated algorihtm and introducing
-multi-threading overhead. However, we can easily configure the
+For an easy optimization problem as stereo with submodular energy, our
+full architecture with solution sharing and multiway fusion actually
+makes convergence slower due too over-sophisticated fusion algorihtm
+and multi-threading overhead. However, we can easily configure the
 architecture to make it better fit the problem, e.g. turn off multiway
 fusion and/or solution sharing.
-
-\hang{The end of stereo experiment......}

### 2016-03-14 paper/results.tex
Hang

@@
 C++ 11 and conducted the experiments on Linux PCs with Intel Core i7
-4790 processor with 4 cores, enabling 8 threads with the hyper
-threading technology. We have used the Graph-cuts optimization code
-written by Veksler, using the libraries provided by Boykov and
-Kolmogorov~\cite{middlebury_mrf,alpha_expansion,what_energy_can_be_min_by_gc, mrf_experimental}.
+4790 processor with 4 cores. We have used the Graph-cuts optimization
+code written by Veksler, using the libraries provided by Boykov and
+Kolmogorov~\cite{middlebury_mrf,alpha_expansion,what_energy_can_be_min_by_gc,mrf_experimental}.
 % [2] Fast Approximate Energy Minimization via Graph Cuts.
@@
 
+To evaluate the effectness of different parallel structures, we plot
+the energy minimization process against time. We define the energy of
+a parallel optimization system at a certain time as the minimum energy
+of all threads at that time.
+
 \input{result_stereo}

### 2016-03-14 paper/stereo.tex
Hang

@@
 \section{Swarm Fusion instantiation}
+\hang{I didn't understand the organization of this section at the
+  first glance. Should it be clearer if we put 'Swarm fusion
+  architectures' in front of 'Competing methods' in each problem?}
+
 We compare SF against competing approaches over three problems in
@@
 %% evaluations. We now explain the details of the three problems.
-
-\hang{Better to explain the methology we used, either here or in
-  Result part. For example:}
-
-\hang{To evaluate the effectness of different parallel structures, we
-  plot the energy minimization process against time. We define the
-  energy of a parallel system at a certain time as the minimum energy
-  of all threads at that time.}
 

### 2016-03-14 paper/conclusion.tex
another pass

@@
 popular inference techniques such as Alpha Expansion, Fusion Move,
-Parallel Alpha Expansion, or Hierarchical Fusion, its special cases. Our
+Parallel Alpha Expansion, and Hierarchical Fusion, its special cases. Our
 experiments have revealed that the framework exploits parallel
@@
 engineers in the world, who currently solve MRF problems. We will share
-our source code and the datasets with the community.
+our source code with the community.

### 2016-03-14 paper/optical_flow.tex
another pass

--- 2016-03-14 paper/optical_flow.tex
@@
 The three swarm architectures in Fig.~\ref{fig:model} (SF-MF, SF-SS, SF)
-have been evaluated against the competing methods. The same
-configurations as in the stereo problem have been used for optical flow,
-that is, one iteration with ($\alpha=0, \beta=1$) in every 5 iterations and other iterations with ($\alpha=1, \beta=0$) for SF-MF, ($\alpha=3$, $\beta=0$) for SF-MF, and one iteration with ($\alpha=0, \beta=3$) in every 5 iterations and other iterations with ($\alpha=3, \beta=0$) for SF-MF.
+have been evaluated against the competing methods.
+For SF-MF, each thread repeats generating solution proposals ($\alpha=1, \beta=0$) for 4 iterations and fuses with one solution from others ($\alpha=0, \beta=1$) in one iteration.
+This pattern is repeated.
+For SF-SS, each thread always generates three solution proposals for fusion in each iteration ($\alpha=3$, $\beta=0$).
+For SF, the repeating pattern is ($\alpha=3, \beta=0$) for 4 iterations and ($\alpha=0, \beta=3$) for one iteration.
 

### 2016-03-14 paper/result_layered_depthmap.tex
another pass

@@
 
+We did our experiments on ours\_1 dataset in~\cite{layered_depthmap}.
 We plot the energy minimization process in figure \ref{fig:layered_depthmap_convergence}.
-From the plot, we can see that, Fusion Move, Parallel Fusion Move, and FS-MF all stalk at a high energy state.
+From the plot, we can see that, Fusion Move, Parallel Fusion Move, and SF-MF all stalk at a high energy state.
 The reason is binary fusion of solution proposals (either from others or self) is too limited to contain a lower energy state due to the complexity of the problem itself.
-Only when multi-way fusion which explores much larger solution space is used (in FS-SS and FS), it becomes possible for the energy to further decrease.
+Only when multi-way fusion which explores much larger solution space is used (in SF-SS and SF), it becomes possible for the energy to further decrease.
 This coincides with the observation in \cite{layered_depthmap} that binary fusion of proposal solutions is not as powerful as their subspace fusion which is a special form of multi-way fusion here.
-Note that FS also utilize multi-way fusion for solution sharing so that it performs better than FS-SS which has no solution sharing.
+Note that SF also utilize multi-way fusion for solution sharing so that it performs better than SF-SS which has no solution sharing.
 
-To further explore the effect of multi-way fusion, we use different $\alpha$ {1, 3, 7, 15} in FS model while keeping other parameters the same and plot the energy minimization process in figure \ref{fig:layered_depthmap_by_alpha}.
+To further explore the effect of multi-way fusion, we use different $\alpha = {1, 3, 7, 15}$ in SF-SS model (disable solution sharing to better observe the effect of multi-way fusion) while keeping other parameters the same and plot the energy minimization process in figure \ref{fig:layered_depthmap_by_alpha}.
 We can see that as the number of ways to fuse becomes larger, each fusion step takes longer time, but the chance of finding a lower energy state increases.
-
-As shown in section \ref{section:results}, the multi-way fusion and solution sharing enabled by our uniform framework play a key role for improving performance in different problem settings.

### 2016-03-14 paper/result_optical_flow.tex
results
another pass

@@
   \caption{The energy minimization process for optical flow estimation of different methods.
-FS-MF has the best performance because of the solution sharing in early stage.}\label{fig:optical_flow_convergence}
+SF-MF has the best performance because of the solution sharing in early stage.}\label{fig:optical_flow_convergence}
 \end{figure}
@@
 
-Figure \ref{fig:optical_flow_convergence} illustrates the convergence rate of three competing methods (alpha expansion, parallel alpha expansion, hierarchical fusion) against
-our swarm fusion method.
-From the figure we can observe that, both conducting binary fusion, FS-MF finds lower energy faster than PFM.
+We did our experiment on the Dimetrodon image pairs in the training set of Middlebury flow datasets~\cite{middlebury_flow}.
+Figure \ref{fig:optical_flow_convergence} illustrates the convergence rate of three competing methods (fusion move (FM), parallel fusion move (PFM), hierarchical fusion move (HFM)) against
+our swarm fusion methods (SF-MF, SF-SS, SF).
+From the figure we can observe that, both conducting binary fusion, SF-MF finds lower energy faster than PFM.
 This is because some solution proposals are more effective than others, so once a thread grabs an effective solution proposal, it find a lower energy quickly.
 Since there is no solution sharing in PFM model, other threads cannot share this lower energy state, and keeps working on its own state.
-On the other hand, FS-MF allows solution sharing, so once a thread grabs an effective solution proposal and moves to a lower energy state, other threads can share this lower energy state.
-To further demonstrate what is happening here, we plot per thread energy in PFM and FS-MF in figure \ref{fig:optical_flow_by_threads}.
+On the other hand, SF-MF allows solution sharing, so once a thread grabs an effective solution proposal and moves to a lower energy state, other threads can share information about this lower energy state.
+In this manner, all threads contribute to further decrease of this low energy state.
+To further demonstrate what is happening here, we plot per thread energy in PFM and SF-MF in figure \ref{fig:optical_flow_by_threads}.
 As we can see from the plots, in PFM model, one thread finds lower energy state faster than others, while other threads keep working at their own energy state.
-But in FS-MF model, all threads exchange information about the lowest energy state and work on improving the lowest energy state together.
-So there are more chance of finding effective proposals faster.
-Since the solution for optical flow can be locally improved by each thread, the final merging of PFM can effectively fuse good local results in different threads together and achieve a similar energy state with FS-MF model.
-But since FS-MF model shares information in the middle, a final merging becomes less necessary.
-Same comparison holds for FS-SS and FS.
-The multi-way fusion is ineffective in this problem setting since solution proposals are relatively independant and fusing multiple solutions together using TRW-S~\cite{TRW-S} is less efficient than fusing them one by one using~\cite{QPBO}.
+But in SF-MF model, all threads exchange information about the lowest energy state frequently and work on improving the lowest energy state together.
+Since the solution for optical flow can be locally improved by each thread, the final merging of PFM can effectively fuse good local results in different threads together and achieve a similar energy state with SF-MF model.
+But as SF-MF model shares information in the middle, a final merging becomes less necessary.
+Same comparison holds for SF-SS and SF.
+The multi-way fusion is inefficient in this problem setting since solution proposals are relatively independent and fusing multiple solutions together using TRW-S~\cite{TRW-S} is less efficient than fusing them one by one using~\cite{QPBO}.
 
@@
 Both factors are controlled by $\beta$.
-As mentioned in the section \label{optical_flow}, we use $\beta = 1$ once in every five iterations and use $\beta = 0$ for all other iterations.
+As mentioned in the section \label{optical_flow}, we use $\beta = 1$ once in every five iterations ($\beta = 0$ for other iterations).
 This means we share one solution in every five iterations.
 To further understand the effect of solution sharing, we did two other experiments for comparison.
-In one experiment, we use $\beta = {0, 1, 2, 3}$ in every five iterations and $\beta = 0$ for other iterations (when $\beta = 0$, it is same with PFM without final merging).
+In one experiment, we use $\beta = {0, 1, 2, 3}$ in every five iterations (when $\beta = 0$, it is same with PFM without final merging).
 While keeping all other factor same, we plot the energy minimization process in figure \ref{fig:optical_flow_by_beta}.
@@
 While sharing multiple solutions might be useful in some other problem setting as it means each thread can get more global information early.
-In another experiment, we change the number of iterations between two consecutive solution sharing iterations (the number of zero $\beta$ between two non-zero $\beta$) and plot the energy minimization process in figure \ref{fig:optical_flow_by_interval}.
+In another experiment, we change the number of iterations $k$ between two consecutive solution sharing iterations (the number of zero $\beta$ between two non-zero $\beta$) and plot the energy minimization process in figure \ref{fig:optical_flow_by_interval}.
 From this figure, we can see that although solution sharing generally speeds up the optimization process, sharing solution too frequently is not a good practice.

### 2016-03-14 paper/result_layered_depthmap.tex
yasu

--- 2016-03-14 paper/result_layered_depthmap.tex
@@
-\mysubsubsection{Layered Depthmap}
+\mysubsubsection{Layered depthmap estimation}
+
+\noindent We have used ``ours\_1'' data in~\cite{layered_depthmap} for
+the experiments. Figure~\ref{fig:layered_depthmap_convergence} shows
+that Fusion Move, Parallel Fusion Move and Sf-MF all got stuck in local
+minima, which is due to the lack of multi-way fusion.  Layered depthmap
+estimation is a challenging problem with very large solution space. The
+binary fusion of solution proposals is too restrictive to make any
+improvements.  This coincides with the observation in
+\cite{layered_depthmap} that binary fusion of proposal solutions is not
+as powerful as their subspace fusion which is a special form of
+multi-way fusion here. Lastly, solution sharing also plays an important
+role for this challenging problem for exactly the same reason, as SF
+performs much better than SF-SS.
+%
+%From the plot, we can see that, Fusion Move, Parallel Fusion Move, and
+%SF-MF all stalk at a high energy state.
+To further study the effects of multi-way fusion, we have varied the
+value of $\alpha$ in controlling the number of solution proposals to be
+fused in SF-SS model (See
+Fig.~\ref{fig:layered_depthmap_by_alpha}). Note that we have used SF-SS
+instead of SS to disable solution sharing and better observe the effects
+of multi-way fusion.
+% SF-SS model (disable solution sharing to
+%better observe the effect of multi-way fusion) while keeping other
+%parameters the same and plot the energy minimization process in figure
+It is interesting to see that more multi-way fusion takes longer to
+converge, but finds a lower energy state at the end.
+%We can see that as the number of
+%ways to fuse becomes larger, each fusion step takes longer time, but the
+%chance of finding a lower energy state increases.
 
@@
   \includegraphics[width=\columnwidth]{figure/layered_depthmap_convergence.png}
-  \caption{The energy minimization process for layered depthmap estimation of different methods.
-Multi-way fusion is shown to be more effectvie than binary fusion in this problem setting.}\label{fig:layered_depthmap_convergence}
+  \caption{Energy plots for the layered depthmap estimation
+ problem. Both the multi-way fusion and the solution sharing are important
+ for this challenging problem.}\label{fig:layered_depthmap_convergence}
 \end{figure}
@@
   \includegraphics[width=\columnwidth]{figure/layered_depthmap_by_alpha.png}
-  \caption{The energy minimization process for layered depthmap estimation with different $\alpha$ values.
-Multi-way fusion generally performs better than binary fusion, but the optimization becomes harder for using more ways in each step.}\label{fig:layered_depthmap_by_alpha}
+ \caption{Energy plots for different values of $\alpha$.
+ More multi-way fusion takes longer to converge but finds a better
+ solution at the end.}\label{fig:layered_depthmap_by_alpha}
 \end{figure}
-
-From the convergence plot of layered depth map estimation, we can see that, Fusion Move, Parallel Fusion Move, and FS-MF all stalk at a high energy state.
-The reason is binary fusion of solution proposals (either from others or self) is too limited to further decrease the energy due to the complexity of the problem itself.
-Only when multi-way fusion is used (in FS-SS and FS), it becomes possible for the energy to further decrease.
-This coincides with the observation in \cite{layered_depthmap} that binary fusion of proposal solutions is not as powerful as their subspace fusion which is a special form of multi-way fusion here.
-To further explore the effect of multi-way fusion, we use different $\alpha$ {1, 3, 7, 15} in FS model while keeping other parameters the same and plot the energy-time curve in figure \ref{fig:layered_depth_map_by_alpha}.
-
-As shown in \ref{section:results}, the multi-way fusion and solution sharing enabled by our uniform framework play a key role for improving performance in different settings.
-For better understanding our framework, we examine the role played by each factor more closely by varying each factor while keeping others the same.

### 2016-03-14 paper/result_optical_flow.tex
yasu

--- 2016-03-14 paper/result_optical_flow.tex
@@
 
-% \hang{figure file missing}
+\noindent
+%
+We have chosen the Dimetrodon image pair from the Middlebury flow
+dataset~\cite{middlebury_flow}. Figure~\ref{fig:optical_flow_convergence}
+shows the energy plots of the three competing methods, Fusion Move
+(FM), parallel fusion move (PFM), and Hierarchical Fusion Move (HFM),
+against our swarm fusion methods (SF-MF, SF-SS, SF). A key observation
+is that SF-MF converges quicker and better than PAE. This is indeed the
+benefits of solution sharing in our network. Optical flow is a more
+difficult problem and many solution proposals are not effective.
+The solution sharing (i.e., SF-MF) allows all the threads to exchange
+effective solution proposal information in the middle of the
+optimization.
 \begin{figure}[tb]
   \includegraphics[width=\columnwidth]{figure/optical_flow_convergence.png}
-  \caption{The energy minimization process for optical flow estimation of different methods.
-FS-MF has the best performance because of the solution sharing in early stage.}\label{fig:optical_flow_convergence}
+  \caption{Energy plots for optical flow estimation. SF-MF has the best
+ performance due to its solution sharing strategy.}\label{fig:optical_flow_convergence}
 \end{figure}
@@
   \includegraphics[width=0.5\columnwidth]{figure/optical_flow_PFM_threads.png}
-  \caption{Per thread energy.
-The left and right figures show the energy minimization process on each working thread of our method in SF-MF configuration and parallel fusion move, respectively.}\label{fig:optical_flow_by_threads}
+ \caption{Energy plots per thread for SF-MF (left) and Parallel Fusion
+ Move (right).}\label{fig:optical_flow_by_threads}
 \end{figure}
+%
+% This is because some solution proposals are more effective than others,
+% so once a thread grabs an effective solution proposal, it find a lower
+% energy quickly. Since there is no solution sharing in PFM model, other
+% threads cannot share this lower energy state, and keeps working on its
+% own state.
+%
+%On the other hand, SF-MF
+%allows solution sharing, so once a thread grabs an effective solution
+%proposal and moves to a lower energy state, other threads can share
+%information about this lower energy state. In this manner, all threads
+%contribute to further decrease of this low energy state. To further
+%demonstrate what is happening here,
+To further investigate the effectiveness of solution sharing,
+Figure~\ref{fig:optical_flow_by_threads} shows the energy plots of PFM
+and SF-MF per thread. As evident from the plot, in PFM, one thread found
+a better solution than others, but other threads keep working
+independently at higher energy states. SF-MF, on the other hand,
+exchanges solutions all the time, and every thread is making an effective
+work in improving the solution.
+%As we can see from the plots, in PFM model, one thread finds lower
+%energy state faster than others, while other threads keep working at
+%their own energy state. But in SF-MF model, all threads exchange
+%information about the lowest energy state frequently and work on
+%improving the lowest energy state together. Since the solution for
+%optical flow can be locally improved by each thread, the final merging
+%of PFM can effectively fuse good local results in different threads
+%together and achieve a similar energy state with SF-MF model. But as
+%SF-MF model shares information in the middle, a final merging becomes
+%less necessary.
+Another key finding from Fig.~\ref{fig:optical_flow_convergence} is that
+SF is slower than SF-MF. Our analysis is that multi-way fusion is
+inefficient in this problem setting, since solution proposals are
+relatively independent and fusing the solution space would not gain much
+benefit. It rather loses performance against QPBO~\cite{QPBO} due to the
+overhead of TRW-S.
+
+There are two factors influencing solution sharing: 1) \textit{the number
+of solutions to share} and 2) \textit{the frequency of solution
+sharing}. Both factors are controlled by $\beta$. As mentioned in
+Section \label{optical_flow}, we have used $\beta = 1$ once in every five
+iterations ($\beta = 0$ for other iterations): We share solutions once in
+every five iterations.  To further understand the effects of solution
+sharing, we did two more experiments. First, we set $\beta$ to 0, 1, 2,
+or 3 in every five iterations,
+% (when $\beta = 0$, it is the same with PFM without final merging).
+while keeping all other parameters the same (See
+Fig.~\ref{fig:optical_flow_by_beta}).  Second, we change the number of
+iterations $k$ between the two consecutive solution sharing iterations
+(See Fig.~\ref{fig:optical_flow_by_interval}).  The first experiment
+revealed that the converegence was faster with the solution sharing than
+without the solution sharing, regarless of $\beta$.
+However, too much solution sharing slows down the converence, and
+$\beta=1$ is the sweet spot for this problem.
+%
+% , energy generally
+% decreases faster with solution sharing. But since we need to perform one
+% fusion for sharing each solution, sharing more solution decreases
+% efficiency in this problem setting. While sharing multiple solutions
+% might be useful in some other problem setting as it means each thread
+% can get more global information early.
+%
+The second experiment has revealed that too frequent solution sharing
+harms the converengece, simply because we have less time generating more
+proposals and exploring the solution space.
+% From this figure, we can see that
+% although solution sharing generally speeds up the optimization process,
+% sharing solution too frequently is not a good practice. This is because
+% when we share solution frequently, we have less time for generating and
+%fusing new proposals.
+Optimal parameter setting depends on each problem setting.
+%A good choice of the solution sharing frequency depends on specific
+%problem setting.
 \begin{figure}[tb]
   \includegraphics[width=\columnwidth]{figure/optical_flow_by_beta.png}
-  \caption{The energy minimization process for optical flow estimation with different $\beta$ values.
-Solution sharing generally makes energy minimization faster, but more solution sharing also means less time for exploring new solution proposals.}\label{fig:optical_flow_by_beta}
+  \caption{Energy plots for optical flow with different values of
+  $\beta$. Solution sharing achieves better convergence. However, too
+  much solution sharing slows down the converence, as it reduces the
+ time for exploration.}\label{fig:optical_flow_by_beta}
 \end{figure}
@@
   \includegraphics[width=\columnwidth]{figure/optical_flow_by_interval.png}
-  \caption{The energy minimization process for optical flow estimation with different solution sharing frequency.
-Solution sharing generally makes energy minimization faster, but frequent solution sharing also means less time for exploring new solution proposals.}\label{fig:optical_flow_by_beta}\label{fig:optical_flow_by_interval}
+  \caption{Energy plots for optical flow with different solution sharing
+  frequencies. Solution sharing is critical, but too frequent solution
+  sharing (less $k$) slows down the convergence.}
+ \label{fig:optical_flow_by_beta}\label{fig:optical_flow_by_interval}
 \end{figure}
-
-Figure \ref{fig:optical_flow_convergence} illustrates the convergence rate of three competing methods (alpha expansion, parallel alpha expansion, hierarchical fusion) against
-our swarm fusion method.
-From the figure we can observe that, both conducting binary fusion, FS-MF finds lower energy faster than PFM.
-This is because some solution proposals are more effective than others, so once a thread grabs an effective solution proposal, it find a lower energy quickly.
-Since there is no solution sharing in PFM model, other threads cannot share this lower energy state, and keeps working on its own state.
-On the other hand, FS-MF allows solution sharing, so once a thread grabs an effective solution proposal and moves to a lower energy state, other threads can share this lower energy state.
-To further demonstrate what is happening here, we plot per thread energy in PFM and FS-MF in figure \ref{fig:optical_flow_by_threads}.
-As we can see from the plots, in PFM model, one thread finds lower energy state faster than others, while other threads keep working at their own energy state.
-But in FS-MF model, all threads exchange information about the lowest energy state and work on improving the lowest energy state together.
-So there are more chance of finding effective proposals faster.
-Since the solution for optical flow can be locally improved by each thread, the final merging of PFM can effectively fuse good local results in different threads together and achieve a similar energy state with FS-MF model.
-But since FS-MF model shares information in the middle, a final merging becomes less necessary.
-Same comparison holds for FS-SS and FS.
-The multi-way fusion is ineffective in this problem setting since solution proposals are relatively independant and fusing multiple solutions together using TRW-S~\cite{TRW-S} is less efficient than fusing them one by one using~\cite{QPBO}.
-
-They are two factors influencing solution sharing: 1) \textit{the number of solutions to share} and 2) \textit{the solution sharing frequency}.
-Both factors are controlled by $\beta$.
-As mentioned in the section \label{optical_flow}, we use $\beta = 1$ once in every five iterations and use $\beta = 0$ for all other iterations.
-This means we share one solution in every five iterations.
-To further understand the effect of solution sharing, we did two other experiments for comparison.
-In one experiment, we use $\beta = {0, 1, 2, 3}$ in every five iterations and $\beta = 0$ for other iterations (when $\beta = 0$, it is same with PFM without final merging).
-While keeping all other factor same, we plot the energy minimization process in figure \ref{fig:optical_flow_by_beta}.
-As shown in the figure, energy generally decreases faster with solution sharing.
-But since we need to perform one fusion for sharing each solution, sharing more solution decreases efficiency in this problem setting.
-While sharing multiple solutions might be useful in some other problem setting as it means each thread can get more global information early.
-In another experiment, we change the number of iterations between two consecutive solution sharing iterations (the number of zero $\beta$ between two non-zero $\beta$) and plot the energy minimization process in figure \ref{fig:optical_flow_by_interval}.
-From this figure, we can see that although solution sharing generally speeds up the optimization process, sharing solution too frequently is not a good practice.
-This is because when we share solution frequently, we have less time for generating and fusing new proposals.
-A good choice of the solution sharing frequency depends on specific problem setting.

### 2016-03-14 paper/result_stereo.tex
Hang
yasu

--- 2016-03-13 paper/result_stereo.tex
@@
 
-We performed our experiments on the half-size Book sequence from Middlebury stereo
-datasets.~\cite{middlebury_stereo}. We use 7 images with the
-resolution of $695\times555$ and optimize for 256 disparity labels. We
-recoreded both single thread energy and system energy (minimum energy
-so far from all threads) against time.
+\noindent We have chosen 7 images with the resolution of $695\times555$
+from the Book sequence of Middlebury stereo dataset for our
+experiment~\cite{middlebury_stereo}. The number of disparity labels is
+set to 256.
+%
+Since the order of labels is important for the expansion techniques,
+we have picked a random order to avoid any bias.
+%
+% In PAE, SF-MF, SF-SS and SF algorithms, the proposal generator in each
+% thread can only generate constant-label proposals within a evenly split
+% subset of all labels.
 
+Figure~\ref{fig:stereo_global} compares the converegence rate of the
+competing methods. Note that we define the energy of a multi-threading
+system to be the energy of the best solution found so far.
+%
 \begin{figure}[tb]
-  \includegraphics[width=\columnwidth]{figure/stereo_global.eps}
-  \caption{The energy minimization process of difference parallel systems.}
-  \label{fig:stereo_global}
+  \includegraphics[width=\columnwidth]{figure/stereo_global.png}
+ \caption{Energy plots for the stereo problem. The energy is in the
+ log scale. For a multi-threading algorithm, the energy at any given
+ moment is defined to be the best solution so far.} \label{fig:stereo_global}
+\end{figure}
+%
+One unusual outcome is that Sequential Alpha Expansion and Parallel
+Alpha Expansion (PAE) have the same convergence speed, indicating that
+the stereo problem is a very easy one. This is well known in a community
+and this fact was rather expected. Our approaches with multi-way fusion
+(SF-SS or SF) are the slowest kind, because the TRW-S for multi-way
+fusion is slower than multiple Alpha Expansion steps, and this stereo
+problem is too easy to gain benefits through mulit-way fusion.
+%
+%Another interesting observation is that the Hierarchical Fusion can
+%achieve good energy only when they merge solutions at the top of the
+%tree.
+%
+%  both PAE and SF-MF converge faster
+% than sequential method. However, since fusing solutions with multiple
+% labels by QPBO is slower than a single $\alpha$-expansion, PAE method
+%
+% Finally, the line of hierarchy fusion only makes
+% jump when fusing on root node of the tree. This is because any fusion
+% step on non-root nodes only have partial label information.
+%We recoreded both single thread energy and system energy against
+%time.
+%
+Figure \ref{fig:stereo_threads} shows the energy plot per thread
+for SF-MF (ours) and PAE. The graph for PAE again confirms that the
+stereo is an easy problem, because all the threads are quickly
+converging to a solution before the final sequential fusion.
+%shows the per-thread energy
+%minimization process in SF-MF and PAE. The per-thread energy in SF-MF
+%architecture decreases more uniformly than that of PAE. In the
+%scenario where we need to query the best solution so far before the
+%whole optimization converges, SF-MF architecture is a better choice.
+\begin{figure}[tb]
+  \includegraphics[width=\columnwidth]{figure/stereo_threads.png}
+  \caption{\yasu{Put a text in the figures showing which one is
+  SF-MF(ours) and which one is parallel alpha expansion} Per thread
+  energy. The left and right figures show the energy minimization
+  process on each working thread of our method in SF-MF configuration
+  and parallel $\alpha$-expansion method, respectively. The energy is in
+  $\log$ scale} \label{fig:stereo_threads}
 \end{figure}
 
-\begin{figure}[tb]
-  \includegraphics[width=\columnwidth]{figure/stereo_threads.png}
-  \caption{Per thread energy. The left and right figures show the
-    energy minimization process on each working thread of our method
-    in SF-MF configuration and parallel $\alpha$-expansion method,
-    respectively. The energy is in $\log$ scale}
-  \label{fig:stereo_threads}
-\end{figure}
+For an easy optimization problem such as stereo with strong unary terms
+and submodular pairwise terms, our full architecture with solution
+sharing and multiway fusion actually makes convergence slower due to the
+overhead of fusion and multi-threading.
 
-Figure \ref{fig:stereo_global} shows the energy minimization process
-against time. In this experiment, both PAE and SF-MF converge faster
-than sequential method. However, since fusing solutions with multiple
-labels by QPBO is slower than a single $\alpha$-expansion, PAE method
-reaches convergence faster than SF-MF. Architectures with multiway
-fusion, e.g. SF and SF-SS perform worse than PAE and SF-MF, because
-the TRWS algorihtm used in multiway fusion is slower than multiple
-$\alpha$-expansion. Finally, the line of hierarchy fusion only makes
-jump when fusing on root node of the tree. This is because any fusion
-step on non-root nodes only have partial label information.
+% over-sophisticated fusion algorihtm and multi-threading
+% overhead. However, we can easily configure the architecture to make it
+% better fit the problem, e.g. turn off multiway fusion and/or solution
+% sharing.
 
-Figure \ref{fig:stereo_threads} shows the per-thread energy
-minimization process in SF-MF and PAE. The per-thread energy in SF-MF
-architecture decreases more uniformly than that of PAE. In the
-scenario where we need to query the best solution so far before the
-whole optimization converges, SF-MF architecture is a better choice.
-
-For a easy optimization problem as shown in this section, our full
-architecture with solution sharing and multiway fusion actually makes
-convergence slower by adopting sophisticated algorihtm and introducing
-multi-threading overhead. However, we can easily configure the
-architecture to make it better fit the problem, e.g. turn off multiway
-fusion and/or solution sharing.
-
-\hang{The end of stereo experiment......}
+% We define the energy of
+% a parallel optimization system at a certain time as the minimum energy
+% of all threads at that time.

### 2016-03-14 paper/results.tex
another pass
yasu

@@
 \section{Experimental results}
-\label{section:results}
-We have implemented the algorithms with multithreading supporting from
-C++ 11 and conducted the experiments on Linux PCs with Intel Core i7
-4790 processor with 4 cores. We have used the Graph-cuts optimization
-code written by Veksler, using the libraries provided by Boykov and
+\label{section:results} We have implemented the algorithms with
+multi-threading support from C++ 11, and conducted the experiments on
+Linux PCs with Intel Core i7 4790 processor with 4 cores. We have used
+the Graph-cuts optimization code written by Veksler, using the libraries
+provided by Boykov and
 Kolmogorov~\cite{middlebury_mrf,alpha_expansion,what_energy_can_be_min_by_gc,mrf_experimental}.
@@
 We have used the QPBO and TRW-S implementations by
-Kolmogorov~\cite{QPBO, TRW-S_implementation}.
+Kolmogorov~\cite{QPBO, TRW-S_implementation}. We now look at our
+experimental results for the three problems one by one.
 
-To evaluate the effectness of different parallel structures, we plot
-the energy minimization process against time. We define the energy of
-a parallel optimization system at a certain time as the minimum energy
-of all threads at that time.
+% To evaluate the effectness of different parallel structures, we plot
+% the energy minimization process against time. We define the energy of
+% a parallel optimization system at a certain time as the minimum energy
+% of all threads at that time.
 
@@
 \input{result_layered_depthmap}
+
+As shown in the above problem settings, the solution sharing and multi-way fusion enabled by our uniform framework play a key role for improving performance in different problem settings.

### 2016-03-14 paper/stereo.tex
yasu

@@
 We compare SF against competing approaches over three problems in
-Computer Vision. SF framework has high degrees of freedom and the
-challenge is to properly quantify the contributions of various
-algorithmic aspects. For this purpose, we have used the three SF
-architectures illustrated in Fig.~\ref{fig:model}.
+Computer Vision, namely, stereo, optical flow, and layered depthmap
+estimation.
+
+% SF framework has high degrees of freedom and the
+%challenge is to properly quantify the contributions of various
+%algorithmic aspects.
+
+%For this purpose, we have used the three SF architectures illustrated in
+%Fig.~\ref{fig:model}.
 %% For some problems, we have further limited the capabilities of SF

### 2016-03-14 paper/result_stereo.tex
yasu

@@
   \includegraphics[width=\columnwidth]{figure/stereo_global.png}
- \caption{Energy plots for the stereo problem. The energy is in the
- log scale. For a multi-threading algorithm, the energy at any given
- moment is defined to be the best solution so far.} \label{fig:stereo_global}
+ \caption{Energy plots for the stereo problem. The energy is in the log
+ scale. For a multi-threading algorithm, the energy at a given moment is
+ defined to be the best solution so far.} \label{fig:stereo_global}
 \end{figure}
@@
   \caption{\yasu{Put a text in the figures showing which one is
-  SF-MF(ours) and which one is parallel alpha expansion} Per thread
-  energy. The left and right figures show the energy minimization
-  process on each working thread of our method in SF-MF configuration
-  and parallel $\alpha$-expansion method, respectively. The energy is in
-  $\log$ scale} \label{fig:stereo_threads}
+  SF-MF(ours) and which one is parallel alpha expansion}
+ Energy plots per thread for the stereo problem for SF-MF (left) and
+ Parallel Alpha Expansion (right).
+} \label{fig:stereo_threads}
 \end{figure}

### 2016-03-14 paper/algorithm.tex
yasu

@@
 %for fusion.
-SF has 1) a {\it proposal generator} for each thread, with which a thread
-picks arbitrary number of proposal generation schemes and generates proposals, and 2) a
-{\it solution pool}, from which a thread picks arbitrary number of
-intermediate solutions generated by the others.
+SF has 1) a {\it proposal generator} which picks
+arbitrary number of proposal generation schemes and generates proposals,
+and 2) a {\it solution pool}, from which a thread picks arbitrary number
+of intermediate solutions generated by the others.
 % threads.
@@
 In our base configuration, the solution pool remembers just the best
-solution from each thread.
+solution for each thread.
 
@@
 This is different with the solution pool which is really there.}
-$\beta_i$ or $0$ solutions from the solution pool, based on a user-defined
-strategy or at random to be simple. (The value of $\alpha_i$ and $\beta_i$ can vary in each iteration to encourage different behaviors.) The thread then fuse all these solutions
-together to find a solution with lower energy state and update the solution pool accordingly.
+$\beta_i$ solutions from the solution pool, based on a user-defined
+strategy or at random to be simple. (The value of $\alpha_i$ and
+$\beta_i$ can vary in each iteration to encourage different behaviors.)
+The thread then fuse all these solutions together to find a solution
+with lower energy state and update the solution pool accordingly.
 %
@@
 The bottom right architecture is the most general one, in which threads
-conduct multi-way fusion of either solution proposals, or some concurrent solutions, or both (i.e.,
-$\alpha\ne 0, \beta \ne 0$).
+conduct multi-way fusion of solution proposals and/or concurrent
+solutions (i.e., $\alpha\ne 0, \beta \ne 0$).
 %
@@
 %% TRW-S~\cite{TRW-S,opengm} exist.
-
+%
 %, and hence we use TRW~\cite{kolmogorov} for the fusion, while any other
@@
 with a (read-write) lock on the data in the solution pool (See
-Algorithm~\ref{algorithm:sf}). The asynchronous computing further unleashes the power of parallism.
+Algorithm~\ref{algorithm:sf}).
+%The asynchronous computing further unleashes the power of parallism.
 %The asynchronous processing could be difficult for cloud parallel
@@
 restricting the proposal generation to constant labels with a single
-thread. Same goes for FM, this time, without the restriction on the
+thread. The same goes for FM, this time, without the restriction on the
 proposal generation scheme. PAE is realized by setting

### 2016-03-14 paper/optical_flow.tex
yasu

@@
 %introduced by Lempitsky et al.~\cite{viktor}.
-We copy their problem setting and use images from the Middlebury optical flow
-benchmark~\cite{middlebury_optical_flow}.
-We share similar proposal generation schemes with Lempitsky et al~\cite{fusion_flow}, but instead of the HS algorithm, we use more recent Farneback algorithm and change its pyramid levels from 1 to 5 and use either 3, 5 or 7 for parameter polyN.
-Besides the clustering idea, we add three simple proposal generation schemes based on the current solution as suggested in ~\cite{fusion_flow}.
-In \textit{shift proposal}, the flow field in the current solution is shifted in either x direction or y direction for either 1, 2 or 3 pixels.
-In \textit{stagger proposal}, the flow field is shifted by a vector randomly drawed from a Gaussian distribution.
-In \textit{disturb proposal}, each flow value in the field is indenpendantly shifted by a vector randomly drawed from a Gaussian distribution.
-We choose schemes randomly when generating proposals.
+We copy their problem setting and use images from the Middlebury optical
+flow benchmark~\cite{middlebury_optical_flow}. We share similar proposal
+generation schemes with Lempitsky et al~\cite{fusion_flow}, but
+%instead of the HS algorithm, we
+use more recent Farneback algorithm with some modifications.~\footnote{First, we
+change the level of pyramids from 1 to 5, then use either 3, 5 or 7 for
+parameter ``polyN''. Besides the clustering idea, we add three simple
+proposal generation schemes based on the current solution as suggested
+in \cite{fusion_flow}. In \textit{shift proposal}, the flow field in the
+current solution is shifted in either x or y directions for
+either 1, 2 or 3 pixels. In \textit{stagger proposal}, the flow field is
+shifted by a vector randomly drawn from a Gaussian distribution. In
+\textit{disturb proposal}, each flow value in the field is
+indenpendantly shifted by a vector randomly drawn from a Gaussian
+distribution. We choose schemes randomly when generating proposals.}
 

### 2016-03-14 paper/stereo.tex
yasu

@@
 \section{Swarm Fusion instantiation}
-\hang{I didn't understand the organization of this section at the
-  first glance. Should it be clearer if we put 'Swarm fusion
-  architectures' in front of 'Competing methods' in each problem?}
+% \hang{I didn't understand the organization of this section at the
+%   first glance. Should it be clearer if we put 'Swarm fusion
+%   architectures' in front of 'Competing methods' in each problem?}
 
@@
 scaling the pairwise term by a factor of $0.005$. For simplicity we
-don't enforce visibility constraint.
+do not enforce the visibility constraint.
 
@@
 \noindent The sophistication of photometric consistency
-function~\cite{mvs_furukawa_survey} makes unary terms dominant in most
-stereo problems.  Our experiments have also supported this, where the
-fusion method (i.e., the use of proposal generation) rather makes it
-slow due to the overhead.\hang{Don't quite understand this
-  sentence. Does the ``dominant'' means running time or energy? In my
-  experiments, unary terms are pre-computed and are not counted into
-  the running time} Therefore, we have chosen single thread Alpha
-Expansion(AE), Parallel Alpha
+function~\cite{mvs_furukawa_survey} makes unary terms highly informative
+in most stereo problems.  Our experiments have also supported this,
+where the fusion method (i.e., the use of proposal generation) rather
+makes it slow due to the overhead.
+%\hang{Don't quite understand this sentence. Does the ``dominant'' means
+%running time or energy? In my experiments, unary terms are pre-computed
+%and are not counted into the running time}
+Therefore, we have chosen single thread Alpha Expansion(AE), Parallel
+Alpha
 Expansion(PAE)~\cite{fusion_moves_for_markov_random_field_optimization}
@@
 %
-SF-SS implies $\beta=0$, where $\alpha$ is the free parameter and set
-to 4. In this case one thread will fuse 4 labels by TRW-S per
-iteration and never exchanges solutions with other threads. SF-MF
-implies $\alpha+\beta=1$, where each thread will expand 3 labels
-(repeat $\alpha=1, \beta=0$ for 3 iterations) and then fuse one
-solution from other threads ($\alpha=0, \beta=1$) by QPBO. In the later
-case, a thread randomly chooses one target thread to grab solution
-from. For standard SF, we have used ($\alpha=4, \beta=1$). For the
-SF-SS architecture, we performed a final fuse of solutions from all
-thread by multiway fusion.
+SF-SS implies $\beta=0$, where $\alpha$ is the free parameter and set to
+4. In this case one thread will fuse 4 labels by TRW-S per iteration and
+never exchanges solutions with other threads. SF-MF implies
+$\alpha+\beta=1$, where each thread will expand 3 labels (repeat
+$\alpha=1, \beta=0$ for 3 iterations) and then fuse one solution from
+other threads ($\alpha=0, \beta=1$) by QPBO. In the later case, a thread
+randomly chooses one target thread to copy a solution. For standard SF,
+we have used ($\alpha=4, \beta=1$). For the SF-SS architecture, we
+perform a multi-way fusion at the end to fuse solutions from all the threads.
 
@@
 proposal as the energy is submodular. QPBO is used in fusing a
-different solution from another thread as the energy is typically
-non-submodular.
+different solution from another thread as the energy is
+non-submodular in general.
 %

### 2016-03-14 paper/layered_depthmap.tex
yasu

@@
 %
-Layered depthmap estimation is one of the most difficult kinds in MRF
-inference due to its massive solution space. The number of labels per
-pixel is exponential in the number of layers, and is usually between 100,000 and 10,000,000. We copy their problem
-formulation and the proposal generation schemes.~\footnote{Authors have
-proposed a novel fusion scheme, where a solution subspace instead of a
-single solution is generated by a proposal generation scheme. Since a
-solution subspace can be represented by a concatenation of multiple solution proposals,
+Layered depthmap estimation is a very challenging MRF inference problem
+due to its massive solution space. The number of labels per pixel is
+exponential in the number of layers, and is usually between 100,000 and
+10,000,000. We copy their problem formulation and the proposal
+generation schemes.~\footnote{Authors have proposed a novel fusion
+scheme, where a solution subspace instead of a single solution is
+generated by a proposal generation scheme. Since a solution subspace can
+be represented by a concatenation of multiple solution proposals,
 % \chen{It is a good explanation for this paper's purpose, but from the perspective of our previous work, I am reluctant to say a subspace equals to multiple solution proposals.
@@
 it impossible to conduct fair comparative evaluations. We choose to use
-a simple solution proposal for experiments in this paper.}
+a simple solution proposal for this experiment.}
 %Lastly, we will evaluate Swarm fusion on a very challenging layered

### 2016-03-14 paper/optical_flow.tex
yasu

@@
 start from solution proposals as opposed to constant labels. One problem
-of HFM is that we need to generate all proposals at the very beginning in order to build the fusion tree.
-This undermines the power of fusion move to dynamically generate solution proposals based on current solution.
-In our experiments, we have manually generate 250 proposals at the beginning.
-We first generate 25 proposals using LK and Farneback algorithms which are independant and generate other proposals based on these initial proposals).
-The fusions are binary in these methods.
-% and we have used QPBO.
+of HFM is that we need to generate all the proposals first to build the
+fusion tree. This undermines the power of fusion move that can
+adaptively generate proposals based on the current solution. In our
+experiments, we have manually generate 250 proposals at the
+beginning.
+%We first generate 25 proposals using LK and Farneback algorithms which
+%are independant and generate other proposals based on these initial
+%proposals).
+The fusions are binary in these methods and we have used QPBO.
 
@@
 The three swarm architectures in Fig.~\ref{fig:model} (SF-MF, SF-SS, SF)
-have been evaluated against the competing methods.
-For SF-MF, each thread repeats generating solution proposals ($\alpha=1, \beta=0$) for 4 iterations and fuses with one solution from others ($\alpha=0, \beta=1$) in one iteration.
-This pattern is repeated.
-For SF-SS, each thread always generates three solution proposals for fusion in each iteration ($\alpha=3$, $\beta=0$).
-For SF, the repeating pattern is ($\alpha=3, \beta=0$) for 4 iterations and ($\alpha=0, \beta=3$) for one iteration.
-
-%
-Note that we have used the same set of proposal generation schemes as
-the competing methods. We have used TRW-S for multi-way fusion and QPBO
-for binary fusion.
+have been evaluated against the competing methods. For SF-MF, each
+thread repeats generating solution proposals ($\alpha=1, \beta=0$) for 4
+iterations and fuses with one solution from others ($\alpha=0, \beta=1$)
+in one iteration. This pattern is repeated. For SF-SS, each thread
+generates three solution proposals for fusion in each iteration
+($\alpha=3$, $\beta=0$). For SF, we repeat ($\alpha=3, \beta=0$) for 4
+iterations and ($\alpha=0, \beta=3$) for one iteration.
+%%
+%Note that we have used the same set of proposal generation schemes as
+%the competing methods.
+We have used TRW-S for multi-way fusion and QPBO for binary fusion.
 % , while our fusions are multi-way, for which we have used TRW-S.

### 2016-03-14 paper/result_layered_depthmap.tex
yasu

@@
 the experiments. Figure~\ref{fig:layered_depthmap_convergence} shows
-that Fusion Move, Parallel Fusion Move and Sf-MF all got stuck in local
+that Fusion Move, Parallel Fusion Move and SF-MF all got stuck in local
 minima, which is due to the lack of multi-way fusion.  Layered depthmap

### 2016-03-14 paper/result_optical_flow.tex
yasu

@@
 We have chosen the Dimetrodon image pair from the Middlebury flow
-dataset~\cite{middlebury_flow}. Figure~\ref{fig:optical_flow_convergence}
+dataset~\cite{middlebury_optical_flow}. Figure~\ref{fig:optical_flow_convergence}
 shows the energy plots of the three competing methods, Fusion Move
@@
 The solution sharing (i.e., SF-MF) allows all the threads to exchange
-effective solution proposal information in the middle of the
+effective solution proposals in the middle of the
 optimization.
@@
 
-There are two factors influencing solution sharing: 1) \textit{the number
-of solutions to share} and 2) \textit{the frequency of solution
+There are two factors influencing solution sharing: 1) \textit{the
+number of solutions to share} and 2) \textit{the frequency of solution
 sharing}. Both factors are controlled by $\beta$. As mentioned in
-Section \label{optical_flow}, we have used $\beta = 1$ once in every five
-iterations ($\beta = 0$ for other iterations): We share solutions once in
-every five iterations.  To further understand the effects of solution
-sharing, we did two more experiments. First, we set $\beta$ to 0, 1, 2,
-or 3 in every five iterations,
+Section~\ref{section:algorithm}, we have used $\beta = 1$ (i.e., share
+solutions) once in every five iterations.  To further understand the
+effects of solution sharing, we did two more experiments. First, we set
+$\beta$ to 0, 1, 2, or 3 in every five iterations,
 % (when $\beta = 0$, it is the same with PFM without final merging).
@@
 (See Fig.~\ref{fig:optical_flow_by_interval}).  The first experiment
-revealed that the converegence was faster with the solution sharing than
-without the solution sharing, regarless of $\beta$.
-However, too much solution sharing slows down the converence, and
-$\beta=1$ is the sweet spot for this problem.
+revealed that the solution sharing makes convergence faster regarless of
+$\beta$.  However, too much solution sharing slows down the converence,
+and $\beta=1$ is the sweet spot for this problem.
 %
@@
 %
-The second experiment has revealed that too frequent solution sharing
+The second experiment has shown that too frequent solution sharing
 harms the converengece, simply because we have less time generating more

### 2016-03-14 paper/results.tex
yasu

@@
 Kolmogorov~\cite{QPBO, TRW-S_implementation}. We now look at our
-experimental results for the three problems one by one.
+experimental results for the three problems.
 
@@
 
-As shown in the above problem settings, the solution sharing and multi-way fusion enabled by our uniform framework play a key role for improving performance in different problem settings.
+%As shown in the above problem settings, the solution sharing and
+%multi-way fusion enabled by our uniform framework play a key role for
+%improving performance in different problem settings.

### 2016-03-14 paper/result_stereo.tex
yasu
Hang

@@
 Since the order of labels is important for the expansion techniques,
-we have picked a random order to avoid any bias.
+we have used the same random order for all algorithms to avoid any
+bias.
 %
@@
 
-Figure~\ref{fig:stereo_global} compares the converegence rate of the
+Fig.~\ref{fig:stereo_global} compares the converegence rate of the
 competing methods. Note that we define the energy of a multi-threading
@@
 Alpha Expansion (PAE) have the same convergence speed, indicating that
-the stereo problem is a very easy one. This is well known in a community
-and this fact was rather expected. Our approaches with multi-way fusion
-(SF-SS or SF) are the slowest kind, because the TRW-S for multi-way
-fusion is slower than multiple Alpha Expansion steps, and this stereo
-problem is too easy to gain benefits through mulit-way fusion.
+the stereo problem is a very easy one.
+%This is well known in a community and this fact was rather expected.
+Our approaches with multi-way fusion (SF-SS or SF) are the slowest kind,
+because the TRW-S for multi-way fusion is slower than multiple Alpha
+Expansion steps, and this stereo problem is too easy to gain benefits
+through mulit-way fusion.
 %
@@
 %
-Figure \ref{fig:stereo_threads} shows the energy plot per thread
+Fig. \ref{fig:stereo_threads} shows the energy plot per thread
 for SF-MF (ours) and PAE. The graph for PAE again confirms that the
@@
   \includegraphics[width=\columnwidth]{figure/stereo_threads.png}
-  \caption{\yasu{Put a text in the figures showing which one is
-  SF-MF(ours) and which one is parallel alpha expansion}
- Energy plots per thread for the stereo problem for SF-MF (left) and
+  \caption{Energy plots per thread for the stereo proble for SF-MF (left) and
  Parallel Alpha Expansion (right).

### 2016-03-14 paper/stereo.tex
Hang

@@
 and Hierarchical
-Fusion~\cite{delong_hierarchical_fusion,olga_hierarchical_alpha_expansion}
+Fusion(HF)~\cite{delong_hierarchical_fusion,olga_hierarchical_alpha_expansion}
 with graph-cuts optimization as the competing methods.

### 2016-03-14 paper/result_stereo.tex
minor changes

--- 2016-03-14 paper/result_stereo.tex
@@
 \noindent We have chosen 7 images with the resolution of $695\times555$
-from the Book sequence of Middlebury stereo dataset for our
-experiment~\cite{middlebury_stereo}. The number of disparity labels is
+from the Book sequence of Middlebury stereo dataset~\cite{middlebury_stereo} for our
+experiment. The number of disparity labels is
 set to 256.
@@
 and submodular pairwise terms, our full architecture with solution
-sharing and multiway fusion actually makes convergence slower due to the
+sharing and multi-way fusion actually makes convergence slower due to the
 overhead of fusion and multi-threading.

### 2016-03-14 LayerDepthMap/Statistics/plotValues.m

@@ -43,7 +43,7 @@ fig_1 = figure(1);
 plot(sequential(:, 1), log(sequential(:, 2)), '--', Victor(:, 1), log(Victor(:, 2)), '--', solution_exchange(:, 1), log(solution_exchange(:, 2)), multiway(:, 1), log(multiway(:, 2)), full(:, 1), log(full(:, 2)), 'LineWidth', 2);
 l = legend('FM', 'PFM', 'SF-MF(ours)', 'SF-SS(ours)', 'SF(ours)');
 xlabel('Time/s');
-ylabel('Energy');
+ylabel('Energy(log-scale)');
 %ylim([8, 9.8]);
 fig_1.Position = [500, 500, 1280, 720];
 
@@ -52,9 +52,10 @@ print(fig_1, '../../paper/figure/layered_depthmap_convergence', '-dpng');
 fig_2 = figure(2);
 %plot(Victor_by_thread{1}(:, 1), log(Victor_by_thread{1}(:, 2)), '-+m', Victor_by_thread{2}(:, 1), log(Victor_by_thread{2}(:, 2)), '-om', Victor_by_thread{3}(:, 1), log(Victor_by_thread{3}(:, 2)), '-*m', Victor_by_thread{4}(:, 1), log(Victor_by_thread{4}(:, 2)), '-xm', solution_exchange_by_thread{1}(:, 1), log(solution_exchange_by_thread{1}(:, 2)), '-+b', solution_exchange_by_thread{2}(:, 1), log(solution_exchange_by_thread{2}(:, 2)), '-+b', solution_exchange_by_thread{3}(:, 1), log(solution_exchange_by_thread{3}(:, 2)), '-*b', solution_exchange_by_thread{4}(:, 1), log(solution_exchange_by_thread{4}(:, 2)), '-xb', 'LineWidth', 2)
 plot(Victor_by_thread{1}(:, 1), log(Victor_by_thread{1}(:, 2)), Victor_by_thread{2}(:, 1), log(Victor_by_thread{2}(:, 2)), Victor_by_thread{3}(:, 1), log(Victor_by_thread{3}(:, 2)), Victor_by_thread{4}(:, 1), log(Victor_by_thread{4}(:, 2)), 'LineWidth', 2);
-legend('Thread 1', 'Thread 2', 'Thread 3', 'Thread 4');
+legend('PFM Thread 1', 'PFM Thread 2', 'PFM Thread 3', 'PFM Thread 4');
[…]

### 2016-03-14 LayerDepthMap/Statistics/plotValuesAlpha.m

@@ -42,7 +42,7 @@ fig = figure(1);
 plot(Victor(:, 1), log(Victor(:, 2)), multiway(:, 1), log(multiway(:, 2)), multiway_5(:, 1), log(multiway_5(:, 2)), multiway_7(:, 1), log(multiway_7(:, 2)), multiway_9(:, 1), log(multiway_9(:, 2)), multiway_11(:, 1), log(multiway_11(:, 2)), 'LineWidth', 2);
 legend('\alpha=1', '\alpha=3', '\alpha=5', '\alpha=7', '\alpha=9', '\alpha=11');
 xlabel('Time/s');
-ylabel('Energy');
+ylabel('Energy(log-scale)');
 fig.Position = [500, 500, 1280, 720];
 
 print(fig, '../../paper/figure/layered_depthmap_by_alpha', '-dpng');

### 2016-03-14 OpticalFlow/Statistics/plotValues.m

@@ -46,7 +46,7 @@ fig_1 = figure(1);
 plot(sequential(:, 1), log(sequential(:, 2)), '--', Victor(:, 1), log(Victor(:, 2)), '--', hierarchy(:, 1), log(hierarchy(:, 2)), '--', solution_exchange(:, 1), log(solution_exchange(:, 2)), multiway(:, 1), log(multiway(:, 2)), full(:, 1), log(full(:, 2)), 'LineWidth', 2);
 l = legend('FM', 'PFM', 'HFM', 'SF-MF(ours)', 'SF-SS(ours)', 'SF(ours)');
 xlabel('Time/s');
-ylabel('Energy');
+ylabel('Energy(log-scale)');
 %ylim([8, 9.8]);
 fig_1.Position = [500, 500, 1280, 720];
 
@@ -55,9 +55,9 @@ print(fig_1, '../../paper/figure/optical_flow_convergence', '-dpng');
 fig_2 = figure(2);
 %plot(Victor_by_thread{1}(:, 1), log(Victor_by_thread{1}(:, 2)), '-+m', Victor_by_thread{2}(:, 1), log(Victor_by_thread{2}(:, 2)), '-om', Victor_by_thread{3}(:, 1), log(Victor_by_thread{3}(:, 2)), '-*m', Victor_by_thread{4}(:, 1), log(Victor_by_thread{4}(:, 2)), '-xm', solution_exchange_by_thread{1}(:, 1), log(solution_exchange_by_thread{1}(:, 2)), '-+b', solution_exchange_by_thread{2}(:, 1), log(solution_exchange_by_thread{2}(:, 2)), '-+b', solution_exchange_by_thread{3}(:, 1), log(solution_exchange_by_thread{3}(:, 2)), '-*b', solution_exchange_by_thread{4}(:, 1), log(solution_exchange_by_thread{4}(:, 2)), '-xb', 'LineWidth', 2)
 plot(Victor_by_thread{1}(:, 1), log(Victor_by_thread{1}(:, 2)), Victor_by_thread{2}(:, 1), log(Victor_by_thread{2}(:, 2)), Victor_by_thread{3}(:, 1), log(Victor_by_thread{3}(:, 2)), Victor_by_thread{4}(:, 1), log(Victor_by_thread{4}(:, 2)), 'LineWidth', 2);
-legend('Thread 1', 'Thread 2', 'Thread 3', 'Thread 4');
[…]

### 2016-03-14 OpticalFlow/Statistics/plotValuesBeta.m

@@ -26,7 +26,7 @@ fig = figure(1);
 plot(Victor(:, 1), log(Victor(:, 2)), solution_exchange(:, 1), log(solution_exchange(:, 2)), solution_exchange_2_other(:, 1), log(solution_exchange_2_other(:, 2)), solution_exchange_3_other(:, 1), log(solution_exchange_3_other(:, 2)), 'LineWidth', 2);
 legend('\beta=0', '\beta=1', '\beta=2', '\beta=3');
 xlabel('Time/s');
-ylabel('Energy');
+ylabel('Energy(log-scale)');
 fig.Position = [500, 500, 1280, 720];
 
 print(fig, '../../paper/figure/optical_flow_by_beta', '-dpng');

### 2016-03-14 OpticalFlow/Statistics/plotValuesInterval.m

@@ -25,9 +25,9 @@ set(0, 'DefaultTextFontSize', 30);
 %2), '-.c', solution_exchange(:, 1), solution_exchange(:, 2), '-*b', multiway(:, 1), multiway(:, 2), '-og', full(:, 1), full(:, 2), '-+r');\
 fig = figure(1);
 plot(solution_exchange_2(:, 1), log(solution_exchange_2(:, 2)), solution_exchange(:, 1), log(solution_exchange(:, 2)), solution_exchange_5(:, 1), log(solution_exchange_5(:, 2)), solution_exchange_9(:, 1), log(solution_exchange_9(:, 2)), Victor(:, 1), log(Victor(:, 2)), 'LineWidth', 2);
-legend('k=2', 'k=3', 'k=5', 'k=9', 'k=\infty');
+legend('k=1', 'k=2', 'k=4', 'k=8', 'k=\infty');
 xlabel('Time/s');
-ylabel('Energy');
+ylabel('Energy(log-scale)');
 fig.Position = [500, 500, 1280, 720];
 
 print(fig, '../../paper/figure/optical_flow_by_interval', '-dpng');

### 2016-03-14 OpticalFlow/OpticalFlowProposalGenerator.cpp
minor chanegs

@@ -276,13 +276,13 @@ namespace flow_fusion {
   void OpticalFlowProposalGenerator::getAllProposals(vector<LabelSpace<pair<double, double> > > &proposals)
   {
     vector<vector<pair<double, double> > > initial_flows;
-    for (int num_levels = 1; num_levels <= 5; num_levels += 2) {
+    for (int num_levels = 1; num_levels <= 5; num_levels += 1) {
       vector<pair<double, double> > proposal_flows = calcFlowsPyrLK(image_1_, image_2_, num_levels);
       initial_flows.push_back(proposal_flows);
     }
 
-    for (int num_levels = 1; num_levels <= 5; num_levels += 2) {
-      for (int poly_n = 3; poly_n <= 7; poly_n += 2) {
+    for (int num_levels = 1; num_levels <= 5; num_levels += 1) {
+      for (int poly_n = 1; poly_n <= 7; poly_n += 2) {
 	for (int flag_index = 0; flag_index <= 0; flag_index++) {
 	  const int FLAGS = flag_index == 0 ? 0 : OPTFLOW_FARNEBACK_GAUSSIAN;
 	  vector<pair<double, double> > proposal_flows = calcFlowsFarneback(image_1_, image_2_, num_levels, poly_n, FLAGS);
@@ -297,12 +297,12 @@ namespace flow_fusion {
       
       current_solution_ = *initial_flow_it;
       
-      for (int proposal_index = 0; proposal_index < 2; proposal_index++) {
+      for (int proposal_index = 0; proposal_index < 4; proposal_index++) {
 	LABELSPACE proposal_label_space;
 	generateProposalMoveAround(proposal_label_space);
 	proposals.push_back(proposal_label_space);
       }
-      for (int proposal_index = 0; proposal_index < 2; proposal_index++) {
+      for (int proposal_index = 0; proposal_index < 4; proposal_index++) {
 	LABELSPACE proposal_label_space;
         generateProposalShift(proposal_label_space);
         proposals.push_back(proposal_label_space);
@@ -312,7 +312,7 @@ namespace flow_fusion {
         generateProposalCluster(proposal_label_space);
         proposals.push_back(proposal_label_space);
       }
-      for (int proposal_index = 0; proposal_index < 1; proposal_index++) {
+      for (int proposal_index = 0; proposal_index < 2; proposal_index++) {
         LABELSPACE proposal_label_space;
         generateProposalDisturb(proposal_label_space);
         proposals.push_back(proposal_label_space);

### 2016-03-14 OpticalFlow/main.cpp

@@ -28,7 +28,7 @@ DEFINE_bool(write_log, true, "Write log file or not.");
 DEFINE_bool(evaluation, false, "Write log file or not.");
 //DEFINE_string(dataset_category, "other-data", "The dataset image category.");
 
-DEFINE_int32(num_threads, 2, "The number of threads.");
+DEFINE_int32(num_threads, 4, "The number of threads.");
 DEFINE_int32(num_iterations, 30, "The number of iterations.");
 
 DEFINE_int32(num_proposals_in_total, 1, "The number of proposals in total.");
@@ -115,7 +115,7 @@ int main(int argc, char *argv[])
   ParallelFusion::ParallelFusionOption option;
   option.num_threads = FLAGS_num_threads;
   option.max_iteration = FLAGS_num_iterations;
-  option.selectionMethod = ParallelFusion::ParallelFusionOption::ALL;
+  option.selectionMethod = ParallelFusion::ParallelFusionOption::RANDOM;
   //option.synchronize = true;
   
   

### 2016-03-14 paper/algorithm.tex
yasu
minor changes

@@
-\section{Multi-way particle swarm fusion}
+\section{Multi-way particle swarm fusion} \label{section:algorithm}
 Multi-way Particle Swarm Fusion is a natural extension of the Fusion
@@
 
-Assuming we have $N$ threads $\{T_i | i=1, 2, \cdots, N\}$, each thread
-$T_i$ maintains and updates a solution $S_i$ in parallel. Alpha
-Expansion picks one label in each iteration to perform fusion. FM
-generates a solution proposal via a proposal generation scheme.
+Assuming we have $N$ threads $\{T_i | i=1, 2, \cdots, N\}$,
+each thread $T_i$ maintains and updates a solution $S_i$ in
+parallel.
+%Alpha
+%Expansion picks one label in each iteration to perform fusion. FM
+%generates a solution proposal via a proposal generation scheme.
 %invokes one proposal generation scheme and generates a solution proposal
@@
 generates $\alpha_i$ solution proposals using its proposal generator, and collects
-%\chen{A proposal pool sounds confusing.
-We often don't really maintain such a pool as many proposals are generated dynamically based on current solution.
-We just have certain strategies right there and in each iteration, we pick some strategies to generate proposals on the fly.
-This is different with the solution pool which is really there.}
+% \chen{A proposal pool sounds confusing. We often don't
+% really maintain such a pool as many proposals are
+% generated dynamically based on current solution. We just
+% have certain strategies right there and in each iteration,
+% we pick some strategies to generate proposals on the
+% fly. This is different with the solution pool which is
+% really there.}
 $\beta_i$ solutions from the solution pool, based on a user-defined
@@
   \ForEach{thread $T_i$ in parallel till convergence}
-  \State Generate $\alpha$ solution proposals $\mathcal{P}$ %\subset \mathcal{P_{\mbox{pool}}}$
-  \State Pick $\beta$ solutions $\mathcal{S} \subset \mathcal{S_{\mbox{pool}}}$
+  \State Generate $\alpha_i$ solution proposals $\mathcal{P}$ %\subset \mathcal{P_{\mbox{pool}}}$
+  \State Pick $\beta_i$ solutions $\mathcal{S} \subset \mathcal{S_{\mbox{pool}}}$
   \State $S_i \leftarrow \mbox{Fuse}(S_i, \mathcal{P}, \mathcal{S})$
@@
 \noindent It is easy to verify that Alpha-Expansion
-(AE)~\cite{alpha_expansion}, Fusion Move (FM)~\cite{fusion_moves_for_markov_random_field_optimization}, Parallel
-Alpha Expansion (PAE)~\cite{fusion_moves_for_markov_random_field_optimization}, and Hierarchical Fusion
-(HF)~\cite{delong_hierarchical_fusion,olga_hierarchical_alpha_expansion} are all special cases of the Swarm
-Fusion method (SF). AE can be realized by setting $(\alpha=1, \beta=0)$ and
-restricting the proposal generation to constant labels with a single
-thread. The same goes for FM, this time, without the restriction on the
-proposal generation scheme. PAE is realized by setting
-$(\alpha=1,\beta=0)$ with multiple threads, again with a restriction on
-the proposal generation scheme (the last sequential fusion in PAE is
-realized by $(\alpha=0, \beta=1)$ with a single thread).
+(AE)~\cite{alpha_expansion}, Fusion Move
+(FM)~\cite{fusion_moves_for_markov_random_field_optimization},
+Parallel Alpha Expansion
+(PAE)~\cite{fusion_moves_for_markov_random_field_optimization},
+and Hierarchical Fusion
+(HF)~\cite{delong_hierarchical_fusion,olga_hierarchical_alpha_expansion}
+are all special cases of the Swarm Fusion method (SF). AE
+can be realized by setting $(\alpha=1, \beta=0)$ and
+restricting the proposal generation to constant labels with
+a single thread. The same goes for FM, this time, without
+the restriction on the proposal generation scheme. PAE is
+realized by setting $(\alpha=1,\beta=0)$ with multiple
+threads, again with a restriction on the proposal generation
+scheme (the last sequential fusion in PAE is realized by
+$(\alpha=0, \beta=1)$ with a single thread).
 %

### 2016-03-14 paper/optical_flow.tex

@@
 shifted by a vector randomly drawn from a Gaussian distribution. In
-\textit{disturb proposal}, each flow value in the field is
-indenpendantly shifted by a vector randomly drawn from a Gaussian
+\textit{perturb proposal}, each flow value in the field is
+independently shifted by a vector randomly drawn from a Gaussian
 distribution. We choose schemes randomly when generating proposals.}
@@
 The last contender is the mix of the Hierarchical Fusion and the Fusion
-Move methods, dubbed ``Hierarchical Fusion Method''(HFM), where they
+Move methods, dubbed ``Hierarchical Fusion Move''(HFM), where they
 start from solution proposals as opposed to constant labels. One problem
@@
 %We first generate 25 proposals using LK and Farneback algorithms which
-%are independant and generate other proposals based on these initial
+%are independent and generate other proposals based on these initial
 %proposals).
@@
 
-\mysubsubsection{Swarm fusion architectures}
+\mysubsubsection{Swarm Fusion architectures}
 
@@
 have been evaluated against the competing methods. For SF-MF, each
-thread repeats generating solution proposals ($\alpha=1, \beta=0$) for 4
+thread repeats generating solution proposals ($\alpha=1, \beta=0$) for four
 iterations and fuses with one solution from others ($\alpha=0, \beta=1$)
@@
 generates three solution proposals for fusion in each iteration
-($\alpha=3$, $\beta=0$). For SF, we repeat ($\alpha=3, \beta=0$) for 4
+($\alpha=3$, $\beta=0$). For SF, we repeat ($\alpha=3, \beta=0$) for four
 iterations and ($\alpha=0, \beta=3$) for one iteration.

### 2016-03-14 paper/related_work.tex

@@
 
-MRF inference has been a very active field in Computer Vision with the
+MRF inference has been a very active field in Computer Vision with
 extensive literature. We refer the readers to survey articles for
@@
 
-\noindent Lempitsky et al. introduces parallel computation to an
+\noindent Lempitsky et al.~\cite{fusion_moves_for_markov_random_field_optimization} introduces parallel computation to an
 alpha-expansion technique, where multiple threads simultaneously fuses
@@
 al.~\cite{hierarchical_graph_cuts_kumar_and_koller}, Delong et
-al.~\cite{delong_hierarchical_fusion}, and Veksler~\cite{olga_hierarchical_alpha_expansion} proposed an hierarchical
+al.~\cite{delong_hierarchical_fusion}, and Veksler et al.~\cite{olga_hierarchical_alpha_expansion} proposed an hierarchical
 approach, where labels can be simultaneously fused from the bottom to
@@
 \noindent The core MAP inference itself can be parallelized.  Strandmark
-et al. parallelized graph-cuts~\cite{strandmark_parallel}.
+et al.~\cite{strandmark_parallel} parallelized graph-cuts.
 %
@@
 
-\mysubsubsection{Fusion Move Methods}
+\mysubsubsection{Fusion Move methods}
 
-\noindent FM was first introduced by Lempitsky et al. in solving an
-optical flow problem~\cite{fusion_flow}. FM has been effectively used to solve challenging
+\noindent FM was first introduced by Lempitsky et al.~\cite{fusion_flow} in solving an
+optical flow problem. FM has been effectively used to solve challenging
 problems in Computer Vision such as stereo with second order smoothness
 priors~\cite{second_order_stereo}, stereo with parameteric surface fitting and
-segmentation (i.e., Surface Stereo)~\cite{surface_stereo}, or multicut
+segmentation (i.e. Surface Stereo)~\cite{surface_stereo}, or multicut
 partitioning~\cite{fusion_moves_for_correlation_clustering}.
@@
 Although conceptually straightforward, we are not aware of {\it Parallel
-Fusion move} algorithms that fuse solution proposals, as opposed to
+  Fusion Move (PFM)} algorithms that fuse solution proposals, as opposed to
 labels, in parallel. This paper seeks to fully unleash the power of
 parallel computation based on FM in the most general setting.
-%for the most general FM via a more general framework.
+% for the most general FM via a more general framework.
 
@@
 %
-GA or PSO has been used to produce great empirical results, for example,
-hand tracking~\cite{pushmeet_hand_tracking}.
+GA or PSO has been used to produce great empirical results,
+hand tracking~\cite{pushmeet_hand_tracking} for example.
 %

### 2016-03-14 paper/result_optical_flow.tex

@@
 shows the energy plots of the three competing methods, Fusion Move
-(FM), parallel fusion move (PFM), and Hierarchical Fusion Move (HFM),
-against our swarm fusion methods (SF-MF, SF-SS, SF). A key observation
-is that SF-MF converges quicker and better than PAE. This is indeed the
+(FM), Parallel Fusion Move (PFM), and Hierarchical Fusion Move (HFM),
+against our Swarm Fusion methods (SF-MF, SF-SS, SF). A key observation
+is that SF-MF converges quicker and better than PFM. This is indeed the
 benefits of solution sharing in our network. Optical flow is a more
@@
   sharing (less $k$) slows down the convergence.}
- \label{fig:optical_flow_by_beta}\label{fig:optical_flow_by_interval}
+ \label{fig:optical_flow_by_interval}
 \end{figure}

### 2016-03-14 paper/layered_depthmap.tex

@@
 It is essentially the same, but a subspace proposal is conceptually more general than concatenated solution proposals.},
-their algorithm can be easily integrated into our swarm fusion framework.
+their algorithm can be easily integrated into our Swarm Fusion framework.
 However, competing fusion methods (e.g., Parallel Fusion Move or
@@
 
-\noindent Solution proposals depend heavily on the current solution,
-eliminating the possibility of using Hierarchical Fusion, which needs to
+\noindent In this problem setting, solution proposals depend heavily on the current solution,
+eliminating the possibility of using Hierarchical Fusion Move (HFM), which needs to
 enumerate all the proposals to start. Therefore, viable competing
-methods are Fusion Move and Parallel Fusion Move.
+methods are Fusion Move (FM) and Parallel Fusion Move (PFM) as in the optical flow problem.
 %
@@
 
-\mysubsubsection{Swarm fusion architectures}
+\mysubsubsection{Swarm Fusion architectures}
 
 \noindent The three swarm architectures with the same configurations as
-in the optical flow problems have been evaluated.
+in the optical flow problem have been evaluated.
 %in Fig.~\ref{fig:model} are evaluated.

### 2016-03-14 paper/result_stereo.tex
Hang

@@
 %
+
 \begin{figure}[tb]
-  \includegraphics[width=\columnwidth]{figure/stereo_global.png}
+\centering
+\includegraphics[width=0.8\textwidth]{figure/stereo_global.png}
 \caption{Energy plots for the stereo problem. The energy is in the log
 scale. For a multi-threading algorithm, the energy at a given moment is
- defined to be the best solution so far.} \label{fig:stereo_global}
+defined to be the best solution so far.}
+\label{fig:stereo_global}
 \end{figure}
 %
+
 One unusual outcome is that Sequential Alpha Expansion and Parallel
@@
 %whole optimization converges, SF-MF architecture is a better choice.
-\begin{figure}[tb]
-  \includegraphics[width=\columnwidth]{figure/stereo_threads.png}
-  \caption{Energy plots per thread for the stereo proble for SF-MF (left) and
- Parallel Alpha Expansion (right).
-} \label{fig:stereo_threads}
-\end{figure}
+
+%% \begin{figure}[tb]
+%% \includegraphics[width=\columnwidth]{figure/stereo_threads.png}
+%% \caption{Energy plots per thread for the stereo proble for SF-MF (left) and
+%% Parallel Alpha Expansion (right).
+%% } \label{fig:stereo_threads}
+%% \end{figure}
 

### 2016-03-14 paper/introduction.tex
figures
Hang

@@
 \section{Introduction}
-\hang{Should we use $\alpha$-expansion instead of alpha-expansion?}
 
 Parallel computation has changed the field of computing.  In the 90s,
-most processors had single cores. In 2016, most processors have multiple
+most processors had single cores while nowadays most processors have multiple
 cores, often 4 or even 8. Cluster computing further expands the
@@
 numerous Computer Vision researchers or engineers, who currently solve
-MRF problems. We will share our implementation of our pipeline which provides
-parallism through simple interfaces.
+MRF problems.
+
+%We will share our implementation of our pipeline which provides
+%parallism through simple interfaces.
 % will instantly benefit every Computer Vision researcher or

### 2016-03-14 paper/introduction.tex
Hang

@@
 Parallel computation has changed the field of computing.  In the 90s,
-most processors had single cores while nowadays most processors have multiple
-cores, often 4 or even 8. Cluster computing further expands the
-potential of parallel computation, where one can easily launch a
+most processors had single cores, while nowadays most processors have
+multiple cores, often 4 or even 8. Cluster computing further expands
+the potential of parallel computation, where one can easily launch a
 processing job using hundreds or even thousands of computational nodes
@@
 %
+%% However, state-of-the-art algorithms are still inherently
+%% sequential in many Computer Vision problems. Take a Fusion Move
+%% method
+%% (FM)~\cite{fusion_flow,fusion_moves_for_markov_random_field_optimization,second_order_stereo}
+%% for example, which has been one of the most effective techniques
+%% for Markov Ran- dom Field (MRF) inference, including the above
+%% problems like image denoising, image stitching, or volumetric
+%% reconstruction. It sequentially improves solution by fusing the
+%% current solution with a solution proposal. Its successful applica-
+%% tions go beyond and also cover optical flow, stereo, image
+%% inpainting, or image segmentation
+%% problems~\cite{fusion_moves_for_markov_random_field_optimization} .
 %
-However, state-of-the-art algorithms are still inherently sequential
-in many Computer Vision problems. Take a Fusion Move method
+The MAP framework, which can be formulated as a Markov Random Field
+(MRF) in many low-level Computer Vision problems, provides a universal
+and powerful way to solve these problems. However, state-of-the-art
+algorithms for MRF inference are still inherently sequential. Take a
+Fusion Move method
 (FM)~\cite{fusion_flow,fusion_moves_for_markov_random_field_optimization,second_order_stereo}
 for example, which has been one of the most effective techniques for
-Markov Random Field (MRF) inference, including the above problems like
-image denoising, image stitching, or volumetric reconstruction.
-%
-It sequentially improves solution by fusing the current solution with a
-solution proposal. Its successful applications go beyond and also cover
-optical flow, stereo, image inpainting, or image segmentation
+MRF inference, it sequentially improves solution by fusing the current solution with
+a solution proposal. Its successful applications cover not only above
+problems, but also popular problmes like optical flow, stereo, image
+inpainting, or image segmentation
 problems~\cite{fusion_moves_for_markov_random_field_optimization}.
@@
 arbitrary combination of proposal generation schemes, even concurrent
-solutions in the other threads, to be fused with the current solution.
+solutions in the other threads, to fuse with the current solution.
 %
@@
 %challenging problems with a large label space.
-Our idea is very simple. We believe that the method is easily
-reproducible with minimal coding, and would have immediate impact on
-numerous Computer Vision researchers or engineers, who currently solve
-MRF problems.
+%
+%Our idea is very simple. We believe that the method is easily
+%reproducible with minimal coding
+%
+We believe that the method can be intergrated into existing algorithms
+with minimal coding, and would have immediate impact on numerous
+Computer Vision researchers or engineers.
 

### 2016-03-14 paper/result_layered_depthmap.tex
change figures

@@
 performs much better than SF-SS.
+
 %
@@
 To further study the effects of multi-way fusion, we have varied the
-value of $\alpha$ in controlling the number of solution proposals to be
+value of $\alpha$ which controls the number of solution proposals to be
 fused in SF-SS model (See
 Fig.~\ref{fig:layered_depthmap_by_alpha}). Note that we have used SF-SS
-instead of SS to disable solution sharing and better observe the effects
+instead of SF to disable solution sharing and better observe the effects
 of multi-way fusion.
@@
 converge, but finds a lower energy state at the end.
+
+At the end we examined the role of multi-threading by varying the number of threads N in our most general model SF (See Fig.~\ref{fig:layered_depthmap_by_N}).~\footnote{Note that we have the constraint that $\beta \leq N-1$, we always use $\beta = N-1$ in this experiment.}  It is natural that our SF model find lower energy faster with more threads.
+While due to the inherited randomness in the proposal and fusion scheme of Fusion Move methods, the speed up is not propotional to the number of threads.
 %We can see that as the number of
@@
 \begin{figure}[tb]
-  \includegraphics[width=\columnwidth]{figure/layered_depthmap_convergence.png}
+  \centering
+  \includegraphics[width=0.8\columnwidth]{figure/layered_depthmap_convergence.png}
   \caption{Energy plots for the layered depthmap estimation
@@
 \end{figure}
+
 \begin{figure}[tb]
+  \centering
+  \begin{subfigure}[b]{0.49\columnwidth}
+    \centering
     \includegraphics[width=\columnwidth]{figure/layered_depthmap_by_alpha.png}
- \caption{Energy plots for different values of $\alpha$.
- More multi-way fusion takes longer to converge but finds a better
- solution at the end.}\label{fig:layered_depthmap_by_alpha}
+    \caption{}
+    \label{fig:optical_flow_by_alpha}
+  \end{subfigure}  
+  \begin{subfigure}[b]{0.49\columnwidth}
+    \centering
+    \includegraphics[width=\columnwidth]{figure/layered_depthmap_by_N.png}
+    \caption{}
+    \label{fig:optical_flow_by_N}
+  \end{subfigure}
+  \caption{(a) Energy plots for layered depthmap estimation with varying
+    $\alpha$. More multi-way fusion takes longer to converge but finds a better   
+    solution at the end. (b) Energy plots for layered depthmap estimation with varying number of threads N. More threads find lower energy faster.}
+  \label{fig:layered_depthmap_by_alpha_N}
 \end{figure}

### 2016-03-14 paper/result_optical_flow.tex
change figures

@@
 \begin{figure}[tb]
-  \includegraphics[width=\columnwidth]{figure/optical_flow_convergence.png}
+  \centering
+  \includegraphics[width=0.8\columnwidth]{figure/optical_flow_convergence.png}
   \caption{Energy plots for optical flow estimation. SF-MF has the best
@@
 \end{figure}
-\begin{figure}[tb]
-  \includegraphics[width=0.5\columnwidth]{figure/optical_flow_SF_MF_threads.png}
-  \includegraphics[width=0.5\columnwidth]{figure/optical_flow_PFM_threads.png}
- \caption{Energy plots per thread for SF-MF (left) and Parallel Fusion
- Move (right).}\label{fig:optical_flow_by_threads}
+
+\begin{figure}[t]
+  \centering
+  \begin{subfigure}[b]{0.49\columnwidth}
+    \centering
+    \includegraphics[width=\columnwidth]{figure/optical_flow_PFM_threads.png}
+    \caption{}
+    \label{fig:optical_flow_PFM_threads}
+  \end{subfigure}  
+  \begin{subfigure}[b]{0.49\columnwidth}
+    \centering
+    \includegraphics[width=\columnwidth]{figure/optical_flow_SF_MF_threads.png}
+    \caption{}
+    \label{fig:optical_flow_SF_MF_threads}
+  \end{subfigure}
+  \caption{Energy plots per thread for (a) Parallel Fusion  
+    Move (PFM) and (b) our FS-MF.}
+  \label{fig:optical_flow_by_threads}  
 \end{figure}
+
 % 
@@
 The second experiment has shown that too frequent solution sharing
-harms the converengece, simply because we have less time generating more
+harms the convergence, simply because we have less time generating more
 proposals and exploring the solution space.
@@
 \begin{figure}[tb]
+  \centering
+  \begin{subfigure}[b]{0.49\columnwidth}
+    \centering
     \includegraphics[width=\columnwidth]{figure/optical_flow_by_beta.png}
-  \caption{Energy plots for optical flow with different values of
-  $\beta$. Solution sharing achieves better convergence. However, too
-  much solution sharing slows down the converence, as it reduces the
- time for exploration.}\label{fig:optical_flow_by_beta}
+    \caption{}
+    \label{fig:optical_flow_by_beta}
+  \end{subfigure}  
+  \begin{subfigure}[b]{0.49\columnwidth}
+    \centering
+    \includegraphics[width=\columnwidth]{figure/optical_flow_by_interval.png}
+    \caption{}
+    \label{fig:optical_flow_by_interval}
+  \end{subfigure}
+  \caption{Energy plots for optical flow with (a) varying
+    $\beta$ and (b) varying solution sharing
+    frequencies.
+Solution sharing achieves better convergence, but sharing too many solutions (larger $\beta$) or sharing solutions too frequently (less $k$) slows down the convergence, as it reduces the time for exploration.}
 \end{figure}
-\begin{figure}[tb]
-  \includegraphics[width=\columnwidth]{figure/optical_flow_by_interval.png}
-  \caption{Energy plots for optical flow with different solution sharing
-  frequencies. Solution sharing is critical, but too frequent solution
-  sharing (less $k$) slows down the convergence.}
- \label{fig:optical_flow_by_interval}
-\end{figure}

### 2016-03-14 LayerDepthMap/Statistics/plotValues.m

@@ -33,21 +33,25 @@ end
 %dlmwrite('thread_solution_exchange.txt', solution_exchange_by_thread, '\t');
 
 set(0, 'DefaultAxesFontName', 'Times New Roman');
-set(0, 'DefaultAxesFontSize', 30);
+set(0, 'DefaultAxesFontSize', 34);
 set(0, 'DefaultTextFontName', 'Times New Roman');
-set(0, 'DefaultTextFontSize', 30);
+set(0, 'DefaultTextFontSize', 34);
 
 %plot(sequential(:, 1), sequential(:, 2), '-xm', Victor(:, 1), Victor(:,
 %2), '-.c', solution_exchange(:, 1), solution_exchange(:, 2), '-*b', multiway(:, 1), multiway(:, 2), '-og', full(:, 1), full(:, 2), '-+r');\
 fig_1 = figure(1);
-plot(sequential(:, 1), log(sequential(:, 2)), '--', Victor(:, 1), log(Victor(:, 2)), '--', solution_exchange(:, 1), log(solution_exchange(:, 2)), multiway(:, 1), log(multiway(:, 2)), full(:, 1), log(full(:, 2)), 'LineWidth', 2);
+plot(sequential(:, 1), log(sequential(:, 2)), '--', Victor(:, 1), log(Victor(:, 2)), '--', solution_exchange(:, 1), log(solution_exchange(:, 2)), multiway(:, 1), log(multiway(:, 2)), full(:, 1), log(full(:, 2)), 'LineWidth', 3);
 l = legend('FM', 'PFM', 'SF-MF(ours)', 'SF-SS(ours)', 'SF(ours)');
 xlabel('Time/s');
 ylabel('Energy(log-scale)');
 %ylim([8, 9.8]);
+box off;
 fig_1.Position = [500, 500, 1280, 720];
 
 print(fig_1, '../../paper/figure/layered_depthmap_convergence', '-dpng');
+
+set(0, 'DefaultAxesFontSize', 30);
+set(0, 'DefaultTextFontSize', 30);
 
 fig_2 = figure(2);
[…]

### 2016-03-14 LayerDepthMap/Statistics/plotValuesAlpha.m

@@ -43,7 +43,8 @@ plot(Victor(:, 1), log(Victor(:, 2)), multiway(:, 1), log(multiway(:, 2)), multi
 legend('\alpha=1', '\alpha=3', '\alpha=5', '\alpha=7', '\alpha=9', '\alpha=11');
 xlabel('Time/s');
 ylabel('Energy(log-scale)');
-fig.Position = [500, 500, 1280, 720];
+box off;
+fig.Position = [500, 500, 640, 500];
 
 print(fig, '../../paper/figure/layered_depthmap_by_alpha', '-dpng');
 

### 2016-03-14 LayerDepthMap/Statistics/plotValuesN.m

@@ -1,0 +1,33 @@
+full_raw_values = load('output_values_full');
+full = convertValues(full_raw_values, 0);
+full_thread_1_raw_values = load('output_values_full_thread_1');
+full_thread_1 = convertValues(full_thread_1_raw_values, 0);
+full_thread_2_raw_values = load('output_values_full_thread_2');
+full_thread_2 = convertValues(full_thread_2_raw_values, 0);
+full_thread_3_raw_values = load('output_values_full_thread_3');
+full_thread_3 = convertValues(full_thread_3_raw_values, 0);
+
+
+
+% dlmwrite('statistics_sequential.txt', sequential, '\t');
+% dlmwrite('statistics_Victor.txt', Victor, '\t');
+% dlmwrite('statistics_solution_exchange.txt', solution_exchange, '\t');
+% dlmwrite('statistics_multiway.txt', multiway, '\t');
+% dlmwrite('statistics_full.txt', full, '\t');
+
+set(0, 'DefaultAxesFontName', 'Times New Roman');
+set(0, 'DefaultAxesFontSize', 30);
+set(0, 'DefaultTextFontName', 'Times New Roman');
+set(0, 'DefaultTextFontSize', 30);
+
+%plot(sequential(:, 1), sequential(:, 2), '-xm', Victor(:, 1), Victor(:,
+%2), '-.c', solution_exchange(:, 1), solution_exchange(:, 2), '-*b', multiway(:, 1), multiway(:, 2), '-og', full(:, 1), full(:, 2), '-+r');\
+fig = figure(1);
+plot(full_thread_1(:, 1), log(full_thread_1(:, 2)), full_thread_2(:, 1), log(full_thread_2(:, 2)), full_thread_3(:, 1), log(full_thread_3(:, 2)), full(:, 1), log(full(:, 2)), 'LineWidth', 2);
+legend('N=1', 'N=2', 'N=3', 'N=4');
+xlabel('Time/s');
+ylabel('Energy(log-scale)');
+box off;
+fig.Position = [500, 500, 640, 500];
+
+print(fig, '../../paper/figure/layered_depthmap_by_N', '-dpng');

### 2016-03-14 LayerDepthMap/Statistics/readNumbers.sh

@@ -20,4 +20,5 @@ cat output_multiway_11| awk '{ print $5 "\t" $8 "\t" $7}' > output_values_multiw
 
 cat output_full_thread_1| awk '{ print $5 "\t" $8 "\t" $7}' > output_values_full_thread_1
 cat output_full_thread_2| awk '{ print $5 "\t" $8 "\t" $7}' > output_values_full_thread_2
+cat output_full_thread_3| awk '{ print $5 "\t" $8 "\t" $7}' > output_values_full_thread_3
 cat output_full_thread_8| awk '{ print $5 "\t" $8 "\t" $7}' > output_values_full_thread_8

### 2016-03-14 OpticalFlow/Statistics/plotValuesInterval.m

@@ -28,6 +28,7 @@ plot(solution_exchange_2(:, 1), log(solution_exchange_2(:, 2)), solution_exchang
 legend('k=1', 'k=2', 'k=4', 'k=8', 'k=\infty');
 xlabel('Time/s');
 ylabel('Energy(log-scale)');
-fig.Position = [500, 500, 1280, 720];
+box off;
+fig.Position = [500, 500, 640, 500];
 
 print(fig, '../../paper/figure/optical_flow_by_interval', '-dpng');

### 2016-03-14 OpticalFlow/Statistics/plotValuesN.m

@@ -1,11 +1,13 @@
-Victor_raw_values = load('output_values_Victor');
-Victor = convertValues(Victor_raw_values, 0);
+full_raw_values = load('output_values_full');
+full = convertValues(full_raw_values, 0);
+%thread_1_raw_values = load('output_values_full_thread_1');
+%thread_1 = convertValues(full_thread_1_raw_values, 0);
+thread_2_raw_values = load('output_values_thread_2');
+thread_2 = convertValues(thread_2_raw_values, 0);
 solution_exchange_raw_values = load('output_values_solution_exchange');
 solution_exchange = convertValues(solution_exchange_raw_values, 0);
-solution_exchange_2_other_raw_values = load('output_values_solution_exchange_2_other');
-solution_exchange_2_other = convertValues(solution_exchange_2_other_raw_values, 0);
-solution_exchange_3_other_raw_values = load('output_values_solution_exchange_3_other');
-solution_exchange_3_other = convertValues(solution_exchange_3_other_raw_values, 0);
+thread_8_raw_values = load('output_values_thread_8');
+thread_8 = convertValues(thread_8_raw_values, 0);
 
 
 
@@ -23,12 +25,10 @@ set(0, 'DefaultTextFontSize', 30);
 %plot(sequential(:, 1), sequential(:, 2), '-xm', Victor(:, 1), Victor(:,
 %2), '-.c', solution_exchange(:, 1), solution_exchange(:, 2), '-*b', multiway(:, 1), multiway(:, 2), '-og', full(:, 1), full(:, 2), '-+r');\
 fig = figure(1);
-plot(Victor(:, 1), log(Victor(:, 2)), solution_exchange(:, 1), log(solution_exchange(:, 2)), solution_exchange_2_other(:, 1), log(solution_exchange_2_other(:, 2)), solution_exchange_3_other(:, 1), log(solution_exchange_3_other(:, 2)), 'LineWidth', 2);
-legend('\beta=0', '\beta=1', '\beta=2', '\beta=3');
+plot(thread_2(:, 1), log(thread_2(:, 2)), thread_2(:, 1), log(thread_2(:, 2)), solution_exchange(:, 1), log(solution_exchange(:, 2)), thread_8(:, 1), log(thread_8(:, 2)), 'LineWidth', 2);
+legend('N=1', 'N=2', 'N=4', 'N=8');
 xlabel('Time/s');
 ylabel('Energy(log-scale)');
-box off;
[…]

### 2016-03-14 paper/algorithm.tex
Hang

@@
 %for fusion.
-SF has 1) a {\it proposal generator} which picks
+SF has 1) a {\it proposal generator} for each thread which picks
 arbitrary number of proposal generation schemes and generates proposals,
@@
 % fused by the threads.
-In our base configuration, the solution pool remembers just the best
-solution for each thread.
+In our base configuration, the solution pool remembers $N$ best
+solutions, one from each thread.
 
@@
 $\beta_i$ solutions from the solution pool, based on a user-defined
-strategy or at random to be simple. (The value of $\alpha_i$ and
-$\beta_i$ can vary in each iteration to encourage different behaviors.)
+strategy or at random to be simple. The value of $\alpha_i$ and
+$\beta_i$ can vary in each iteration to encourage different behaviors.
 The thread then fuse all these solutions together to find a solution
@@
 %
-The bottom right architecture is the most general one, in which threads
-conduct multi-way fusion of solution proposals and/or concurrent
-solutions (i.e., $\alpha\ne 0, \beta \ne 0$).
+The bottom right architecture is the most general one, in which
+threads conduct multi-way fusion of their current solution, proposals
+from their own proposal generators and/or concurrent solutions (i.e.,
+$\alpha\ne 0, \beta \ne 0$).
 %
@@
 submodular energy, one can use
-graph-cuts~\cite{alpha_expansion}. If a certain fusion step is a
-binary fusion with non-submodular energy, one can use
-QPBO~\cite{second_order_stereo}.
+alpha-expansion~\cite{alpha_expansion}.
 %
+%If a certain fusion step is a
+%binary fusion with non-submodular energy, one can use
+%QPBO~\cite{second_order_stereo}.
+%
+QPBO~\cite{QPBO} can be used to perform binary fusion of non-submodular energy.
 Note that the threads appear synchronized in the figure only for

### 2016-03-14 paper/stereo.tex
minor changes
Hang

--- 2016-03-14 paper/stereo.tex
@@
 
-\noindent The sophistication of photometric consistency
-function~\cite{mvs_furukawa_survey} makes unary terms highly informative
-in most stereo problems.  Our experiments have also supported this,
-where the fusion method (i.e., the use of proposal generation) rather
-makes it slow due to the overhead.
-%\hang{Don't quite understand this sentence. Does the ``dominant'' means
-%running time or energy? In my experiments, unary terms are pre-computed
-%and are not counted into the running time}
-Therefore, we have chosen single thread Alpha Expansion(AE), Parallel
-Alpha
+\noindent For simple stereo problems as ours, the sophistication of
+photometric consistency function~\cite{mvs_furukawa_survey} makes
+unary terms highly informative, thus eliminates the necessity of
+adopting sophicticated proposals. Our experiments have also supported
+this, where the fusion method (i.e., the use of proposal generation)
+rather makes it slow due to the overhead, while not improving final
+energy. Therefore, we have chosen algorithms based on Alpha Expansion,
+namely single thread Alpha Expansion(AE), Parallel Alpha
 Expansion(PAE)~\cite{fusion_moves_for_markov_random_field_optimization}
-and Hierarchical
-Fusion~\cite{delong_hierarchical_fusion,olga_hierarchical_alpha_expansion}
-with graph-cuts optimization as the competing methods.
+and Hierarchical Fusion(HF)~\cite{olga_hierarchical_alpha_expansion}
+for competing methods. For HF, we use Alpha Expansion when either of
+the child node is leaf node (constant label) and QPBO for all other
+nodes.
 
@@
 \noindent The three swarm architectures in Fig.~\ref{fig:model} have
-been evaluated: SF-SS (SF without solution sharing), SF-MF (SF without
-multi-way fusion), and the standard SF.
+been evaluated: SF-MF (SF without multi-way fusion), SF-SS (SF without
+solution sharing), and the standard SF.
 %
-SF-SS implies $\beta=0$, where $\alpha$ is the free parameter and set to
-4. In this case one thread will fuse 4 labels by TRW-S per iteration and
-never exchanges solutions with other threads. SF-MF implies
-$\alpha+\beta=1$, where each thread will expand 3 labels (repeat
-$\alpha=1, \beta=0$ for 3 iterations) and then fuse one solution from
-other threads ($\alpha=0, \beta=1$) by QPBO. In the later case, a thread
-randomly chooses one target thread to copy a solution. For standard SF,
-we have used ($\alpha=4, \beta=1$). For the SF-SS architecture, we
-perform a multi-way fusion at the end to fuse solutions from all the threads.
+SF-MF implies $\alpha+\beta=1$, where each thread will expand 4 labels
+(repeat $\alpha=1, \beta=0$ for 4 iterations) with Alpha Expansion and
+then fuse one solution from other threads ($\alpha=0, \beta=1$) by
+QPBO. In the later case, a thread randomly chooses one target thread
+to take its solution for fusion. SF-SS implies $\beta=0$, where
+$\alpha$ is the free parameter and set to 4. In this case one thread
+will fuse 4 labels, together with current solution by TRW-S per
+iteration and never exchanges solutions with other threads. We perform
+a multi-way fusion at the end to fuse solutions from all the threads
+(similar to PAE). For standard SF, we have used ($\alpha=4, \beta=1$).
 
@@
 in each thread to only generate constant-label proposals within a
-subset of all labels. Graph-cuts is used in fusing a constant-label
-proposal as the energy is submodular. QPBO is used in fusing a
-different solution from another thread as the energy is
-non-submodular in general.
+subset of all labels.
 %

### 2016-03-14 paper/conclusion.tex
spell checking

@@
 experiments have revealed that the framework exploits parallel
-computational resources and achieves faster convergence, epseically for
+computational resources and achieves faster convergence, especially for
 challenging problems.  Our first future work is to conduct experiments
@@
 Parallel MRF inference has been a relatively under-explored topic in
-Computer Vsion. Our idea is very simple, where adapting the Swarm Fusion
+Computer Vision. Our idea is very simple, where adapting the Swarm Fusion
 framework require minimal coding. We believe that this paper would

### 2016-03-14 paper/result_layered_depthmap.tex
Hang
figure placement
spell checking

@@
 performs much better than SF-SS.
+
+\begin{figure}[!h]
+  \centering
+  \includegraphics[width=0.8\columnwidth]{figure/layered_depthmap_convergence.png}
+  \caption{Energy plots for the layered depthmap estimation
+    problem. Both the multi-way fusion and the solution sharing are important
+    for this challenging problem.}\label{fig:layered_depthmap_convergence}
+\end{figure}
+
+\begin{figure}[!h]
+  \centering
+  \begin{subfigure}[b]{0.49\columnwidth}
+    \centering
+    \includegraphics[width=\columnwidth]{figure/layered_depthmap_by_alpha.png}
+    \caption{}
+    \label{fig:layered_depthmap_by_alpha}
+  \end{subfigure}  
+  \begin{subfigure}[b]{0.49\columnwidth}
+    \centering
+    \includegraphics[width=\columnwidth]{figure/layered_depthmap_by_N.png}
+    \caption{}
+    \label{fig:layered_depthmap_by_N}
+  \end{subfigure}
+  \caption{(a) Energy plots for layered depthmap estimation with varying
+    $\alpha$. More multi-way fusion takes longer to converge but finds a better   
+    solution at the end. (b) Energy plots for layered depthmap estimation with varying number of threads N. More threads find lower energy faster.}
+  \label{fig:layered_depthmap_by_alpha_N}
+\end{figure}
 
@@
 At the end we examined the role of multi-threading by varying the number of threads N in our most general model SF (See Fig.~\ref{fig:layered_depthmap_by_N}).~\footnote{Note that we have the constraint that $\beta \leq N-1$, we always use $\beta = N-1$ in this experiment.}  It is natural that our SF model find lower energy faster with more threads.
-While due to the inherited randomness in the proposal and fusion scheme of Fusion Move methods, the speed up is not propotional to the number of threads.
+While due to the inherited randomness in the proposal and fusion scheme of Fusion Move methods, the speed up is not proportional to the number of threads.
 %We can see that as the number of
@@
 %chance of finding a lower energy state increases.
-
-\begin{figure}[tb]
-  \centering
-  \includegraphics[width=0.8\columnwidth]{figure/layered_depthmap_convergence.png}
-  \caption{Energy plots for the layered depthmap estimation
- problem. Both the multi-way fusion and the solution sharing are important
- for this challenging problem.}\label{fig:layered_depthmap_convergence}
-\end{figure}
-
-\begin{figure}[tb]
-  \centering
-  \begin{subfigure}[b]{0.49\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure/layered_depthmap_by_alpha.png}
-    \caption{}
-    \label{fig:optical_flow_by_alpha}
-  \end{subfigure}  
-  \begin{subfigure}[b]{0.49\columnwidth}
-    \centering
-    \includegraphics[width=\columnwidth]{figure/layered_depthmap_by_N.png}
-    \caption{}
-    \label{fig:optical_flow_by_N}
-  \end{subfigure}
-  \caption{(a) Energy plots for layered depthmap estimation with varying
-    $\alpha$. More multi-way fusion takes longer to converge but finds a better   
-    solution at the end. (b) Energy plots for layered depthmap estimation with varying number of threads N. More threads find lower energy faster.}
-  \label{fig:layered_depthmap_by_alpha_N}
-\end{figure}

### 2016-03-14 paper/result_optical_flow.tex
Hang
spell checking

@@
 optimization.
-\begin{figure}[tb]
+
+\begin{figure}[!h]
   \centering
@@
 
-\begin{figure}[t]
+\begin{figure}[!h]
   \centering
@@
 (See Fig.~\ref{fig:optical_flow_by_interval}).  The first experiment
-revealed that the solution sharing makes convergence faster regarless of
-$\beta$.  However, too much solution sharing slows down the converence,
+revealed that the solution sharing makes convergence faster regardless of
+$\beta$.  However, too much solution sharing slows down the convergence,
 and $\beta=1$ is the sweet spot for this problem.
@@
 %problem setting.
-\begin{figure}[tb]
+
+\begin{figure}[!h]
   \centering

### 2016-03-14 paper/introduction.tex

@@
 a solution proposal. Its successful applications cover not only above
-problems, but also popular problmes like optical flow, stereo, image
+problems, but also popular problems like optical flow, stereo, image
 inpainting, or image segmentation
@@
 %
-We believe that the method can be intergrated into existing algorithms
+We believe that the method can be integrated into existing algorithms
 with minimal coding, and would have immediate impact on numerous

### 2016-03-14 paper/result_layered_depthmap.tex
minor changes

@@
 
-At the end we examined the role of multi-threading by varying the number of threads N in our most general model SF (See Fig.~\ref{fig:layered_depthmap_by_N}).~\footnote{Note that we have the constraint that $\beta \leq N-1$, we always use $\beta = N-1$ in this experiment.}  It is natural that our SF model find lower energy faster with more threads.
-While due to the inherited randomness in the proposal and fusion scheme of Fusion Move methods, the speed up is not proportional to the number of threads.
+At the end we examined the role of multi-threading by varying the number of threads N in our most general model SF (See Fig.~\ref{fig:layered_depthmap_by_N})~\footnote{Note that we have the constraint that $\beta \leq N-1$, we always use $\beta = N-1$ in this experiment.}.
+The plot shows that SF finds low energy faster with more threads.
+In Fusion Move like methods, parallism speed up convergence by exploring solution proposals faster.
+While due to the inherited randomness in the proposal generation scheme, the speed up is often not proportional to the number of threads.
 %We can see that as the number of

### 2016-03-14 paper/result_optical_flow.tex
minor changes

@@
 We have chosen the Dimetrodon image pair from the Middlebury flow
-dataset~\cite{middlebury_optical_flow}. Figure~\ref{fig:optical_flow_convergence}
+dataset~\cite{middlebury_optical_flow}. Fig.~\ref{fig:optical_flow_convergence}
 shows the energy plots of the three competing methods, Fusion Move
@@
 To further investigate the effectiveness of solution sharing,
-Figure~\ref{fig:optical_flow_by_threads} shows the energy plots of PFM
+Fig.~\ref{fig:optical_flow_by_threads} shows the energy plots of PFM
 and SF-MF per thread. As evident from the plot, in PFM, one thread found

### 2016-03-14 paper/result_layered_depthmap.tex
minor changes

@@
 \noindent We have used ``ours\_1'' data in~\cite{layered_depthmap} for
-the experiments. Figure~\ref{fig:layered_depthmap_convergence} shows
+the experiments. Fig.~\ref{fig:layered_depthmap_convergence} shows
 that Fusion Move, Parallel Fusion Move and SF-MF all got stuck in local

### 2016-03-14 paper/result_stereo.tex
Hang

--- 2016-03-14 paper/result_stereo.tex
@@
 %
-Fig. \ref{fig:stereo_threads} shows the energy plot per thread
-for SF-MF (ours) and PAE. The graph for PAE again confirms that the
-stereo is an easy problem, because all the threads are quickly
-converging to a solution before the final sequential fusion.
+Fig. \ref{fig:stereo_threads} shows the energy plot per thread for
+SF-MF (ours) and PAE. With solution sharing, the energy of a single
+thread in SF-MF decreases more uniformly, while in PAE the energy
+makes dramatic decrease at the final fusion.
+%
+%The graph for PAE again confirms that the
+%stereo is an easy problem, because all the threads are quickly
+%converging to a solution before the final sequential fusion.
 %shows the per-thread energy
@@
 %whole optimization converges, SF-MF architecture is a better choice.
+
 \begin{figure}[tb]

### 2016-03-14 paper/result_layered_depthmap.tex
minor changes

@@
 
-At the end we examined the role of multi-threading by varying the number of threads N in our most general model SF (See Fig.~\ref{fig:layered_depthmap_by_N})~\footnote{Note that we have the constraint that $\beta \leq N-1$, we always use $\beta = N-1$ in this experiment.}.
+At the end we examined the role of multi-threading by varying the number of threads N in our most general model SF (See Fig.~\ref{fig:layered_depthmap_by_N})~\footnote{While keeping other parameters the same, we have to change $beta$ with $N$ because of the constraint $\beta \leq N-1$.
+We always use $\beta = N-1$ in this experiment.}.
 The plot shows that SF finds low energy faster with more threads.
 In Fusion Move like methods, parallism speed up convergence by exploring solution proposals faster.
-While due to the inherited randomness in the proposal generation scheme, the speed up is often not proportional to the number of threads.
+Due to the inherited randomness in the proposal generation scheme, the speed up is often not proportional to the number of threads.
 %We can see that as the number of

### 2016-03-14 paper/result_stereo.tex
Hang

@@
 \includegraphics[width=0.8\textwidth]{figure/stereo_global.png}
-\caption{Energy plots for the stereo problem. The energy is in the log
-scale. For a multi-threading algorithm, the energy at a given moment is
+\caption{Energy plots for the stereo problem. For a multi-threading algorithm, the energy at a given moment is
 defined to be the best solution so far.}
@@
 
-One unusual outcome is that Sequential Alpha Expansion and Parallel
-Alpha Expansion (PAE) have the same convergence speed, indicating that
-the stereo problem is a very easy one.
+%One unusual outcome is that Sequential Alpha Expansion and Parallel
+%Alpha Expansion (PAE) have the same convergence speed, indicating that
+%the stereo problem is a very easy one.
+PAE and SF-MF converges faster than the single thread AE. However, the
+speedup is not significant, which confirms the fact that the problem
+is an easy one.
 %This is well known in a community and this fact was rather expected.
-Our approaches with multi-way fusion (SF-SS or SF) are the slowest kind,
-because the TRW-S for multi-way fusion is slower than multiple Alpha
-Expansion steps, and this stereo problem is too easy to gain benefits
-through mulit-way fusion.
+Our approaches with multi-way fusion (SF-SS or SF) are the slowest
+kind, because the TRW-S for multi-way fusion is slower than multiple
+Alpha Expansion steps, and this stereo problem is too easy to gain
+benefits through mulit-way fusion. HF doesn't perform well either
+because for nodes with two non-leaf children, the algorithm has to
+perform QPBO.
 %
@@
 
-\begin{figure}[tb]
-\includegraphics[width=\columnwidth]{figure/stereo_threads.png}
-\caption{Energy plots per thread for the stereo proble for SF-MF (left) and
-Parallel Alpha Expansion (right).
-} \label{fig:stereo_threads}
+\begin{figure}[!h]
+\centering
+\begin{subfigure}{0.49\textwidth}
+\includegraphics[width=\textwidth]{figure/stereo_thread_pae.png}
+\caption{}
+\end{subfigure}
+\begin{subfigure}{0.49\textwidth}
+\includegraphics[width=\textwidth]{figure/stereo_thread_sf.png}
+\caption{}
+\end{subfigure}
+\caption{Energy plots per thread for the stereo proble for (a) PAE and (b)
+SF-MF.}
+\label{fig:stereo_threads}
 \end{figure}
 
-For an easy optimization problem such as stereo with strong unary terms
-and submodular pairwise terms, our full architecture with solution
-sharing and multi-way fusion actually makes convergence slower due to the
-overhead of fusion and multi-threading.
+For an easy optimization problem such as stereo with strong unary
+terms and submodular pairwise terms, our full architecture with
+solution sharing and multi-way fusion actually makes convergence
+slower compared with PAE due to overhead of sophisticated fusion.
 

### 2016-03-14 stereo/code/plotEnergy.m

@@ -30,7 +30,7 @@ for i=1:nm
 end
 legend(legend_name_global);
 xlabel('Time/s');
-ylabel('Energy(log scale)');
+ylabel('Energy(log-scale)');
 fig_glb.Position = [500,500,1280,720];
 
 %subfigure for thread
@@ -42,23 +42,32 @@ end
 
 hold off;
 
-% for i=2:2:4
-%     fig_thread = figure(i+1);
-%     hold on;
-%     mid = i;
-%     for j=1:nt
-%         filepath = sprintf('%s/plot_%s_thread%d.txt', dataset, method_name{mid}, j-1);
-%         disp(filepath);
-%         thd = dlmread(filepath);
-%         thd_trun = thd(thd(:,1) < max_time / 2, :);
-%         plot(thd_trun(:,1), log(thd_trun(:,2)), 'LineWidth', line_width);
-%     end
-%     legend('Thread 1', 'Thread 2', 'Thread 3', 'Thread 4');
-%     xlabel('Time/s');
-%     ylabel('Energy');
-%     fig_thread.Position = [500,500,640,500];
-%     hold off;
-% end
+set(0, 'DefaultAxesFontName', 'Times New Roman');
+set(0, 'DefaultAxesFontSize',30);
+set(0, 'DefaultTextFontname', 'Times New Roman');
+set(0, 'DefaultTextFontSize', 30);
+line_width = 2.0;
+for i=4:-2:2
+    fig_thread = figure(i+1);
+    hold on;
+    mid = i;
+    for j=1:nt
+        filepath = sprintf('%s/plot_%s_thread%d.txt', dataset, method_name{mid}, j-1);
+        disp(filepath);
+        thd = dlmread(filepath);
+        thd_trun = thd(thd(:,1) < max_time / 2, :);
+        plot(thd_trun(:,1), log(thd_trun(:,2)), 'LineWidth', line_width);
+    end
+    if i==2
+        legend('PAE Thread 1', 'PAE Thread 2', 'PAE Thread 3', 'PAE Thread 4');
+    else
+        legend('SM-MF(ours) Thread 1', 'SM-MF(ours) Thread 2', 'SM-MF(ours) Thread 3', 'SM-MF(ours) Thread 4');
+    end
+    xlabel('Time/s');
+    ylabel('Energy(log-scale)');
+    fig_thread.Position = [500,500,640,500];
+    hold off;
+end
 
 %draw energy vs. number of threads
 % figure_nthreads = figure(10);

### 2016-03-15 paper/algorithm.tex
minor changes
Hang

@@
 Swarm Fusion framework is very flexible and yields various data
-processing architectures as shown in Figure~\ref{fig:model}.
+processing architectures as shown in Fig.~\ref{fig:model}.
 %
@@
  each thread takes arbitrary number of solution proposals and concurrent
- solutions from other threads for fusion. The framework is flexible and
+ solutions for fusion. The framework is flexible and
  can realize other data processing architectures depending on the
@@
  as Alpha Expansion~\cite{alpha_expansion}, Fusion Move~\cite{fusion_moves_for_markov_random_field_optimization},
- Parallel Alpha Expansion~\cite{olga_hierarchical_alpha_expansion}, or Hierarchical
+ Parallel Alpha Expansion~\cite{olga_hierarchical_alpha_expansion}, and Hierarchical
  Fusion~\cite{delong_hierarchical_fusion}, are all special cases of
@@
 threads conduct multi-way fusion of their current solution, proposals
-from their own proposal generators and/or concurrent solutions (i.e.,
-$\alpha\ne 0, \beta \ne 0$).
+from their own proposal generators and/or concurrent solutions.
 %
@@
 %
-QPBO~\cite{QPBO} can be used to perform binary fusion of non-submodular energy.
+QPBO~\cite{QPBO} can be used to perform binary fusion with non-submodular energy.
 Note that the threads appear synchronized in the figure only for
@@
 %
-\begin{algorithm}
+\begin{algorithm}[t]
  \caption{Swarm Fusion method}
@@
   \Procedure{} {$\alpha, \beta$}
-  \State $\mathcal{S}_{pool} \leftarrow \emptyset$ //
-  Solution pool
+  \State $\mathcal{S}_{pool} \leftarrow \emptyset$ \ \ \ //Solution pool
   %\State Initialize $\mathcal{P}_{pool}$ // Proposal pool
@@
 can be realized by setting $(\alpha=1, \beta=0)$ and
-restricting the proposal generation to constant labels with
+restricting the proposals to be constant labels with
 a single thread. The same goes for FM, this time, without

### 2016-03-15 paper/related_work.tex
hang
Hang

@@
 
-\noindent Lempitsky et al.~\cite{fusion_moves_for_markov_random_field_optimization} introduces parallel computation to an
-alpha-expansion technique, where multiple threads simultaneously fuses
-mutually exclusive sets of labels. Kumar et
-al.~\cite{hierarchical_graph_cuts_kumar_and_koller}, Delong et
-al.~\cite{delong_hierarchical_fusion}, and Veksler et al.~\cite{olga_hierarchical_alpha_expansion} proposed an hierarchical
-approach, where labels can be simultaneously fused from the bottom to
+\noindent Lempitsky et
+al.~\cite{fusion_moves_for_markov_random_field_optimization}
+introduces parallel computation to the alpha-expansion technique,
+where multiple threads simultaneously fuse mutually exclusive sets of
+labels. Kumar et al.~\cite{hierarchical_graph_cuts_kumar_and_koller},
+Delong et al.~\cite{delong_hierarchical_fusion}, and Veksler et
+al.~\cite{olga_hierarchical_alpha_expansion} investigated hierarchical
+approachs, where labels can be simultaneously fused from the bottom to
 the top in a tree of labels.
@@
 
-\noindent FM was first introduced by Lempitsky et al.~\cite{fusion_flow} in solving an
+\noindent FM was first introduced by Lempitsky et al.~\cite{fusion_flow} in solving the
 optical flow problem. FM has been effectively used to solve challenging
@@
 priors~\cite{second_order_stereo}, stereo with parameteric surface fitting and
-segmentation (i.e. Surface Stereo)~\cite{surface_stereo}, or multicut
+segmentation (i.e. Surface Stereo)~\cite{surface_stereo}, and multicut
 partitioning~\cite{fusion_moves_for_correlation_clustering}.
 %
-FM has two main advantages over the other general inference
+FM has two main advantages over other general inference
 techniques~\cite{TRW-S,loopy_belief_propagation}. First, FM allows us to
-exploit domain-specific knowledge in customizing proposal generation
+exploit domain-specific knowledge by customizing proposal generation
 schemes. Second, FM can handle problems with very large label spaces
@@
 GA or PSO has been used to produce great empirical results,
-hand tracking~\cite{pushmeet_hand_tracking} for example.
+e.g. in hand tracking~\cite{pushmeet_hand_tracking}.
 %

### 2016-03-15 paper/abstract.tex

@@
 general, making popular existing inference techniques such as
-alpha-expansion, fusion move, parallel alpha-expansion, or hierarchical
+alpha-expansion, fusion move, parallel alpha-expansion, and hierarchical
 fusion, its special cases. We have evaluated the effectiveness of our

### 2016-03-15 paper/introduction.tex

@@
 Parallel computation has changed the field of computing.  In the 90s,
-most processors had single cores, while nowadays most processors have
-multiple cores, often 4 or even 8. Cluster computing further expands
-the potential of parallel computation, where one can easily launch a
+most processors had single cores, while nowadays processors with 4 or
+8 cores are commonly used. Cluster computing further expands the
+potential of parallel computation, where one can easily launch a
 processing job using hundreds or even thousands of computational nodes
@@
 %
-The MAP framework, which can be formulated as a Markov Random Field
-(MRF) in many low-level Computer Vision problems, provides a universal
-and powerful way to solve these problems. However, state-of-the-art
-algorithms for MRF inference are still inherently sequential. Take a
-Fusion Move method
+Markov Random Field (MRF) provides a universal and powerful way to
+solve many low-level Computer Vision problems. However,
+state-of-the-art algorithms for MRF inference are still inherently
+sequential. Take a Fusion Move method
 (FM)~\cite{fusion_flow,fusion_moves_for_markov_random_field_optimization,second_order_stereo}
 for example, which has been one of the most effective techniques for
-MRF inference, it sequentially improves solution by fusing the current solution with
-a solution proposal. Its successful applications cover not only above
-problems, but also popular problems like optical flow, stereo, image
-inpainting, or image segmentation
+MRF inference. It sequentially improves solution by fusing the current
+solution with a solution proposal. Its successful applications cover
+not only above problems, but also popular problems like optical flow,
+stereo, image inpainting, or image segmentation
 problems~\cite{fusion_moves_for_markov_random_field_optimization}.
@@
 We believe that the method can be integrated into existing algorithms
-with minimal coding, and would have immediate impact on numerous
+with minimal coding, and would have immediate benefit to numerous
 Computer Vision researchers or engineers.

### 2016-03-15 paper/optical_flow.tex

@@
 flow benchmark~\cite{middlebury_optical_flow}. We share similar proposal
-generation schemes with Lempitsky et al~\cite{fusion_flow}, but
+generation schemes with Lempitsky et al~\cite{fusion_flow}
 %instead of the HS algorithm, we
-use more recent Farneback algorithm with some modifications.~\footnote{First, we
-change the level of pyramids from 1 to 5, then use either 3, 5 or 7 for
-parameter ``polyN''. Besides the clustering idea, we add three simple
-proposal generation schemes based on the current solution as suggested
-in \cite{fusion_flow}. In \textit{shift proposal}, the flow field in the
-current solution is shifted in either x or y directions for
-either 1, 2 or 3 pixels. In \textit{stagger proposal}, the flow field is
-shifted by a vector randomly drawn from a Gaussian distribution. In
-\textit{perturb proposal}, each flow value in the field is
-independently shifted by a vector randomly drawn from a Gaussian
-distribution. We choose schemes randomly when generating proposals.}
+ with some modifications.~\footnote{First, we use more recent
+   Farneback algorithm and change the level of pyramids from 1 to 5,
+   then use either 3, 5 or 7 for parameter ``polyN''. Besides the
+   clustering idea, we add three simple proposal generation schemes
+   based on the current solution as suggested in
+   \cite{fusion_flow}. In \textit{shift proposal}, the flow field in
+   the current solution is shifted in either x or y directions for
+   either 1, 2 or 3 pixels. In \textit{stagger proposal}, the flow
+   field is shifted by a vector randomly drawn from a Gaussian
+   distribution. In \textit{perturb proposal}, each flow value in the
+   field is independently shifted by a vector randomly drawn from a
+   Gaussian distribution. We choose schemes randomly when generating
+   proposals.}
 
@@
 %are used to evaluate the effectiveness of our method.
-The three swarm architectures in Fig.~\ref{fig:model} (SF-MF, SF-SS, SF)
-have been evaluated against the competing methods. For SF-MF, each
-thread repeats generating solution proposals ($\alpha=1, \beta=0$) for four
-iterations and fuses with one solution from others ($\alpha=0, \beta=1$)
-in one iteration. This pattern is repeated. For SF-SS, each thread
-generates three solution proposals for fusion in each iteration
-($\alpha=3$, $\beta=0$). For SF, we repeat ($\alpha=3, \beta=0$) for four
-iterations and ($\alpha=0, \beta=3$) for one iteration.
+The three swarm architectures in Fig.~\ref{fig:model} (SF-MF, SF-SS,
+SF) have been evaluated against the competing methods. For SF-MF, each
+thread repeats generating solution proposals ($\alpha=1, \beta=0$) for
+four iterations and fuses with one solution from others ($\alpha=0,
+\beta=1$) in one iteration. This pattern is repeated. For SF-SS, each
+thread generates three solution proposals for fusion in each iteration
+($\alpha=3$, $\beta=0$). For SF, we repeat the pattern of four
+iterations with ($\alpha=3, \beta=0$) plus one iteration with ($\alpha=0,
+\beta=3$).
 %%

### 2016-03-15 paper/result_stereo.tex

@@
 Alpha Expansion steps, and this stereo problem is too easy to gain
-benefits through mulit-way fusion. HF doesn't perform well either
-because for nodes with two non-leaf children, the algorithm has to
-perform QPBO.
+benefits through mulit-way fusion. HF doesn't perform well because the
+algorithm has to perform QPBO for all nodes with two non-leaf
+children.
 %
@@
 Fig. \ref{fig:stereo_threads} shows the energy plot per thread for
-SF-MF (ours) and PAE. With solution sharing, the energy of a single
-thread in SF-MF decreases more uniformly, while in PAE the energy
-makes dramatic decrease at the final fusion.
+SF-MF (ours) and PAE. With solution sharing, the energy in SF-MF
+decreases more uniformly, while in PAE the energy makes dramatic
+decrease at the final fusion.
 %
@@
 \end{subfigure}
-\caption{Energy plots per thread for the stereo proble for (a) PAE and (b)
+\caption{Energy plots per thread for the stereo problem for (a) PAE and (b)
 SF-MF.}

### 2016-03-15 paper/result_layered_depthmap.tex
minor changes

@@
 %
-%From the plot, we can see that, Fusion Move, Parallel Fusion Move, and
+% From the plot, we can see that, Fusion Move, Parallel Fusion Move, and
 %SF-MF all stalk at a high energy state.
@@
 
-At the end we examined the role of multi-threading by varying the number of threads N in our most general model SF (See Fig.~\ref{fig:layered_depthmap_by_N})~\footnote{While keeping other parameters the same, we have to change $beta$ with $N$ because of the constraint $\beta \leq N-1$.
+At the end we examined the role of multi-threading by varying the number of threads N in our most general model SF (See Fig.~\ref{fig:layered_depthmap_by_N})~\footnote{While keeping other parameters the same, we have to change $\beta$ with $N$ because of the constraint $\beta \leq N-1$.
 We always use $\beta = N-1$ in this experiment.}.
 The plot shows that SF finds low energy faster with more threads.
-In Fusion Move like methods, parallism speed up convergence by exploring solution proposals faster.
+In Fusion Move like methods, parallelism speeds up convergence by exploring solution proposals faster.
 Due to the inherited randomness in the proposal generation scheme, the speed up is often not proportional to the number of threads.

### 2016-03-15 LayerDepthMap/Statistics/convertValues.m
minor changes

@@ -20,7 +20,7 @@ for i = 2:size(raw_values, 1)
         end
         previous_energy = raw_values(i, 2);
     end
-    if (raw_values(i, 1) > start_time + 420)
+    if (raw_values(i, 1) > start_time + 4200)
         break;
     end
 end

### 2016-03-15 paper/result_optical_flow.tex

@@
   \caption{Energy plots per thread for (a) Parallel Fusion  
-    Move (PFM) and (b) our FS-MF.}
+    Move (PFM) and (b) our SF-MF.}
   \label{fig:optical_flow_by_threads}  
@@
 Fig.~\ref{fig:optical_flow_by_beta}).  Second, we change the number of
-iterations $k$ between the two consecutive solution sharing iterations
+iterations $k$ between two consecutive solution sharing iterations
 (See Fig.~\ref{fig:optical_flow_by_interval}).  The first experiment

### 2016-03-15 paper/stereo.tex

@@
   \includegraphics[width=\columnwidth]{figure/problem.pdf} \caption{We
-    compare our Swarm Fusion method against competing approaches on a
-    depthmap stereo~\cite{middlebury_stereo}, an optical
-    flow~\cite{middlebury_optical_flow}, or a layered depthmap
+    compare our Swarm Fusion method against competing approaches on the
+    depthmap stereo~\cite{middlebury_stereo}, the optical
+    flow~\cite{middlebury_optical_flow} and the layered depthmap
     estimation~\cite{layered_depthmap} problem. In the layered
     depthmap problem, the input is an RGBD image, and the output is
-    multiple layeres of depthmaps. Each layer is a piecewise smooth
+    multiple layers of depthmaps. Each layer is a piecewise smooth
     parametric surface model.}\label{fig:problem}
@@
 
-\noindent For simple stereo problems as ours, the sophistication of
-photometric consistency function~\cite{mvs_furukawa_survey} makes
-unary terms highly informative, thus eliminates the necessity of
-adopting sophicticated proposals. Our experiments have also supported
-this, where the fusion method (i.e., the use of proposal generation)
-rather makes it slow due to the overhead, while not improving final
-energy. Therefore, we have chosen algorithms based on Alpha Expansion,
-namely single thread Alpha Expansion(AE), Parallel Alpha
+\noindent For simple stereo problems with submodular energy as ours,
+the sophistication of photometric consistency
+function~\cite{mvs_furukawa_survey} makes unary terms highly
+informative, where highly efficient algorithms such as graph-cuts
+exist. Our experiments have also supported this, where the fusion
+method (i.e., the use of proposal generation) rather makes it slow due
+to the overhead, while not improving final energy. Therefore, we have
+chosen algorithms based on Alpha-Expansion, namely single thread Alpha
+Expansion(AE), Parallel Alpha
 Expansion(PAE)~\cite{fusion_moves_for_markov_random_field_optimization}
 and Hierarchical Fusion(HF)~\cite{olga_hierarchical_alpha_expansion}
-for competing methods. For HF, we use Alpha Expansion when either of
+to be competing methods. For HF, we use Alpha-Expansion when either of
 the child node is leaf node (constant label) and QPBO for all other
@@
 then fuse one solution from other threads ($\alpha=0, \beta=1$) by
-QPBO. In the later case, a thread randomly chooses one target thread
-to take its solution for fusion. SF-SS implies $\beta=0$, where
-$\alpha$ is the free parameter and set to 4. In this case one thread
-will fuse 4 labels, together with current solution by TRW-S per
-iteration and never exchanges solutions with other threads. We perform
-a multi-way fusion at the end to fuse solutions from all the threads
-(similar to PAE). For standard SF, we have used ($\alpha=4, \beta=1$).
+QPBO. In the later case, a thread randomly chooses one solution from
+the solution pool for fusion. SF-SS implies $\beta=0$, where $\alpha$
+is the free parameter and set to 4. In this case one thread will fuse
+4 labels, together with current solution by TRW-S per iteration and
+never exchanges solutions with other threads. We perform a multi-way
+fusion at the end to fuse solutions from all the threads (similar to
+PAE). For standard SF, we have used ($\alpha=4, \beta=1$).
 

### 2016-03-15 paper/abstract.tex
yasu

@@
 Fusion Move method. Every thread (in a case of multi-threading
-environments) maintains and updates a solution. At every iteration, a
+environments) maintains and updates a solution. At each iteration, a
 thread can generate arbitrary number of solution proposals and take

### 2016-03-15 paper/algorithm.tex
yasu

@@
 Move method (FM). We call our method Swarm Fusion (SF) in short. Let us
-take a multi-threading environment to explain our idea, while the
+take multi-threading environment to explain our idea, while the
 technique is also applicable to other parallel programming model such as
@@
 SF has two main parameters $\alpha_i$, $\beta_i$ (for each thread
-$T_i$), determining its processing flow: In each fusion step, a thread
+$T_i$), determining its behaviors: In each fusion step, a thread
 generates $\alpha_i$ solution proposals using its proposal generator, and collects
@@
 $\beta_i$ solutions from the solution pool, based on a user-defined
-strategy or at random to be simple. The value of $\alpha_i$ and
-$\beta_i$ can vary in each iteration to encourage different behaviors.
-The thread then fuse all these solutions together to find a solution
+strategy or at random to be simple. The values of $\alpha_i$ and
+$\beta_i$ can vary per iteration for flexibility.
+The thread then fuse all these proposals and/or solutions to find a solution
 with lower energy state and update the solution pool accordingly.

### 2016-03-15 paper/introduction.tex
yasu

@@
 Parallel computation has changed the field of computing.  In the 90s,
-most processors had single cores, while nowadays processors with 4 or
-8 cores are commonly used. Cluster computing further expands the
-potential of parallel computation, where one can easily launch a
-processing job using hundreds or even thousands of computational nodes
-in a cloud.
+most processors had single cores. In 2016, processors have often 4 cores,
+or even 8. Cluster computing further expands the potential
+of parallel computation, where one can easily launch a processing job
+using hundreds or even thousands of computational nodes in a cloud.
 %
@@
 %
-Markov Random Field (MRF) provides a universal and powerful way to
-solve many low-level Computer Vision problems. However,
-state-of-the-art algorithms for MRF inference are still inherently
-sequential. Take a Fusion Move method
+Markov Random Field (MRF) has been a very successful framework to solve
+these problems in Computer Vision. However, state-of-the-art algorithms
+for MRF inference are still inherently sequential. Take a Fusion Move
+method
 (FM)~\cite{fusion_flow,fusion_moves_for_markov_random_field_optimization,second_order_stereo}
-for example, which has been one of the most effective techniques for
-MRF inference. It sequentially improves solution by fusing the current
-solution with a solution proposal. Its successful applications cover
-not only above problems, but also popular problems like optical flow,
-stereo, image inpainting, or image segmentation
-problems~\cite{fusion_moves_for_markov_random_field_optimization}.
+for example, which has been one of the most effective techniques for MRF
+inference. It sequentially improves solution by fusing the current
+solution with a solution proposal. It has been successfully applied to
+many problems such as optical flow, stereo, image inpainting, or image
+segmentation~\cite{fusion_moves_for_markov_random_field_optimization}.
 
@@
 %
-Our approach, dubbed {\it Swarm Fusion} method (SF), makes a
-few key distinctions from existing approaches: 1) Multiple threads (or
-computing nodes) simultaneously keep and improve solutions; and 2) Each
-fusion in each thread can take arbitrary number of proposals from
-arbitrary combination of proposal generation schemes, even concurrent
-solutions in the other threads, to fuse with the current solution.
+Our approach, dubbed {\it Swarm Fusion} method (SF), makes a few key
+distinctions from existing approaches: 1) Multiple threads (or computing
+nodes) simultaneously keep and improve solutions; and 2) Each fusion in
+each thread can generate arbitrary number of solution proposals and use
+arbitrary number of concurrent solutions in the other threads, to be fused
+with the current solution.
 %
@@
 We have evaluated the effectiveness of our approach over three problems
-in Computer Vision, stereo, optical flow, and layered
+in Computer Vision, specifically, stereo, optical flow, and layered
 depthmap estimation.
@@
 %
-We believe that the method can be integrated into existing algorithms
-with minimal coding, and would have immediate benefit to numerous
-Computer Vision researchers or engineers.
+Our idea is extremely simple and the new inference framework can be
+integrated into existing system with minimal coding. We believe that
+this paper would have immediate impact on numerous Computer Vision
+researchers or engineers, currently solving MRF problems with
+conventional methods.
 

### 2016-03-15 paper/related_work.tex
yasu

@@
 
-\noindent FM was first introduced by Lempitsky et al.~\cite{fusion_flow} in solving the
-optical flow problem. FM has been effectively used to solve challenging
-problems in Computer Vision such as stereo with second order smoothness
-priors~\cite{second_order_stereo}, stereo with parameteric surface fitting and
-segmentation (i.e. Surface Stereo)~\cite{surface_stereo}, and multicut
+\noindent FM was first introduced by Lempitsky et al.~\cite{fusion_flow}
+in solving the optical flow problem. FM has been effectively used to
+solve other challenging problems in Computer Vision such as stereo with
+second order smoothness priors~\cite{second_order_stereo}, stereo with
+parameteric surface fitting and segmentation (i.e. Surface
+Stereo)~\cite{surface_stereo}, and multicut
 partitioning~\cite{fusion_moves_for_correlation_clustering}.

### 2016-03-15 paper/result_layered_depthmap.tex
minor changes
hang
yasu

@@
 \noindent We have used ``ours\_1'' data in~\cite{layered_depthmap} for
-the experiments. Fig.~\ref{fig:layered_depthmap_convergence} shows
-that Fusion Move, Parallel Fusion Move and SF-MF all got stuck in local
+the experiments. Fig.~\ref{fig:layered_depthmap_convergence} shows that
+Fusion Move, Parallel Fusion Move and SF-MF all got stuck in local
 minima, which is due to the lack of multi-way fusion.  Layered depthmap
@@
 multi-way fusion here. Lastly, solution sharing also plays an important
-role for this challenging problem for exactly the same reason, as SF
-performs much better than SF-SS.
+role for this challenging problem, as SF performs much better than
+SF-SS.
 
@@
   \caption{(a) Energy plots for layered depthmap estimation with varying
-    $\alpha$. More multi-way fusion takes longer to converge but finds a better   
-    solution at the end. (b) Energy plots for layered depthmap estimation with varying number of threads N. More threads find lower energy faster.}
+    $\alpha$. (b) Energy plots for layered depthmap estimation with varying number of threads N.}
   \label{fig:layered_depthmap_by_alpha_N}
@@
 
-At the end we examined the role of multi-threading by varying the number of threads N in our most general model SF (See Fig.~\ref{fig:layered_depthmap_by_N})~\footnote{While keeping other parameters the same, we have to change $\beta$ with $N$ because of the constraint $\beta \leq N-1$.
-We always use $\beta = N-1$ in this experiment.}.
-The plot shows that SF finds low energy faster with more threads.
-In Fusion Move like methods, parallelism speeds up convergence by exploring solution proposals faster.
-Due to the inherited randomness in the proposal generation scheme, the speed up is often not proportional to the number of threads.
+Finally, we have examined the role of multi-threading by varying the
+number of threads N in our most general model SF (See
+Fig.~\ref{fig:layered_depthmap_by_N})~\footnote{While keeping other
+parameters the same, we have to change $\beta$ with $N$ because of the
+constraint $\beta \leq N-1$. We have always used $\beta = N-1$ in this
+experiment.}. More threads lead to faster convergence as expected,
+although the rate of speed-up is not proportional to the number of
+threads due to the randomness in the proposal generation scheme.
+%The plot shows that SF finds low energy faster with more
+%threads.
+% In Fusion Move like methods, parallelism speeds up convergence
+% by exploring solution proposals faster. Due to the inherited randomness
+% in the proposal generation scheme, the speed up is often not
+% proportional to the number of threads.
 %We can see that as the number of

### 2016-03-15 paper/result_optical_flow.tex
yasu

--- 2016-03-14 paper/result_optical_flow.tex
@@
 Figure~\ref{fig:optical_flow_by_threads} shows the energy plots of PFM
-and SF-MF per thread. As evident from the plot, in PFM, one thread found
-a better solution than others, but other threads keep working
-independently at higher energy states. SF-MF, on the other hand,
-exchanges solutions all the time, and every thread is making an effective
-work in improving the solution.
+and SF-MF per thread. As evident from the plot, in PFM, threads need to
+keep working independently at higher energy states.
+%in PFM, one thread found a better solution than others, but other
+%threads keep working independently at higher energy states.
+SF-MF, on the other hand, exchanges solutions all the time, and every
+thread is making an effective work in improving the solution.
 %As we can see from the plots, in PFM model, one thread finds lower
@@
 solutions) once in every five iterations.  To further understand the
-effects of solution sharing, we did two more experiments. First, we set
-$\beta$ to 0, 1, 2, or 3 in every five iterations,
+effects of solution sharing, we conducted two more experiments. First,
+we set $\beta$ to 0, 1, 2, or 3 in every five iterations,
 % (when $\beta = 0$, it is the same with PFM without final merging).
@@
 The second experiment has shown that too frequent solution sharing
-harms the convergence, simply because we have less time generating more
+harms the convergence, simply because threads have less time generating more
 proposals and exploring the solution space.

### 2016-03-15 paper/result_stereo.tex
yasu

@@
 \noindent We have chosen 7 images with the resolution of $695\times555$
-from the Book sequence of Middlebury stereo dataset~\cite{middlebury_stereo} for our
-experiment. The number of disparity labels is
-set to 256. 
+from the Book sequence of Middlebury stereo
+dataset~\cite{middlebury_stereo}. The number of disparity labels is set
+to 256.
 %
@@
 
-Fig.~\ref{fig:stereo_global} compares the converegence rate of the
+Figure~\ref{fig:stereo_global} compares the converegence rate of the
 competing methods. Note that we define the energy of a multi-threading
@@
 %
-
 \begin{figure}[tb]
@@
 %
-
 %One unusual outcome is that Sequential Alpha Expansion and Parallel
@@
 Alpha Expansion steps, and this stereo problem is too easy to gain
-benefits through mulit-way fusion. HF doesn't perform well because the
-algorithm has to perform QPBO for all nodes with two non-leaf
-children.
+benefits through mulit-way fusion.
+%HF does not perform well because the algorithm has to perform QPBO for
+%all nodes with two non-leaf children.
 %
@@
 %
-Fig. \ref{fig:stereo_threads} shows the energy plot per thread for
+Figure~\ref{fig:stereo_threads} shows the energy plot per thread for
 SF-MF (ours) and PAE. With solution sharing, the energy in SF-MF
@@
 solution sharing and multi-way fusion actually makes convergence
-slower compared with PAE due to overhead of sophisticated fusion.
+slower compared with PAE due to its overhead.
+% of sophisticated fusion.
 

### 2016-03-15 paper/stereo.tex
yasu

@@
 We compare SF against competing approaches over three problems in
-Computer Vision, namely, stereo, optical flow, and layered depthmap
-estimation.
+Computer Vision, specifically, stereo, optical flow, and layered
+depthmap estimation.
 
@@
 
-\noindent For simple stereo problems with submodular energy as ours,
-the sophistication of photometric consistency
+\noindent For simple stereo problems with submodular energy as ours, the
+sophistication of photometric consistency
 function~\cite{mvs_furukawa_survey} makes unary terms highly
-informative, where highly efficient algorithms such as graph-cuts
-exist. Our experiments have also supported this, where the fusion
-method (i.e., the use of proposal generation) rather makes it slow due
-to the overhead, while not improving final energy. Therefore, we have
-chosen algorithms based on Alpha-Expansion, namely single thread Alpha
-Expansion(AE), Parallel Alpha
+informative, where efficient inference algorithms such as graph-cuts
+exist.
+%Our experiments have also supported this, where the fusion method
+%(i.e., the use of proposal generation) rather makes it slow due to the
+%overhead, while not improving final energy.
+Therefore, we have chosen algorithms based on Alpha-Expansion, namely
+single thread Alpha Expansion(AE), Parallel Alpha
 Expansion(PAE)~\cite{fusion_moves_for_markov_random_field_optimization}
-and Hierarchical Fusion(HF)~\cite{olga_hierarchical_alpha_expansion}
-to be competing methods. For HF, we use Alpha-Expansion when either of
-the child node is leaf node (constant label) and QPBO for all other
-nodes.
+and Hierarchical Fusion(HF)~\cite{olga_hierarchical_alpha_expansion} to
+be competing methods. For HF, we use Alpha-Expansion at the leaf node of
+the label tree or QPBO in the other cases.
+%when either of the
+%child node is leaf node (constant label) and QPBO for all other nodes.
 
@@
 %
-SF-MF implies $\alpha+\beta=1$, where each thread will expand 4 labels
-(repeat $\alpha=1, \beta=0$ for 4 iterations) with Alpha Expansion and
-then fuse one solution from other threads ($\alpha=0, \beta=1$) by
-QPBO. In the later case, a thread randomly chooses one solution from
-the solution pool for fusion. SF-SS implies $\beta=0$, where $\alpha$
-is the free parameter and set to 4. In this case one thread will fuse
-4 labels, together with current solution by TRW-S per iteration and
-never exchanges solutions with other threads. We perform a multi-way
-fusion at the end to fuse solutions from all the threads (similar to
-PAE). For standard SF, we have used ($\alpha=4, \beta=1$).
-
+SF-MF implies $\alpha+\beta=1$, where each thread repeats
+fusing a solution proposal ($\alpha=1, \beta=0$) for four iterations
+by Graph-cuts and fusing a concurrent solution  ($\alpha=0, \beta=1$)
+for one iteration by QPBO.
+%expand 4 labels (repeat $\alpha=1, \beta=0$ for 4 iterations) with Alpha
+%Expansion and then fuse one solution from other threads ($\alpha=0,
+%\beta=1$) by QPBO.
+In the later case, a thread randomly chooses one solution from the
+solution pool for fusion. SF-SS implies $\beta=0$, where $\alpha$ is the
+free parameter and set to 4. In this case one thread will fuse 4 labels,
+together with current solution by TRW-S per iteration and never
+exchanges solutions with other threads. We perform a multi-way fusion
+of solutions from all the threads at the end to obtain a final solution
+% at
+% the end to fuse solutions from all the threads to a single solution
+(similar to PAE). For standard SF, we have used ($\alpha=4, \beta=1$).
 %
@@
 %
-To make the comparison simple, we restrict our proposal generator
-in each thread to only generate constant-label proposals within a
-subset of all labels.
+To make the comparison simple, we restrict our solution proposals
+to be constant-label proposals.
 %

### 2016-03-15 paper/result_layered_depthmap.tex
Hang

@@
     \includegraphics[width=\columnwidth]{figure/layered_depthmap_by_alpha.png}
-    \caption{}
-    \label{fig:layered_depthmap_by_alpha}
   \end{subfigure}  
@@
     \includegraphics[width=\columnwidth]{figure/layered_depthmap_by_N.png}
-    \caption{}
-    \label{fig:layered_depthmap_by_N}
   \end{subfigure}
@@
     $\alpha$. (b) Energy plots for layered depthmap estimation with varying number of threads N.}
-  \label{fig:layered_depthmap_by_alpha_N}
+  \label{fig:layered_depthmap_configuration}
 \end{figure}
@@
 fused in SF-SS model (See
-Fig.~\ref{fig:layered_depthmap_by_alpha}). Note that we have used SF-SS
+Fig.~\ref{fig:layered_depthmap_configuration}(left)). Note that we have used SF-SS
 instead of SF to disable solution sharing and better observe the effects
@@
 number of threads N in our most general model SF (See
-Fig.~\ref{fig:layered_depthmap_by_N})~\footnote{While keeping other
+Fig.~\ref{fig:layered_depthmap_configuration}(right))~\footnote{While keeping other
 parameters the same, we have to change $\beta$ with $N$ because of the

### 2016-03-15 paper/result_optical_flow.tex
Hang

@@
     \includegraphics[width=\columnwidth]{figure/optical_flow_PFM_threads.png}
-    \caption{}
-    \label{fig:optical_flow_PFM_threads}
   \end{subfigure}  
@@
     \includegraphics[width=\columnwidth]{figure/optical_flow_SF_MF_threads.png}
-    \caption{}
-    \label{fig:optical_flow_SF_MF_threads}
   \end{subfigure}
-  \caption{Energy plots per thread for (a) Parallel Fusion  
-    Move (PFM) and (b) our SF-MF.}
+  \caption{Energy plots per thread. Left: Parallel Fusion  
+    Move (PFM). Right: SF-MF(ours).}
   \label{fig:optical_flow_by_threads}  
@@
 while keeping all other parameters the same (See
-Fig.~\ref{fig:optical_flow_by_beta}).  Second, we change the number of
+Fig.~\ref{fig:opticalflow_configuration}(left)).  Second, we change the number of
 iterations $k$ between the two consecutive solution sharing iterations
-(See Fig.~\ref{fig:optical_flow_by_interval}).  The first experiment
+(See Fig.~\ref{fig:opticalflow_configuration}(right)).  The first experiment
 revealed that the solution sharing makes convergence faster regardless of
@@
 \begin{subfigure}[b]{0.49\columnwidth}
-    \centering
 \includegraphics[width=\columnwidth]{figure/optical_flow_by_beta.png}
-    \caption{}
-    \label{fig:optical_flow_by_beta}
 \end{subfigure}
 \begin{subfigure}[b]{0.49\columnwidth}
-    \centering
 \includegraphics[width=\columnwidth]{figure/optical_flow_by_interval.png}
-    \caption{}
-    \label{fig:optical_flow_by_interval}
 \end{subfigure}
-  \caption{Energy plots for optical flow with (a) varying
-    $\beta$ and (b) varying solution sharing
-    frequencies.
-Solution sharing achieves better convergence, but sharing too many solutions (larger $\beta$) or sharing solutions too frequently (less $k$) slows down the convergence, as it reduces the time for exploration.}
+\caption{Energy
+  plots for optical flow under difference configurations. Left:
+  varying $\beta$; right: varying solution sharing
+  frequencies. Solution sharing achieves better convergence, but
+  sharing too many solutions (larger $\beta$) or sharing solutions too
+  frequently (less $k$) slows down the convergence, as it reduces the
+  time for exploration.}
+  \label{opticalflow_configuration}
 \end{figure}

### 2016-03-15 paper/result_optical_flow.tex
Hang

@@
 
-\begin{figure}[!h]
+\begin{figure}[!ht]
   \centering
@@
 
-\begin{figure}[!h]
+\begin{figure}[!ht]
 \centering
@@
   frequently (less $k$) slows down the convergence, as it reduces the
-  time for exploration.}
-  \label{opticalflow_configuration}
+  time for exploration.} \label{fig:opticalflow_configuration}
 \end{figure}

### 2016-03-15 paper/stereo.tex
Hang

@@
 be competing methods. For HF, we use Alpha-Expansion at the leaf node of
-the label tree or QPBO in the other cases.
+the label tree and QPBO in the other cases.
 %when either of the
@@
 In the later case, a thread randomly chooses one solution from the
-solution pool for fusion. SF-SS implies $\beta=0$, where $\alpha$ is the
-free parameter and set to 4. In this case one thread will fuse 4 labels,
-together with current solution by TRW-S per iteration and never
-exchanges solutions with other threads. We perform a multi-way fusion
-of solutions from all the threads at the end to obtain a final solution
+solution pool for fusion. SF-SS implies $\beta=0$, where $\alpha$ is
+the free parameter and set to 4. In this case one thread will fuse 4
+labels, together with current solution in that thread by TRW-S in each
+iteration and never exchanges solutions with other threads. We perform
+a multi-way fusion of solutions from all the threads at the end to
+obtain a final solution
 % at
 % the end to fuse solutions from all the threads to a single solution
-(similar to PAE). For standard SF, we have used ($\alpha=4, \beta=1$).
-%
-%
-%
-%
-To make the comparison simple, we restrict our solution proposals
-to be constant-label proposals.
+(similar to PAE). For standard SF architecture, we have used
+($\alpha=4, \beta=1$).  To make the comparison simple, we restrict our
+solution proposals to be constant-label proposals.
 %

### 2016-03-15 paper/stereo.tex
minor changes

@@
 %
-Unary terms are computed as the average robust photoconsistancy
+The unary terms are computed as the average robust photoconsistancy
 score~\cite{second_order_stereo} between the reference image and the others
-inside a $7\times 7$ pixels window.  Pairwise terms are simple
+inside a $7\times 7$ pixels window. The pairwise terms are simple
 truncated absolute label difference with maximum label difference
 $\sigma_s=4$. The total energy is defined by the sum of the two, while
-scaling the pairwise term by a factor of $0.005$. For simplicity we
+scaling the pairwise terms by a factor of $0.005$. For simplicity we
 do not enforce the visibility constraint.

### 2016-03-15 paper/stereo.tex
figure 2

@@
 Computer Vision, specifically, stereo, optical flow, and layered
-depthmap estimation.
+depthmap estimation (see Fig.~\ref{fig:problem}).
 

### 2016-03-15 paper/result_optical_flow.tex
figure change

@@
   \includegraphics[width=0.8\columnwidth]{figure/optical_flow_convergence.png}
-  \caption{Energy plots for optical flow estimation. SF-MF has the best
+  \caption{Energy plots for the optical flow problem. SF-MF has the best
     performance due to its solution sharing strategy.}\label{fig:optical_flow_convergence}
@@
   \end{subfigure}
-  \caption{Energy plots per thread. Left: Parallel Fusion  
+  \caption{Energy plots per thread for the optical flow problem. Left: Parallel Fusion  
     Move (PFM). Right: SF-MF(ours).}
@@
 \caption{Energy
-  plots for optical flow under difference configurations. Left:
-  varying $\beta$; right: varying solution sharing
+  plots for optical flow under different configurations. Left:
+  varying $\beta$; Right: varying solution sharing
   frequencies. Solution sharing achieves better convergence, but

### 2016-03-15 LayerDepthMap/Statistics/plotValuesAlpha.m

@@ -12,7 +12,7 @@ full_15_3_raw_values = load('output_values_full_15_3');
 full_15_3= convertValues(full_15_3_raw_values, 0);
 
 Victor_raw_values = load('output_values_Victor');
-Victor = convertValues(Victor_raw_values, 1);
+Victor = convertValues(Victor_raw_values, 0);
 multiway_raw_values = load('output_values_multiway');
 multiway = convertValues(multiway_raw_values, 0);
 multiway_5_raw_values = load('output_values_multiway_5');

### 2016-03-15 paper/optical_flow.tex
yasu

@@
 \subsection{Swarm Fusion optical flow}
-
 Fusion Move was first introduced by Lempitsky et al.~\cite{fusion_flow} to
@@
 %are used to evaluate the effectiveness of our method.
-The three swarm architectures in Fig.~\ref{fig:model} (SF-MF, SF-SS,
-SF) have been evaluated against the competing methods. For SF-MF, each
+The three swarm architectures in Fig.~\ref{fig:model} (SF-MF, SF-SS, SF)
+have been evaluated against the competing methods. For SF-MF, each
 thread repeats generating solution proposals ($\alpha=1, \beta=0$) for
@@
 thread generates three solution proposals for fusion in each iteration
-($\alpha=3$, $\beta=0$). For SF, we repeat the pattern of four
-iterations with ($\alpha=3, \beta=0$) plus one iteration with ($\alpha=0,
-\beta=3$).
+($\alpha=3$, $\beta=0$). For SF, we repeat four iterations of
+($\alpha=3, \beta=0$) and  one iteration of ($\alpha=0, \beta=3$).
 %%

### 2016-03-15 paper/result_optical_flow.tex
Hang
ref

@@
 relatively independent and fusing the solution space would not gain much
-benefit. It rather loses performance against QPBO~\cite{QPBO} due to the
+benefit. It rather loses performance against QPBO due to the
 overhead of TRW-S.
@@
 sharing}. Both factors are controlled by $\beta$. As mentioned in
-Section~\ref{section:algorithm}, we have used $\beta = 1$ (i.e., share
+Section~\ref{section:optical_flow}, we have used $\beta = 1$ (i.e., share
 solutions) once in every five iterations.  To further understand the

### 2016-03-17 paper/introduction.tex

@@
 only a single proposal generation scheme is used in each fusion
-step.~\footnote{Recently, an extension of FM was proposed for layered
+step.~\footnote{Recently, an extension of FM was introduced for layered
 depthmap estimation~\cite{layered_depthmap}, where a solution subspace, instead

### 2016-03-17 paper/layered_depthmap.tex

@@
 \subsection{Swarm Fusion layered depthmap estimation}
-
 Our last problem is layered depthmap estimation, recently proposed
@@
 supplementary material).  The problem seeks to infer layered depthmap
-representation from an RGBD image, where each layer is a piecewise
+representation from a RGBD image, where each layer is a piecewise
 smooth segmented depthmap. This is essentially a multi-layer extension

### 2016-03-17 paper/result_layered_depthmap.tex

@@
 \noindent We have used ``ours\_1'' data in~\cite{layered_depthmap} for
-the experiments. Fig.~\ref{fig:layered_depthmap_convergence} shows that
+the experiments. Figure.~\ref{fig:layered_depthmap_convergence} shows that
 Fusion Move, Parallel Fusion Move and SF-MF all got stuck in local
@@
   \end{subfigure}
-  \caption{(a) Energy plots for layered depthmap estimation with varying
-    $\alpha$. (b) Energy plots for layered depthmap estimation with varying number of threads N.}
+  \caption{Left: Energy plots for layered depthmap estimation with varying
+    $\alpha$. Right: Energy plots for layered depthmap estimation with varying number of threads N.}
   \label{fig:layered_depthmap_configuration}

### 2016-03-17 paper/stereo.tex
minor changes
Hang

@@
     estimation~\cite{layered_depthmap} problem. In the layered
-    depthmap problem, the input is an RGBD image, and the output is
+    depthmap problem, the input is a RGBD image, and the output is
     multiple layers of depthmaps. Each layer is a piecewise smooth
@@
 \end{figure}
-
+%
+%
+%
 \subsection{Swarm Fusion stereo}
@@
 pairwise terms. We employ submodular pairwise terms to make this
-stereo represent relatively ``easy'' MRF inference problems.
+stereo represent relatively ``easy'' MRF inference problem.
 %

### 2016-05-30 paper/rebuttal.tex
rebuttal draft

% #BIBTEX /Library/Tex/texbin/bibtex eccv2016
% last updated in April 2002 by Antje Endemann
% Based on CVPR 07 and LNCS, with modifications by DAF, AZ and elle, 2008 and AA, 2010, and CC, 2011; TT, 2014; AAS, 2016

\documentclass[runningheads]{llncs}
\usepackage{graphicx}
\usepackage{subcaption}
\captionsetup{compatibility=false}
\usepackage{amsmath,amssymb} % define this before the line numbering.
\usepackage{ruler}
\usepackage{color}
% \usepackage{tensor}
\usepackage{algorithm}
\usepackage{algpseudocode}
\usepackage{ulem}
\usepackage{url}
\usepackage{cite}

\usepackage[width=122mm,left=12mm,paperwidth=146mm,height=193mm,top=12mm,paperheight=217mm]{geometry}

\algnewcommand\algorithmicforeach{\textbf{for each}}
\algdef{S}[FOR]{ForEach}[1]{\algorithmicforeach\ #1\ \algorithmicdo}

\newcommand{\mysubsubsection}[1]{\vspace{0.2cm} \noindent
  \underline{{\bf #1}} \vspace{0.1cm}}
\newcommand{\mysubsubsubsection}[1]{\vspace{0.1cm} \noindent {\bf #1}:}

% \newcommand{\pushmeet}[1]{\textcolor{blue}{pushmeet:{#1}}}
% \newcommand{\yasu}[1]{\textcolor{magenta}{[yasu: {#1}]}}
\newcommand{\chen}[1]{\textcolor{cyan}{[chen: {#1}]}}
% \newcommand{\hang}[1]{\textcolor{green}{[hang: {#1}]}}
% \newcommand{\pushmeet}[1]{}
% \newcommand{\chen}[1]{}
% \newcommand{\yasu}[1]{}
% \newcommand{\hang}[1]{}

\ifx\pdfoptionalwaysusepdfpagebox\relax\else
\pdfoptionalwaysusepdfpagebox5
\fi

\begin{document}
% \renewcommand\thelinenumber{\color[rgb]{0.2,0.5,0.8}\normalfont\sffamily\scriptsize\arabic{linenumber}\color[rgb]{0,0,0}}
% \renewcommand\makeLineNumber {\hss\thelinenumber\ \hspace{6mm} \rlap{\hskip\textwidth\ \hspace{6.5mm}\thelinenumber}}
% \linenumbers
\pagestyle{headings}
\mainmatter
\def\ECCV16SubNumber{1569}  % Insert your submission number here

% \title{Parallelizing Hypothesis Fusion for Rapid MAP inference}
\title{Multi-way Particle Swarm Fusion}

\maketitle
\thispagestyle{empty}

%%%%%%%%% BODY TEXT - ENTER YOUR RESPONSE BELOW
We thank the reviewers for insightful comments. Major comments are
the limitation of using only 4 threads and the problem specific choice of architectures. We first address these major comments.

\vspace{0.15cm}
\noindent {\bf The lack of technical contribution:} We
believe that this paper proposes an effective parallel
framework which, based on the novel concept of solution
sharing and multi-way fusion, generalizes several existing
methods. With simple parameter tuning, our framework can be
specialized as an effective parallel architecture for any
given MRF inference tasks. We will also make our framework implementation public, so that researchers can utilize maximum parallelism by simply providing the energy function and solution proposals. So the
impact of this work would be huge.

\vspace{0.15cm}
\noindent {\bf The choice of architectures:} We agree with
R1 and R3 that the best fusing architecture is problem
specific. However, our parallel framework is general,
achieving all the architectures mentioned in the paper via
different parameter settings. This is indeed an advantage of
our framework because the best architecture can be found by
simple grid search over parameter space in the same
framework instead of trying various existing methods. And
existing methods, as the special cases of our framework, are
very unlikely to be the best architecture for any problem
settings. Note that there are only three parameters
($\alpha$, $\beta$, and the frequency of solution sharing)
controlling the parallel architecture, and all these three
are small integer numbers, so the grid search space can be
easily conducted. Note that in order to illustrate the
intuition behind solution sharing and multi-way fusion, we
only presented three special architecture of our framework
in the paper, namely SF-SS, SF-MF, and SF (despite of its
name, we use maximal solution sharing and multi-way fusion
in all our experiments). But to solve a
problem in practice, a grid search is required to find the best
parameter setting. We will add the discussion here to the
paper and provide codes for automatic parameter tuning.

\vspace{0.15cm} We believe that this paper proposes a novel
parallel framework which will benefit many researchers with
more effective parallel architectures over existing
methods. The best architecture for any given problem can be
found via simple grid search in the parameter space. Now, we
answer remaining questions from each reviewer. We will
clarify these points in the paper, too.

\vspace{0.15cm}
\noindent {\bf Reviewer 1}

\vspace{0.15cm}
\noindent $\bullet$ (The number of threads:) Note that the
complexity for each thread is independent of the number of
threads in total. With this nature, we can apply our
parallel scheme to any number of threads or even distributed
systems. To make comparison fair in our experiments, we only
use 4 threads to make sure all threads including the
additional monitor thread run on its own physical core. The
experiments focus more on the intuition behind solution
sharing and multi-way fusion instead of pursuing best performance. But in
practice, our current implementation allows the usage of any
number of threads. A future work would be implementing our
parallel scheme on distributed environments.

\noindent $\bullet$ (Compliants about Fig. 3:) Thanks for
pointing it out. This figure is indeed incomplete as we want
to stress speed difference and explain this intuition of
solution sharing. The complete figure is shown in Fig. 1
here. As the energy is submodular in this problem setting,
all the architectures can find the global minimum at the
end.

\noindent $\bullet$ (Line 416-417 statement contradicts SF-MF in Fig. 1:) As indicated by the red arrows, the last thread of SF-MF on the figure (far right) also explores solutions generated by other thread (which is not shown on the figure). We will make the figure more clear.

\noindent $\bullet$ (Underlining paragraph titles:) Thanks for pointing it out. We will change the format.

% \section{R2}
\vspace{0.15cm}
\noindent {\bf Reviewer 2}
\noindent $\bullet$ (Missing reference:) We thank R2 for
pointing out this paper, Simultaneous Fusion Moves for
3D­Label Stereo. However, to our understanding, the
multi-label fusion move proposed in this paper is different
with out multi-way fusion. Their multi-label fusion move
conduct one single TRW inference (with many iterations) to
fuse all proposals together, whereas our multi-way fusion
conduct one TRW inference to fuse only a subset of proposals
and repeat the fusion until convergence. When the energy
function becomes more complex or the number of proposals is
large, a single TRW over all proposals is very hard to
converge, but our multi-way fusion will still work by
repeatedly fusing small subset of proposals.

\chen{\noindent $\bullet$ (The benefit of multi-threading:)
  We admit that the multi-threading does not help the
  algorithm for some applications if run to
  convergence. However, it consistently benefits online
  optimization as it provides better results at each
  timestamp.}

\vspace{0.15cm}
\noindent {\bf Reviewer 3}

\noindent $\bullet$ (The intuition behind Swarm Fusion:) We
illustrate the benefit of utilizing solution sharing and
multi-way fusion through experiments and explain the
intution behind. The Swarm Fusion combines both ideas and is
a general scheme. These two ideas are intuitive and
effective. We are not aware of other relevant ideas.

\noindent $\bullet$ (Lack of exciting results:) We
appreciate the comment that some results we show are not
exciting. However, our experiments use extreme cases to
illustrate the idea of solution sharing and multi-way
fusion. While in practice, the best parameter setting is
unlikely to be any of these extreme cases and should be
found by a grid search over parameter space. However,
instead of achieving the best performance, we are more
excited about the effectivenss and applicability of our
framework, which makes it a handy tool for speeding up many
MRF inference problem. We will add relevant discussion in
the paper.

\noindent $\bullet$ (Dependent on proposal generations:) We
agree with R3 that the performance is highly dependent on
proposal generation scheme. This fact causes trouble for
fair comparison as some proposals are not applicable or
despite certain architectures. To make the comparison fair,
we often discard certain proposal generation schemes
in the cost of performance.

\noindent $\bullet$ (Proposal generation schemes from [15]:) \chen{I am not sure what this compliant is about as none of our experiments is about [15]}

\end{document}

### 2017-01-27 paper/rebuttal.tex

@@
 specialized as an effective parallel architecture for any
-given MRF inference tasks.
-We will also make our framework implementation public, so that researchers can utilize maximum parallelism by simply providing the energy function and solution proposals.
-So the
-impact of this work would be huge.
+given MRF inference tasks. We will also make our framework
+implementation public, so that researchers can utilize
+maximum parallelism by simply providing the energy function
+and solution proposals. So the impact of this work would be
+huge.
 
@@
 R1 and R3 that the best fusing architecture is problem
-specific. However, our parallel framework is general,
-achieving all the architectures mentioned in the paper via
-different parameter settings. This is indeed an advantage of
-our framework because the best architecture can be found by
-simple grid search over parameter space in the same
-framework instead of trying various existing methods. And
-existing methods, as the special cases of our framework, are
-very unlikely to be the best architecture for any problem
-settings. Note that there are only three parameters
+specific. However, our parallel framework is general in the
+sense that it achieves all the architectures mentioned in
+the paper via different parameter settings. This is indeed
+one advantage of our framework because the best architecture
+can be found by a simple grid search over parameter space in
+the same framework instead of trying various existing
+methods. And existing methods, as the special cases of our
+framework, are very unlikely to be the best
+architecture. Note that there are only three parameters
 ($\alpha$, $\beta$, and the frequency of solution sharing)
 controlling the parallel architecture, and all these three
-are small integer numbers, so the grid search space can be
-easily conducted. Note that in order to illustrate the
+are small integer numbers, so the grid search can be
+easily conducted. Note that, in order to illustrate the
 intuition behind solution sharing and multi-way fusion, we
@@
 name, we use maximal solution sharing and multi-way fusion
-in all our experiments). But to solve a
-problem in practice, a grid search is required to find the best
-parameter setting. We will add the discussion here to the
-paper and provide codes for automatic parameter tuning.
+in all our experiments). But to solve a problem in practice,
+a grid search is required to find the best parameter
+setting. We will add the discussion to the paper and
+provide codes for automatic parameter tuning.
 
@@
 pointing it out. This figure is indeed incomplete as we want
-to stress speed difference and explain this intuition of
-solution sharing. The complete figure is shown in Fig. 1
-here. As the energy is submodular in this problem setting,
+to focus on speed difference and explain this intuition behind
+solution sharing. As the energy is submodular in this problem setting,
 all the architectures can find the global minimum at the
-end.
+end. We will add the complete graph to the paper.
 
@@
 with out multi-way fusion. Their multi-label fusion move
-conduct one single TRW inference (with many iterations) to
+conducts one single TRW inference (with many iterations) to
 fuse all proposals together, whereas our multi-way fusion
-conduct one TRW inference to fuse only a subset of proposals
+conducts one TRW inference to fuse only a subset of proposals
 and repeat the fusion until convergence. When the energy
@@
 large, a single TRW over all proposals is very hard to
-converge, but our multi-way fusion will still work by
+converge, but our multi-way fusion will still work well by
 repeatedly fusing small subset of proposals.
@@
 excited about the effectivenss and applicability of our
-framework, which makes it a handy tool for speeding up many
-MRF inference problem. We will add relevant discussion in
+framework, which makes our framework a handy tool for speeding up many
+MRF inference problems. We will add relevant discussion in
 the paper.
@@
 
-\noindent $\bullet$ (Proposal generation schemes from [15]:) \chen{I am not sure what this compliant is about as none of our experiments is about [15]}
+\noindent $\bullet$ (Proposal generation schemes from [15]:)
+\chen{I am not sure what this compliant is about as none of
+  our experiments is about [15]}
 

### 2017-01-27 paper/rebuttal.txt

We thank the reviewers for insightful comments. Reviewers are overall in favor of the idea, but are concerned that 1) the optimal architecture depends on each problem, and 2) the performance still depends on a problem-specific proposal generation scheme.
 
We now regret the way we presented our work, as these factors exactly demonstrate the strength of our approach. We have presented an approach that unifies  different move making algorithms in one common parallelized framework for MAP inference. In our experiments, three hyper-parameters (alpha, beta, and the frequency of solution sharing) control the architecture. A research can employ a simple grid-search (or more sophisticated Bayesian optimization) over these hyper-parameters to identify the architecture best suited for a given problem. Our latest experiments have confirmed that the grid search can indeed identify the optimal configuration under certain measurement for each problem within 100 search iterations.

We presented three particular architectures in the paper to 1) distinguish the effects of the solution-sharing and the multi-way fusion; and 2) avoid unfair comparisons against existing methods that cannot optimize architectures. However, we agree with the reviewers that the process of finding the architecture (and its unfairness) is an important aspect of the work.

We also agree that our approach still relies on problem-specific proposal generation schemes. However, this is true to any other existing methods. We need problem-specific proposals to solve challenging problems, which cannot be solved by a general-purpose method. This framework can quickly find the optimal hyper-parameters and the architecture for you, given a proposal generation scheme.

We will modify the paper to address all these points and add the hyper-parameter optimization algorithm (less than 10 lines) and its results. We hope to convince R1 and R3 that this paper presents a rather unique holistic view and parameterization of the parallel inference algorithm family. The idea is easy to understand and implement with immediate impact to every Computer Vision researcher or engineer, who currently solves a challenging graphical model inference problem.

We now address the remaining concerns from the reviewers.

The number of threads: Our parallel scheme can be applied to any number of threads or even distributed systems. We also did experiments on 8 threads and had same observations. That is, solution sharing speeds up convergence in most experiments and multi-way fusion can find lower energy in complex problem settings. We will show experiment results on 8 threads in the paper as utilizing 8 threads has a larger impact. A future work would be implementing our parallel scheme on distributed systems.

Incomplete Fig. 3: We only show part of the figure to put speed difference in focus. As the energy is submodular in this problem setting, all the architectures can find the global minimum at the end. We will show the complete graph in the paper.

SF-MF in Fig. 1: As indicated by the red arrows, the last thread of SF-MF on the figure also explores solutions generated by another thread (which is not shown). We will clarify the figure.

Missing reference: We thank R2 and will cite it. But note that their multi-label fusion move is different with our multi-way fusion. They conduct only one TRW inference to fuse all proposals at once and call each iteration a move, whereas we conducts one TRW inference (a move) to fuse only a subset of proposals and repeat the fusion until convergence. This strategy makes our method applicable to problem with more complex energy or larger number of proposals.

Intuition behind Swarm Fusion: We confirm the benefit of solution sharing and multi-way fusion in our experiments. The Swarm Fusion is a general scheme incorporating both ideas. We are not aware of other intuitive ideas.

Lack of exciting results: We use extreme cases to illustrate the idea of solution sharing and multi-way fusion. While in practice, the best parameter setting is unlikely to be any of these extreme cases and should be found by a grid search.
